### 2017-02-11 Papers/Loop Shaping Voltage Loop (CERN)/Latex/Draft/Draft.tex
adding files to git (11/2/2017)

\documentclass[a4paper, 10pt, conference]{ieeeconf}  
%\documentclass[letterpaper, 10 pt, conference]{ieeeconf}  % Use this for US paper
\IEEEoverridecommandlockouts
\overrideIEEEmargins
\bibliographystyle{IEEEtran}
%\usepackage{natbib}

\usepackage{graphicx}  % Add graphics capabilities
\usepackage{color}
\usepackage{amsmath} % assumes amsmath package installed
\usepackage{amssymb}  % assumes amsmath package installed
\usepackage{mathrsfs}
%\usepackage{amsthm}
\usepackage{epstopdf}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{definition}{Definition}
\newcommand{\jo}{(j\omega)}
\newcommand{\jok}{(e^{-j\omega_k})}
\newcommand{\jro}{(e^{-j\omega},\rho)}
\newcommand{\jrok}{(e^{-j\omega_k},\rho)}

\title{A Data-Driven Loop-Shaping Approach to Design Controllers for Power Converters} 
% Title, preferably not more than 10 words.

\author{Achille Nicoletti$^{1}$ and Michele Martino$^{1}$ and Alireza Karimi$^{2}$% <-this % stops a space
\thanks{*This work was not supported by any organization}% <-this % stops a space
\thanks{$^{1}$Achille Nicoletti and Michele Martino are both with the European Organization for Nuclear Research (CERN), 
 CH-1211 Geneva 23, Switzerland
        {\tt\small  e-mail: achille.nicoletti@cern.ch / michele.martino@cern.ch}}%
\thanks{$^{2}$Alireza Karimi is with Ecole Polytechnique F\'{e}d\'{e}rale de Lausanne (EPFL), Institute of Mechanical Engineering (IGM),
   CH-1015 Lausanne, Switzerland
        {\tt\small e-mail: alireza.karimi@epfl.ch}}%
}

%\thanks[footnoteinfo]{Sponsor and financial support acknowledgment
%goes here. Paper titles should be written in uppercase and lowercase
%letters, not all uppercase.}

%\author[First]{Achille Nicoletti} 
%\author[First]{Michele Martino} 
%\author[Second]{Alireza Karimi}

%\address[First]{The European Organization for Nuclear Research (CERN), 
  % CH-1211 Geneva 23, Switzerland (e-mail: achille.nicoletti@cern.ch / michele.martino@cern.ch)}
%\address[Second]{Ecole Polytechnique F\'{e}d\'{e}rale de Lausanne (EPFL), 
   %CH-1015 Lausanne, Switzerland (e-mail: alireza.karimi@epfl.ch)}

\begin{document}

\maketitle
\thispagestyle{empty}
\pagestyle{empty}

\begin{abstract}                % Abstract of not more than 250 words.
A new loop-shaping data-driven approach is presented for synthesizing controllers for the CERN power converter control system. This method uses the frequency response function (FRF) of a system in order to avoid the problem of unmodeled dynamics associated with parametric models. For this particular application, it is shown that a convex optimization problem can be formulated (in either the $H_\infty$ or $H_2$ sense) to shape the closed-loop FRF while guaranteeing the closed-loop stability. This optimization problem is realized by linearizing a non-convex constraint around a stabilizing operating point. The effectiveness of the method is illustrated by designing a controller for the SATURN power converter which is used in the Large Hadron Collider, in injector machines, and for pulsed applications at CERN. Experimental validation in the time domain is also presented. 
\end{abstract}

%===============================================================================
\section{Introduction}
Today's industrial processes pose challenging problems to control engineers due to the increasing complexities of system structures. In order to simplify the controller design process, these systems are approximated with low-order models; this reduces both time and effort in synthesizing a controller. However, this approximation can create stability and performance problems since these low-order models are subject to model uncertainty. Data-driven control methods seek to alleviate this problem by synthesizing controllers based on time-domain or frequency-domain data (i.e., synthesis is model independant). A survey on the differences associated with model-based control and data-driven control has been addressed in \cite{HW13} and \cite{BCE12}; the authors assert that model-based control methods are inherently less robust due to the unmodeled dynamics of a process, and that these controllers are unsafe for practical applications. In other words, the parametric uncertainties and the unmodeled dynamics associated with the data-driven scheme are irrelevant, and the only source of uncertainty is the measurement noise.

Data-driven controllers can be synthesized either on-line or off-line; the on-line methods such as the classical direct adaptive control (MRAC) \cite{LLMK11}, model-free adaptive control (MFAC) \cite{HJ13}, and the unfalsified control (UC) \cite{ST97} methodologies design controllers using time-domain data. Iterative feedback tuning (IFT) \cite{Hja02}, correlation-based tuning (CBT) \cite{KMB02a}, virtual reference feedback tuning (VRFT) \cite{CLS02}, non-iterative data-driven model reference control \cite{KVB07} methodologies are all off-line time-domain data-driven methods.  The widely used PID controller are usually tuned based on a set of time-domain or frequency-domain data.

Frequency-domain based controller synthesis methods are design schemes that continue to spark the interest of many researchers. The authors in \cite{KNND13b} establish a robust frequency-domain controller design methods that requires a solution to a non-linear optimization problem. A frequency-domain loop-shaping method for fixed-structure controllers is proposed in \cite{KNND13c}; however, stability is not guaranteed with this method and must be verified a posteriori. Controller synthesis methods belonging to the $\mathcal{H}_{\infty}$ control framework minimizes the $\mathcal{H}_{\infty}$ norm of a weighted closed-loop sensitivity function. A convex optimization approach is used to design linearly-parameterized (LP) controllers with loop shaping and $\mathcal{H}_{\infty}$ performance in \cite{KG10}. This method is extended to multiple-input multiple-output (MIMO) systems for computing decoupling LP-MIMO controllers in \cite{GKL10b}. In \cite{NK14}, this method of designing LP controllers was further extended to MIMO systems with delay. Recently, the necessary and sufficient conditions for the existence of $\mathcal{H}_{\infty}$ controllers for SISO systems represented by their frequency response has been proposed in \cite{KNZ16}.

The proposed method in this paper invokes a new data-driven control design scheme for a specific power converter application at CERN. Currently, the load (i.e., the magnet of the particle accelerator) is approximated as a simple first-order system (series $RL$ circuit); however, as shown in \cite{GB65}, the parameters of the magnet are frequency dependent. Additionally, it has been shown in \cite{KZ98} that the vacuum chamber of the magnet is also frequency dependent (due to the skin depth effect and the chamber geometry). Therefore, it is appropriate to consider a data-driven based design to regulate the power converter control system.  In this work, it is shown that a loop-shaping design in the $\mathcal{H}_\infty$ or $\mathcal{H}_2$ sense can be formulated through a convex optimization problem; however, the methods described in this paper can also be applied to mixed $\mathcal{H}_2$ and $\mathcal{H}_\infty$ problems (i.e., minimizing the norm of weighted sensitivity functions). Additionally, with certain conditions on the controller parameters, it is shown that the closed-loop stability is guaranteed.

The paper is organized as follows. The class of models represented by FRF's are addressed in section \ref{sec:prelim}. Section \ref{sec:system} discusses the framework of the power converter control system and its functionality at CERN. The main results and theoretical bases are addressed in section \ref{sec:main}; in this section, loop-shaping constraints are formulated for the power converter control system. Section \ref{sec:case} is dedicated to a case study where the effectiveness of the method is demonstrated by applying the proposed design scheme to a power converter control system for a specific accelerator requirement. Finally, the concluding remarks are given in section \ref{sec:conclusion}.

\section{Preliminaries}
\label{sec:prelim}
The class of systems discussed in this paper will be Linear Time-Invariant Single-Input Single-Output (LTI-SISO) systems that will be represented by a FRF $G\jo$.  The FRF can be obtained directly with a given transfer function (TF) model, or through an identification experiment using the Fourier analysis method. Let $U\jo$ and $Y\jo$ represent the FRF's of the system input and output signals, respectively. Then the FRF of the system can be represented as 
\begin{equation}
G\jo = Y\jo U^{-1}\jo
\end{equation}
If the data is noisy, then $G\jo$ is characterized as the Empirical Transfer Function Estimate (ETFE) and is asymptotically unbiased \cite{Lju99}. For such systems, a multiplicative uncertainty can be considered to ensure robustness in the presence of noise perturbations. In general, a set $\mathcal{G}$ can be formulated to represent a plant model containing $p$ FRF models:
\begin{equation}
\mathcal{G} = \{G_l\jo; \quad l=1,\ldots,p; \quad \forall \omega \in \Omega\}
\end{equation} 
$\Omega \in [0,\infty)$. For simplicity, one model from the set $\mathcal{G}$ will be considered, and the subscript $l$ will be omitted. However, in general, the design procedures outlined in this paper can be applied to the multi-model case.

Additionally, for notation purposes, let us define $\mathscr{S}$ as the set of all strictly proper (stable) TF's and $\mathscr{P}$ as the set of all proper (stable) TF's.

\section{System Framework}
\label{sec:system}
\begin{figure}
\centering
\includegraphics[width=\columnwidth]{../pics/circuit_partial_a}
\caption{Power converter filter schematic (from $v_i$ to $v_0$). The magnet represents the load of the process.}
\label{fig:circuit}
\end{figure}
The power converter voltage source filter has the structure shown in Fig.~\ref{fig:circuit}. The input voltage $v_i$ is the output of a pulse-width modulated signal (which will be discussed in more detail in section \ref{sec:case}). The TF from $v_i$ to $v_0$ describes the filter of the power converter. The magnet (i.e., the load) is connected to the output of the converter. For general applications at CERN, the objective is to control the current in the magnet (through $L_m$) such that the error between this output current and a delayed version of the reference current is minimized. However, the objective of this paper is to design and implement a controller to shape the FRF between the reference voltage and $v_0$. This intermediate control is performed due to the fact that the power converter typically possesses large resonances, and a controller is required to attenuate these resonances in order to ensure better performance in the current loop. Another reason for implementing this type of control structure at CERN is for commissioning purposes; if/when faults occur in the system, each loop can be verified one at a time to ensure quality operation.

The system structure for this application is shown in Fig.~\ref{fig:damping_loop}. 
\begin{figure}
\centering
\includegraphics[width=\columnwidth]{../pics/damping_loop_full}
\caption{Interconnection of the power converter control system. }
\label{fig:damping_loop}
\end{figure}
$G_0(s)$ represents the TF from $v_i$ to $v_0$ in Fig.~\ref{fig:circuit}; $H(s)$ represents the TF from $v_0$ to $i_c$; $P_1(s)$ and $P_2(s)$ are sensors (i.e., low-pass filters); $k_i$ and $k_u$ are the control variable gains; $T_\alpha \: [s]$ is an actuation delay; and $C(s)$ is a PI controller (i.e., $C(s) = k_{p_1} + s^{-1}k_{p_2}$). From this framework, it can be observed that the inner feedback loops are reminiscent of a state-feedback control architecture while the system (as a whole) is a common unity feedback structure with feedforward action. For this application, note that $\{G_0,P_1,P_2 \} \in \mathscr{S}$ and $H \in \mathscr{P}$. The objective of this application is to design controllers such the TF from $v_d$ to $v_0$ and $v_r$ to $v_0$ both achieve the desired loop-shapes.

In order to simplify the system framework, let us define the following quantities:
\begin{equation} \label{eq:new_var}
\begin{aligned}
k_{m_1} &:= k_{p_1}(1+k_u) ;  &k_{m_2} &:= k_{p_2}(1+k_u)  \\
H_1(s,k) &:= k_iP_1(s)H(s);  &H_2(s,k) &:= k_uP_2(s) \\
G_d(s) &:= G_0(s)e^{-sT_\alpha}; &C_m(s,k) &:= k_{m_1}+s^{-1}k_{m_2}\\ 
\end{aligned}
\end{equation}
where $k \in \{k_i,k_u,k_{m_1},k_{m_2}\}$. Let the TF from $v_d$ to $v_0$ be denoted as $T^{\prime}(s,k)$ and the TF from $v_r$ to $v_0$ be denoted as $T(s,k)$.  Then these closed-loop TF's can easily be derived as follows:

\begin{align}
T^{\prime}(s,k) &= \frac{G_d(s)(1+k_u)}{1+G_d(s)[H_1(s,k)+H_2(s,k)]} \label{eq:Tclp}  \\ 
T(s,k) &= \frac{G_d(s)[1+k_u+C_m(s,k)]}{1+G_d(s)[H_1(s,k)+H_2(s,k)+C_m(s,k)]}  \label{eq:Tcl} 
\end{align}

For the remaining theoretical portions of this document, the loop-shaping technique will only be shown for $T(s,k)$, since the same procedures can also be applied to $T^{\prime}(s,k)$. Additionally, for notation purposes, the dependency in $s$ will be omitted and reiterated when deemed necessary. Additionally, all functions discussed hereafter will be FRF's with $s = j\omega$. For example, the denotation $T(k)$ represents $T(j\omega,k)$.

\section{Main Results}
\label{sec:main}
In this section, it will be demonstrated that the performance specification of the control problem will be achieved by formulating a convex optimization problem. The controllers will be synthesized by only considering the FRF of the system components.

\subsection{Convex Approximation}
The type of optimization problem that will be considered in the paper will have the following form:

\begin{equation} \label{eq:con_cav}
\begin{aligned}
& \underset{ x }{\text{minimize}}
& & \gamma  \\
& \text{subject to:} & & y(x)-z(x) < \gamma 
\end{aligned}
\end{equation}

where $y(x)$ and $z(x)$ are both convex functions of $x$ and $\{ \gamma \in \mathbb{R} : \gamma > 0\}$. This type of problem is convex-concave (due to the $-z(x)$ term); one solution to convexify this problem is to linearize $z(x)$ around an operating point $x_0$ and obtain the following optimization problem:

\begin{equation} \label{eq:con_lin}
\begin{aligned}
& \underset{ x }{\text{minimize}}
& & \gamma  \\
& \text{subject to:} & & y(x)-\bigl[ \nabla z(x_0) \bigr]^{\top} (x-x_0) < \gamma 
\end{aligned}
\end{equation}

 where $\nabla z(x_0)$ is the gradient of $z(x)$ evaluated at $x_0$.

The control methodology in this paper is based on minimizing a control objective in the $\mathcal{H}_\infty$ or $\mathcal{H}_2$ sense. In subsequent sections, it will be shown that these performance constraints will have the following quadratic form:

\begin{equation} \label{eq:basic_ineq}
y^{\star}(x) \gamma^{-1} y(x) - z^{\star}(x)z(x) < 0 
\end{equation}

where $y(x)$ and $z(x)$ are complex affine functions of the decision variable $x$ and $(\cdot)^{\star}$ denotes the complex conjugate of the argument. Let $f(x) = z^{\star}(x)z(x)$ with $z(x)$ defined as

$$z(x) = a_0 + a_1x_1 + a_2x_2 + ,\ldots , + a_nx_n$$

where $z:\mathbb{R}^n \rightarrow \mathbb{C}$ and $f:\mathbb{R}^n \rightarrow \mathbb{R}$. A first order Taylor series of $f(x)$ around an operating point $x_0$ can be formulated as follows:

\begin{equation} \label{eq:lin_fx}
f(x) \approx f(x_0) + D_f(x_0)[x-x_0]
\end{equation}

where
$$D_f(x_0) = \left[ \frac{\partial f(x)}{x_1}\Bigr|_{x=x_0}, \frac{\partial f(x)}{x_2}\Bigr|_{x=x_0},\ldots, \frac{\partial f(x)}{x_n}\Bigr|_{x=x_0}\right]$$

Without loss of generality, it can be shown that the left-hand side of (\ref{eq:lin_fx}) will always be greater than or equal to the right-hand side, i.e.,

\begin{equation} \label{eq:lin_inequality}
z^{\star}(x)z(x) \geq z^{\star}(x)z_0 + z(x)z_0^{\star} - z_0^{\star}z_0
\end{equation}

where $z_0 = z(x_0)$. The condition in (\ref{eq:lin_inequality}) can easily be established by realizing the following inequality:

\begin{equation}
[z(x)-z_0]^{\star}[z(x)-z_0] \geq 0
\end{equation}

With this linearization, a sufficient condition for the inequality in (\ref{eq:basic_ineq}) can be developed as follows:

\begin{equation}
y^{\star}(x) \gamma^{-1} y(x) - [z^{\star}(x)z_0 + z(x)z_0^{\star} - z_0^{\star}z_0]< 0 
\end{equation}

By using the Shur Complement Lemma \cite{BEN09}, the above condition can be expressed in terms of a Linear-Matrix-Inequality (LMI):

\begin{equation} \label{eq:LMI_1}
\begin{bmatrix}
z^{\star}(x)z_0 + z(x)z_0^{\star} - z_0^{\star}z_0 & \phantom{xx} y^{\star}(x) \\
y(x) & \phantom{xx} \gamma
\end{bmatrix}
\succ 0
\end{equation}

This type of formulation will be used in section \ref{sec:loop_shape} in order to construct a loop-shaping constraint on the closed-loop FRF.

\subsection{Control Performance}
Since the control methods discussed in this paper are based on the $\mathcal{H}_\infty$ criterion, it is appropriate to first define this criterion in the context of this work. A typical control objective is to design a controller such that the following constraint is satisfied:
\begin{equation} \label{eq:WS_lt1}
\| W_q \mathcal{S}_q\| < 1
\end{equation}
where $\mathcal{S}_q$ is the $q$-th sensitivity function of interest, and $W_q$ is a stable weighting function such that $\| W_q \mathcal{S}_q\|$ is bounded. The norm considered in (\ref{eq:WS_lt1}) can be either the 2- or infinity-norm.

For SISO systems, and for a stable system $X(s)$, the 2- and infinity-norms are defined as follows:
\begin{align*}
\| X\|_2^2 & := \frac{1}{2\pi} \int_{- \infty}^\infty |X(j\omega)|^2 d\omega \\
\| X\|_\infty & :=  \sup_{\omega} |X(j\omega)|
\end{align*}
It is imperative to note that the boundedness of spectral norm $X$ does not guarantee the stability of $X$.

A loop-shaping criterion can also be considered as a form of control performance. If $T$ is the closed-loop FRF and $T_d$ is the desired FRF, then one can consider minimizing $(T-T_d)$ in either the 2- or infinity-norm sense in order to shape $T$.  The next section will discuss how an optimization problem can be formulated for this type of control methodology.

\subsection{Loop-Shaping Design}
\label{sec:loop_shape}
As asserted in section \ref{sec:system}, the objective of this control problem is to shape the FRF of $T(k)$. Suppose that a desired loop-shape is specified as $T_d$; the objective is to design gains in $k$ such that the closed-loop system $T(k)$ coincides with $T_d$ in the $\mathcal{H}_\infty$ or $\mathcal{H}_2$ sense. In the $\mathcal{H}_\infty$ sense, the objective is to minimize $ \|T(k) - T_d \|_\infty$; an equivalent representation of this objective is to minimize $\gamma$ such that $ \|T(k) - T_d \|_\infty < \gamma$. This criterion is satisfied if the the following optimization problem is considered:

 \begin{equation} \label{eq:min_loopshape}
\begin{aligned}
& \underset{ k \in \mathbb{R}}{\text{minimize}}
& & \gamma  \\
& \text{subject to:} & & \bigl[T(k)-T_d\bigr]^{\star}\bigl[T(k)-T_d\bigr] < \gamma
\end{aligned}
\end{equation}
for all $\omega \in \Omega$. It can be observed that the constraint in (\ref{eq:min_loopshape}) is not convex. Let $z(k) = 1+G_d[H_1(k)+H_2(k)+C_m(k)]$ and $N(k) = G_d[1+k_u+C_m(k)]$; then the above constraint can be written as:

\begin{equation}
\bigl[N(k)-z(k)T_d \bigr]^{\star}\gamma^{-1} \bigl[N(k)-z(k)T_d \bigr] - z^{\star}(k)z(k)<0
\end{equation}

Note that this constraint has the exact form as in (\ref{eq:basic_ineq}); therefore, the convex constraint in (\ref{eq:LMI_1}) can be utilized to construct the loop-shaping optimization problem as follows:

\begin{equation} \label{eq:loop_shape_LMI_inf}
\begin{aligned}
& \underset{ k \in \mathbb{R}}{\text{minimize}} \hspace{0.5cm} \gamma  \\
& \text{subject to:} \\
&
\begin{bmatrix}
z^{\star}(k)z_0 + z_0^{\star}z(k) - z_0^{\star}z_0 & \phantom{xx}[N(k)-z(k)T_d]^{\star} \\ 
N(k)-z(k)T_d & \phantom{xx}\gamma
\end{bmatrix} \succ 0
\end{aligned}
\end{equation}
for all $\omega \in \Omega$, where $z_0 = 1+G_d[H_1(k_0) + H_2(k_0)+C_m(k_0)]$ and $k_0 \in \{k_{i,0},k_{u,0},k_{m_1,0},k_{m_2,0}  \}$ are the initializing gains. In a similar manner, the following convex optimization problem can be considered for minimizing  $ \|T(k)- T_d \|_2^2$, as follows:

\begin{equation} \label{eq:loop_shape_LMI_2}
\begin{aligned}
& \underset{ k \in \mathbb{R}}{\text{minimize}} \hspace{0.5cm} \int_0^\infty \gamma(\omega) d\omega  \\
& \text{subject to:} \\
&
\begin{bmatrix}
z^{\star}(k)z_0 + z_0^{\star}z(k) - z_0^{\star}z_0 & \phantom{xx}[N(k)-z(k)T_d]^{\star} \\ 
N(k)-z(k)T_d & \phantom{xx}\gamma(\omega)
\end{bmatrix} \succ 0
\end{aligned}
\end{equation}
for all $\omega \in \Omega$. For this $\mathcal{H}_2$ problem, note that $\gamma$ is now a function of $\omega$ (which contrasts with the optimization problem in the $\mathcal{H}_\infty$ sense).

\iffalse
If it is desired to minimize the $\mathcal{H}_\infty$ norm of a weighted sensitivity function, one can easily formulate an optimization problem to minimize $ \|W_q \mathcal{S}_q(k)\|_\infty$, i.e.,
 \begin{equation} \label{eq:min_weighted_norm}
\begin{aligned}
& \underset{ k \in \mathbb{R}}{\text{minimize}}
& & \gamma  \\
& \text{subject to:} & & \bigl[W_q \mathcal{S}_q(k)\bigr]^{\star}\bigl[W_q \mathcal{S}_q(k)\bigr] < \gamma
\end{aligned}
\end{equation}
Then, as was shown in (\ref{eq:min_loopshape})-(\ref{eq:loop_shape_LMI_inf}) for the loop-shaping problem, a corresponding LMI can be derived for the $\infty$-norm of the weighted sensitivity function. In a similar manner, the convex optimization problem can be derived for minimizing the 2-norm of the weighted sensitivity function (i.e., minimize $ \|W_q \mathcal{S}_q(k)\|_2^2$). 
\fi

{\bf Remark:} 
\textit{Note that the choice of the initializing gains in $k_0$ may affect the stability of the closed-loop system (for either the optimization problems concerning the $\mathcal{H}_\infty$ or $\mathcal{H}_2$ norms). The next section will discuss how to select these gains in order to ensure stability. \\ 
Additionally, note that these optimization problems are considering the gains for $C_m(k)$; however, once an optimal solution is obtained for the gains in $k$, then the definitions in (\ref{eq:new_var}) can be used to revert back to the original gains (i.e., $k_{p_1}$ and $k_{p_2}$.)}

\subsection{Stability Analysis}
The loop-shaping constraints developed in the previous section do not guarantee the closed-loop stability of the closed-loop system. Setting a desired FRF to shape a closed-loop FRF is analogous to bounding the closed-loop FRF; it can be shown that unstable systems can still possess bounded FRF's.

The initializing gains in $k_0$ play an important role in guaranteeing the stability of the closed-loop system. By using the Nyquist criterion for continuous-time systems, the stability of the closed-loop system can be ensured if certain conditions are met for these initializing gains. Let us first recall the Nyquist stability criterion with the following Lemma:
\begin{lemma}
A closed-loop system with a plant $G(s)$ and a controller $C(s)$ in a unity-feedback structure is stable if and only if the Nyquist plot of $1+G(s)C(s)$
\begin{itemize}
\item makes $n_G + n_C$ counterclockwise encirclements of the origin, where $n_G$ and $n_C$ are the number of right-half-plane (RHP) poles of $G(s)$ and $C(s)$, respectively
\item does not pass through the origin
\end{itemize}
\end{lemma}
Note that in this Nyquist stability criterion, the term $GC$ refers to the open-loop system. In this paper, it is assumed that the Nyquist contour has some small detours around the poles of $G$ and $C$ on the imaginary axis.

The following properties will be needed in order to properly analyze the stability conditions of the system:
\begin{definition}
Let wno$\{ A(s)\}$ refer to the winding number; in the counterclockwise sense, wno$\{ A(s)\}$ represents the image of $A(s)$ around the origin when $s$ traverses the Nyquist contour (with small detours around the poles of $A(s)$ on the imaginary axis). Then the following properties hold:
\begin{align}
\text{wno}\bigl\{ A_1(s)A_2(s) \bigr\} &= \text{wno}\bigl\{ A_1(s) \bigr\} + \text{wno}\bigl\{ A_2(s) \bigr\}  \label{eq:wno_add}\\ 
\text{wno}\bigl\{ A(s)\bigr\} &= -\text{wno}\bigl\{ A^{\star}(s)\bigr\} \label{eq:wno_conj} \\ 
\text{wno}\bigl\{ A(s)\bigr\} &= -\text{wno}\bigl\{ A^{-1}(s)\bigr\} \label{eq:wno_inv}
\end{align}
\end{definition}

The open-loop FRF from the system in Fig.~\ref{fig:damping_loop} is given as $$L(k) = G_d[H_1(k)+H_2(k)+C_m(k)].$$ Let $F(k) = H_1(k)+H_2(k)+C_m(k)$ such that $L(k) = G_dF(k)$; by the Nyquist stability criterion, the closed-loop system is stable if and only if $1+G_dF$ makes $n_{G_d}+n_F$ counter-clockwise encirclements of the origin (where $n_{G_d}$ and $n_F$ are, respectively, the number of RHP poles of $G_d$ and $F$). The Nyquist plot of $1+G_dF$ must also not pass through the origin.

\begin{theorem} \label{Thm1}
Suppose that $k_i$, $k_u$, $k_{m_1}$, and $k_{m_2}$ are feasible solutions to the following constraint:
\begin{equation} \label{eq:theorem1_cond}
\begin{split}
z^{\star}(k)z_0+z_0^{\star}z(k) > 0 \\
\forall \omega \in \Omega
\end{split}
\end{equation}
where 
\begin{align*}
z(k) &= 1+G_d[H_1(k)+H_2(k)+C_m(k)] \\
z_0 &= 1+G_d[H_1(k_0)+H_2(k_0)+C_m(k_0)]
\end{align*}
with $\{G_d,H_1,H_2\} \in \mathscr{S}$. Then the closed-loop system $T$ is stable if the parameters in the set $k_0$ are stabilizing initial gains.
\end{theorem}

\textit{Proof:}
The proof is based on the Nyquist stability criterion and the properties of the winding number. The winding number of $z^{\star}(k)z_0$ is given as follows:
\begin{equation} \label{eq:winding_proof}
\begin{aligned}
{\mbox{wno}} \{ z^{\star}(k)z_0\} &= {\mbox{wno}} \{ z^{\star}\} + {\mbox{wno}} \{ z_0\} \\
&= -{\mbox{wno}} \{ 1+G_dF(k)\} \\
&\phantom{=} + {\mbox{wno}} \{ 1+G_dF(k_0)\} \\
\end{aligned}
\end{equation}
where $F(k_0) = H_1(k_0) + H_2(k_0) + C_m(k_0)$. Note that $F(k)$ is strictly proper and $G_dF(k)$ is strictly proper; therefore, the winding number of $z^{\star}(k)z_0$ can be evaluated over $\Omega$ instead of the $D$-contour. Additionally, the constraint in (\ref{eq:theorem1_cond}) implies that $\Re\{ z^{\star}(k)z_0\} > 0$ (where $\Re\{ \cdot \}$ indicates the real part of the argument), which signifies that the Nyquist plot of $z^{\star}(k)z_0$ will not pass through or encircle the origin. Therefore, $\mbox{wno} \{ z^{\star}(k)z_0\} = 0$; from (\ref{eq:winding_proof}), the following condition can then be realized:
\begin{equation} \label{eq:winding_proof3}
\mbox{wno} \{ 1+G_dF(k)\} = {\mbox{wno}} \{ 1+G_dF(k_0)\}
\end{equation}
The condition in (\ref{eq:winding_proof3}) implies that if the initializing controllers $k_0$ are stabilizing (i.e., the open-loop system $G_dF(k_0)$ meets the Nyquist stability criterion), then the closed-loop system will be stable.
{\hfill \ensuremath{\blacksquare}}

\subsection{Initializing Controller}
For the given structure in Figure.~\ref{fig:damping_loop} , it remains to show how to select the initial stabilizing controllers in order to guarantee the stability of the closed-loop system. From the control structure of the power converter control system, it can be observed that if all the gains in Figure.~\ref{fig:damping_loop} are set to zero, then the system will be in open-loop. However, since $G_d \in \mathscr{S}$, then selecting $k_0 = 0$ will guarentee the stability of the closed-loop system.

If the initializing controllers are selected such that the performance with these controllers is far from the desired performance, then it is possible that either the optimization problem yields no feasible solution, or that the solver runs into numerical problems (which leads to infeasible solutions). One method to resolve this problem is to apply relaxation techniques where a relaxed optimization problem is solved; the solution to the relaxed problem is then used as the initializing controllers for the non-relaxed problem.

\subsection{Convex Optimization via Semi-Definite Programming}
All of the optimization problems considered in section \ref{sec:loop_shape} are known as semi-infinite programming (SIP) problems since there are a finite number of optimization variables $k$ and an infinite number of constraints with respect to $\omega$. To solve any of these problems, the optimization algorithm can be converted to a semi-definite programming (SDP) problem. In this manner, a predefined frequency grid can be implemented in order to solve a finite number of constraints. In other words, for a finite number of frequency points $n$ selected in $\omega \in [0,\infty)$, then $n$ constraints must be satisfied. This frequency grid can be predefined in a variety of manners (see \cite{SVBB11}, \cite{GKL10b}, \cite{FR05}).

\section{Case Study}
\label{sec:case}
The focus of this case study will be on the SATURN power converter, which incorporates the control methodology shown in Figure.~\ref{fig:damping_loop} and uses the filter shown in Figure.~\ref{fig:circuit}. The SATURN converter is used in the Large Hardron Collider, in injector machines, in experimental areas to power warm magnets, and for DC or pulsed applications. In this power converter, a $18\:kV/50\:Hz$ transformer is used with a diode rectifier and a DC-Link filter for the AC/DC conversion. An IGBT bridge (4 quadrant operation) is then used for a DC/DC conversion, and the output of this bridge is then fed into the filter (i.e, $v_i$ in Fig.~\ref{fig:circuit}). For this application, two identical modules are assembled in series (which doubles the output voltage) where the equivalent switching frequency of this bridge is $5 \: kHz$. A schematic of the SATURN modules are shown in Fig.~ \ref{fig:schematic}. A complete assembly of the SATURN power converter is shown in Fig.~\ref{fig:saturn_pc} while the load (i.e., the $RL$ circuit representing the magnet) is shown in Fig.~\ref{fig:load}.

\begin{figure}
\centering
\includegraphics[width=\columnwidth]{../pics/schematic}
\caption{Schematic of the SATURN modules set in series.}
\label{fig:schematic}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=\columnwidth]{../pics/Saturn_1}
\caption{SATURN power converter used for various applications at CERN.}
\label{fig:saturn_pc}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=\columnwidth, height=8cm]{../pics/load}
\caption{The SATURN load which is used to mimic the dynamics of the magnet.}
\label{fig:load}
\end{figure}

\subsection{Frequency Response Measurement}
Since the proposed method uses a data-driven methodology with frequency-domain data, the frequency response of each subsystem within the power converter control system must be obtained. In other words, we must obtain the frequency responses of $G_d$, $H$, $P_1$, and $P_2$. The signals that are accessible for the measurements are the inputs to the capacitor banks ($U_{dc}$ in Fig.~\ref{fig:schematic}), and the outputs of the sensors $P_1$ and $P_2$. Therefore, when all of the controller gains are set to zero, we are able to obtain the frequency responses of $G_dHP_1$ and $G_dP_2$. However, note that $G_d$ appears independently of $P_2$ in (\ref{eq:Tclp}) and (\ref{eq:Tcl}); since $P_1$ and $P_2$ are sensors with very high bandwidths relative to $G_d$ (approximately $10 \: kHz$), then $G_d \approx G_dP_2$  at frequencies less than $1 \: kHz$.

The frequency response of the subsystems were obtained with a transfer function analyzer (Powertek GP102) which implements a sine-sweep method that recovers the gain and phase of a system at discrete frequency points. The appropriate scaling factors were taken into account for the measurements (due to the series connection of the SATURN modules) in order to coincide with the structure used in Fig.~\ref{fig:damping_loop}. The frequency responses of $G_dP_2$ and $G_dHP_1$ are shown in Fig.~\ref{fig:G} and Fig.~\ref{fig:GHP1}, respectively.

\begin{figure}
\centering
\includegraphics[width=\columnwidth]{../pics/G.eps}
\caption{Frequency response measurement from the input of the capacitor banks to the output of sensor $P_2$ (with all controller gains set to zero).}
\label{fig:G}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=\columnwidth]{../pics/GHP1.eps}
\caption{Frequency response measurement from the input of the capacitor banks to the output of sensor $P_1$ (with all controller gains set to zero).}
\label{fig:GHP1}
\end{figure}

\subsection{Controller Synthesis}
For this application, it was desired to shape $T^{\prime}(k)$ and $T(k)$ such that a bandwidth of $300 \: Hz$ and $500 \: Hz$ is attained, respectively (where both achieve a damping of $\zeta = 0.8$). Note that in both of these TF's, a pure delay appears in the numerator; therefore, the performance of the loop-shape algorithm can be improved by specifying a desired loop-shape $T_d = T_d^*e^{-sT_\alpha}$ where $T_d^*$ was selected as a standard second order process, i.e.,
\begin{equation}
T_d^*(s) = \frac{\omega_d^2}{s^2 + 2\zeta \omega_d s + \omega_d^2}
\end{equation}
where $\zeta$ is the damping factor and
\begin{equation*}
\omega_d = \frac{2 \pi f_d}{\sqrt{1-2\zeta^2 + \sqrt{2-4\zeta^2 + 4\zeta^4}}}
\end{equation*}
where $f_d$ is the desired closed-loop bandwidth. In other words, $T_d$ is simply a delayed version of the second order process.

Although the delay in $G_d$ was captured in the frequency response measurement, it is known that there also exists an additional measurement delay $T_\beta$ that was not captured in the identification experiment. This delay occurs after digitization of the analog signals at the outputs of $P_1$ and $P_2$. The value of the delay is uncertain and is known to be in the range of $T_\beta \in [0,30]\mu s$. Therefore, a multi-model design can be considered where the additional delay can be gridded in this range and incorporated into the closed-loop TF's. The grid was established in intervals of $5 \: \mu s$ (i.e., $T_{\beta_i} = [0,5,\ldots30] \mu s$, $i = 1,\ldots,7$).

In the $\mathcal{H}_{\infty}$ sense, the optimization problem to consider for this case study is as follows:
 \begin{equation} \label{eq:case_study_opt}
\begin{aligned}
& \underset{ k \in \mathbb{R}}{\text{minimize}}
& & \gamma  \\
& \text{subject to:} & & \|T_i(k)-T_d\|_{\infty}< \gamma \\
& &  &\|T_i^{\prime}(k)-T_d^{\prime}\|_{\infty}< \gamma \\ 
& & & i = 1,\ldots,7
\end{aligned}
\end{equation}
where $T_i(k)$ and $T_i^{\prime}(k)$ are the closed-loop TF's that incorporate the additional $i$-th delay in $T_{\beta_i}$; $T_d$ is the desired closed-loop TF for loop-shaping $T(k)$ (with a desired bandwidth of $f_d = 500 \: Hz$ and damping $\zeta = 0.8$); $T_d^{\prime}$ is the desired closed-loop TF for loop-shaping $T^{\prime}(k)$ (with a desired bandwidth of $f_d^{\prime} = 300 \: Hz$ and damping $\zeta^{\prime} = \zeta$). A similar optimization problem can be considered for minimizing the $\mathcal{H}_2$ norm of the process. This optimization problem can be transformed to the convex problem by implementing the methods outlined in section \ref{sec:loop_shape}. 
\subsection{Experimental Results}
The constraints in the optimization problem in (\ref{eq:case_study_opt}) were first converted to LMI constraints; the problem was then converted to an SDP problem (since the transfer function analyzer provides the gain and phase at discrete frequency points). For solving the $\mathcal{H}_2$ problem in SDP form, the objective function in (\ref{eq:loop_shape_LMI_2}) must be discretized where $\int \gamma(\omega) d\omega \rightarrow \sum_i \gamma(\omega_i)$.

For comparative purposes, controllers were designed by considering the model of the process. There is uncertainty associated with the delay $T_\alpha$; the range of this uncertainty is $T_\alpha \in [0,200]\mu s$. Therefore, for the model-based design, the problem in (\ref{eq:case_study_opt}) was solved by gridding in both $T_\alpha$ and $T_\beta$.

Fig.~\ref{fig:d_loop} shows the closed-loop frequency response of $|T^{\prime}(j\omega)|$ while Fig.~\ref{fig:v_loop} shows the closed-loop frequency response of $|T(j\omega)|$ for the solutions obtained by minimizing both the $\mathcal{H}_{\infty}$ and $\mathcal{H}_2$ norms of the process. From these figures, it can be observed that that model-based design produces the worst performance while the data-driven based design achieves the desired performance for both TF's. The performance achieved by the data-driven method (in both the $\mathcal{H}_{\infty}$ and $\mathcal{H}_2$ minimization cases) are comparable. 
\begin{figure}
\centering
\includegraphics[width=\columnwidth]{../pics/d_loop_mag.eps}
\caption{The closed-loop response of $|T^{\prime}(j\omega)|$; data-driven method with $\mathcal{H}_{\infty}$ performance (red line); data-driven method with $\mathcal{H}_2$ performance (blue line); model-based approach with $\mathcal{H}_{\infty}$ performance (yellow line); $-3 \: dB$ point representing $300 \: Hz$ bandwidth (dashed-black line).}
\label{fig:d_loop}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=\columnwidth]{../pics/v_loop_mag.eps}
\caption{The closed-loop response of $|T(j\omega)|$; data-driven method with $\mathcal{H}_{\infty}$ performance (red line); data-driven method with $\mathcal{H}_2$ performance (blue line); model-based approach with $\mathcal{H}_{\infty}$ performance (yellow line); $-3 \: dB$ point representing $500 \: Hz$ bandwidth (dashed-black line).}
\label{fig:v_loop}
\end{figure}

\section{Conclusion}
\label{sec:conclusion}
A new data-driven method for computing a controller for the CERN power converter control system that attains $\mathcal{H}_2$ or $\mathcal{H}_{\infty}$ performance has been presented. A frequency-domain approach has been used in order to avoid the problem of unmodeled dynamics associated with parametric models. A non-convex loop-shaping constraint was convexified by linearizing the non-convex function around a stabilizing operating point. This linearization process allowed the use of the Shur Complement Lemma to construct an LMI and solve a convex optimization problem. This method has been applied to a power converter control system which uses a specific controller structure and is used for experimental purposes at CERN. In the case study presented in this paper, it has been shown that the proposed data-driven method offers a systematic optimization-based approach that meets the challenging specifications required for the application. In future work, it would be

\bibliography{linear}
\end{document}

### 2017-02-11 Papers/Nonlinear Optimization/Latex/Draft/Draft.tex
adding files to git (11/2/2017)

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%2345678901234567890123456789012345678901234567890123456789012345678901234567890
%        1         2         3         4         5         6         7         8

\documentclass[letterpaper, 10 pt, conference]{ieeeconf}  % Comment this line out if you need a4paper

%\documentclass[a4paper, 10pt, conference]{ieeeconf}      % Use this line for a4 paper

\IEEEoverridecommandlockouts                              % This command is only needed if 
                                                          % you want to use the \thanks command

\overrideIEEEmargins                                      % Needed to meet printer requirements.

\bibliographystyle{IEEEtran}
\pdfminorversion=4

\usepackage{graphicx}  % Add graphics capabilities
\usepackage{epstopdf} % to include .eps graphics files with pdfLaTeX
 \usepackage{epsfig}
 %\usepackage{psfrag}
 \usepackage{color}
%\usepackage{mathptmx} % assumes new font selection scheme installed
%\usepackage{times} % assumes new font selection scheme installed
\usepackage{amsmath} % assumes amsmath package installed
\usepackage{amssymb}  % assumes amsmath package installed
\usepackage{mathrsfs}
\let\proof\relax
\let\endproof\relax
\usepackage{amsthm}

%\usepackage{graphicx,psfrag,url}

\newtheorem{theorem}{Theorem}
\newtheorem*{remark*}{Remark}
\newtheorem{lemma}{Lemma}
\newtheorem{definition}{Definition}
%\newtheorem{prop}{Proposition}

\DeclareMathOperator*{\argmin}{arg\,min}
\usepackage{bm}
\renewcommand{\qedsymbol}{$\blacksquare$}

\title{Designing Robust Controllers With $H_{\infty}$ Performance Using Frequency-Domain Data}

\author{Achille Nicoletti$^{1}$, and Alireza Karimi$^{1}$
\thanks{$^{1}$A. Nicoletti and A. Karimi are with the Automatic Control Laboratory at Ecole Polytechnique F\'ed\'erale de Lausanne (EPFL), Switzerland.
       Corresponding author: Alireza Karimi: {\tt\small alireza.karimi@epfl.ch}}
\date{September 2015}
}

\begin{document}

\maketitle
\thispagestyle{empty}
\pagestyle{empty}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
In this paper, a new frequency-domain method for designing robust controllers is proposed that provides optimal $\mathcal{H}_{\infty}$ performance. A nonlinear optimization problem is formulated which guarantees the stability of the closed-loop system whilst ensuring robust performance. A convexified version of the $\mathcal{H}_{\infty}$ criterion has been established in many works and have utilized a similar frequency gridding process; therefore, it is of interest to determine the definiteness of the solution produced by this convex optimization method with respect to the solution of the optimal $\mathcal{H}_{\infty}$ problem proposed in this work. 
\end{abstract}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
The uncertainties associated with many of today's complex systems pose challenging tasks for engineers and researchers within the control systems community. These uncertainties can cause performance degradations and stability problems that may lead to catastrophic events. Robust controller design methods seek to rectify this issue by designing controllers that ensure proper stability margins whilst maintaining suitable performance.

The robust controller design methodology can be realized in two manners: using time-domain or frequency-domain data. In this paper, the frequency-domain approach will be utilized for the controller design scheme. In a data-driven setting, this frequency domain approach can be used to avoid unmodeled dynamics associated with parametric models. A survey on the differences associated with model-based control and data-driven control has been addressed in \cite{HW13} and \cite{BCE12}. The authors in \cite{HDAV10} use the frequency response data of a stable system to design an optimal controller through a symmetric root locus technique. A robust frequency-domain control design method has been established in \cite{KNND13b} that requires a solution to a non-linear optimization problem. A frequency-domain loop-shaping approach to design fixed-structure controllers is presented in \cite{KNND13c}. However, in this method, the closed-loop stability is not guaranteed and should be verified a posteriori.

Robust controller design methods belonging to the $\mathcal{H}_{\infty}$ control framework minimizes the $\mathcal{H}_{\infty}$ norm of a weighted closed-loop sensitivity function. Solving the $\mathcal{H}_{\infty}$ problem can be accomplished in a variety of manners. A convex approximation of the $\mathcal{H}_\infty$ criterion has been discussed in \cite{KG10} and \cite{KGL08} where convex constraints are imposed on the Nyquist diagram. The problem is convexified by constructing a linearly parameterized controller and devising linear constraints with respect to a desired open-loop transfer function.  A frequency-domain approach for computing low-order multivariable linearly parameterized controllers is presented in \cite{SOW10}. The $\mathcal{H}_{\infty}$ constraints are convexified around an initial stabilizing controller. An iterative algorithm is used that converges to a local optimal solution of the non-convex problem. However, in \cite{HAB13},  a convex-concave approximation of the $\mathcal{H}_{\infty}$ constraint is used which is based on an initial stabilizing controller. The extension of this method to design multivariable PID controllers for stable systems is presented in \cite{BHA16}. This method uses the same convex approximation as in  \cite{SOW10} but is limited to stable systems and PID structure.

In the works asserted above, it has been proved that a convex approximation of the $\mathcal{H}_{\infty}$ problem yields favorable results; however, these approximations do not yield the true global optimal solution to the $\mathcal{H}_{\infty}$ problem. This paper presents an extension of the work in \cite{KNZ16}, and its purpose is to devise a new frequency-domain approach for obtaining the optimal solution to the $\mathcal{H}_{\infty}$ problem. In \cite{KNZ16}, it was shown that the optimal solution is obtained when the order of the controller increases to infinity; in the proposed method, the optimal solution can be obtained for a fixed low-order controller (which has desirable practical implications). A nonlinear optimization problem is formulated to guarantee stability of the closed-loop system while ensuring robust performance (without any approximation). Additionally, it will be shown that the proposed method produces a solution that converges to the global optimal solution of the $\mathcal{H}_{\infty}$ problem under certain conditions. A preset frequency grid will be used to satisfy the robust performance condition and solve for a finite number of constraints. It is desired to compare the solutions produced from the convex optimization algorithms in \cite{KNZ16} with the proposed algorithm and correlate the .

This paper is organized as follows: In Section \ref{sec:pre}, the class of models, controllers and control objectives are defined. Section \ref{sec:problem_form} will address the conditions required for robust performance and the optimization methods used to obtain a solution to the $\mathcal{H}_{\infty}$ problem. Section \ref{sec:sim} will demonstrate the effectiveness of the proposed method and establish the efficacy for the convex approximation of the $\mathcal{H}_{\infty}$ criterion. Finally the concluding remarks are given in Section \ref{sec:conclusion}.

\textbf{Notation}: In order to avoid the risk of any confusion, the notation for the symbols employed in this paper will be defined here. Bolded symbols will represent vectors.
\begin{align*}
\mathbb{R} &: \ \mbox{the set of all real numbers.} \\
\mathbb{R}_+ &: \ \mbox{the set of all real numbers greater than zero.} \\
\Re\{\cdot \} &: \ \mbox{the real part of a complex variable.} \\
\Im\{\cdot \} &: \ \mbox{the imaginary part of a complex variable.} \\
\bm{v} &: \ \mbox{column vector }\bm{v} \mbox{ with elements }[v_1,\ldots,v_n]^{\top}. \\
s &: \ \parbox[t]{18em}{complex frequency variable used to represent continuous-time systems.} \\
z &: \ \parbox[t]{18em}{complex frequency variable used to represent discrete-time systems.}
\end{align*}

\section{Preliminaries} \label{sec:pre}
\subsection{Class of Models}
The set of all linear time-invariant (LTI) single-input-signal-output (SISO) stable strictly proper models belonging to the family of perturbed plants with multiplicative uncertainty can be defined as follows:
\begin{equation}\label{eq:uncert_set}
\mathcal{G} = \{ G_p(s)[1+\Delta_p(s) W_{2_{p}}(s)]; \quad p=1,\ldots,q\}
\end{equation}  
where $G_p(s)$ is the nominal model of the process, $W_{2_{p}}(s)$ is an uncertainty weight with bounded infinity norm, and $\Delta_p(s)$ is an unknown stable transfer function satisfying $\| \Delta_p \|_{\infty}<1$. For simplicity, one model from the set $\mathcal{G}$ will be analyzed, and the subscript $p$ will be omitted.

Let the set $\mathscr{P}$ represent the family of all stable, proper, real-rational transfer functions. It is imperative to note that $\mathscr{P}$ is closed under multiplication and addition; in other words, if $P_1(s),P_2(s) \in \mathscr{P}$, then 
\begin{equation}
\{ P_1(s)+P_2(s),P_1(s)P_2(s)\} \in \mathscr{P}
\end{equation}
This definition will also apply to both continuous-time and discrete-time systems. Suppose that a SISO feedback control system structure is used where the plant is represented as $G(s) = N(s)M^{-1}(s)$ such that $\{N(s),M(s)\} \in \mathscr{P}$. As asserted in \cite{ZD98} and \cite{DFT92}, if $\{N(s), M(s)\} \in \mathscr{P}$, then $G(s) = N(s)M^{-1}(s)$ is called a \textit{coprime factorization} of $G(s)$ over $\mathscr{P}$. The controller $K(s) =X(s)Y^{-1}(s)$ can also be described in coprime form, where $\{X(s), Y(s)\} \in \mathscr{P}$.

\subsection{Class of Controllers}
The controllers $X(s)$ and $Y(s)$ for this control scheme will be parameterized in the decision vector $\bm{\rho}$, and can be expressed as
\begin{equation}
\begin{aligned} \label{eq:cont}
X(\bm{\rho},s) &= \bm{\rho}_x^{\top} \bm{\phi}_x(\bm{\rho},s)\\
Y(\bm{\rho},s) &= \bm{\rho}_y^{\top} \bm{\phi}_y(\bm{\rho},s)\\
\end{aligned}
\end{equation}
where $\bm{\rho}_x \in \mathbb{R}^{n_x}$, $\bm{\rho}_y \in \mathbb{R}^{n_y}$, and $\{\bm{\phi}_x(\bm{\rho},s), \bm{\phi}_y(\bm{\rho},s)\}$ are vectors of stable transfer functions chosen from a set of orthogonal basis functions. An example of such a function is the Laguerre basis function \cite{Kar13}:
\begin{equation} \label{eq:Laguerre}
\phi_{\{x,y\}_1}(s)=1,\quad \phi_{\{x,y\}_q}(\bm{\rho},s) = \frac{\sqrt{2 \rho_c}(s-\rho_c)^{q-2}}{(s+\rho_c)^{q-1}}
\end{equation}
for $q = 2,\ldots,n$, where $\rho_c \in \mathbb{R}_+$. For discrete-time systems, the Laguerre basis function can be expressed as follows:
\begin{equation} \label{eq:Laguerre_z}
\phi_{\{x,y\}_1}(z)=1,\quad \phi_{\{x,y\}_q}(\bm{\rho},z) = \frac{\rho_d^*(1-\rho_d z)^{q-2}}{(z-\rho_d)^{q-1}}
\end{equation}
where $\rho_d^* = \sqrt{1-\rho_d^2}$ and $\{\rho_d \in \mathbb{R}: -1 < \rho_d < 1\}$. Note that when $\rho_d = 0$, the discrete-time Laguerre basis function becomes a simple finite-impulse response (FIR) filter.

A PID controller can also be represented in coprime form. Suppose that the desired controller structure is given as:
\begin{equation} \label{eq:pid}
K(\bm{\rho},s)=\rho_1 + \rho_2 \frac{1}{s} + \rho_3 \frac{s}{T_fs+1}
\end{equation}
Then the coprime controllers can be expressed as follows:
\begin{equation}
\begin{aligned} \label{eq:pid_2}
X(\bm{\rho},s) &= \frac{(\rho_1 T_f+\rho_3)s^2 + (\rho_1+\rho_2 T_f)s + \rho_2}{(s+\rho_c^{\prime})^2}\\
Y(\bm{\rho},s) &= \frac{s(T_fs+1)}{(s+\rho_c^{\prime})^2}
\end{aligned}
\end{equation}
where $\rho_c^{\prime} \in \mathbb{R}_+$. With the PID, note that if $\rho_c^{\prime}$ is fixed, then the coprime $X$ is linearly parameterized while $Y$ is a TF independent of the decision variables. This will always be the case when the controller $K$ is linearly parameterized.
\section{Problem Formulation} \label{sec:problem_form}
The methods described in this paper are associated with minimizing the $\mathcal{H}_{\infty}$ norm of a desired weighted sensitivity function. The sensitivity function $S(s)$ and complementary sensitivity function $T(s)$ associated with this control scheme can be formulated as follows:
\begin{equation}
\begin{aligned} \label{eq:S}
S(s) &:= e/r =[1+L(\bm{\rho},s)]^{-1} \\ &=  M(s)Y(\bm{\rho},s)[N(s)X(\bm{\rho},s)+M(s)Y(\bm{\rho},s)]^{-1}\\
\end{aligned}
\end{equation}
\begin{equation}
\begin{aligned} \label{eq:T}
T(s) &:= y/r =L(\bm{\rho},s)[1+L(\bm{\rho},s)]^{-1} \\ &=  N(s)X(\bm{\rho},s)[N(s)X(\bm{\rho},s)+M(s)Y(\bm{\rho},s)]^{-1}\\
\end{aligned}
\end{equation}
where $L(s) = G(s)K(s)$; $r$ is the reference input; $y$ is the system output; $e$ is the tracking error signal (i.e., $e = r-y$). From the above definitions of the sensitivity functions, it can be observed that $S(s)+T(s)=1$.

\subsection{Robust Performance via Convex Optimization}
Consider a process from the multiplicative uncertainty set in (\ref{eq:uncert_set}). Given a performance weighting filter $W_1(s)$ with bounded infinity norm, a necessary and sufficient condition for achieving robust performance is given by \cite{DFT92}:
\begin{equation}\label{eq:inf_norm}
\| |W_1 S| + |W_2 T| \|_{\infty} < \gamma
\end{equation}
where $\gamma = 1$. However, the problem of minimizing the upper bound $\gamma$ will be considered in this paper, where $ \gamma \in \mathbb{R}_+$. The condition in (\ref{eq:inf_norm}) can also be expressed as
\begin{equation} \label{eq:inf_norm2}
|W_1(j\omega)S(\bm{\rho},j\omega)|+|W_2(j\omega)T(\bm{\rho},j\omega)|<\gamma, \quad \forall \omega \in \Omega
\end{equation}
where $\Omega \in [0,\infty)$. For notation purposes, the dependence in $j\omega$ will be omitted and will only be reiterated when deemed necessary. The dependence on $\bm{\rho}$ will continue to be highlighted. By substituting (\ref{eq:S}) and (\ref{eq:T}) into (\ref{eq:inf_norm2}), the condition for robust performance can be expressed as
\begin{equation} \label{eq:circle}
\gamma^{-1}\left[ |W_1MY(\bm{\rho})| + |W_2 NX(\bm{\rho})| \right] < |\psi(\bm{\rho})|, \quad \forall \omega \in \Omega
\end{equation}

\begin{figure}
\centering
\includegraphics[width=0.7\columnwidth]{../pics/circle_rotation_RP.pdf}
\caption{Graphical interpretation of the $\mathcal{H}_\infty$ robust performance constraint in the complex plane.}
\label{fig:circle}
\end{figure}

where $\psi(\bm{\rho}) = NX(\bm{\rho})+MY(\bm{\rho})$. Consider a circle in the complex plane at a specific frequency in $\Omega$ which is centered at $\psi(\bm{\rho})$ and has radius $\gamma^{-1}\left[ |W_1MY(\bm{\rho})| + |W_2 NX(\bm{\rho})| \right]$ (as shown in Fig.~\ref{fig:circle}). The constraint in (\ref{eq:circle}) ensures that for any frequency point in $\Omega$, the circle associated with this frequency point will not encircle the origin. In \cite{KNZ16}, the authors show that there exists a function $F(s)$ that can rotate this circle such that it lies on the right-hand side of the $j\omega$ axis of the complex plane (i.e., all values on and within the circle have positive real parts). This condition is recalled with the following Lemma:

\begin{lemma}   \label{lem1}
Suppose that 
\begin{equation*}
\begin{aligned}
H_1(\bm{\rho}) &=W_1MY(\bm{\rho}) \psi^{-1}(\bm{\rho})\\   H_2(\bm{\rho}) &=W_2NX(\bm{\rho}) \psi^{-1}(\bm{\rho})
\end{aligned}
\end{equation*}
are frequency responses of bounded analytic functions in the right-half plane. Then, the following constraint is met
\begin{equation} \label{eq4}
\sup_{\omega \in \Omega}  \big(|H_1(\bm{\rho}) | + |H_2(\bm{\rho}) | \big) < \gamma
\end{equation}
if and only if there exists a stable transfer function $F(s)$ that satisfies
$$
\Re\{\psi(\bm{\rho})F\}>\gamma^{-1}\left[ |W_1MY(\bm{\rho})F| + |W_2 NX(\bm{\rho})F| \right]
$$
for all $\omega \in \Omega $
\end{lemma}
{\it Proof :} 
The proof of a similar condition has been formally documented in \cite{KNZ16}. Here, the condition has been extended for attaining robust performance instead of nominal performance.
{\hfill \ensuremath{\blacksquare}}

With the above Lemma, a necessary and sufficient condition can be derived for attaining robust performance. In \cite{KNZ16}, it is shown that if $X(\bm{\rho})$ and $Y(\bm{\rho})$ are linearly parameterized, then a convex optimization problem can be formulated as follows: 
\begin{equation} \label{eq:convex_con}
\begin{aligned}
& \underset{ \bm{\rho}}{\text{minimize}}
& & \gamma  \\
& \text{subject to:} & & \gamma^{-1} \left[  |W_1MY(\bm{\rho})| + |W_2 NX(\bm{\rho})| \right] < \Re\{\psi(\bm{\rho}) \}  \\ 
& & & \forall \omega \in \Omega \quad 
\end{aligned}
\end{equation}
Notice that (\ref{eq:convex_con}) is a semi-infinite programming (SIP) optimization problem since there are a finite number of optimization variables and an infinite number of constraints. This problem can be solved by presetting a frequency grid $\omega$ and solving a finite number of constraints. This frequency grid can be predefined in a variety of manners (see \cite{SVBB11}, \cite{GKL10b}).

\subsection{Optimal Performance via Nonlinear Programming}
In \cite{KNZ16}, it is shown that when the orders of $X(\bm{\rho})$ and $Y(\bm{\rho})$ approach infinity, then $\gamma$ from (\ref{eq:convex_con}) approaches the optimal solution to the $\mathcal{H}_{\infty}$ problem. However, it is impractical and sometimes impossible to implement large order controllers in a real system.

One solution to this problem is to find the optimal solution for a fixed low-order controller. According to Lemma \ref{lem1}, it is known that there exists a stable transfer function $F$ such that the constraint to the $\mathcal{H}_{\infty}$ problem is satisfied. Therefore, the optimal solution to this problem can be accomplished by fixing the orders of $X(\bm{\rho})$ and $Y(\bm{\rho})$ and implementing the following optimization problem:
\begin{equation} \label{eq:opt_true}
\begin{aligned}
& \underset{ \bm{\rho}}{\text{minimize}}
& & \gamma  \\
& \text{subject to:} & & \gamma^{-1} |F(\bm{\rho})|\big[  |W_1MY(\bm{\rho})| + |W_2 NX(\bm{\rho})| \big] \\ &&& \hspace{3.3cm}<   \Re\{F(\bm{\rho})\psi(\bm{\rho}) \}  \\ 
& & & \forall \omega \in \Omega \quad 
\end{aligned}
\end{equation}
where $F(\bm{\rho})$ can be chosen such that it incorporates the Laguerre basis functions defined in (\ref{eq:Laguerre}), i.e.,
\begin{equation} \label{eq:Laguerre_sum_c}
F(\bm{\rho}) = \rho_{f_{1}}+ \sum_{p=2}^{q} \rho_{f_{p}}\frac{\sqrt{2 \rho_o}(s-\rho_o)^{p-2}}{(s+\rho_o)^{p-1}}
\end{equation}
where $\rho_o \in \mathbb{R}_+$. It will now be shown that the solution to the optimization problem in (\ref{eq:opt_true}) converges to the optimal solution of the $\mathcal{H}_\infty$ problem as the order of $F(\bm{\rho})$ increases. The proof will omit the dependence on $\bm{\rho}$ since the result is independent on the parameterization of the basis functions.

\begin{theorem} \label{thm_1}
Suppose that the controller $K_o(s)$ achieves the optimal $\mathcal{H}_\infty$ robust performance condition for the plant model $G(s) = N(s)M^{-1}(s)$ such that
\begin{equation}
\gamma_o = \sup_{\omega \in \Omega} \bigg(  \left|W_1(1+L_o)^{-1}\right|  + \left|W_2L_o(1+L_o)^{-1}\right|  \bigg)
\end{equation}
where $L_o = GK_o$. Additionally, suppose that $\gamma_n$ is the optimal solution of the problem in (\ref{eq:opt_true}) when $X$ and $Y$ are constructed such that $K = XY^{-1}$ has the same structure as $K_o$ and $F$ is parameterized by an $n$ dimensional orthogonal basis function. Then $\gamma_n$ converges monotonically from above to $\gamma_o$ when $n \rightarrow \infty$.
\end{theorem}
{\it Proof :} 
According to Lemma.\ref{lem1}, there exists $\{X_o(s),Y_o(s)\} \in \mathscr{P}$ and stable transfer function $F_o(s)$ such that $K_o(s) = X_o(s)Y_o^{-1}(s)$ and
\begin{equation}\label{eq:the_eq_1}
\gamma_o = \sup_{\omega \in \Omega} \bigg(  \left|\frac{W_1MY_oF_o}{\Re \{ \psi_oF_o\}} \right| +\left|\frac{W_2NX_oF_o}{\Re \{ \psi_oF_o\}} \right| \bigg)
\end{equation}
where $\psi_o = NX_o+MY_o$. Now take $F_n^*$ as the projection of $F_o$ into the subspace spanned by an $n$ dimensional orthogonal basis function and define the following quantity:
\begin{equation} \label{eq:the_eq_2}
\gamma_n^* = \sup_{\omega \in \Omega} \bigg(  \left|\frac{W_1MY_oF_n^*}{\Re \{ \psi_oF_n^*\}} \right| +\left|\frac{W_2NX_oF_n^*}{\Re \{ \psi_oF_n^*\}} \right| \bigg)
\end{equation}
By contradiction, is can be shown that $\gamma_n^*$ is a bounded function (using the fact that $\Re \{ \psi_oF_o\} > \epsilon > 0$); assume that $j\omega^*$ is a zero of $\Re \{ \psi_o F_n^*\}$. Therefore, at $\omega=\omega^*$,
\begin{equation}
\Re \{ \psi_oF_o\}  = \Re \{ \psi_o(F_o-F_n^*)\} > \epsilon
\end{equation}
However, $\Re \{ \psi_o(F_o-F_n^*)\}$ can be made arbitrarily small by increasing $n$; therefore, for a large but finite $n$, $\Re \{ \psi_o F_n^*\} \neq 0$.

By using the relations in (\ref{eq:the_eq_1}) and (\ref{eq:the_eq_2}), one can compute $|\gamma_o - \gamma_n^*|$ as follows:
\begin{equation}
\begin{split}
|\gamma_o - \gamma_n^*|  & \leq \sup_{\omega \in \Omega} \bigg| \frac{|W_1MY_oF_o| + |W_2NX_oF_o|}{|\Re \{\psi_o F_o \}|}  \\  & \hspace{2cm}- \frac{|W_1MY_oF_n^*| + |W_2NX_oF_n^*|}{| \Re \{\psi_o F_n^* \}|} \bigg|
\end{split}
\end{equation}
However, according to \cite{AN99b}, it is known that
\begin{equation}
\lim_{n \to \infty} \|F_o - F_n^* \|_{\infty} = 0
\end{equation}
From this relation, it can be deduced that $\lim_{n \to \infty} |F_n^*| \rightarrow |F_o|$ and $\lim_{n \to \infty} \Re \{F_n^*\} \rightarrow \Re\{F_o\}$. Therefore, we obtain the following result:
\begin{equation}
\lim_{n \to \infty} |\gamma_o - \gamma_n^*|  = 0
\end{equation}
However, $\gamma_n$ (the solution to the optimization problem in (\ref{eq:opt_true})) is always less than or equal to $\gamma_n^*$ and greater that the optimal solution $\gamma_o$ if the structures of $X$ and $Y$ are the same as $X_o$ and $Y_o$, respectively. Therefore, $\gamma_n$ converges from above to $\gamma_o$, and this convergence is monotonic because the basis functions $F_n$ of order $n$ are a subset of those of order $n+1$, which ensures that $\gamma_{n+1} \leq \gamma_n$.
{\hfill \ensuremath{\blacksquare}}

Note that the constraint in the optimization problem (\ref{eq:opt_true}) is not convex and a non-linear optimization algorithm will need to be implemented in order to solve this problem. In this manner, the parameter $\rho_o$ in $F(\bm{\rho})$ need not be fixed, and the optimal solution can be obtained for a lower-order $F(\bm{\rho})$ (as will be demonstrated in subsequent sections of this paper).

\begin{remark*}
One problem with solving the nonlinear problem in (\ref{eq:opt_true}) is defining the initial conditions. Since there can be many variables involved in this optimization problem, defining the initial conditions to achieve the global optimal solution to the $\mathcal{H}_{\infty}$ problem may not be trivial. One solution to this problem is to first solve the convex optimization problem in (\ref{eq:convex_con}) and use the solution to this problem as the initial conditions for the nonlinear problem in (\ref{eq:opt_true}). In this manner, the likelihood of obtaining the global optimal solution to the nonlinear problem will significantly increase. 
\end{remark*}

\iffalse
PSO is a powerful optimization method that can solve both linear and nonlinear problems. It is based on the principle that groups of individuals work together to improve both their collective and individual performance \cite{Sim13}. Due to the constraints imposed in (\ref{eq:opt_true}), an exterior method (i.e., Non-Death-Penalty approach) will be implemented in order to obtain the optimal solution to the problem. With this method, the constrained optimization problem can be transformed to the following unconstrained problem:
\begin{equation} \label{eq:pso_obj}
\underset{ \{ \bm{\rho}\in \mathbb{R}^n,\gamma \in \mathbb{R}\}}{\text{minimize}} \ \ \Phi(\bm{\rho},\gamma)
\end{equation}
where
\begin{equation} \label{eq:pso_hinf}
\begin{aligned}
\Phi(\bm{\rho},\gamma) &= \gamma + \frac{1}{N}\sum_{k=1}^N \alpha_k Z_k(\bm{\rho},\gamma) \\
Z_k(\bm{\rho},\gamma) &= [\mbox{max}(0,z_k(\bm{\rho},\gamma))]^\beta \\
z_k(\bm{\rho},\gamma) &=   |W_1(j\omega_k)M(j\omega_k)Y(\bm{\rho},j\omega_k)F(\bm{\rho},j\omega_k)| \\ & \hspace{1cm}+ |W_2(j\omega_k) N(j\omega_k)X(\bm{\rho},j\omega_k)F(\bm{\rho},j\omega_k)|  \\ &\hspace{3cm} -  \gamma \Re\{F(\bm{\rho},j\omega_k)\psi(\bm{\rho},j\omega_k) \}  
\end{aligned}
\end{equation}
The value of $\beta$ is usually taken to be $1$ or $2$ and $\alpha_k \in \mathbb{R}$ is the penalty factor \cite{Sim13} . In this paper, $\beta=1$ will be considered. For this particular problem, the value of $\alpha_k$ will be a constant, since the weighting factor for each constraint should be the same ($\alpha_k=\alpha$). In other words, the constraint should not be weighted differently for varying frequencies. Since $\gamma \geq 1$, the value of $\alpha$ should be chosen such that $\psi(\bm{\rho},\gamma) \gg 1$ for all particles in the initialized population.

The PSO algorithm seeks to find an optimal solution by implementing a swarm of $m_p$ particles. Let $\bm{x}_i$ denote the position of the $i^{th}$ particle; for the decision variables considered in (\ref{eq:pso_hinf}), the $i^{th}$ particle occupies the position\footnote{Note that $\gamma_i$ in this context represents the position of the $i^{th}$ particle, and not the $i^{th}$ iteration of the bisection algorithm asserted in the remark in the previous section.}
\begin{equation}
\bm{x}_i := [\rho_{i,1},\rho_{i,2},\ldots,\rho_{i,n},\gamma_i]^{\top} \in \mathbb{R}^{n+1} 
\end{equation}
where $i \in \{1,\ldots,m_p \}$. The velocity of the $i^{th}$ particle (at which it moves though the search space) is denoted as
\begin{equation}
\bm{v}_i := [v_{i,1},v_{i,2},\ldots,v_{i,n},v_{i,\gamma}]^{\top} \in \mathbb{R}^{n+1}. 
\end{equation}
One approach in expressing the manner in which the position and velocity of the $i^{th}$ particle is updated can be realized as
\begin{equation} \label{eq:update}
\begin{aligned}
\bm{x}_i^{l+1} &= \bm{x}_i^{l} + \bm{v}_i^{l+1} \\
\bm{v}_i^{l+1} &= K [ \bm{v}_i^l + \theta_1 r_{1,i}^l(\bm{b}_i^l-\bm{x}_i^l) + \theta_2 r_{2,i}^l(\bm{h}_i^l-\bm{x}_i^l) \\
& \hspace{3.7cm}+ \theta_3 r_{3,i}^l(\bm{g}^l-\bm{x}_i^l) ]
\end{aligned}
\end{equation}
where $K \in \mathbb{R}$ is the constriction coefficient, and $\theta_c \in \mathbb{R}$ for $c \in \{1,2,3 \}$ are the learning rates ($\theta_1$ is the cognitive learning rate, $\theta_2$ is the social learning rate, and $\theta_3$ is the learning rate influencing the best individual found so far since the first generation). The random numbers $r_{c,i}^l$ are uniformly distributed in $[0, 1]$ and represent the stochastic behavior associated with the algorithm. For a stable PSO algorithm, the constriction coefficient should be chosen as follows \cite{Sim13}: 
\begin{equation}
K = \frac{2 k_\alpha}{\theta_T-2}
\end{equation}
where $k_\alpha \in (0,1)$ and $\theta_T = \theta_1 + \theta_2 +\theta_3$. The best-so-far position of the $i^{th}$ particle is defined as
\begin{equation}
\bm{b}_i^l = \argmin_{ \bm{x}_i^t} \{\Phi(\bm{x}_i^t),0\leq t \leq l \}.
\end{equation}
For a given neighborhood size $\sigma$, the best-so-far position of $\sigma$ close neighbors is determined as follows:
\begin{equation}
\bm{h}_i^l = \argmin_{\bm{x}_i^t} \{\Phi(\bm{x}_i^t),0\leq t \leq l\mid \bm{x}_i^t \in H_i^t \}
\end{equation}
where $H_i^t$ are the $\sigma$ nearest neighbors of $\bm{x}_i^t$. The best position of the entire swarm for the current iteration $l$ is defined as
\begin{equation}
\bm{g}^l = \argmin_{\bm{x}_i^l} \{\Phi(\bm{x}_i^l), \forall i \}.
\end{equation}
The PSO algorithm can be summarized with the following steps:

\begin{enumerate}
  \def\makelabel{Step~}
  \item{Initialize a population of $m_p$ particles with random positions $\bm{x}_i^0 \ \forall i$ and velocities $\bm{v}_i^0=0$. Evaluate $\psi(\bm{x}_i^0)$. For a given value of $\alpha_k$ in (\ref{eq:pso_hinf}), ensure that $\psi(\bm{x}_i^0) \gg 1$ for every particle in the population. If $\psi(\bm{x}_i^0) < 1 \ \forall i$, increase the value of $\alpha_k$. Set $l=0$ and determine $\bm{b}_i^0$, $\bm{h}_i^0$, and $\bm{g}^0$.}
  \item{Apply the update equations in (\ref{eq:update}) and evaluate the cost function with the new population. }
  \item{If the termination criterion is satisfied, then the algorithm returns the optimal solution 
  \begin{equation}
  \bm{x}^{\star} = \argmin_{\bm{x}_i^k} \{\psi(\bm{x}_i^k), \forall i,k \}.
  \end{equation} Otherwise, go to the next step.}
  \item{Set $l=l+1$ and determine $\bm{b}_i^l$, $\bm{h}_i^l$, and $\bm{g}^l$. Then return to Step $2$.}
\end{enumerate}
The optimal values of $\theta_c$ may vary depending on the problem that is being analyzed; in general, it is recommended that $\theta_c=2.1 \ \forall c$ \cite{Sim13}. A similar rationalization can be made with the selection of $k_\alpha$; a larger value of $k_\alpha$ encourages exploration while a smaller value of $k_\alpha$ bolsters exploitation. 
 \fi

\section{Simulation Examples} \label{sec:sim}
Let us now consider several examples in order to determine the validity of the proposed method. For each example, the \texttt{MATLAB} software was used in conjunction with the \texttt{fmincon} function to solve the proposed optimization problem.

\subsection{Example 1: Robust Performance}
Consider the unstable non-minimum phase system analyzed in \cite{Zhe10}  and \cite{Ho03} (which is subject to multiplicative uncertainty):
\begin{equation}
G(s) = \frac{s-1}{s^2+0.8s-0.2}
\end{equation}
The objective of this case study is to design a stabilizing PID controller such that the robust performance condition in (\ref{eq:inf_norm}) is satisfied. The weighting filters for this design will be chosen as those defined in \cite{Zhe10}:
\begin{equation}
W_1(s) = \frac{10}{100s+1}, \quad W_2(s) = \frac{s+0.1}{s+1}
\end{equation}
Since $G(s)$ is unstable, the coprime functions can be selected as follows:
\begin{equation}
N(\bm{\rho},s) = \frac{s-1}{(s+\rho_g)^2}, \quad M(\bm{\rho},s) = \frac{(s^2+0.8s-0.2)}{(s+\rho_g)^2}
\end{equation}
where $\rho_g \in \mathbb{R}_+$. For a PID controller, the structure of the controllers $X(\bm{\rho})$ and $Y(\bm{\rho})$ can be selected as those defined in (\ref{eq:pid_2}) with $T_f = 0.01$. 
\subsubsection{Simulation Results}
The problem in (\ref{eq:opt_true}) is solved by converting it to an SDP problem and gridding the frequency from $10^{-3}$ to $10^{3} \ rad/s$ (using $500$ logarithmically spaced points). A $20$-th order basis function for $F(\bm{\rho})$ is selected (as defined in (\ref{eq:Laguerre_sum_c})). For comparative purposes, the \texttt{MATLAB} \texttt{mixsyn} function from the Robust Control Toolbox is used to compute a controller with the given weighting filters; the toolbox yields a $4$-th order controller.

Table.\ref{tab:ex1_1} shows the values of the optimal solutions obtained from various methods. The convex problem in (\ref{eq:convex_con}) was solved with $\rho_g = \rho_c^{\prime} = 1$. Since \texttt{mixsyn} minimizes $\|[W_1S \ \ W_2T] \|_\infty$, it can be observed that a smaller value of this criteria is obtained (with a $4$-th order controller). However, with a simple PID controller, the proposed method yields the best performance for the \textit{true} robust performance criteria in (\ref{eq:inf_norm}). The optimal value for the the decision variable of $F(\bm{\rho})$ was obtained as $\rho_o^{\star} = 0.933$, while the optimal values of the remaining decision variables (for both the convex and proposed optimization methods) are shown in Table.\ref{tab:ex1_2}.

\begin{table}[]
\centering
\caption{My caption}
\label{tab:ex1_1}
\begin{tabular}{c|c|c}
                                                                                                          & $\| |W_1S| + |W_2T| \|_{\infty}$ & $\left\| \begin{matrix} W_1S \\[2pt] W_2T \end{matrix} \right\|_{\infty} $ \\ \hline
\texttt{MATLAB\textsuperscript{\tiny{\textregistered}}} (\texttt{mixsyn})                                                                           & $1.111$                          & $0.789$                                                     \\ \hline
\begin{tabular}[c]{@{}c@{}}$\mathcal{H}_\infty$ parametric\\ approach in \cite{Kar13}\end{tabular}                                                                                     & $1.205$                          & $0.923$                                                     \\ \hline
\begin{tabular}[c]{@{}c@{}}Proposed method\end{tabular}  & $1.019$                          & $0.966$ \\ \hline                                                                                                 
\begin{tabular}[c]{@{}c@{}}Convex method (\ref{eq:convex_con})\end{tabular}  & $1.327$                          & $1.223$
\end{tabular}
\end{table}

\begin{table}[]
\centering
\caption{My caption}
\label{tab:ex1_2}
\begin{tabular}{c|c|cccc}
                                                          & $\rho_1^{\star}$ & $\rho_2^{\star}$              & $\rho_3^{\star}$              & $\rho_g^{\star}$             & $(\rho_c^{\prime})^{\star}$ \\ \hline
\begin{tabular}[c]{@{}c@{}}Convex\\ Method (\ref{eq:convex_con})\end{tabular}   & $-0.565$         & \multicolumn{1}{c|}{$-0.013$} & \multicolumn{1}{c|}{$-0.397$} & \multicolumn{1}{c|}{$1$}     & $1$                         \\ \hline
\begin{tabular}[c]{@{}c@{}}Proposed\\ Method (\ref{eq:opt_true})\end{tabular} & $-0.486$         & \multicolumn{1}{c|}{$-0.021$} & \multicolumn{1}{c|}{$-0.486$} & \multicolumn{1}{c|}{$1.647$} & $1.647$                    
\end{tabular}
\end{table}

\subsection{Example 2: Convergence to Optimal Solution}
Consider the following discrete time SISO system:
\begin{equation}
G(z) = \frac{z-0.186}{z^3 - 1.116z^2 + 0.465z-0.093}
\end{equation}
Note that since this system is stable, then the coprimes can be selected as $N(z) = G(z)$ and $M(z) = 1$. The control objective of this case study is to design a controller (with integral action) that minimizes the nominal performance condition $\|W_1S \|_{\infty}$ (i.e., minimize $\gamma$ in $\|W_1S \|_{\infty} < \gamma$), where
\begin{equation}
W_1(z) = \frac{0.4902(z^2-1.0431z+0.3263)}{(z-1)(z-0.282)}
\end{equation}
For this controller synthesis, we can simply select the basis functions in (\ref{eq:Laguerre_z}) to be FIR filters (i.e., $\rho_d = 0$) for $X(\bm{\rho})$ and $Y(\bm{\rho})$. In order to avoid unboundedness of $W_1$ at $\omega = 0$ and have integral action, the basis functions for $Y(\bm{\rho})$ will be multiplied by $(z-1)/z$. It will be shown that as the order of $F(\bm{\rho})$ increases, the optimal solution $\gamma$ will decrease monotonically and converge to the optimal solution.

\subsubsection{Simulation Results}
The \texttt{mixsyn} command from \texttt{MATLAB}'s Robust Control toolbox yields an optimal value of $\gamma^* = 0.5522$ with a fifth-order controller. Therefore, according to Theorem.\ref{thm_1}, a fifth-order controller was also implemented with the proposed method (i.e., to ensure convergence to the optimal solution). Additionally, two simulations were performed with the proposed method; one simulation with $F(\bm{\rho})$ selected such that the basis function is an FIR filter (i.e., Laguerre basis functions in (\ref{eq:Laguerre_z}) with $\rho_d = 0$) and one simulation with $F(\bm{\rho})$ selected such that $\rho_d$ is a decision variable.  Let $F_{n_f}(\bm{\rho})$ denote the function $F(\bm{\rho})$ of $n_f$-th order and $\gamma_{n_f}$ denote the optimal solution of the nominal performance condition for a given order of $F_{n_f}(\bm{\rho})$. Figure.~\ref{fig:ex2} shows the convergence of the optimal solution $\gamma_{n_f}$ as a function $n_f$; it can be observed that with the proposed frequency-domain method, the optimal solution to the $\mathcal{H}_{\infty}$ problem converges monotonically as the order of $F(\bm{\rho})$ increases. Additionally, when the parameter $\rho_d$ is a decision variable, the convergence time is reduced.

\begin{figure}
\centering
\includegraphics[width=\columnwidth]{../pics/gamma_convergence.eps}
\caption{Optimal solution obtained from \texttt{mixsyn} command (straight-red line); $\gamma_{n_f}$ for $F(\rho)$ as an FIR filter ({\color{red}{- -$\square$- -}});  $\gamma_{n_f}$ for $F(\rho)$ with $\rho_d$ as a decision variable ({\color{red}{- -$*$- -}}); the value of $\rho_d$ when used as a decision variable  ({\color{blue}{- -$\circ$- -}}) }
\label{fig:ex2}
\end{figure}

\subsection{Example 3: Multimodel Uncertainty}
For this example, a robust controller will be designed for a family of unstable systems. This example is taken from the Robust Control Toolbox of \texttt{MATLAB}. The nominal plant model for this family of systems is given as follows:
\begin{equation}
G_0(s) = \frac{2}{s-2}
\end{equation}
This model is perturbed through various types of uncertainties such as time delay, high frequency resonance, pole/gain migration, and extra lag; the family of perturbed models are given as follows:
\begin{equation}
  \begin{split}
    G_1(s) &= G_0(s) \frac{1}{0.06s+1}\\       
    G_2(s) &= G_0(s) \frac{50^2}{s^2+10s+50^2}\\        
    G_3(s) &= G_0(s) \frac{70^2}{s^2+28s+70^2}
  \end{split}
\quad  
  \begin{split}
    G_4(s) &= G_0(s)e^{-0.04s}\\        
    G_5(s) &= \frac{2.4}{s-2.2}\\        
    G_6(s) &= \frac{1.6}{s-1.8}
  \end{split}
\end{equation}
The performance filter $W_1(s)$ and noise filter $W_2(s)$ are chosen to be equal to the filters asserted in \cite{Kar13}, i.e.,:
\begin{equation}
  \begin{split}
    W_1(s) &= \frac{0.33s+4.248}{s+0.008496}\\       
    W_2(s) &= \frac{0.1975s^2+0.6284s+1}{7.901\cdot 10^{-5}s^2+0.2514s+400}
  \end{split}
\end{equation}
For this problem, the control objective is to minimize $\gamma$ and satisfy the following criteria for all seven models:
\begin{equation} \label{eq:mixed_syn}
\|W_1S_{\ell} \|_{\infty} < \gamma \quad \mbox{and} \quad \|W_2T_{\ell} \|_{\infty} < \gamma
\end{equation}
for ${\ell} = 0,\ldots,6$. Note that this control objective satisfies the mixed sensitivity robust condition, and not the robust performance condition in (\ref{eq:inf_norm}). The $\mu$-synthesis approach in the \texttt{MATLAB} Robust Control Toolbox uses this criteria to design a controller. In this approach, a multiplicative uncertainty is considered and an appropriate weighting filter is designed to ensure that the condition in (\ref{eq:mixed_syn}) is satisfied for all seven models. The controller produced by \texttt{MATLAB} with this $\mu$-synthesis approach yields an $18$-th order controller and satisfies the control objective for all models.

The same problem is now solved using the proposed approach. First, the coprime factors $N_{\ell}(s)$ and $M_{\ell}(s)$ for ${\ell} = 0,\ldots,6$ must be established. Since each model is unstable, then each coprime factor must be selected such that $\{N_{\ell}(s),M_{\ell}(s) \}  \in \mathscr{P}$ for all ${\ell}$. A simple choice is to divide both the numerator and denominator of each model by a factor $(s+\rho_p)^{\lambda_{\ell}}$, where $\rho_p \in \mathbb{R}_+$ and ${\lambda_{\ell}}$ is the largest degree of the denominator of the $\ell$-th respective plant model. For example, the coprime factors for the plant $G_2(s)$ can be formed as follows:
\begin{equation}
N_2(s) = \frac{2 \cdot 50^2 }{(s+\rho_p)^3}, \ M_2(s) = \frac{(s-2)(s^2+10s+50^2) }{(s+\rho_p)^3}
\end{equation}
From these relations, it is evident that $G_2(s) = N_2(s)M_2^{-1}(s)$. To further simplify the design, the same $\rho_p$ can be selected for each $\ell$-th coprime. To solve the convex optimization problem in (\ref{eq:convex_con}), $\rho_p$ must be fixed a priori; however, with the proposed method, $\rho_p$ need not be fixed.

The optimization problem (with the proposed approach) for the mixed $\mathcal{H}_\infty$ criteria in (\ref{eq:mixed_syn}) can be formulated as follows:
\begin{equation} \label{eq:opt_true_ex3}
\begin{aligned}
& \underset{ \bm{\rho}}{\text{minimize}}
& & \gamma  \\
& \text{subject to:} & & \gamma^{-1} |W_1M_{\ell}(\bm{\rho})Y(\bm{\rho})F(\bm{\rho})| < \Re\{\psi_{\ell}(\bm{\rho}) F(\bm{\rho})\} \\ 
& & &  \gamma^{-1} |W_2N_{\ell}(\bm{\rho})X(\bm{\rho})F(\bm{\rho})| < \Re\{\psi_{\ell}(\bm{\rho}) F(\bm{\rho})\}   \\ 
& & & \omega \in \Omega, \ell = 0,\ldots,6
\end{aligned}
\end{equation}
where $\psi_{\ell} = N_{\ell}(\bm{\rho})X(\bm{\rho}) + M_{\ell}(\bm{\rho})Y(\bm{\rho})$. In solving the above optimization problem, the parameters in $\{\rho_c,\rho_p,\rho_o \}$ will not be fixed, and will be optimized by the nonlinear programming algorithm (as shown with the notation $N_{\ell}(\bm{\rho})$ and $M_{\ell}(\bm{\rho})$).

\subsubsection{Simulation Results}
The problem in (\ref{eq:opt_true_ex3}) is converted to a SDP problem by considering a logarithmically spaced frequency grid with $Q$ = $200$ points from $\omega_1 = 10^{-3} \: rad/s$ to $\omega_{200} = 10^{4} \: rad/s$. For the convex problem, a $6$-th order controller ($5$-th order controller with one integrator) will be designed by using the Laguerre basis functions defined in (\ref{eq:Laguerre}) with $\rho_c = 20$ and $\rho_p = 100$ (as defined in \cite{KNZ16}). With the proposed method (and for comparative purposes), a $6$-th order controller will also be used while a $20$-th order Laguerre basis function will be considered for $F(\bm{\rho})$ (as defined in (\ref{eq:Laguerre_sum_c})).

The optimal solutions from several optimization algorithms for satisfying the criteria in (\ref{eq:mixed_syn}) are tabulated in Table.\ref{tab:ex3} (where $n$ is the controller order of the respective method). The table also shows the solutions when the convex optimization problem in \cite{KNZ16} is solved when the variables $\rho_c$ and $\rho_p$ are decision variables (thus making the problem non-convex). It can be observed that the proposed method produces the best performance.

\begin{table}[]
\centering
\caption{Comparison of optimal solutions}
\label{tab:ex3}
\begin{tabular}{c|c|c|c|c||c}
                                                                              & \begin{tabular}[c]{@{}c@{}} $n$ \end{tabular} & $\rho_c$ & $\rho_p$ & $\rho_o$ & $\gamma$ \\ \hline
\texttt{MATLAB} $\mu$-Synthesis                                               & $18$                                                        & $-$      & $-$      & $-$      & $1.024$  \\ \hline

\begin{tabular}[c]{@{}c@{}}Algorithm in \cite{KNZ16} \\ (Convex) \end{tabular}   & $6$                                                         & $20$    & $100$     & $-$      & $0.881$  \\ \hline

\begin{tabular}[c]{@{}c@{}}Algorithm in \cite{KNZ16} \\ $\{\rho_p,\rho_c\} \rightarrow$ variable \end{tabular}   & $6$                                                         & $23.89$    & $73.87$     & $-$      & $0.870$  \\ \hline

Proposed method                                                               & $6$                                                         & $16.72$    & $127.1$     & $63.68$     & $0.814$   
\end{tabular}
\end{table}

Figure.~\ref{fig:ex3_1} shows the step response of $S(s)$ (disturbance response) for all seven models using the convex optimization algorithm, while Figure.~\ref{fig:ex3_2} shows the step response of $S(s)$ using the proposed method. It can be observed that the proposed method produces shorter settling times and reduced overshoot. 
\begin{figure}
\centering
\includegraphics[width=\columnwidth]{../pics/step_multi_convex.eps}
\caption{Step response of $S(s)$ for all seven models using the convex optimization algorithm in \cite{KNZ16}.}
\label{fig:ex3_1}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=\columnwidth]{../pics/step_multi_optimal.eps}
\caption{Closed-loop step responses with the PID controller parameters asserted in Table.~2 (with $\tau = \tau_n$). Response associated with the proposed PSO algorithm (solid-blue); response associated with the convex optimization algorithm (solid-green); response associated with the robust stability method in \cite{EW09} (solid-red).}
\label{fig:ex3_2}
\end{figure}

\begin{remark*}
The $\mu$-synthesis approach by \texttt{MATLAB} introduces some conservatism in determining the optimal controller. Additionally, with the $\mu$-synthesis approach, the plant $G_4(s)$ was approximated with a first-order Pade function, since pure delay's cannot be used for synthesis. In the proposed approach, the true delay function can be considered in the design while eliminating the conservatism associated with modeling the multi-model uncertainties. 
\end{remark*}

\section{Conclusion} \label{sec:conclusion}
Robust performance can be accomplished by considering the $\mathcal{H}_{\infty}$ control problem. By presetting a frequency grid, an optimization problem can be formulated to minimize the upper-bound of the robust performance condition and solve a finite amount of constraints in the frequency-domain. In this paper, a Non-Death-Penalty approach has been implemented to solve an unconstrained $\mathcal{H}_{\infty}$ problem; the solution to this problem was obtained by realizing a PSO algorithm. From the examples considered in this paper, it is evident that the solutions obtained from the PSO algorithm generate favorable closed-loop responses (with respect to the other methods considered in this paper). In terms of performance, the convex optimization algorithm produces a solution that is comparable to that of the PSO. From the simulation examples, it can be deduced that the solution obtained from the convex optimization algorithm is a good approximation to the solution obtained from the original problem. For further research, it will be desired to investigate how the solution obtained from the PSO algorithm with the $\epsilon$-level comparisons correlates with the solutions obtained in this work.

\bibliography{linear}

\end{document}

### 2017-02-11 Papers/PUBLISHED - MIMO Smith Predictor (book chapter)/Karimi.tex
adding files to git (11/2/2017)

\documentclass[default]{svmult}

% choose options for [] as required from the list
% in the Reference Guide

\usepackage{mathptmx}       % selects Times Roman as basic font
\usepackage{helvet}         % selects Helvetica as sans-serif font
\usepackage{courier}        % selects Courier as typewriter font
\usepackage{type1cm}        % activate if the above 3 fonts are
                            % not available on your system
%
\usepackage{makeidx}         % allows index generation
\usepackage{graphicx}        % standard LaTeX graphics tool
                             % when including figure files
\usepackage{multicol}        % used for the two-column index
\usepackage[bottom]{footmisc}% places footnotes at page bottom
\usepackage{times}

\usepackage{amsmath}%
\usepackage{amsfonts}%
\usepackage{amssymb}%
\usepackage{color}
\usepackage{graphicx,psfrag}
\usepackage{float}

% see the list of further useful packages
% in the Reference Guide

\makeindex             % used for the subject index
                       % please use the style svind.ist with
                       % your makeindex program

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\title*{Robust Smith Predictor Design for Time-Delayed Systems with ${H_{\infty}}$ Performance}
% Use \titlerunning{Short Title} for an abbreviated version of
% your contribution title if the original one is too long
\author{Vinicius de Oliveira, Achille Nicoletti, Alireza Karimi}
% Use \authorrunning{Short Title} for an abbreviated version of
% your contribution title if the original one is too long
\institute{Vinicius de Oliveira \at Department of Chemical Engineering, Norwegian University of Science and Technology, Norway.
\and Achille Nicoletti \at Automatic Control Laboratory, Ecole Polytechnique F\'ed\'erale de Lausanne (EPFL), Switzerland. \email{achille.nicoletti@epfl.ch}
\and Alireza Karimi (Corresponding author) \at Automatic Control Laboratory, Ecole Polytechnique F\'ed\'erale de Lausanne (EPFL), Switzerland. \email{alireza.karimi@epfl.ch}}
%
% Use the package "url.sty" to avoid
% problems with special characters
% used in your e-mail or web address
%
\maketitle

\abstract*{A new method for robust fixed-order $H_{\infty}$ controller design for uncertain time-delay systems is presented. It is shown that the $H_{\infty}$ robust performance condition can be represented by a set of convex constraints with respect to the parameters of a linearly parameterized primary controller in the Smith predictor structure. Therefore, the parameters of the primary controller can be obtained by convex optimization. The proposed method can be applied to stable single-input-single-output (SISO) and multiple-input-multiple-output (MIMO) models with uncertain dead-time and with multimodel and frequency-dependent uncertainty. It is also shown that how the design method can be extended to unstable SISO models. The design of robust gain-scheduled dead-time compensators is also investigated. The performance of the method is illustrated for both SISO and MIMO systems by simulation examples.}

\abstract{A new method for robust fixed-order $H_{\infty}$ controller design for uncertain time-delay systems is presented. It is shown that the $H_{\infty}$ robust performance condition can be represented by a set of convex constraints with respect to the parameters of a linearly parameterized primary controller in the Smith predictor structure. Therefore, the parameters of the primary controller can be obtained by convex optimization. The proposed method can be applied to stable SISO and MIMO models with uncertain dead-time and with multimodel and frequency-dependent uncertainty. It is also shown that how the design method can be extended to unstable SISO models. The design of robust gain-scheduled dead-time compensators is also investigated. The performance of the method is illustrated for both SISO and MIMO systems by simulation examples.}

\section{Introduction}
\label{sec:1}
Most industrial processes present dead time in their dynamics. Generally, dead times are caused by the time needed to transport energy, mass or information, but they also can be caused by processing time or by accumulation of time lags in a sequence of simple dynamic systems interconnected in series (\cite{NC07}).

The presence of dead times in the control loops has two main consequences: it greatly complicates the analysis and the design of feedback controllers  and it makes satisfactory control performance more difficult to achieve (\cite{Pal96}). Dead-time compensators can be used to improve the closed-loop performance of classical controllers (PI or PID controllers) for processes with delay. The Smith Predictor (SP) (See Fig.\ref{fig:dtc}), proposed in the late 1950s by \cite{Smi57}, was the first dead-time compensation structure used to improve the performance of the classical
controllers and became the most known and used algorithm to compensate dead time in the industry.

Although the SP offers potential improvement of the closed-loop performance of process with large dead-time, it requires a good model since small modeling errors can lead to very poor performance. %In fact, even if the SP is nominally stabilizing, the closed-loop system may become unstable for infinitesimal change in the process dynamics (\cite{Pal80}).
For this reason, research efforts have been focused on robustness issues of the SP. A tuning method for models with one uncertain parameter is proposed by \cite{Bro79}.
Easy tuning rules for SP in the presence of dead-time uncertainty is addressed in \cite{SS93} and a guideline for selection the closed-loop bandwidth based on the dead-time uncertainty bound is proposed.
In \cite{PB94}, a robust tuning rule is developed  which considers the modeling error in the dead time.  Robust PID tuning for SP considering model uncertainty is proposed by \cite{LLSL99}. In particular, first and second order plus dead-time systems which may contain uncertainty in multiple parameters of the model are considered. In \cite{MZ00}, tuning guidelines are presented for setpoint tracking considering model mismatches in the dead-time.

Many researchers are interested in the optimal control of dead-time
systems, especially $H_{\infty}$ control, i.e., to find a controller to
internally stabilize the system and to minimize the $H_{\infty}$-norm of an associated transfer
function. Many relevant results have been presented in this framework using 
modified versions of the SP. See, for instance, \cite{Mir03}, \cite{MZ00} and \cite{Zho03a}. Recently, the SISO SP has been extended and generalized for MIMO systems. In \cite{SBP09}, a structured uncertainty approach was implemented for SP's with diagonal delay matrices. This method, however, does not consider general and distinct time delays for each element of the plant transfer matrix. A diagonal $H_2$ optimal controller for non-square plants is designed by factorization methods in \cite{ZL06}. In \cite{NC00}, a generalized predictive control (GPC) method is implemented on MIMO SP systems with multiple delays.  
Nonetheless, these control techniques are quite complex and their implementation can be involved.

%Nonetheless, as pointed out by \cite{Zho03b}, these controllers are too involved and the predictor always includes additional unstable hidden modes even for stable plants. As the author argues, these hidden modes are not safe as they tend to destabilize the system when implemented. Therefore, the practical significance of these results are limited.

This paper presents a new method to design fixed-order SP controllers that considers uncertainty simultaneously in the dead-time and in the rational part of the model.  The performance specification, like the standard $H_{\infty}$ control problem, is a constraint on the infinity norm of the weighted sensitivity function and is represented by a set of convex constraints in the Nyquist diagram. The extension to MIMO systems will be based on the idea presented in \cite{GKL10b} for designing decoupling MIMO controllers. In \cite{GKL10b}, a convex optimization approach was implemented to design a linearly parameterized controller for a MIMO system. In this paper, this concept will be extended to MIMO SP's with process plants that possess uncertain time delays. 
%A line search on the upper bound $\gamma$ of the infinity norm of the weighted sensitivity function can be used in association to a convex feasibility problem to determine the primary controller parameters. The proposed method can be used for PID primary controllers, which are of great practical interest, as well as for higher order linearly parametrized controllers in discrete or continuous time.

%It is important to point out that a method to design fixed-order controllers for standard control loops based on convex constraints in the Nyquist diagram has been firstly proposed in \cite{KG10}. Although, this method can be used for time-delay systems, it does not explore the structure of Smith Predictor to compensate for time delay. This may lead to very high order controller or poor performance. This paper uses the same framework to design Smith Predictor compensators for time-delay systems.

This paper is organized as follows: In Section \ref{sec:2} the class of models, controllers and the control objectives for SISO systems are
defined. Section \ref{sec:3} will extend the class of controllers and control objectives to MIMO systems. Sections \ref{sec:2} and \ref{sec:3} will also discuss the control design methodology and stability conditions for the SISO and MIMO Smith predictor configurations, respectively. This methodology is based on the convex constraints in the Nyquist diagram. In Section \ref{sec:4} the results are extended to unstable time-delay SISO systems. Gain-scheduled SP is designed for time-delay systems in Section \ref{sec:5}. Each section will end with an illustrative example. Finally the concluding remarks are given.

\section{SISO Problem Formulation}
\label{sec:2}
\subsection{Class of models}
Consider the class of stable time-delay LTI-SISO systems with bounded infinity norm. It is assumed that the plant model can be represented by:
\begin{equation}\label{model}
P(s)=G(s)e^{-\tau s}
\end{equation}
where the time delay $\tau$  is unknown but belongs to a finite set $\{\tau_1, \tau_2, \ldots, \tau_q \}$ and the dead-time free part of the model has unstructured multiplicative uncertainty described as:
\begin{equation}\label{uncertainty}
G(s)=G_n(s)[1+\Delta(s) W_2(s)]
\end{equation}
where $W_2(s)$ is a known stable uncertainty filter, $G_n(s)$ the nominal dead-time free model and  $\Delta(s)$  an unknown stable transfer function with $\| \Delta\|_{\infty}<1$.  
Therefore, we can assume that $P(s)$ belongs to a set $\mathbb{P}$ of $q$ models given by:
\begin{equation}
\mathbb{P}\stackrel{\triangle}{=}\{ P_i(s)[1+\Delta(s) W_2(s)]; \: i=1,\dots, q \}
\label{setP}
\end{equation}
where $P_i(s)=G_n(s)e^{-\tau_i s}$.
%We can also define the set of nominal models as:
%\begin{equation}
%\mathcal{P}_n\stackrel{\triangle}{=}\{ P_i(s)=G_n(s)e^{-\tau_i s}; \: i=1,\dots, q \}
%\label{setPn}
%\end{equation}

\subsection{Class of controllers} \label{sec:siso_cls}

The SP control structure shown in Fig.\ref{fig:dtc} is considered. The nominal model $P_0(s)=G_n(s)e^{-\tau_n s}$ with $\tau_n \in [\tau_1, \tau_q ]$ is used for the implementation of the controller.
\begin{figure}[h]
\centering
\psfrag{rr}{\small $r$}
\psfrag{cc}{\small $C(s)$}
\psfrag{uu}{\small $u$}
\psfrag{pp}{\small $P(s)$}
\psfrag{gn}{\small $G_n(s)$}
\psfrag{ex}{\small $e^{-\tau_n s}$}
\psfrag{yp}{\small $y_p$}
\psfrag{yy}{\small $y$}
\psfrag{pl}{\small $+$}
\psfrag{mi}{\small $-$}
\psfrag{dis}{\small $d$}
\includegraphics[width=0.8\columnwidth]{fig/SISO_block.eps}
\caption{Smith Predictor}
\label{fig:dtc}
\end{figure}%

The primary controller $C(s)$ is linearly parametrized by
\begin{equation}\label{eq:controller}
C(s)= \rho^T \phi(s)
\end{equation}
 where 
$
 \rho^T=[\rho_1,\rho_2, \ldots, \rho_{n_c}] 
$
is an $n_c$ dimensional vector of the controller parameters and $\phi^T(s)=[\phi_1(s),\phi_2(s), \ldots, \phi_{n_c}(s)]$ is a vector of basis functions with $\phi_i(s)$ transfer functions with no RHP poles. For instance, a PID controller could be linearly parametrized by
$$\rho^T=[K_p,K_i, K_d] \quad , \quad  \phi^T(s)=[1, \frac{1}{s},\frac{s}{1+T_fs}] $$

\subsection{Design specifications}

As stated in \cite{DFT92}, the sensitivity and complementary functions of a system are invoked to test the robust performance and robust stability conditions. From Fig. \ref{fig:dtc}, the sensitivity functions for the nominal models $P_i(s)$ can be determined by obtaining the transfer function from the output disturbance $d$ to the system output $y$:
\begin{equation}\label{eq:sensitivity}
S_i(s)=\frac{1+C(s)H(s)}{1+C(s)[H(s)+P_i(s)]}
\end{equation}
where $H(s)=G_n(s)-P_0(s)=G_n(s)(1-e^{-\tau_n s})$. The complementary sensitivity functions for the nominal models will be the transfer function from the reference input $r$ to $y$ (which is also equal to $1-S_i(s)$):
\begin{equation}\label{eq:sensitivity_comple}
T_i(s)=\frac{C(s)P_i(s)}{1+C(s)[H(s)+P_i(s)]}
\end{equation}
A standard robust control problem is to design a controller that satisfies $\| W_1S_i\|_{\infty}<1$ for a set of models where $W_1(s)$ is the performance weighting filter. If the model is described by unstructured multiplicative uncertainty, the necessary and sufficient condition for robust performance is given by \cite{DFT92}:
\begin{equation}\label{eq:robust_performance}
\|  |W_1S_i| + |W_2T_i| \|_{\infty}<1  \quad \mbox{for} \quad i=1,\ldots, q
\end{equation}
The goal of the proposed approach is to design the primary controller $C(s)$ in the SP structure to guarantee robust performance of the closed-loop system.

\subsection{Proposed method} \label{sec:siso_pro}

The robust performance condition (\ref{eq:robust_performance}) can be written as: 
\begin{equation}\label{eq:robust_performance2}
\left| W_{1}(j\omega)S_i(j\omega)| + |W_{2}(j\omega)T_i(j\omega) \right|<1,\quad \forall \omega
\end{equation}
for $i=1,\ldots, q$. Let $L_i(s,\rho)$ be defined as the open-loop transfer function of the SISO SP. From Fig. \ref{fig:dtc}, the transfer function from the input of $C(s)$ to $y_p$ will represent this open-loop transfer function:
\begin{equation}
L_i(s,\rho)=C(s,\rho)(H(s)+P_i(s))
\end{equation} 
The dependency on frequency $\omega$ and $s$ will be omitted for brevity but the dependency on the controller parameter $\rho$ will be highlighted.

The main result of this section is given in the following theorem.
\begin{theorem}\label{th:siso}
Consider the  set of models $\mathbb{P}$  in (\ref{setP}) with multiplicative uncertainty filter $W_{2}(j\omega)$, then the linearly parametrized controller in (\ref{eq:controller}) in the SP structure guarantees closed-loop stability and satisfy the following robust performance condition:
\begin{equation} \label{RobPer}
\| |W_{1}S_i| + |W_{2}T_i|  \|_{\infty}<1\quad \mbox{for }i=1,\ldots,q  
\end{equation}
if
\begin{multline} \label{eq:cond_theorem1}
\left[\big|W_{1}(j\omega)[1+C(j\omega,\rho)H(j\omega)] \big | \right.+ 
\left.\big | W_{2}(j\omega)C(j\omega,\rho)P_i(j\omega) \big | \right] |1+L_d(j\omega)|  \\
- Re\{[1+L^{\ast}_d(j\omega)][1+L_i(j\omega,\rho)]\}<0 \\  \forall \omega \quad \mbox{ for }i=1,\ldots,q
\end{multline}
where $L_d(j\omega)$ is a strictly proper transfer function which does not encircle the critical point and $L_d^*(j\omega)$ is its complex conjugate. 
\end{theorem}

\begin{proof} 
\smartqed
Since the real part of a complex number is less than or equal to its magnitude, we have
\begin{equation} \label{UpperBound}
Re\{[1+L^{\ast}_d][1+L_{i}(\rho)]\}\leq |[1+L^{\ast}_d][1+L_{i}(\rho)]|
\end{equation}
Then, using (\ref{eq:cond_theorem1}) and the fact that $|1+L_d|=|1+L^*_d|$, one obtains 				
\begin{eqnarray}
\big|W_{1}(1+C(\rho)H)\big| + \big | W_{2}C(\rho)P_i \big| - 
|1+L_i(\rho)|<0 \nonumber\\
 \forall \omega \: \mbox{ for }i=1,\ldots,q 
\end{eqnarray}
Using $L_i(\rho)=C(\rho)(H+P_i)$ we have 
\begin{eqnarray}\label{eq:siso_rob}
\frac{|W_{1}(1+C(\rho)H)| + |W_{2}C(\rho)P_i | }{|1+C(\rho)(H+P_i)|} <1 \nonumber\\
 \forall \omega \: \mbox{ for }i=1,\ldots,q  
\end{eqnarray}
that leads directly to (\ref{RobPer}).
To prove that all  closed-loop transfer functions are stable, consider (\ref{eq:cond_theorem1})  which gives:
\begin{equation}
Re\{[1+L^{\ast}_d(j\omega)][1+L_i(j\omega,\rho)]\}>0 \quad \forall \omega
\end{equation}
or, alternatively, 
\begin{equation}
wno\{[1+L^{\ast}_d(j\omega)][1+L_i(j\omega,\rho)] \}=0
\end{equation}
where $wno$ stands for winding number around the origin. Since both $L^{\ast}_d(j\omega)$ and $L_i(j\omega,\rho)$ are constant or zero for the semi-circle with infinity radius of the Nyquist contour 
the $wno$ depends only on the variation of $s$ in the imaginary axis. Thus,
\begin{equation}
wno\{[1+L_d(j\omega)]\}  =wno\{[1+L_i(j\omega,\rho)] \}
\end{equation}
Since $L_d(j\omega)$ satisfies the Nyquist stability criterion $L_i(j\omega,\rho)$ will do so and 
all zeros of $1+L_i(j\omega,\rho)$ will be in the left-hand side of the complex plan. Since the zeros of
$1+L_i(j\omega,\rho)$ are the closed-loop poles, the system will be internally stable.
\qed
\end{proof}

\subsection{Primary controller design}
The problem of minimizing the upper bound $\gamma$ of the infinity norm of the weighted sensitivity function is considered. Therefore, the primary controller should be obtained from the following optimization problem: 
\begin{eqnarray}\label{eq:min_hinf}
\min_{\rho} \gamma \nonumber \\\mbox{Subject to:}\\ \nonumber
 \|  |W_1S_i| +& |W_2T_i| \|_{\infty}<\gamma \quad \mbox{for } i=1,\dots,q\nonumber
\end{eqnarray}
This optimization can be convexified using Theorem \ref{th:siso} and solved by an iterative bisection algorithm. At each iteration $j$, $\gamma_j$ is fixed and $W_1$ and $W_2$ are replaced by $W_1/\gamma_j$ and $W_2/\gamma_j$. Then, a feasibility problem is solved under the convex constraints (\ref{eq:cond_theorem1}). If the problem is feasible, $\gamma_{j+1}$ is chosen smaller than $\gamma_{j}$. Otherwise $\gamma_{j+1}$ is increased.

Notice that the condition (\ref{eq:cond_theorem1}) is defined for every frequency $\omega$ leading to infinite number of constraints. In practice, a frequency  grid can be used  with a sufficiently large number of frequency points $N$ (a finer grid can be used around the crossover frequency). The effect of gridding on the stability and performance of the closed loop system has been studied in \cite{GKL10a}.

{\bf Remark I:} 
The constraint in (\ref{eq:cond_theorem1}) is an inner convex approximation of the non convex constraint in (\ref{RobPer}) or 
(\ref{eq:robust_performance2}). The quality of this approximation depends on the choice of $L_d$.  It can be shown that better approximation is achieved if $L_d$ is chosen such that its frequency response is close to that of $L_i(\rho)$ (\cite{KG10}).

%Note that $L_i(\rho)$ can be written as:
%\begin{equation}\label{eq:new_ld}
%L_i(\rho)=C(\rho)G_n+C(\rho)(P_i-P_0)\end{equation}Therefore, If  $\tau_i$ is close to $\tau_n$ or the model mismatch $P_i-P_0$ is small, $L_{d}$ can be seen as the desired open loop transfer function of the system without dead-time, i.e.,  $C(\rho)G_n$.  For systems with large uncertainty in the time delay, different $L_d$ can be considered for each model $P_i$. Since it is desired to obtain an open-loop transfer function which is ideally $C(\rho)G_n$, we can substitute $C(\rho)\approx L_d/G_n$ in (\ref{eq:new_ld}). In this case, $L_{d_i}$ can be computed as follows:\begin{equation}{L}_{d_i}=L_{d}+\frac{L_d}{G_n}(P_i-P_0)\end{equation}To ensure stability, for stable plant models, the number of counterclockwise encirclements of $L_d$ around the critical point should be equal to zero. An iterative algorithm can be used to improve the results. In  this algorithm $L_d$ in the $(k+1)$-th iteration is computed using the controller of the last iteration  $C_{k}(\rho)$ and (\ref{eq:new_ld}):\begin{equation}{L}_{d_i}=C_{k}(\rho)G_n+C_k(\rho)(P_i-P_0)\end{equation}

%\textbf{Remark II:}
%It is also possible to handle multimodel uncertainty in the proposed approach. Consider that the plant  belongs to a set of stable models $\mathcal{P}$ where:
%\begin{equation}
%\mathcal{P} = \{ G_1e^{-\tau_1 s}, G_2e^{-\tau_2 s},\ldots, G_me^{-\tau_m s}  \}
%\end{equation}
%It is assumed that nominal model $P_0=G_ne^{-\tau_n s}$ representing the set is available. In this case, the robust performance condition is
%\begin{equation}
% \|  W_{1i}S_i \|_{\infty}<\gamma \quad \mbox{for } i=1,\dots,m
%\end{equation}
%which can be approximated by the following convex constraints:
%\begin{multline} \label{eq:cond_multi}
%|W_{1i}(j\omega_k)[1+C(j\omega_k,\rho)H(j\omega_k)] [1+L_{d_i}(j\omega_k)]|- \\
%Re\{[1+L^{\ast}_{d_i}(j\omega_k)][1+L_i(j\omega_k,\rho)]\}<0 \\
%k=1,\ldots,N; m=1,\ldots, m 
%\end{multline}
%Note that different performance specification can be defined for each model in the set (by different $W_{1i}$ and $L_{d_i}$).

\subparagraph{Example 1}
Consider the process described by (\ref{model}) with multiplicative uncertainty as in (\ref{uncertainty}) with 
\begin{equation}
G_n(s)=\frac{1}{(5s+1)(10s+1)}
\end{equation}
and 
\begin{equation}
 W_2(s)=\frac{ -s^2 - 2 s}{s^2 + 2 s + 1}
\end{equation}
The unknown time delay $\tau$  belongs to the set $\{4.5, 5, 5.5\}$.
The nominal model used in the SP structure is chosen as $P_0(s)=G_n(s)e^{-5s}$.
%By griding the range of allowable dead-times a set $ \mathcal{P}=\{P_i(s),\: i=1,\ldots,q\}$ of models is generated where:
%\begin{equation}
%P_i(s)=G_n(s)e^{-\tau_is}, \; i=1,\ldots,q
%\end{equation}
%In this example $q=3$ is chosen. 
The performance specification is defined by the following filter:
 \begin{equation}
 W_1(s)=\frac{2}{(30s+1)^2}
\end{equation}
A PID primary controller with $T_f=0.01$ that minimizes $\| |W_1S_i|+|W_2T_i|  \|_{\infty}<\gamma$ for $i=1,2,3$ should be computed.

Since the controller has an integrator, $L_d$ is chosen as $L_d(s)=\omega_c/s$ where $\omega_c=0.1$ rad/s which is 20\% higher than open loop bandwidth. Then, the optimization problem (\ref{eq:min_hinf}) is solved considering $N=100$ equally spaced frequency points between $10^{-3}$ and $10^3$ rad/s. The resulting primary controller is:
\begin{equation}
C(s)=\frac{12.3 s^2 + 3.28 s + 0.2201}{0.01 s^2 + s}
\end{equation}
and leads to $\gamma=0.313$.
This controller is compared to that proposed in \cite{Kay01}. Kaya's controllers performs better than other controllers presented in the literature (\cite{PB94}, \cite{Hag92} and \cite{HWC95}).
Fig. \ref{fig:example1} depicts 
the performance of both controller on unitary step setpoint change considering the time-delay $\tau=4.5s$, $\tau=5.0s$ and $\tau=5.5s$. As it can be seen, both controller performed well, however, the proposed controller achieves faster response. % (see Table \ref{table:performance}).
\begin{figure}[H]
\centering
\includegraphics[scale=0.31]{fig/example1_final_paper}
\caption{Example 1: Blue solid line: proposed;  black dot-dashed line: ref \cite{Kay01} }
\label{fig:example1}
\end{figure}%
\section{MIMO Problem Formulation}
\label{sec:3}
In this section, the SP for MIMO systems with generalized time delays will be investigated . An example of how to design a linearly parameterized MIMO controller for such a system will be presented at the end of this section. For notation purposes, bold face characters will represent transfer function matrices.
\subsection{Class of models}
Let $n_o$ and $n_i$ represent the number of outputs and the number of inputs of a system, respectively. The set of all LTI-MIMO strictly proper uncertain models with uncertain time delays can be defined as follows: 
\begin{equation}\label{eq:setpmimo}
\mathcal{P}=\{\vec{P}_c(s)[\vec{I}+\Delta \vec{W}_2]; c=1,\ldots,m\}
\end{equation}
where each element in $\vec{P}_c(s)$ possesses a time delay that can vary over a range of specified values, and $\vec{W}_2$ is a matrix that represents the multiplicative input uncertainty of the system. For simplicity, one model from the set $\mathcal{P}$ will be investigated, and the subscript $c$ will be omitted. The uncertain $n_o \times n_i$ time delayed plant has the following form:
\begin{equation}\label{eq:mimo_p}
\vec{P}(s)=
\begin{bmatrix}
G_{11}(s)e^{-\tau_{11} s} & \cdots & G_{1n_{i}}(s)e^{-\tau_{1n_{i}} s} \\ \vdots & \ddots & \vdots \\ G_{n_{o}1}(s)e^{-\tau_{n_{o}1} s} & \cdots & G_{n_{o}n_{i}}(s)e^{-\tau_{n_{o}n_{i}} s}
\end{bmatrix}
\end{equation}
where $G_{qp}(s)$ is a strictly proper delay-free transfer function, and $\tau_{qp}$ is the uncertain time-delay of the process for $p=1,\ldots, n_i$ and $q=1,\ldots, n_o$.

\subsection{Class of controllers}
As stated in \cite{GKL10b}, an $n_i \times n_o$ matrix can be formed to represent the controller $\vec{K}(s,\rho)$. The elements of $\vec{K}(s,\rho)$ will possess linearly parameterized elements $K_{pq}(s)=\rho^T_{pq}\phi_{pq}(s)$, where $\rho^T_{pq}$ is a vector of parameters, and $\phi_{pq}(s)$ is a vector of stable transfer functions chosen from a set of orthogonal basis functions. The non-diagonal elements of $\vec{K}(s,\rho)$ strive to decouple the system, while the diagonal elements aim to control the single-loop subsystems. As with the SISO case, the main purpose of parameterizing the controller in this manner is due to the fact that the components of the open loop transfer function can be written as a linear function of the control parameters $\rho$,
\begin{equation}
\rho=[\rho_{11},\ldots,\rho_{1_{n_{i}}},\ldots,\rho_{n_{o}1},\ldots,\rho_{n_{o}n_{i}}]
\end{equation}
\subsection{Design specifications}\label{sec:mimo_des}
Fig. \ref{fig:mimo_block} displays the SP for the MIMO case,
%\footnote{Note that the block diagram for the SP has been reconfigured for the MIMO case. In this manner, the uncertain plant is generalized where each element in (\ref{eq:mimo_p}) can posses a distinct and unique range of time delays.}. 
where $\vec{G}_n(s)$ is an $n_o \times n_i$ nominal delay-free transfer function matrix with elements $G_{qp}(s)$, and $\vec{P}_n(s)$ is an $n_o \times n_i$ nominal transfer function matrix which includes the nominal values of the time delays, which is comprised of elements $G_{qp}(s)e^{-\zeta_{qp}}$ (where $\zeta_{qp}$ represents the $qp$-th nominal time delay). Both $\vec{Y}(s)$ and $\vec{X}(s)$ are $n_o \times 1$ column vectors that possess elements $y_q(s)$ and $x_q(s)$, respectively. The transfer function from the inputs of $\vec{C}(s)$ to $\vec{Y}_p(s)$ will represent the open-loop transfer function,
\begin{equation}\label{eq:oltfmimo}
\vec{L}(s)=[\vec{P}(s)+\vec{H}(s)]\vec{C}(s)
\end{equation}
where $\vec{H}(s)=\vec{G}_n(s)-\vec{P}_n(s)$. Notice that if $\vec{P}(s)=\vec{P}_n(s)$, then $\vec{L}(s)=\vec{G}_n(s)\vec{C}(s)$. Since the class of controllers to be designed for this system are linearly parameterized, the elements of the controller $\vec{C}(s)$ will actually be a function of the controller parameters $\rho$. Therefore, $\vec{C}(s)$ will be represented as $\vec{C}(s,\rho)$.
\begin{figure}
\centering
\psfrag{cc}{$\vec{C}(s)$}
\psfrag{yy}{$\vec{Y}(s)$}
\psfrag{yp}{$\vec{Y}_p(s)$}
\psfrag{pp}{$\vec{P}(s)$}
\psfrag{pl}{$+$}
\psfrag{mi}{$-$}
\psfrag{gn}{$\vec{G}_n(s)$}
\psfrag{gnd}{$\vec{P}_n(s)$}
\psfrag{dd}{\hspace{-0.2cm}$\vec{D}(s)$}
\psfrag{uu}{$\vec{U}(s)$}
\psfrag{rr}{\hspace{-0.1cm} $\vec{X}(s)$}
\includegraphics[scale=0.6]{fig/mimo_b3.eps}
\caption{MIMO representation of the Smith Predictor}
\label{fig:mimo_block}
\end{figure}
%For MIMO systems, the robust stability conditions are dependent on the type of perturbed model. For example, the robust conditions for MIMO systems with input multiplicative perturbations will differ for systems with output multiplicative perturbations. For a system with multiple unstructured uncertainties, the structured singular value method is typically used to prove the robust stability and robust performance of a system \cite{ZhoDoy}.

The transfer function from the output disturbance $\vec{D}(s)$ to $\vec{Y}(s)$ is the output sensitivity function $\vec{S}(s,\rho)$, while the transfer function from $\vec{X}(s)$ to $\vec{Y}(s)$ is the complementary sensitivity function $\vec{T}(s,\rho)$:
\begin{align}\label{eq:sens_mimo}
&\vec{S}(s,\rho)=[\vec{I}+\vec{H}(s)\vec{C}(s,\rho)]\vec{Z}^{-1}(s,\rho) \nonumber\\ &\vec{T}(s,\rho)=\vec{P}(s) \vec{C}(s,\rho) \vec{Z}^{-1}(s,\rho)
\end{align}
where $\vec{Z}(s,\rho)=[\vec{I}+\vec{L}(s,\rho)]$. As with the SISO case, the goal here is to determine the controller $\vec{C}(s,\rho)$ that will guarantee the robust performance and robust stability of the closed-loop SP system.

%Note that $\vec{S}(s,\rho)$ and $\vec{T}(s,\rho)$ will in general contain non diagonal elements, and will not be diagonally dominant. Moreover, the eigenvalues of the open-loop transfer function (\ref{eq:oltfmimo}) are non convex functions of the linear control parameters $\rho$ \cite{GKL10b}.

\subsection{Proposed method}
Suppose that $\vec{S}(s,\rho)$ and $\vec{T}(s,\rho)$ are diagonal transfer matrices (the closed-loop system is fully decoupled). Then the MIMO sensitivity and complementary functions can essentially be treated as functions containing independent SISO subsystems. Let $\vec{W}_1(s)$ be a diagonal filter with diagonal elements $W_{1_{q}}$ and  a diagonal filter $\vec{W}_2(s)$ with diagonal elements $W_{2_{q}}$ representing, respectively, the nominal performance and multiplicative uncertainty for the SISO subsystem. Therefore, the robust criterion that was proved for the SISO case in section (\ref{sec:siso_pro}) will be satisfied for each SISO subsystem of the decoupled MIMO system. Thus it is judicious to express the robust criterion for the decoupled system as follows:
\begin{align} \label{eq:mimo_hinf}
&\| |W_{1_{q}}S_{qq}|+ |W_{2_{q}}T_{qq}| \|_{\infty} < 1 \nonumber\\
&\mbox{for }q=1,\ldots,n_o
\end{align}
where $S_{qq}$ and $T_{qq}$ are the $q$-th diagonal elements of $\vec{S}(s,\rho)$ and $\vec{T}(s,\rho)$, respectively.

%In order to decouple the system, it is desired to minimize the off-diagonal elements of the open-loop transfer function. 
%However, decoupling the MIMO system will not necessarily generate the desired single-loop responses, since it is the diagonal elements of $\vec{L}(s,\rho)$ that represent the single-loop responses of the system. 
The objective is to effectuate decoupling while simultaneously optimize the diagonal elements to achieve the desired single-loop performance. The proposed method will be to define a diagonal open-loop transfer function matrix $\vec{L}_D(s)$, where the diagonal elements satisfy the desired single open-loop response. Therefore, by minimizing the objective function $\| \vec{L}(s,\rho)-\vec{L}_D(s) \|_{2}^{2}$, a controller can be designed to simultaneously  minimize the magnitudes of the off-diagonal elements of $\vec{L}(s,\rho)$ and drive the diagonal elements to be approximately equal to $L_{D_{q}}(s)$ (where $L_{D_{q}}(s)$ is the $q$-th diagonal element in $\vec{L}_D(s)$).

However, the resulting controller will stabilize the closed-loop system only if it is fully decoupled. In practice, with a finite order controller, it is not always possible to make the off-diagonal elements of  $\vec{L}(j\omega,\rho)$ equal to zero. In this case, the generalized Nyquist stability criterion should be used to guarantee the stability of the MIMO system. According to this theorem, the eigenvalues of the open-loop transfer function (\ref{eq:oltfmimo}) should not encircle the critical point. However, these eigenvalues are non-convex functions of the linear control parameters, which complicates the design process. A possible solution to this problem is to implement the Gershgorin band theorem in order to approximate the eigenvalues of $\vec{L}(j\omega,\rho)$. The Gershgorin bands represented by disks centered at the diagonal elements of a matrix that include the eigenvalues. For the open-loop transfer matrix $\vec{L}(j\omega,\rho)$, the radius of these disks are computed by: 
\begin{equation}
r_{q}(\omega_k,\rho)=\sum_{p=1,p\neq q}^{n_o} |L_{qp}(j\omega_k,\rho)| 
\end{equation}
which is convex with respect to the control parameter $\rho$. Therefore, the closed-loop stability of the MIMO system is guaranteed if these disks do not encircle the critical point. This condition can be approximated with a convex constraint as it is shown in \cite{GKL10b}.

\subsection{Primary controller design}
In designing the controller $\vec{C}(s,\rho)$ for the MIMO SP, one must consider all of the possible combinations of the uncertain delay parameters $\tau_{qp}$.  Suppose that the cardinality of  $\tau_{qp}$ is $\beta_{qp}$. Then the total number of possible combinations that must be considered in the design of the controller is,
\begin{align}
&\hspace{1cm} m=\prod \beta_{qp} \nonumber \\
&\forall \;\; q=1,\ldots,n_o;\;p=1,\ldots,n_i
\end{align}
Therefore,  one can define the following optimization problem for the multimodel system:

\begin{align}\label{eq:long_con}
&\hspace{3cm} \min_\rho \sum_{c=1}^{m} \sum_{k=1}^N \|\vec{L}_c(j\omega_k,\rho)-\vec{L}_{D_{c}}(j\omega_k)\|_F \nonumber\\
&\mbox{ Subject to: } \nonumber\\
&|r_{q_{c}}(j\omega_k,\rho)[1+L_{D_{q_{c}}}(j\omega_k)]|-R_e\{[1+L^*_{D_{q_{c}}}(j\omega_k)][1+L_{qq_{c}}(j\omega_k,\rho)]\}<0 \nonumber\\
&\{|W_{1_{q_{c}}}(j\omega_k)[1+M_{qq_{c}}(j\omega_k,\rho)]|+|W_{2_{q_{c}}}(j\omega_k)N_{qq_{c}}(j\omega_k,\rho)|\}|1+L_{D_{q_{c}}}(j\omega_k)| \nonumber\\
&-R_e\{[1+L^*_{D_{q_{c}}}(j\omega_k)][1+L_{qq_{c}}(j\omega_k,\rho)]\}<0 \nonumber\\
&\mbox{for } k=1,\ldots,N;\;  q=1,\ldots,n_o; \; c=1,\ldots,m
\end{align}
where 
\begin{align*}
&M_{qq_{c}}(j\omega_k,\rho)=\sum_{z=1}^{n_o} G_{qz_{c}}(j\omega_k)(1-e^{-j\omega_k \zeta_{qz_{c}}})C_{zq_{c}}(j\omega_k,\rho) \\
&N_{qq_{c}}(j\omega_k,\rho)=\sum_{z=1}^{n_o} P_{qz_{c}}(j\omega_k)C_{zq_{c}}(j\omega_k,\rho)  \\
&L_{qp_{c}}(j\omega_k,\rho)=\sum_{z=1}^{n_i} G_{qz_{c}}(j\omega_k)(1+e^{-j\omega_k \tau_{qz_{c}}}-e^{-j\omega_k \zeta_{qz_{c}}})C_{zp_{c}}(j\omega_k,\rho)
\end{align*}
and $\|\cdot\|_{F}$ is the Frobenius norm of a matrix. 
Note that the first inequality shows that the Gershgorin bands do not encircle the critical point and so the MIMO system remains stable even if it is not fully decoupled. The second inequality guarantees the robust performance for the SISO subsystems of the decoupled MIMO system.  Note also that $M_{qq_{c}}(j\omega_k,\rho)$ represents the diagonal elements of $\vec{H}_c(j\omega_k)\vec{C}_c(j\omega_k,\rho)$ and $N_{qq_{c}}(j\omega_k,\rho)$ represents the diagonal elements of $\vec{P}_c(j\omega_k)\vec{C}_c(j\omega_k,\rho)$. The objective function in (\ref{eq:long_con}) is convex with respect to the controller parameters $\rho$.
\subparagraph{Example 2}
The proposed optimization problem will now be applied to an uncertain time delayed MIMO system. Consider a $2 \times 2$ plant model (i.e., $x_q(s)$ and $y_q(s)$ for $q=1,2$), similar to the system defined in \cite{GKL10b}, with uncertain time delays as:
\begin{equation}
\renewcommand{\arraystretch}{2.2}
\vec{P}(s)=
\begin{bmatrix}
         \dfrac{10e^{-\tau_{11}s}}{8s+1} & \dfrac{5e^{-\tau_{12}s}}{30s+1}\\
         \dfrac{-8e^{-\tau_{21}s}}{40s+1} & \dfrac{2e^{-\tau_{22}s}}{10s+1}
\end{bmatrix}
\end{equation}
where the time delays $\tau_{qp}$ possess values in the following sets:
\begin{align}\label{eq:mimo_un}
&\tau_{11}=\{3,9\}  &\tau_{12}=\{7,13\} \nonumber\\
&\tau_{21}=\{9,15\} &\tau_{22}=\{5,11\}
\end{align}
The nominal model  with time delays is defined as:
\begin{equation}
\renewcommand{\arraystretch}{2.2}
\vec{P}_n(s)=
\begin{bmatrix}
         G_{11}(s)e^{-6s} & G_{12}(s)e^{-10s}\\
         G_{21}(s)e^{-12s} & G_{22}(s)e^{-8s}
\end{bmatrix}
=
\begin{bmatrix}
         \dfrac{10e^{-6s}}{8s+1} & \dfrac{5e^{-10s}}{30s+1}\\
         \dfrac{-8e^{-12s}}{40s+1} & \dfrac{2e^{-8s}}{10s+1}
\end{bmatrix}
\end{equation}
where the time scale is defined in minutes. The elements $G_{qp}(s)$ for $q=1,2$ and $p=1,2$ represent the strictly proper delay-free transfer functions in $\vec{G}_n(s)$. The relative gain array (RGA) analysis of this system shows that this process is not diagonally dominant.

%In order to observe the interactions of this process, the relative gain array (RGA), defined as $\Lambda[\Gamma]=\Gamma\ast (\Gamma^{-1})^T$ (where the symbol $\ast$ denotes element wise multiplication), can be used to analyze the coupling affects between each pairing of the elements in $\vec{P}_n(s)$. The frequency dependent RGA is shown in Fig. \ref{fig:RGA}. 
%\begin{figure}[H]
%\centering
%\psfrag{omega}{\hspace{-0.4cm} \raisebox{-0.2cm}{$\omega \; \left[\frac{rad}{min}\right]$}}
%\psfrag{RGA}{\hspace{-0.4cm} $\Lambda [\vec{P}_n(j\omega)]$}
%\centerline{\includegraphics[scale=0.15]{fig/RG.eps}}
%\caption{RGA plot of $\vec{P}_n(s)$: diagonal elements of $\Lambda [\vec{P}_n(j\omega)]$ (blue, solid), off diagonal elements of $\Lambda [\vec{P}_n(j\omega)]$ (red, solid).}
%\label{fig:RGA}
%\end{figure}
%The most severe interaction occurs where $\Lambda_{qp}=0.5$ for $q=1,2$ and $p=1,2$. This can be seen in Fig. \ref{fig:RGA} as the intersecting point of $\Lambda [\vec{P}_n(j\omega)]$, which occurs at a frequency of approximately  0.0307 rad/min.
%Consider the case when $s=0$ (steady state response to a step input). The RGA matrix can be determined to be the following: 
%\begin{equation}
%\Lambda[\vec{P}_n(s)]\Big|_{s=0}=
%\begin{bmatrix}
%0.3333 & 0.6667 \\ 0.6667 & 0.3333
%\end{bmatrix}
%\end{equation}
%Since $0< \Lambda_{qp} < 1$ for $p,q=1,2$, interactions do exist, and the system is coupled. The permuted identity matrix can also be computed as follows:
%\begin{equation}
%\lim_{k \to \infty} \Lambda^k[\vec{P}_n(s)]\Big|_{s=0} = \begin{bmatrix}
%0.5 & 0.5\\0.5 & 0.5
%\end{bmatrix}
%\end{equation}
%which confirms that the plant process is not diagonally dominant at steady state. 
The performance and uncertainty filters chosen for this example will be identical to those in \cite{GKL10b},
\begin{equation}
W_{1_{q}}=0.5 \qquad W_{2_{q}}=0.5\left(\frac{2s+1}{s+1}\right) \qquad  q=1,2
\end{equation}
The desired diagonal open-loop transfer function $\vec{L}_D(s)$ will be chosen as simple integrators with time constants equal to 7 minutes (i.e, $\vec{L}_D(s)=diag\left(\frac{1}{7s}\right)$). For simplicity, a PI controller will be designed for this process. Since $\beta_{11}=\beta_{12}=\beta_{21}=\beta_{22}=2$, there will be a total of $m=16$ possible cases to consider in the design process. The optimization problem in (\ref{eq:long_con}) can now be solved by repeating the stability constraints for each combination of the uncertainties in (\ref{eq:mimo_un}). The frequency grid will be chosen to be between $10^{-2}$ and $10^{1}$ rad/min with $N=150$ equally spaced points. The PI MIMO controller obtained from the optimization problem is as follows:
\begin{equation}
\renewcommand{\arraystretch}{2.2}
\vec{C}(s)=
\begin{bmatrix}
\dfrac{0.06234s + 0.001464}{s} & \dfrac{-0.04803s - 0.005408}{s} \\
\dfrac{0.1585s + 0.0168}{s} & \dfrac{0.3113s + 0.005995}{s}
\end{bmatrix}
\end{equation}
Fig. \ref{fig:mimo1} displays the closed-loop MIMO response to a step input. Notice that with this controller, the MIMO process achieves robust performance while simultaneously decoupling the system. The Gershgorin bands are depicted in Fig. \ref{fig:mimo2} for the system possessing the largest delay time uncertainty ($\tau_{11}=9$, $\tau_{12}=13$, $\tau_{21}=15$, $\tau_{22}=11$). The red and blue bands possess a radius of $|r_{q}(j\omega_k)|$ for $q=1,2$ and $k=1,\ldots,N$. 
\begin{figure}[H]
\centering
\psfrag{tit1}{\hspace{-0.45cm} \scriptsize From $x_1$}
\psfrag{tit2}{\hspace{-0.45cm} \scriptsize From $x_2$}
\psfrag{tit3}{\hspace{-0.45cm} \scriptsize From $x_1$}
\psfrag{tit4}{\hspace{-0.45cm} \scriptsize From $x_2$}
\psfrag{im1}{\hspace{-0.3cm} \raisebox{0.1cm}{\scriptsize To $y_1$}}
\psfrag{im2}{\hspace{-0.3cm} \raisebox{0.1cm}{\scriptsize To $y_1$}}
\psfrag{im3}{\hspace{-0.3cm} \raisebox{0.1cm}{\scriptsize To $y_2$}}
\psfrag{im4}{\hspace{-0.3cm} \raisebox{0.1cm}{\scriptsize To $y_2$}}
\psfrag{re}{\hspace{-0.7cm} \raisebox{-0.05cm}{\scriptsize Time (minutes)}}
\centerline{\includegraphics[width=13cm,height=6.5cm]{fig/test.eps}}
\caption{MIMO response to a unit step input: reference signal (black,dash), the remaining $\Omega=16$ closed-loop responses are for all possible combinations of the time delay parameters in (\ref{eq:mimo_un}).}
\label{fig:mimo1}
\end{figure}
\begin{figure}[H]
\vspace{-0.7cm}
\centering
\psfrag{R}{\hspace{-0.5cm}$\Re_e \{Z(j\omega) \}$}
\psfrag{Y}{\hspace{-0.7cm}$\Im_m \{Z(j\omega) \}$}
\centerline{\includegraphics[scale=0.18]{fig/gersh.eps}}
\caption{Gershgorin bands for $L_{qq}$ with the largest time delay combination in (\ref{eq:mimo_un}): performance filter with $|W_{1_{q}}|=0.5$ (green circle), Gershgorin bands corresponding to $q=1$ (blue circles), Gershgorin bands corresponding to $q=2$ (red circles). Note that $Z(j\omega)$ is simply the complex number representation of each circle in the plot.}
\label{fig:mimo2}
\end{figure}
Notice how the Gershgorin bands never intersect with the performance circle centered at $(-1+j0)$. This proves that the MIMO system is stable, robust, and satisfies the optimization criterion in (\ref{eq:long_con}).  
\section{Extension to Unstable SISO Systems}
\label{sec:4}
The SP in the scheme shown in Fig. \ref{fig:dtc} cannot be used for unstable plants since the controller will contain zeros in right-hand side of the s-plan which cancel the unstable poles in the plant and leads to instability. 
To avoid this unstable zero-pole cancellation, the control structure shown in Fig.\ref{fig:dtc} should be changed. 
Several alternatives are available in literature to cope with unstable processes with dead-time (see, for example, \cite{Dep85,MA98,LCGZ05,NC07,NC09}).

Consider, for instance, the SP with modified dead-time free model depicted in Fig.~\ref{fig:dtc_modified} which is discussed in \cite{NC07}. 
\begin{figure}
\centering
\psfrag{c}[cc][cc]{$C(s)$}
\psfrag{p}[cc][cc]{$P(s)$}
\psfrag{m}[cc][cc]{$G_m(s)-P_n(s)$}
\psfrag{y}[cc][cc]{$y$}
\psfrag{u}[cc][cc]{$u$}
\psfrag{r}[cc][cc]{$r$}
\centerline{{\includegraphics[scale=.26]{fig/uns.eps}}}
\caption{Smith Predictor with modified dead-time free model}
\label{fig:dtc_modified}
\end{figure}%
In this case, the dead-time free model is defined as $G_m=\frac{N_m}{D_n}$ and $H=G_m-P_0=(N_m -N_ne^{-\tau s})\frac{1}{D_n}$. Therefore, $N_m$ must be tuned such that the zeros of $N_m -N_ne^{-\tau s}$ cancel the unstable poles in $D_n$. Once $N_m$ has been properly designed, the primary controller can be obtained by solving the optimization problem in (\ref{eq:min_hinf}) redefining $H=G_m-P_0$ and
$L_i(\rho)=(G_m-P_0+P_i)C(\rho)$. Here, care should be taken in the choice of $L_d$. As it has been shown, the $wno$ of $1+L_i$ equals the $wno$ of $1+L_d$. Therefore, $L_d$ should be chosen such that the number of encirclement of the critical point $(-1+0j)$ by its Nyquist plot is equal to the number of unstable poles in $P_i$.

\subparagraph{Example 3}
Consider the model studied in \cite{MZ00} given by:
\begin{equation}
P(s)=\frac{k}{s-a}[1+\Delta(s)W_2(s)]e^{-\tau s}
\end{equation}  
where $k=1$, $a=1$, $\tau=\tau_n \pm 0.02$ and $\tau_n=0.2$. The interval of variation of $\tau$ is gridded using $q=3$ equally spaced points. A finer grid just increases the number of constraints and for this example does not change significantly the final controller.
The performance and uncertainty filters are respectively chosen as:
\begin{equation}
W_1(s)=2\left(\frac{s+1}{10s+1}\right) \quad \mbox{and} \quad  W_2(s)=0.2\left(\frac{s+1.1}{s+1}\right)
\end{equation}
%The objective is to minimize $\gamma$ such that the robust performance condition $\|  |W_1S_i|+|W_2T_i|	  \|_{\infty}<\gamma$ holds for $i=1,2,3$.

Here, we use the SP with modified dead-time free model (Fig. \ref{fig:dtc_modified}) due to its simplicity. The dead-time free model $G_m(s)$ is chosen as
\begin{equation}
G_m(s)=\frac{T_ms+1}{s-1}.
\end{equation}
$T_m$ is computed in order to obtain $H(s)=G_m(s)-P_0(s)$ without a pole in $s=1$.
Since 
\begin{equation}
H(s)=\frac{1}{s-1}[T_ms+1-e^{-0.2s}],
\end{equation}
if $T_m=e^{-0.2}-1$, then $s=1$ is a zero of $H(s)$.

A PI as the primary controller is designed. The first step is to choose the transfer function $L_d(s)$, which must encircle the critical point in the Nyquist diagram once and must contain one integrator. Therefore, it is chosen as
\begin{equation}
L_d(s)=10\frac{s+1}{s(s-1)}.
\end{equation}
Optimization problem (\ref{eq:min_hinf}) is solved considering $N=100$ equally spaced frequency points between $\omega=10^{-3}$rad/s and $\omega=10^{3}$rad/s and the following controller is obtained:
\begin{equation}
C_{0}(s)=(3.582 s + 0.5838)/s
\end{equation}  
which yields $\gamma= 0.6854$. This result can be further improved by using a new $L_d(s)$ based on $C_0(s)$ in the optimization problem. With this new $L_d(s)=G_m(s)C_0(s)$ the optimal primary controller is: 
\begin{equation}
C(s)=(2.994 s + 0.4612)/s
\end{equation}  
and $\gamma=0.6074$. Figure \ref{fig:example3} depicts the function 
$$\Gamma_i(j\omega)=|W_1(j\omega)S_i(j\omega)|+|W_2(j\omega)T_i(j\omega)|$$
where $S_i$ and $T_i$ are respectively given by (\ref{eq:sensitivity}) and (\ref{eq:sensitivity_comple}) with $H=G_m-P_0$ and $P_i$ is obtained by gridding of $\tau$. Note that the maximum value of the function is $0.6072$, which occurs when $\tau=\tau_n+0.02=0.22$, is close to the bound $\gamma$. It is worth to point out that, although the conditions given in Theorem \ref{th:siso} are only sufficient to guarantee $\| \Gamma_i \|_{\infty}<\gamma$, with a proper choice of $L_d$ it is possible to obtain 
a solution with very low conservatism. Furthermore, the resulting controller is a standard PI 
which can be implemented in a straightforward manner and has great practical significance.
\begin{figure}[!h]
\centering
\includegraphics[width=0.7\columnwidth]{fig/shaped_sensitivity}
\caption{Example 2: Blue solid line: $\Gamma$ for $\tau=0.18$; green solid line: $\Gamma$ for $\tau=0.2$;  black solid line: Blue solid line: $\Gamma$ for $\tau=0.22$; red dot-dashed line: $\gamma$.}
\label{fig:example3}
\end{figure}

%The equivalent controller $C_{eq}$ obtained in \cite{MZ00} can be written as
%\begin{equation}
%C_{eq}=\frac{K}{1-KF_{stab}}
%\end{equation}
%where the primary controller $K$ is:
%\begin{equation}
%K=\frac{4.6971s^2+5.6971s+1}{0.000016s^3+1.4414s^2+1.4792s+0.0379}
%\end{equation}
%and the predictor $F_{stab}$ is given by:
%\begin{equation} 
%F_{stab}=\frac{-10.75 s^2 - 0.245 s + 0.3298}{12.03 s^3 - 12.03 s^2 + s - 1
%}+\frac{(13.16 s^2 - 0.1316)e^{-0.2s}
%}{12.03 s^3 - 12.03 s^2 + s - 1}
%\end{equation}
%The $\Gamma_i(j\omega)$ function for this controller with $i=1,2,3$ is depicted on Fig. \ref{fig:unstable_compare}.

For the same example, controller designed in \cite{MZ00} leads to  the optimal $\gamma = 0.9407$ which is 55\% higher than the value obtained with the proposed method. It should be mentioned that the true robust performance criterion in (\ref{eq:min_hinf}) is not minimized in \cite{MZ00}. Instead, the maximum singular value of $[W_1(j\omega)S(j\omega) \quad W_2(j\omega)T(j\omega)]$ for all $\omega$ is minimized by the $H_\infty$ control theory.

%\begin{figure}[!h]
%\centering
%\includegraphics[width=\columnwidth]{pics/example2/gamma_compare}
%\caption{Example 2, controller from \cite{MZ00}:  Blue solid line: $\Gamma$ for $\tau=0.18$; green solid line: $\Gamma$ for $\tau=0.2$;  black solid line: Blue solid line: $\Gamma$ for $\tau=0.22$.}
%\label{fig:unstable_compare}
%\end{figure}
%

\section{Gain-scheduled Controller Design}
\label{sec:5}
Consider an uncertain plant $P(s,\theta)$ belonging to the set:
\begin{equation}
\mathsf{P}_\theta=\{G(s,\theta)e^{-\tau_i(\theta)s}, \; i=1,\dots, q \}
\end{equation}
where the dead-time free part of the model has unstructured multiplicative uncertainty and is described as:
\begin{equation}
G(s,\theta)=G_n(s,\theta)[1+\Delta(s) W_2(s)]
\end{equation}
and $\theta$ is a vector of scheduling parameters that belongs to a finite set $\Theta=\{\theta_1, \theta_2, \ldots, \theta_m   \}$ (corresponding e.g. to the different operating point parameters). It is assumed that the operating point does not frequently change (the stability and performance are achieved for the frozen scheduling parameter). The dead-time is also a function of the scheduling parameter and uncertain, so for a given value of $\theta$ it belongs to the set $\{ \tau_1(\theta), \tau_2(\theta), \ldots, \tau_q(\theta)    \}$.

We will consider the SP shown in Fig. \ref{fig:dtc_lpv} where both, the nominal model $P_0(s,\theta)=G_n(s,\theta)e^{-\tau_n(\theta)s}$ and the primary controller $C(s,\theta)$ are functions of the scheduling parameter vector $\theta$. The goal is to compute a primary gain-scheduled controller for this scheme that meets the $H_\infty$ robust performance specification. 
\begin{figure}
\centering
\psfrag{rr}{\small $r$}
\psfrag{cc}{\small \hspace{-0.1cm}$C(s,\theta)$}
\psfrag{uu}{\small $u$}
\psfrag{pp}{\small \hspace{-0.15cm}$P(s,\theta)$}
\psfrag{gn}{\small \hspace{-0.2cm}$G_n(s,\theta)$}
\psfrag{ex}{\small \hspace{-0.2cm}$e^{-\tau_n(\theta) s}$}
\psfrag{yp}{\small $y_p$}
\psfrag{yy}{\small $y$}
\psfrag{pl}{\small $+$}
\psfrag{mi}{\small $-$}
\psfrag{dis}{\small $d$}
\includegraphics[scale=0.7]{fig/SISO_block.eps}
\caption{Gain-Scheduled Smith Predictor}
\label{fig:dtc_lpv}
\end{figure}%

The primary controller ${C}(s,\theta)$ is linearly parametrized by:
$
C(s,\theta)=\rho^T(\theta) \phi(s)
$,
where the basis function vector $\phi(s)$ is defined as in section (\ref{sec:siso_cls}) and $\rho^T(\theta)$
is given by
\begin{equation}	
 \rho^T(\theta)=[\rho_{1}(\theta),\rho_{2}(\theta), \ldots, \rho_{n}(\theta)]
\end{equation}
Every gain is a polynomial function of order $\delta$  of the scheduling parameters and is defined as
\begin{equation}
\rho_{i}(\theta)=(\nu_{i, \delta})^T\theta^{\delta}+\ldots+(\nu_{i, 1})^T\theta+ \nu_{i, 0}
\end{equation}
and $\theta^{k}$ denotes element-by-element power of $k$ of vector $\theta$.
In Fig. (\ref{fig:dtc_lpv}), the transfer function from the output disturbance $d$ to $y$ is the sensitivity function $S_i(s,\theta)$, while the transfer function from $r$ to $y$ is the complementary function $T_i(s,\theta)$:
\begin{align}
S_i(s,\theta)&=\frac{1+C(s,\theta)H(s,\theta)}{1+C(s,\theta)(H(s,\theta)+P_i(s,\theta)) } \\ \nonumber
T_i(s,\theta)&=\frac{C(s,\theta)P_i(s,\theta)}{1+C(s,\theta)(H(s,\theta)+P_i(s,\theta)) }, \; \forall \theta \in \Theta
\end{align}
where $H(s,\theta)=G_n(s,\theta)-P_0(s,\theta)$. The primary controller is obtained from the following optimization problem:
\begin{align}\label{eq:min_hinf_lpv}
&\qquad \min_{\rho} \gamma \nonumber \\\mbox{Subject to:} &\\ \nonumber
& \|  |W_1S_i(s,\theta)| + |W_2T_i(s,\theta)| \|_{\infty}<\gamma\\ 
& \mbox{for } i=1,\dots,q,  \quad \forall \theta \in \Theta \nonumber
\end{align}

%
%As an LPV model is available, there will be an infinity
%number of models corresponding to different values of the
%scheduling parameters. 
%This problem can be solved by gridding
%$\theta$ leading to $m$ different LTI models. Considering the multimodel uncertainty,
%the procedure should be repeated for each one of the $q$ uncertain models.

Optimization problem (\ref{eq:min_hinf_lpv}) is again solved using an iterative bisection algorithm as previously presented. At each iteration, a feasibility problem is solved with the following convex constraints:
\begin{eqnarray} \label{eq:cond_lpv}
\Big [ |W_{1}(j\omega_k)[1+C(j\omega_k,\theta_l)H(j\omega_k,\theta_l)|+|W_{2}(j\omega_k)C(j\omega_k,\theta_l)P(j\omega_k,\theta_l) | \Big ] \nonumber\\ \times |1+L_{d}(j\omega_k)|-
Re\{[1+L^{\ast}_{d}(j\omega_k)][1+L_i(j\omega_k,\theta_l)]\}<0 \nonumber\\ \mbox{for } k=1,\dots,N,\quad  i=1,\ldots,q, \quad l=1,\ldots,m  
\end{eqnarray}
%where $\theta_l$ is a vector with particular values of the scheduling
%parameters $\theta$ obtained from the gridding.

%It should be noted that since the design is performed in the frequency domain, the designed controller guarantees the closed-loop stability and performance for frozen scheduling parameters.

\subparagraph{Example 4}
The design method is applied on a simulated system having a resonance
whose frequency changes as a function of a scheduling
parameter $\theta$. Consider the following plant model
\begin{equation}
P(s,\theta)=G(s,\theta)e^{-\tau s}
\end{equation}
where $G(s,\theta)=G_n(s,\theta)[1+\Delta(s)W_2(s)]$ and
\begin{eqnarray}
G_n(s,\theta)&=&\frac{(2+0.2\theta)^2 }{s^2+0.2(2+0.2\theta)s+(2+0.2\theta)^2} \\
W_2(s)&=&0.8\frac{1.1337s^2+6.8857s + 9}{(s+1)(s+10)}
\end{eqnarray}
and $\theta \in [-1, -0.5, 0, 0.5, 1]$.
%This model could represent the dynamics of a mechatronic
%system, where the frequency of the resonance is a function of
%the moving mass. 
Consider also that the dead-time is within the interval $\tau \in [2.7, 3.0, 3.3]$ but its exact value is unknown in runtime. 
The objective is to design a primary gain-scheduling PID controller for the Smith Predictor structure  considering the performance filter 
$
 W_1(s)=\frac{2}{(20s+1)^2}
$.
 The parameters $\rho$ of the primary controller will be affine functions of the scheduling parameter $\theta$. The filter of the derivative
action is chosen to have a time constant of $T_f=0.01$s.
%The range of the scheduling parameter $\theta$ is gridded using $m=5$ points. The uncertainty interval of the dead-time is gridded using $q=3$ points.

Finally, optimization problem (\ref{eq:min_hinf_lpv}) is solved considering $L_d=1/s$ and $N=100$ equally spaced frequency points between $10^{-2}$ and $10^2$ rad/s. 
The resulting gain-scheduled controller is given by:
$K_p(\theta)=   -0.0168 \theta +     0.2152$, $K_i(\theta)=  0.0144\theta +   2.4736$, 
$K_d(\theta)=-0.1224 \theta+   0.6424$.

This controller leads to:
\begin{align}
&\|  |W_1S_i(s,\theta_l)| + |W_2T_i(s,\theta_l)| \|_{\infty}<\gamma=0.8928\\ \nonumber
&l=1,\ldots,5, \quad i=1,2,3
\end{align}
The gain-scheduled controller is evaluated considering $\theta=-1,0,1$ and $\tau=3.3$s. The performance is compared to a fixed-gain PID designed for the nominal case ($\theta=0$ and $\tau= 3$s). Figure \ref{fig:example2} shows the step response of the gain-scheduled controller in all conditions (blue, red and green solid lines) compared with the fixed PID controller (black dashed line, highly oscillating). 
\begin{figure}[H]
\centering
\includegraphics[scale=0.4]{fig/exampleLPV_min_gamma}
\caption{Example 3: Blue, red and green solid line: gain-scheduled PID Smith Predictor and $G_2$ using  $\theta_1=-1$, $\theta_3=0$ and $\theta_5=1$ respectively;  black dashed line: fixed PID Smith Predictor using $\theta=-1$.}
\label{fig:example2}
\end{figure}%

\section{Conclusions}
This paper presents a new method to design a robust Smith Predictor for uncertain SISO and MIMO time-delay systems using convex optimization techniques. The proposed approached allows one to design PI/PID as well as higher order primary controllers in the Smith Predictor structure which provide robust $H_{\infty}$ performance for systems with uncertain dead-time and multiplicative or multimodel uncertainty in the dead-time free model of the system. The method is based on a convex approximation of the $H_\infty$ robust performance criterion in the Nyquist diagram. This approximation relies on the choice of a desired open-loop transfer function $L_d$ for the dead-time free model of the plant. For the SISO case, a bisection algorithm was implemented to solve the convex constrained problem. For the MIMO case, a controller was designed such that the system became decoupled and simultaneously optimized the single-loop performances of the SISO subsystems.

%The controller design examples shown for both MIMO and SISO cases considered a finite amount of discrete values to represent the uncertainties in the time delays. However, the proposed optimization methods can be applied for a system(s) with $\alpha$ number of uncertainties within a specified range, where $\{\exists\alpha \in \mathbb{Z}^+ | \; 0<\alpha<\infty \} $.

%For SISO systems, the number of combinations to consider in the controller design will simply be the number of elements $M$ in the uncertain set. However, for MIMO systems, the number of combinations will be $M^{n_o n_i}$ (assuming the same number of uncertainties for each time delay). For example, a SISO system containing a range of time delays with three uncertainties will have to compute a controller for $M=3$ combinations. On the other hand, a $3 \times 3$ MIMO system with the same number of uncertainties will have to consider $M^{n_o n_i}=3^9=19,683$ combinations. Thus the controller design for MIMO systems will be computationally expensive for systems with a large amount of inputs and outputs.
\begin{thebibliography}{99.}%
% and use \bibitem to create references.
%
% Use the following syntax and markup for your references if
% the subject of your book is from the field
% "Mathematics, Physics, Statistics, Computer Science"
%
% Contribution
\bibitem{Bro79} C. B. Brosilow. The structure and design of Smith
predictors from the viewpoint of inferential control.
In Proceedings of Joint American Control Conference,
Denver, Colorado, 1979.
%
\bibitem{Dep85} A. M. De Paor. A modified Smith predictor and controlled
for unstable processes with time delay. International
Journal of Control, 41(4):1025--1036, 1985.
%
\bibitem{DFT92} C. J. Doyle, B. A. Francis, and A. R. Tannenbaum.
Feedback Control Theory. Mc Millan, New York, 1992.
%
\bibitem{GKL10a} G. Galdos, A. Karimi, and R. Longchamp. Robust controller
design by convex optimization based on finite
frequency samples of spectral models. In 49th IEEE
Conference on Decision and Control, Atlanta, USA,
2010a.
%
\bibitem{GKL10b} G. Galdos, A. Karimi, and R. Longchamp. $H_{\infty}$ controller
design for spectral MIMO models by convex optimization.
Journal of Process Control, 20(10):1175--1182,
2010b.
%
\bibitem{Hag92} T. Hagglund. A predictive PI controller for processes with
long dead times. IEEE Control Systems Magazine, 12
(1):57--60, 1992.
%
\bibitem{HWC95} C. C. Hang, Q. Wang, and L. S. Cao. Self-tuning Smith
predictors for processes with long dead time. International
journal of adaptive control and signal processing,
9(3):255--270, 1995.
%
\bibitem{KG10} A. Karimi and G. Galdos. Fixed-order $H_{\infty}$ controller design
for nonparametric models by convex optimization.
Automatica, 46(8):1388--1394, 2010.
%
\bibitem{Kay01} I. Kaya. Tuning Smith predictors using simple formulas
derived from optimal responses. Industrial and engineering
chemistry research, 40(12):2654--2659, 2001.
%
\bibitem{LLSL99} D. Lee, M. Lee, S. Sung, and I. Lee. Robust PID tuning
for Smith predictor in the presence of model uncertainty.
Journal of Process Control, 9(1):79--85, 1999.
%
\bibitem{LCGZ05} T. Liu, Y. Z. Cai, D. Y. Gu, and W. D. Zhang. New
modified Smith predictor scheme for integrating and
unstable processes with time delay. IEE Proceedings-
Control Theory and Applications, 152(2):238--246, 2005.
%
\bibitem{MA98} S. Majhi and D. P. Atherton. A new Smith predictor and
controller for unstable and integrating processes with
time delay. In Proceedings of the 37th IEEE Conference
on Decision and Control, pages 1341--1345, 1998.
%
\bibitem{MZ00} G. Meinsma and H. Zwart. On $H_\infty$ control for dead-time
systems. IEEE Transactions on Automatic Control, 45
(2):272--285, 2000.
%
\bibitem{Mir03} L. Mirkin. On the extraction of dead-time controllers
and estimators from delay-free parametrizations. IEEE
Transactions on Automatic Control, 48(4):543--553,
2003.
%
\bibitem{NC00} J. E. Normey-Rico and E. F. Camacho. Multivariable generalised predictive controller based on the Smith predictor. IEEE Proceedings in Control Theory Applications, Vol. 147, No. 5, 2000.
%
\bibitem{NC07} J. E. Normey-Rico and E. F. Camacho. Control of dead-time
processes. Springer Verlag, 2007.
%
\bibitem{NC09} J. E. Normey-Rico and E. F. Camacho. Unified approach
for robust dead-time compensator design. Journal of
Process Control, 19(1):38--47, 2009.
%
\bibitem{Pal80} Z. J. Palmor. Stability properties of Smith dead-time compensator
controllers. International Journal of Control,
32:937--949, 1980.
%
\bibitem{Pal96} Z. J. Palmor. Time-delay compensation Smith predictor
and its modifications. In W. Levine, editor, The Control
Handbook. CRC Press, Boca Raton, FL, 1996.
%
\bibitem{PB94} Z. J. Palmor and M. Blau. An auto-tuner for Smith dead
time compensator. International Journal of Control, 60
(1):117--135, 1994.
%
\bibitem{SBP09} R. S. Sanchez-Pena, Y. Bolea and V. Puig. MIMO Smith predictor: Global and structured robust performance analysis. Journal of Process Control 19:163-177, 2009.
%
\bibitem{SS93} C. Santacesaria and R. Scattolini. Easy tuning of Smith
predictor in presence of delay uncertainty. Automatica,
29(6):1595--1597, 1993.
%
\bibitem{Sko} S. Skogestad and I. Postlethwaite. Multivariable Feedback Control; Analysis and Design. John Wiley and Sons, England, 1996.
%
\bibitem{Smi57} O. J. M. Smith. Closer control of loops with dead time.
Chemical Engineering Progress, 53(5):217--219, 1957.
%
\bibitem{ZL06} W. Zhang and C. Lin. Multivariable Smith Predictors Design for Nonsquare Plants. IEEE Transactions on Control Systems Technology,
Vol. 14, No. 6, 2006.
%
\bibitem{Zho03a} Q. C. Zhong. On standard $H_\infty$ control of processes with a single delay. IEEE Transactions on Automatic Control,
48(6):1097--1103, 2003.
%
\bibitem{ZhoDoy} K. Zhou and J. Doyle. Essentials of Robust Control. Prentice-Hall, Upper Saddle River, New Jersey, USA, 1998.
%
\bigskip
\end{thebibliography}

\end{document}

### 2017-02-11 Papers/PUBLISHED - MIMO Smith Predictor/MSC_Nicoletti_Karimi.tex
adding files to git (11/2/2017)

\documentclass[A4, 10pt, conference]{ieeeconf}

\IEEEoverridecommandlockouts                              
\overrideIEEEmargins
% Autres classes disponibles : report, book, slides
% Options possibles : 	11pt, 12pt (taille de la fonte)
%                     			oneside (recto simple)
%                     			twoside (document recto-verso)
\usepackage{color,graphicx}
\usepackage{psfrag}
\usepackage[english]{babel}
\usepackage{amsmath,amssymb,xfrac}

\topmargin +8pt
\oddsidemargin -25pt
\evensidemargin -25pt

%\usepackage{mathabx}
\usepackage[thref]{ntheorem}
\usepackage{float}
\newcommand{\jo}{(j\omega,\rho)}
%\renewcommand{\IEEEQED}{\IEEEQEDopen}
\renewcommand{\vec}[1]{\mathbf{#1}}
%\DeclareRobustCommand*{\IEEEauthorrefmark}[1]{%
  %\raisebox{0pt}[0pt][0pt]{\textsuperscript{\footnotesize\ensuremath{#1}}}}

\begin{document}

\title{\LARGE \bf $H_{\infty}$ Smith Predictor Design for Time-Delayed MIMO Systems via Convex Optimization}

\author{Achille Nicoletti$^{1,2}$ and Alireza Karimi$^{1,3}$% <-this % stops a space
\thanks{$^{1}$Automatic Control Laboratory
Ecole Polytechnique F\'{e}d\'{e}rale de Lausanne (EPFL),
1015 Lausanne, Switzerland}%
\thanks{$^{2}$ {\tt\small achille.nicoletti@epfl.ch}}%
\thanks{$^{3}$ {\tt\small alireza.karimi@epfl.ch}}%
}

\maketitle
\thispagestyle{empty}
\pagestyle{empty}

\begin{abstract}
A new method for robust fixed-order $H_{\infty}$ controller design for uncertain time-delayed MIMO systems is presented. It is shown that the $H_{\infty}$ robust performance condition can be represented by a set of convex constraints with respect to the parameters of a linearly parameterized primary controller in the Smith predictor structure. Therefore, the parameters of the primary controller can be obtained by convex optimization. The proposed method will be applied to stable MIMO models with uncertain dead-time and with multimodel and frequency-dependent uncertainty. The performance of this method is illustrated by simulation examples of industrial processes.
\end{abstract}

%\begin{IEEEkeywords}
%Robust controller, convex optimization, H-infinity, transfer function %uncertainty, Smith predictor, MIMO time delay.
%\end{IEEEkeywords}

\section{Introduction}
Many dynamical systems in the industry possess unavoidable time delays. These delays can be caused by accumulation of time lags for dynamic systems interconnected in series, transportation delay or measurement delay \cite{NC07}. Time delays in control loops can cause significant complications in modern industrial applications. The rapid development in data and communication network technologies has caused a need for real-time data processing \cite{LHW08}. The first time-delay compensation method was proposed in the late 1950s by \cite{Smi57}. This method is known as the Smith Predictor (SP), and it has become one of the most widely implemented control schemes used to regulate industrial systems with time delays.

The SP, however, is somewhat limited in its performance, since an accurate model of the system is generally required for satisfactory operation. In certain circumstances, small modeling errors may lead to undesirable performance, where the system can become unstable. For this reason, research efforts have been focused on robustness issues of the SP.

\iffalse
\begin{figure}[h]
\centering
\psfrag{rr}{\small $r$}
\psfrag{cc}{\small $C(s)$}
\psfrag{uu}{\small $u$}
\psfrag{pp}{\hspace{-0.15cm}\small $P(s)$}
\psfrag{gn}{\hspace{-0.2cm}\small $G_n(s)$}
\psfrag{ex}{\hspace{-0.2cm}\small $e^{-\tau_n s}$}
\psfrag{yp}{\small $y_p$}
\psfrag{yy}{\small $y$}
\psfrag{pl}{\scriptsize $+$}
\psfrag{mi}{\scriptsize $-$}
\psfrag{dis}{\small $d$}
\includegraphics[width=0.8\columnwidth]{pics/SISO_block.eps}
\caption{Smith Predictor}
\label{fig:smith_siso}
\end{figure}%
\fi

Many researchers are interested in the optimal control of dead-time
systems, especially $H_{\infty}$ control, i.e., to find a controller to
internally stabilize the system and to minimize the $H_{\infty}$-norm of an associated transfer
function. Many relevant results have been presented in this framework using 
modified versions of the SP. See, for instance, \cite{Mir03}, \cite{MZ00} and \cite{Zho03a}. Recently, the single-input-single-output (SISO) SP has been extended and generalized for multiple-input-multiple-output (MIMO) systems. In \cite{SBP09}, a structured uncertainty approach was implemented for SP's with diagonal delay matrices. This method, however, does not consider general and distinct time delays for each element of the plant transfer matrix. A diagonal $H_2$ optimal controller for non-square plants is designed by factorization methods in \cite{ZL06}. In \cite{NC00}, a generalized predictive control (GPC) method is implemented on MIMO SP systems with multiple delays.   
These control techniques, although efficient, are quite complex from both the design and implementation perspective.

There are a wide variety of industrial applications that involve MIMO processes with time delays, and it is of practical interest to develop robust control techniques for such systems. The proposed control scheme is based on the ideas presented in \cite{VK13}  for SP design of SISO systems and in \cite{GKL10b} for designing decoupling MIMO controllers. However, in this paper, the SP design method for computing $H_\infty$ controllers for SISO models is extended to MIMO SP's with process plants that possess uncertain time delays. A convex optimization approach is implemented to design a linearly parameterized primary controller in a SP structure for a MIMO system with uncertain time delays. %Due to the number of time delay uncertainties associated with the SISO subsystems of the overall MIMO process, a controller must be designed such that the $H_\infty$ performance criterion is satisfied for each combination of these uncertainties.

This paper is organized as follows: In Section (\ref{sec:2}), the class of models, controllers and control objectives are defined. Section (\ref{sec:3}) will discuss the control design methodology and stability conditions of the proposed method for the MIMO Smith predictor. This methodology is based on the convex constraints in the Nyquist diagram. Section (\ref{sec:4}) will demonstrate the effectiveness of the proposed method by considering several case studies from industrial processes. Finally the concluding remarks are given in Section (\ref{sec:5}). 
\section{Problem Formulation}
\label{sec:2}
In this section, the SP for MIMO systems with generalized time delays is investigated. For notation purposes, bold face characters will represent transfer function matrices.
\subsection{Class of models}
Let $n_o$ and $n_i$ represent the number of outputs and the number of inputs of a system, respectively. The set of LTI-MIMO stable strictly proper  models with multiplicative uncertainty and  uncertain time delays can be defined as follows: 
\begin{equation}\label{eq:setpmimo}
\mathcal{P}=\{\vec{P}_c(s)[\vec{I}+\Delta_c(s) \vec{W}_{2_{c}}(s)];\hspace{0.5cm} c=1,\ldots,m\}
\end{equation}
where each element in $\vec{P}_c(s)$ possesses a time delay that can vary over a range of specified values, and $\vec{W}_{2_{c}}$ is a transfer function matrix that represents the multiplicative input uncertainty of the system. $\Delta_c(s)$ represents the unknown stable transfer function matrix satisfying $\| \Delta_c \|_{\infty} < 1 $. For simplicity, one model from the set $\mathcal{P}$ will be investigated, and the subscript $c$ will be omitted. The uncertain $n_o \times n_i$ time delayed plant has the following form:
\begin{equation}\label{eq:mimo_p}
\vec{P}(s)=
\begin{bmatrix}
G_{11}(s)e^{-\tau_{11} s} & \cdots & G_{1n_{i}}(s)e^{-\tau_{1n_{i}} s} \\ \vdots & \ddots & \vdots \\ G_{n_{o}1}(s)e^{-\tau_{n_{o}1} s} & \cdots & G_{n_{o}n_{i}}(s)e^{-\tau_{n_{o}n_{i}} s}
\end{bmatrix}
\end{equation}
where $G_{qp}(s)$ is a strictly proper delay-free transfer function, and $\tau_{qp}$ is the uncertain time-delay of the process for $p=1,\ldots, n_i$ and $q=1,\ldots, n_o$. Note that $\tau_{qp}$ is a set that is composed of elements $\tau_{qp_{i}}$ for $i=1,\ldots, l$ and belongs in the domain $\{ \tau_{qp} \in \mathbb{R}:\tau_{qp_{i}} > 0 \ \forall \: \{p,q,i\} \}$.

\subsection{Class of controllers}
As stated in \cite{GKL10b}, an $n_i \times n_o$ matrix can be formed to represent the controller $\vec{C}(s,\rho)$. The elements of $\vec{C}(s,\rho)$ will possess linearly parameterized elements
\begin{equation} \label{eq:mimo_con}
C_{pq}(s,\rho)=\rho^T_{pq}\phi_{pq}(s)
\end{equation}
where $\rho^T_{pq}$ is a vector of parameters, and $\phi_{pq}(s)$ is a vector of stable transfer functions chosen from a set of orthogonal basis functions. The non-diagonal elements of $\vec{C}(s,\rho)$ strive to decouple the system, while the diagonal elements aim to control the single-loop subsystems. The main purpose of parameterizing the controller in this manner is due to the fact that the components of the open loop transfer function can be written as a linear function of the control parameters $\rho$,
\begin{equation}
\rho=[\rho_{11},\ldots,\rho_{1_{n_{i}}},\ldots,\rho_{n_{o}1},\ldots,\rho_{n_{o}n_{i}}]
\end{equation}
\subsection{Design specifications}\label{sec:mimo_des}
Fig. \ref{fig:mimo_block} displays the SP for the MIMO case,
%\footnote{Note that the block diagram for the SP has been reconfigured for the MIMO case. In this manner, the uncertain plant is generalized where each element in (\ref{eq:mimo_p}) can posses a distinct and unique range of time delays.}. 
where $\vec{G}_n(s)$ is an $n_o \times n_i$ nominal delay-free transfer function matrix with elements $G_{qp}(s)$, and $\vec{P}_n(s)$ is an $n_o \times n_i$ nominal transfer function matrix that includes the nominal values of the time delays, which is comprised of elements $G_{qp}(s)e^{-\zeta_{qp}s}$ (where $\zeta_{qp}$ represents the $qp$-th nominal time delay). Both $\vec{Y}(s)$ and $\vec{R}(s)$ are $n_o \times 1$ column vectors that possess elements $y_q(s)$ and $r_q(s)$, respectively. The transfer function from the inputs of $\vec{C}(s)$ to $\vec{Y}_p(s)$ will represent the open-loop transfer function,
\begin{equation}\label{eq:oltfmimo}
\vec{L}(s)=[\vec{P}(s)+\vec{H}(s)]\vec{C}(s)
\end{equation}
where $\vec{H}(s)=\vec{G}_n(s)-\vec{P}_n(s)$. Notice that if $\vec{P}(s)=\vec{P}_n(s)$, then $\vec{L}(s)=\vec{G}_n(s)\vec{C}(s)$. Since the class of controllers to be designed for this system are linearly parameterized, the elements of the controller $\vec{C}(s)$ will actually be a linear function of the controller parameters $\rho$. Therefore, $\vec{C}(s)$ will be represented as $\vec{C}(s,\rho)$ with elements $C_{pq}(s,\rho)$, as asserted in (\ref{eq:mimo_con}).
\begin{figure}
\centering
\psfrag{cc}{\hspace{-0.1cm}$\vec{C}(s)$}
\psfrag{yy}{$\vec{Y}(s)$}
\psfrag{yp}{$\vec{Y}_p(s)$}
\psfrag{pp}{$\vec{P}(s)$}
\psfrag{pl}{\scriptsize $+$}
\psfrag{mi}{\scriptsize $-$}
\psfrag{gn}{\hspace{-0.3cm} $\vec{G}_n(s)$}
\psfrag{gnd}{\hspace{-0.2cm}$\vec{P}_n(s)$}
\psfrag{dd}{\hspace{0.37cm} \raisebox{-0.3cm}{$\vec{D}(s)$}}
\psfrag{uu}{$\vec{U}(s)$}
\psfrag{rr}{\hspace{-0.3cm} $\vec{R}(s)$}
\includegraphics[scale=0.55]{pics/mimo_b3.eps}
\caption{MIMO representation of the Smith Predictor}
\label{fig:mimo_block}
\end{figure}
%For MIMO systems, the robust stability conditions are dependent on the type of perturbed model. For example, the robust conditions for MIMO systems with input multiplicative perturbations will differ for systems with output multiplicative perturbations. For a system with multiple unstructured uncertainties, the structured singular value method is typically used to prove the robust stability and robust performance of a system \cite{ZhoDoy}.

The transfer function from the output disturbance $\vec{D}(s)$ to $\vec{Y}(s)$ is the output sensitivity function $\vec{S}(s,\rho)$, while the transfer function from $\vec{R}(s)$ to $\vec{Y}(s)$ is the complementary sensitivity function $\vec{T}(s,\rho)$:
\begin{equation}  \label{eq:sens_mimo}
\begin{split}
\vec{S}(s,\rho)&=[\vec{I}+\vec{H}(s)\vec{C}(s,\rho)]\vec{Z}^{-1}(s,\rho) \\ \vec{T}(s,\rho)&=\vec{P}(s) \vec{C}(s,\rho) \vec{Z}^{-1}(s,\rho) 
\end{split}
\end{equation}
where $\vec{Z}(s,\rho)=[\vec{I}+\vec{L}(s,\rho)]$. The objective is to determine the controller $\vec{C}(s,\rho)$ that will guarantee the robust performance and robust stability of the closed-loop SP system. 
\section{Proposed method}
\label{sec:3}
It is well known that if a SISO model is described by unstructured multiplicative uncertainty, and possesses both robustness and performance weighing functions $W_1$ and $W_2$, then the necessary and sufficient condition for robust performance is given by \cite{DFT92}:
\begin{equation}
\||W_1S|+|W_2T|\|_{\infty}<1
\end{equation}
where $S$ and $T$ are the sensitivity and complementary  sensitivity functions of a SISO system, respectively.

For the moment, assume the case when a closed-loop MIMO system is fully decoupled. Then the MIMO sensitivity and complementary sensitivity functions can essentially be treated as functions containing independent SISO subsystems. Thus it is judicious to define $\vec{W}_1(s)$ as a diagonal filter with diagonal elements $W_{1_{q}}$ and a diagonal filter $\vec{W}_2(s)$ with diagonal elements $W_{2_{q}}$ representing, respectively, the nominal performance and multiplicative uncertainty for the SISO subsystems. This rationalization leads to the following theorem:

\newtheorem{theorem}{Theorem} %Use this when you're stating a theorem
\begin{theorem} 
\label{rob_per}
Let $M_{qq}(j\omega,\rho)$ represent the diagonal elements of $\vec{H}(j\omega)\vec{C}(j\omega,\rho)$ and $N_{qq}(j\omega,\rho)$ represent the diagonal elements of $\vec{P}(j\omega)\vec{C}(j\omega,\rho)$. Suppose that $\vec{S}(s,\rho)$ and $\vec{T}(s,\rho)$ in (\ref{eq:sens_mimo}) are diagonal transfer function matrices (the closed-loop system is fully decoupled). Then the linearly parameterized controller in (\ref{eq:mimo_con}) will guarantee the closed-loop stability of the system and satisfy the following robust performance criterion:
\begin{eqnarray} \label{eq:mimo_hinf}
\| |W_{1_{q}}(j\omega)S_{qq}\jo|+ |W_{2_{q}}(j\omega)T_{qq}\jo| \|_{\infty} < 1 \nonumber\\
\mbox{for }q=1,\ldots,n_o
\end{eqnarray}
if
\begin{eqnarray} \label{eq:mimo_approx}
\{|W_{1_{q}}(j\omega)[1+M_{qq}\jo]|+|W_{2_{q}}(j\omega)N_{qq}\jo|\} \nonumber\\
\times |1+L_{D_{q}}(j\omega)| -\Psi_q\jo<0 \nonumber\\
\forall \omega \: \mbox{ for }q=1,\ldots,n_o  
\end{eqnarray}
where 
$$
\Psi_q\jo=R_e\{[1+L^*_{D_{q}}(j\omega)][1+L_{qq}\jo]\}
$$
and $S_{qq}$ and $T_{qq}$ are the $q$-th diagonal elements of $\vec{S}(s,\rho)$ and $\vec{T}(s,\rho)$, respectively. $L_{D_{q}}(s)$ is the $q$-th diagonal element of a diagonal transfer function matrix $\vec{L}_D(s)$ that contains strictly proper transfer functions which do not encircle the critical point, and $L^*_{D_{q}}$ is its complex conjugate.   
\end{theorem}
\begin{proof} %This is if you have proofs
If the closed-loop MIMO system is fully decoupled, then the MIMO sensitivity and complementary sensitivity functions can be considered as systems containing independent SISO systems. 
Since the real part of a complex number is less than or equal to its magnitude, we have
\begin{eqnarray} \label{UpperBound}
Re\{[1+L^{\ast}_{D_{q}}(j\omega)][1+L_{qq}(j\omega,\rho)]\}
\nonumber\\ \leq |[1+L^{\ast}_D(j\omega)][1+L_{qq}(j\omega,\rho)]|
\end{eqnarray}
Then, by combining (\ref{UpperBound}) and (\ref{eq:mimo_approx}) (and noting that $|1+L_{D_{q}}|=|1+L^*_{D_{q}}|$), one obtains 				
\begin{eqnarray}
\big|W_{1_{q}}(1+M_{qq} \jo)\big| + \big | W_{2_{q}}N_{qq} \jo\big| \nonumber\\ - |1+L_{qq}(\jo)|<0 \nonumber\\
 \forall \omega \: \mbox{ for }q=1,\ldots,n_o
\end{eqnarray}
The above equation can be rearranged and expressed as follows:
\begin{eqnarray}\label{eq:rob_proof}
\frac{|W_{1_{q}}(1+M_{qq}\jo)| + |W_{2_{q}}N_{qq}\jo| }{|1+L_{qq}(\jo|} <1 \nonumber\\
 \forall \omega \: \mbox{ for }q=1,\ldots,n_o 
\end{eqnarray}
Since $M_{qq}$ and $N_{qq}$ are the $q-th$ diagonal elements of $\vec{H}(s)\vec{C}(s,\rho)$ and $\vec{P}(s)\vec{C}(s,\rho)$ in (\ref{eq:sens_mimo}), respectively, it can be seen that (\ref{eq:rob_proof}) leads directly to (\ref{eq:mimo_hinf}).
\end{proof}

In order to fully decouple the MIMO system, a controller must be designed such that the off-diagonal elements of the open-loop transfer function matrix are equal to zero.
%However, decoupling the MIMO system will not necessarily generate the desired single-loop responses, since it is the diagonal elements of $\vec{L}(s,\rho)$ that represent the single-loop responses of the system. 
%Thus the objective is to effectuate decoupling while simultaneously optimize the diagonal elements to achieve the desired single-loop performance. 
The proposed method will be to define a diagonal open-loop transfer function matrix $\vec{L}_D(s)$, where the diagonal elements satisfy the desired performance for single loop systems. Therefore, by minimizing the objective function $\| \vec{L}(s,\rho)-\vec{L}_D(s) \|_{2}^{2}$, a controller can be designed to simultaneously  minimize the magnitudes of the off-diagonal elements of $\vec{L}(s,\rho)$ and drive the diagonal elements to be approximately equal to $L_{D_{q}}(s)$.

However, the resulting controller will stabilize the closed-loop system only if it is fully decoupled. In practice, with a finite order controller, it is not always possible to make the off-diagonal elements of  $\vec{L}(j\omega,\rho)$ equal to zero. In this case, the generalized Nyquist stability criterion should be used to guarantee the stability of the MIMO system. According to this theorem, the eigenvalues of the open-loop transfer function (\ref{eq:oltfmimo}) should not encircle the critical point. However, these eigenvalues are non-convex functions of the linear control parameters, which complicates the design process. A possible solution to this problem is to implement the Gershgorin band theorem in order to approximate the eigenvalues of $\vec{L}(j\omega,\rho)$. The Gershgorin bands represent disks centered at the diagonal elements of a matrix that include the eigenvalues.  For the open-loop transfer matrix $\vec{L}(j\omega,\rho)$, the radius of these disks are computed by: 
\begin{equation}
r_{q}(\omega,\rho)=\sum_{p=1,p\neq q}^{n_o} |L_{qp}(j\omega,\rho)| 
\end{equation}
where $L_{qp}(j\omega,\rho)$ represents the $qp$-th element of $\vec{L}(j\omega,\rho)$. Note that $r_{q}(\omega,\rho)$ is convex with respect to the control parameter $\rho$. The closed-loop stability of the MIMO system is guaranteed if these disks do not encircle the critical point. This precondition leads to the following theorem:
%This condition can be approximated with a convex constraint as it is shown in (\cite{GKL10b}).

\begin{theorem} 
\label{rob_stab}
Given the open loop transfer function matrix $\vec{L}\jo$, the linearly parameterized controller (\ref{eq:mimo_con}) stabilizes the closed-loop system if
\begin{eqnarray} \label{eq:gersh_con}
|r_{q}(j\omega,\rho)[1+L_{D_{q}}(j\omega)]|-\Psi_{q}(\rho,\omega)<0 \nonumber\\
\forall \omega \; \mbox{ for }q=1,\ldots,n_o
\end{eqnarray}
\end{theorem}
\begin{proof} 
%Since the real part of a complex number is less than or equal to its magnitude, we have
%\begin{eqnarray} \label{eq:r_lt_m}
%Re\{[1+L^{\ast}_{D_{q}}(j\omega)][1+L_{qq}(j\omega,\rho)]\}
%\nonumber\\ \leq |[1+L^{\ast}_D(j\omega)][1+L_{qq}(j\omega,\rho)]|
%\end{eqnarray}
By combining the constraint in (\ref{eq:gersh_con}) and (\ref{UpperBound}) (and noting that $|1+L_{D_{q}}|=|1+L^*_{D_{q}}|$), one obtains 				
\begin{eqnarray} \label{eq:gersh_stab}
|r_{q}\jo | < |1+L_{qq}\jo | \nonumber\\
 \forall \omega \: \mbox{ for }q=1,\ldots,n_o
\end{eqnarray}
The constraint in (\ref{eq:gersh_stab}) guarantees that the disk with radius $r_q\jo$ centered at $L_{qq}\jo$ does not encircle the critical point $(-1+j0)$, and thus the system remains stable for all $\omega$.%\footnote{A more general proof for unstable systems is given in \cite{GKL10b}.}.
\end{proof}

\subsection{Primary controller design}
In designing the controller $\vec{C}(s,\rho)$ for the MIMO SP, one must consider all of the possible combinations of the uncertain delay parameters $\tau_{qp}$.  Suppose that the cardinality of  $\tau_{qp}$ is $\beta_{qp}$. Then the total number of possible combinations that must be considered in the design of the controller is given by the rule of product,
\begin{align}
&\hspace{1cm} m=\prod \beta_{qp} \nonumber \\
&\forall \;\; q=1,\ldots,n_o;\;p=1,\ldots,n_i
\end{align}
If the number of uncertainties are equal for each $\tau_{qp}$ (i.e., $\beta_{qp}=\beta_{pq}=\beta\; \forall \; \{p,q\}$), then the total number of combinations will be $m=\beta^{n_o n_i}$. By combining the constraints presented in \thref{rob_per} and \thref{rob_stab}, one can define the following optimization problem for the multimodel system:
\begin{align}\label{eq:long_con}
&\hspace{2cm} \min_\rho \sum_{c=1}^{m} \sum_{k=1}^N \|\mathbf{L}_c(j\omega_k,\rho)-\mathbf{L}_{D_{c}}(j\omega_k)\|_F \nonumber\\
&\mbox{ Subject to: } \nonumber\\
&|r_{q_{c}}(j\omega_k,\rho)[1+L_{D_{q_{c}}}(j\omega_k)]|-\Psi_{q_{c}}(\rho,\omega_k)<0 \nonumber\\
&
\{|W_{1_{q_{c}}}(j\omega_k)[1+M_{qq_{c}}(j\omega_k,\rho)]|+ \nonumber \\
&|W_{2_{q_{c}}}(j\omega_k)N_{qq_{c}}(j\omega_k,\rho)|\} 
|1+L_{D_{q_{c}}}(j\omega_k)| \nonumber \\ &-\Psi_{q_{c}}(\rho,\omega_k)<0 \nonumber\\
&\mbox{for } k=1,\ldots,N;\;  q=1,\ldots,n_o; \; c=1,\ldots,m
\end{align}
where 
\begin{align*}
\Psi_{q_{c}}(j\omega_k,\rho)&=R_e\{[1+L^*_{D_{q_{c}}}(j\omega_k)][1+L_{qq_{c}}(j\omega_k,\rho)]\} \\
M_{qq_{c}}(j\omega_k,\rho)&=\sum_{z=1}^{n_o} G_{qz_{c}}(j\omega_k)(1-e^{-j\omega_k \zeta_{qz_{c}}})C_{zq_{c}}(j\omega_k,\rho) \\
N_{qq_{c}}(j\omega_k,\rho)&=\sum_{z=1}^{n_o} P_{qz_{c}}(j\omega_k)C_{zq_{c}}(j\omega_k,\rho)
\end{align*}
and $\|\cdot\|_{F}$ is the Frobenius norm. The objective function in (\ref{eq:long_con}), which is an approximation of the 2-norm,  is convex with respect to the controller parameters $\rho$. Note that the first inequality shows that the Gershgorin bands do not encircle the critical point and so the MIMO system remains stable even if it is not fully decoupled. The second inequality guarantees the robust performance for the SISO subsystems of the decoupled MIMO system. %Notice that $M_{qq_{c}}$, $N_{qq_{c}}$, and $\Psi_{q_{c}}$ represent the $c$-th models defined in \thref{rob_per}.

%It should be noted that the number of frequency points $N$ depends on the number of optimization variables of the particular problem. A scenario approach in selecting the minimum amount of frequency points was thoroughly discussed in \cite{GKL10b}. It is worth to reiterate the result; the number of frequency points $N$ should be chosen such that
%\begin{equation} \label{eq:freq_point}
%N \geq \frac{1}{\epsilon} \left(\ln \frac{1}{\eta}+n-1+\sqrt{2(n-1) \ln\frac{1}{\eta}}\right)
%\end{equation} 
%where the \textit{violation parameter} $\epsilon \in (0,1)$ and the \textit{confidence parameter} $\eta \in (0,1)$.

\section{Industrial Case Studies}
\label{sec:4}
The following examples will demonstrate the effectiveness of the proposed method for several industrial processes proposed in literature.
\subsection{Case 1 - SP with fixed time delays} \label{ex:1}
In \cite{GKL10b}, the proposed method was applied to a unity feedback MIMO system with fixed time delays. The plant model is represented by a $2 \times 2$ interactive chemical process which is used in industrial applications, and was defined as:
\begin{align} \label{eq:plant}
\renewcommand{\arraystretch}{2.2}
\mathbf{P}(s)&=
\begin{bmatrix}
         G_{11}(s)e^{-6s} & G_{12}(s)e^{-10s}\\
         G_{21}(s)e^{-12s} & G_{22}(s)e^{-8s}
\end{bmatrix} \nonumber \\
&=
\begin{bmatrix}
         \dfrac{10e^{-6s}}{8s+1} & \dfrac{5e^{-10s}}{30s+1}\\[1em]
         \dfrac{-8e^{-12s}}{40s+1} & \dfrac{2e^{-8s}}{10s+1}
\end{bmatrix}
\end{align}
where the time scale is defined in minutes. The elements $G_{qp}(s)$ for $q=1,2$ and $p=1,2$ represent the strictly proper delay-free transfer functions in $\mathbf{G}_n(s)$. A relative-gain-array (RGA) analysis confirms that the system is not diagonally dominant.

Since the time delay parameters are fixed for this process, the nominal time-delayed plant model $\mathbf{P}_n(s)$ will be chosen to be equal to $\mathbf{P}(s)$. In this manner, the open loop transfer function will be $\mathbf{L}(s,\rho)=\mathbf{G}_n(s)\mathbf{C}(s,\rho)$. The performance and uncertainty filters chosen for this case will be identical to those in \cite{GKL10b},
\begin{equation}
W_{1_{q}}=0.5 \quad , \quad W_{2_{q}}=0.5\left(\frac{2s+1}{s+1}\right) \qquad q=1,2
\end{equation}
For comparative purposes, a PI MIMO controller will be designed for this process. Thus the linearly parameterized controller will posses the following matrix form:
\begin{equation}
\renewcommand{\arraystretch}{1.3}
\vec{C}(s,\rho)=
\begin{bmatrix}
[\rho_{11_{1}} \;\; \rho_{11_{2}}]\vec{\phi}^T(s) & \;\; [\rho_{12_{1}} \;\; \rho_{12_{2}}]\vec{\phi}^T(s) \\
[\rho_{21_{1}} \;\; \rho_{21_{2}}]\vec{\phi}^T(s) & \;\; [\rho_{22_{1}} \;\; \rho_{22_{2}}]\vec{\phi}^T(s)
\end{bmatrix}
\end{equation}
where $\vec{\phi}(s)=\left[1 \;\;\;\; 1/s\right]$.
Additionally, the desired diagonal open-loop transfer function $\mathbf{L}_D(s)$ will be chosen as simple integrators with time constants equal to 30 minutes (i.e., $\vec{L}_D(s)=(\sfrac{1}{30s})\vec{I}$). The optimization problem in (\ref{eq:long_con}) can now be solved by repeating the stability constraints for each $\omega_k$. 
%Since the PI MIMO controller possesses 8 optimization variables (i.e., $n=8$), and choosing $\eta=\epsilon=0.1$, the inequality in (\ref{eq:freq_point}) suggests that a minimum of $N=150$ frequency points should be selected for evaluation. 
The frequency grid will be chosen to be between $10^{-2}$ and $10$ rad/min with $N=150$ equally spaced points. The PI MIMO controller obtained from optimization is:
$$
\renewcommand{\arraystretch}{1.3}
\mathbf{C}(s)=
\begin{bmatrix}
\dfrac{0.03289s + 0.001272}{s} & \dfrac{-0.03511s - 0.00311}{s} \\[0.4em]
\dfrac{0.05056s + 0.004511}{s} & \dfrac{0.2128s + 0.006133}{s}
\end{bmatrix}
$$
Fig. \ref{fig:comp} displays the closed loop response of the system with the controller obtained in \cite{GKL10b} and with the controller obtained with the SP. It can be seen that the controller for the SP produces no overshoot and asymptotically decouples the system much faster. Note that if the time constant of the desired open-loop transfer function matrix is decreased to 5 minutes, the rise and settling time of the system response is significantly improved.

\begin{figure*}
\centering
\psfrag{tit1}{\hspace{-0.45cm} \tiny From $x_1$}
\psfrag{tit2}{\hspace{-0.45cm} \tiny From $x_2$}
\psfrag{tit3}{\hspace{-0.45cm} \tiny From $x_1$}
\psfrag{tit4}{\hspace{-0.45cm} \tiny From $x_2$}
\psfrag{im1}{\hspace{-0.3cm} \raisebox{0.1cm}{\tiny To $y_1$}}
\psfrag{im2}{\hspace{-0.3cm} \raisebox{0.1cm}{\tiny To $y_1$}}
\psfrag{im3}{\hspace{-0.3cm} \raisebox{0.1cm}{\tiny To $y_2$}}
\psfrag{im4}{\hspace{-0.3cm} \raisebox{0.1cm}{\tiny To $y_2$}}
\psfrag{re}{\hspace{-0.7cm} \raisebox{-0.08cm}{\tiny Time (minutes)}}
\hspace*{-0.3cm}\includegraphics[width=0.85\textwidth]{pics/comp_ld_2.eps}
\caption{Closed loop comparison between time delayed MIMO system with unity feedback and time delayed MIMO SP: unit step reference signal (black, dash), response with system proposed in \cite{GKL10b} (red, solid), response with SP and with $diag \left(\mathbf{L}_D(s)\right)=\frac{1}{30s}$ (blue, solid), response with SP and with $diag \left(\mathbf{L}_D(s)\right)=\frac{1}{5s}$ (green, solid).}
\label{fig:comp}
\end{figure*}

\subsection{Case 2 - SP with uncertain time delays} \label{ex:2}
The proposed optimization problem will now be applied to an uncertain time-delayed MIMO SP. Consider the $2 \times 2$ plant process $\mathbf{P}(s)$ ($\mbox{i.e., }c=1$) that was analyzed in Case (1). The time delays for this plant will now possess uncertain values that will belong to a set. This plant will now be represented as follows:
\begin{equation}\label{eq:uncert_plant}
\renewcommand{\arraystretch}{2.2}
\vec{P}(s)=
\begin{bmatrix}
         \dfrac{10e^{-\tau_{11}s}}{8s+1} & \dfrac{5e^{-\tau_{12}s}}{30s+1}\\[0.6em]
         \dfrac{-8e^{-\tau_{21}s}}{40s+1} & \dfrac{2e^{-\tau_{22}s}}{10s+1}
\end{bmatrix}
\end{equation}
where the time delays $\tau_{qp}$ possess values in the sets:
\begin{equation}\label{eq:mimo_un}
\tau_{11}=\{3,9\} \quad \tau_{12}=\{7,13\} \quad
\tau_{21}=\{9,15\} \quad \tau_{22}=\{5,11\}
\end{equation}
The nominal model  is the same as defined in (\ref{eq:plant}).
%\begin{align}
%\renewcommand{\arraystretch}{2.2}
%\vec{P}_n(s)&=
%\begin{bmatrix}
%         G_{11}(s)e^{-6s} & G_{12}(s)e^{-10s}\\
%         G_{21}(s)e^{-12s} & G_{22}(s)e^{-8s}
%\end{bmatrix} \nonumber\\
%&=
%\begin{bmatrix}
%         \frac{10e^{-6s}}{8s+1} & \frac{5e^{-10s}}{30s+1}\\[1em]
%         \frac{-8e^{-12s}}{40s+1} & \frac{2e^{-8s}}{10s+1}
%\end{bmatrix}
%\end{align}
Again, the elements $G_{qp}(s)$ for $q=1,2$ and $p=1,2$ represent the strictly proper delay-free transfer functions in $\vec{G}_n(s)$. The performance and uncertainty filters chosen for this example will be identical to those in section (\ref{ex:1}). The desired diagonal open-loop transfer function $\vec{L}_D(s)$ will be chosen as simple integrators with time constants equal to 7 minutes (i.e., $\vec{L}_D(s)=(\sfrac{1}{7s})\vec{I}$).

%Comment out RGA analysis
\iffalse
In order to observe the interactions of this process, the relative gain array (RGA), defined as $\Lambda[\Gamma]=\Gamma\ast (\Gamma^{-1})^T$ (where the symbol $\ast$ denotes element wise multiplication), can be used to analyze the coupling affects between each pairing of the elements in $\vec{P}_n(s)$. The frequency dependent RGA of $\vec{P}_n(s)$ is shown in Fig. \ref{fig:RGA}. 
\begin{figure}[H]
\centering
\psfrag{omega}{\hspace{-0.4cm} \raisebox{-0.2cm}{\scriptsize $\omega \; \left[\frac{rad}{min}\right]$}}
\psfrag{RGA}{\hspace{-0.7cm} \scriptsize $\Lambda [\vec{P}_n(j\omega)]$}
\centerline{\includegraphics[scale=0.11]{pics/RG.eps}}
\caption{RGA plot of $\vec{P}_n(s)$: diagonal elements of $\Lambda [\vec{P}_n(j\omega)]$ (blue, solid), off diagonal elements of $\Lambda [\vec{P}_n(j\omega)]$ (red, solid).}
\label{fig:RGA}
\end{figure}
The most severe interaction occurs when $\Lambda_{qp}=0.5$ for $q=1,2$ and $p=1,2$. This can be seen in Fig. \ref{fig:RGA} as the intersecting point of  all functions $\Lambda_{qp}$, which occurs at a frequency of approximately  0.0307 rad/min.
Consider the case when $s=0$ (steady state response to a step input). The RGA matrix for this case will be: 
\begin{equation}
\Lambda[\vec{P}_n(s)]\Big|_{s=0}=
\begin{bmatrix}
0.3333 & 0.6667 \\ 0.6667 & 0.3333
\end{bmatrix}
\end{equation}
Since $0< \Lambda_{qp} < 1$ for $p,q=1,2$, interactions do exist, and the system is coupled. The permuted identity matrix can also be computed as follows:
\begin{equation}
\lim_{k \to \infty} \Lambda^k[\vec{P}_n(s)]\Big|_{s=0} = \begin{bmatrix}
0.5 & 0.5\\0.5 & 0.5
\end{bmatrix}
\end{equation}
which confirms that the plant process is not diagonally dominant at steady state. 
\fi

For simplicity, a PI controller will be designed for this process. Note that in designing this controller, all possible combinations of the uncertainties in (\ref{eq:mimo_un}) must be considered. Therefore, since $\beta_{qp}=2 \; \forall \; \{p,q\}$, there will be a total of $m=2^4$ possible cases to consider. The optimization problem in (\ref{eq:long_con}) can now be solved by repeating the stability constraints for each combination of the uncertainties in (\ref{eq:mimo_un}). The frequency grid will be chosen to be between $10^{-2}$ and $10$ rad/min with $N=150$ equally spaced points. The PI MIMO controller obtained from the optimization problem is:
$$
\renewcommand{\arraystretch}{1.3}
\vec{C}(s)=
\begin{bmatrix}
\dfrac{0.06234s + 0.001464}{s} & \dfrac{-0.04803s - 0.005408}{s} \\[0.4em]
\dfrac{0.1585s + 0.0168}{s} & \dfrac{0.3113s + 0.005995}{s}
\end{bmatrix}
$$
Fig. \ref{fig:mimo1} displays the closed-loop MIMO response to a step input. Notice that with this controller, the MIMO process achieves robust performance while simultaneously decoupling the system. The Gershgorin bands are depicted in Fig. \ref{fig:mimo2} for the system possessing the largest delay time uncertainty ($\tau_{11}=9$, $\tau_{12}=13$, $\tau_{21}=15$, $\tau_{22}=11$). The red and blue bands possess a radius of $|r_{q}(j\omega_k)|$ for $q=1,2$ and $k=1,\ldots,N$. 
\begin{figure*}
\centering
\psfrag{tit1}{\hspace{-0.45cm} \tiny From $x_1$}
\psfrag{tit2}{\hspace{-0.45cm} \tiny From $x_2$}
\psfrag{tit3}{\hspace{-0.45cm} \tiny From $x_1$}
\psfrag{tit4}{\hspace{-0.45cm} \tiny From $x_2$}
\psfrag{im1}{\hspace{-0.3cm} \raisebox{0.1cm}{\tiny To $y_1$}}
\psfrag{im2}{\hspace{-0.3cm} \raisebox{0.1cm}{\tiny To $y_1$}}
\psfrag{im3}{\hspace{-0.3cm} \raisebox{0.1cm}{\tiny To $y_2$}}
\psfrag{im4}{\hspace{-0.3cm} \raisebox{0.1cm}{\tiny To $y_2$}}
\psfrag{re}{\hspace{-0.7cm} \raisebox{-0.05cm}{\tiny Time (minutes)}}
\centerline{\includegraphics[width=0.85\textwidth]{pics/test.eps}}
\caption{MIMO response to a unit step input: reference signal (black,dash), the remaining $\Omega=16$ closed-loop responses are for all possible combinations of the time delay parameters in (\ref{eq:mimo_un}).}
\label{fig:mimo1}
\end{figure*}
Notice how the Gershgorin bands never intersect with the performance filter centered at $(-1+j0)$. This proves that the MIMO system is stable, robust, and satisfies the optimization criterion in (\ref{eq:long_con}).
%\vspace{0.7cm}
\begin{figure}
%\vspace{-0.7cm}
\centering
\psfrag{R}{\hspace{-0.5cm} \raisebox{-0.15cm}{\small $\Re_e \{Z(j\omega) \}$}}
\psfrag{Y}{\hspace{-0.7cm} \small $\Im_m \{Z(j\omega) \}$}
\hspace*{-0.3cm}\includegraphics[scale=0.5]{pics/gersh.eps}
\caption{Gershgorin bands centered at $L_{qq}$ with the largest time delay combination in (\ref{eq:mimo_un}): performance filter with $|W_{1_{q}}|=0.5$ (green circle), Gershgorin bands corresponding to $q=1$ (blue circles), Gershgorin bands corresponding to $q=2$ (red circles). Note that $Z(j\omega)$ is simply the complex number representation of each circle in the plot.}
\label{fig:mimo2}
\end{figure}

\subsection{Case 3 - The Shell control problem} \label{ex:3}
The multivariable heavy oil fractionator (known as the Shell process) is a highly coupled system which is predominantly used in petrochemical processes. Efficient control methods are essential for attaining viable production rates, minimizing energy consumption, and reducing the overall operating costs. These types of systems are difficult to control for two reasons: the system interactions are strong, and the large time delays that are inherent to the system dynamics.

Consider the $2 \times 3$ industrial Shell problem in \cite{RC06}, 
\begin{align}\label{eq:shell_nom}
\renewcommand{\arraystretch}{2.2}
\vec{P}_n(s)&=
\begin{bmatrix}
         G_{11}(s)e^{-81s} & G_{12}(s)e^{-84s} & G_{13}(s)e^{-81s}\\
         G_{21}(s)e^{-54s} & G_{22}(s)e^{-42s} & G_{32}(s)e^{-45s}
\end{bmatrix} \nonumber\\
&=
\begin{bmatrix}
         \dfrac{4.05e^{-81s}}{50s+1} & \dfrac{1.77e^{-84s}}{60s+1} & \dfrac{5.88e^{-81s}}{50s+1}\\[1em]
         \dfrac{5.39e^{-54s}}{50s+1} & \dfrac{5.72e^{-42s}}{60s+1} & \dfrac{6.9e^{-45s}}{40s+1}
\end{bmatrix}
\end{align}
where the time scale is defined in minutes. Note that (\ref{eq:shell_nom}) is represented as the nominal model of the process. 
It should be noted that the controller outputs $[u_1(t) \; u_2(t) \; u_3(t)]^T$ should be within the saturation bounds of the physical system : $[-0.5 \, , \, 0.5]$ (see \cite{VWG02}). 
The elements $G_{qp}(s)$ for $q=1,2$ and $p=1,2,3$ represent the strictly proper delay-free transfer functions in $\vec{G}_n(s)$. Now consider the case when the time delays are varied to $+20\%$ of their nominal values shown in (\ref{eq:shell_nom}). As with the previous example, the plant $\vec{P}(s)$ can be represented as a system with uncertain time delays. Since $\beta_{qp}=2 \; \forall \; \{p,q\}$, there will be a total of $m=2^6=64$ possible cases to consider.%\footnote{Note that the nominal time delays are also being considered in the controller design process, since it is desired that the controller remains robust for all combinations of perturbed time delays.}.

For comparative purposes, a PI controller will be designed for this process. Thus the controller $\vec{C}(s,\rho)$ will be a $3 \times 2$ transfer function matrix with $n=12$ optimization parameters $\rho$. 
%By selecting $\eta=\epsilon=0.1$, the inequality in (\ref{eq:freq_point}) suggests that a minimum of $N=205$ frequency points should be selected for evaluation. 
The frequency grid will be chosen to be between $10^{-4}$ and $10$ rad/min with $N=200$ equally spaced points (since the frequencies of interest of the open-loop system lie within this range). The desired diagonal open-loop transfer function matrix will be chosen as simple integrators with bandwidths that are approximately $20\%$ greater than the open-loop system bandwidths (i.e., $\vec{L}_D(s)=(\sfrac{1}{35s})\vec{I}$). By solving the optimization problem in (\ref{eq:long_con}) for each combination of the uncertainties (i.e., $\{\tau_{11},\ldots,\tau_{qp}\} \; \forall \; \{p,q\}$ where $\tau_{qp} \in \{\zeta_{qp},1.2\zeta_{qp}\} $), one obtains the following PI controller
$$
\renewcommand{\arraystretch}{1.3}
\vec{C}(s)=
\begin{bmatrix}
\dfrac{0.2053s + 0.004997}{s} & \dfrac{-0.01315s - 0.00146}{s} \\[0.4em]
\dfrac{-0.6735s - 0.01008}{s} & \dfrac{0.4977s + 0.008098}{s} \\[0.4em]
\dfrac{0.2839s + 0.004451}{s} & \dfrac{-0.1041s - 0.001432}{s}
\end{bmatrix}
$$
Fig. \ref{fig:shell_no_del} displays the closed-loop step response of the SP for the nominal delay case, while Fig. \ref{fig:shell_del} displays the response with the worst case delay (the case where $\tau_{qp}=1.2\zeta_{qp} \; \forall \; \{p,q\}$).

\begin{figure*}[]
\centering
\psfrag{tit1}{\hspace{-0.45cm} \scriptsize From $x_1$}
\psfrag{tit2}{\hspace{-0.45cm} \scriptsize From $x_2$}
\psfrag{tit3}{\hspace{-0.45cm} \scriptsize From $x_1$}
\psfrag{tit4}{\hspace{-0.45cm} \scriptsize From $x_2$}
\psfrag{im1}{\hspace{-0.3cm} \raisebox{0.1cm}{\scriptsize To $y_1$}}
\psfrag{im2}{\hspace{-0.3cm} \raisebox{0.1cm}{\scriptsize To $y_1$}}
\psfrag{im3}{\hspace{-0.3cm} \raisebox{0.1cm}{\scriptsize To $y_2$}}
\psfrag{im4}{\hspace{-0.3cm} \raisebox{0.1cm}{\scriptsize To $y_2$}}
\psfrag{re}{\hspace{-0.7cm} \raisebox{-0.05cm}{\scriptsize Time (minutes)}}
\centerline{\includegraphics[width=0.7\textwidth]{pics/Rob_comp_LD35_1.eps}}
\caption{MIMO SP closed-loop response to a unit step input with $\tau_{qp}=\zeta_{qp} \; \forall \; \{p,q\}$: reference signal (black,dash), output response with the proposed optimization method (blue, solid), output response with the proposed method in \cite{RC06} (red, solid), which is based on the ``squared down" method.}
\label{fig:shell_no_del}
\end{figure*}

\begin{figure*}[]
\centering
\psfrag{tit1}{\hspace{-0.45cm} \scriptsize From $x_1$}
\psfrag{tit2}{\hspace{-0.45cm} \scriptsize From $x_2$}
\psfrag{tit3}{\hspace{-0.45cm} \scriptsize From $x_1$}
\psfrag{tit4}{\hspace{-0.45cm} \scriptsize From $x_2$}
\psfrag{im1}{\hspace{-0.3cm} \raisebox{0.1cm}{\scriptsize To $y_1$}}
\psfrag{im2}{\hspace{-0.3cm} \raisebox{0.1cm}{\scriptsize To $y_1$}}
\psfrag{im3}{\hspace{-0.3cm} \raisebox{0.1cm}{\scriptsize To $y_2$}}
\psfrag{im4}{\hspace{-0.3cm} \raisebox{0.1cm}{\scriptsize To $y_2$}}
\psfrag{re}{\hspace{-0.7cm} \raisebox{-0.05cm}{\scriptsize Time (minutes)}}
\centerline{\includegraphics[width=0.7\textwidth]{pics/Rob_comp_LD35_2.eps}}
\caption{MIMO SP closed-loop response to a unit step input with $\tau_{qp}=1.2\zeta_{qp} \; \forall \; \{p,q\}$: reference signal (black,dash), output response with the proposed optimization method (blue, solid), output response with the proposed method in \cite{RC06} (red, solid), which is based on the ``squared down" method.}
\label{fig:shell_del}
\end{figure*}
From Fig. \ref{fig:shell_no_del} and Fig. \ref{fig:shell_del}, it can be observed that the purposed method in this paper produces improved SISO subsystem performance with minimal overshoot. In addition, the decoupling transients are significantly reduced for both the nominal and worst case output responses. Fig. \ref{fig:shell_in} displays the controller outputs of the system. 
\begin{figure*}[]
\centering
\psfrag{im1}{\hspace{-0.3cm} \raisebox{0.1cm}{\scriptsize$u_1(t)$}}
\psfrag{im2}{\hspace{-0.3cm} \raisebox{0.1cm}{\scriptsize$u_2(t)$}}
\psfrag{im3}{\hspace{-0.3cm} \raisebox{0.1cm}{\scriptsize$u_3(t)$}}
\psfrag{re}{\hspace{-0.7cm} \raisebox{-0.2cm}{\tiny Time (minutes)}}
\centerline{\includegraphics[width=0.9\textwidth]{pics/Rob_comp_LD35_in2.eps}}
\caption{MIMO SP controller output response to a unit step reference: Controller output response of proposed method with $\tau_{qp}=\zeta_{qp}$ (blue, solid), controller output response of ``squared down" method in \cite{RC06} with $\tau_{qp}=\zeta_{qp}$ (red, solid), controller output response of proposed method with $\tau_{qp}=1.2\zeta_{qp}$ (blue, dash), controller output response of ``squared down" method in \cite{RC06} with $\tau_{qp}=1.2\zeta_{qp}$ (red, dash)}
\label{fig:shell_in}
\end{figure*}

\section{Conclusion}
\label{sec:5}
This paper has proposed a new method for computing multivariable SP controllers with $H_\infty$ performance. The method is based on a convex approximation of the $H_\infty$ robust performance criterion in the Nyquist diagram. This approximation relies on the choice of a desired open-loop transfer function $\vec{L}_D$ for the dead-time free model of the plant. With a linearly parameterized controller, one possesses the flexibility to design PI, PID, or higher order controllers for a system. For the industrial processes considered in this paper, the proposed method has been proven to be robust; $H_{\infty}$ performance was achieved for MIMO systems with both multiplicative and time delay uncertainties. The solution to the optimization problem generates a controller such that a system becomes decoupled and simultaneously optimizes the single-loop performances of the SISO subsystems.

%The controller design examples illustrated in this paper considered a finite amount of discrete values to represent the uncertainties in the time delays. However, the proposed optimization methods can be applied for a system(s) with $\alpha$ number of uncertainties within a specified range, where $\{\exists\alpha \in \mathbb{Z}^+ | \; 0<\alpha<\infty \} $.

%\appendix[Proof of Equations] %Put your appendix here
\iffalse

%\section*{Acknowledgment}
%\addcontentsline{toc}{section}{Acknowledgment}
%Your acknowledgments go here.
\begin{thebibliography}{99.}%
% and use \bibitem to create references.
%
% Use the following syntax and markup for your references if
% the subject of your book is from the field
% "Mathematics, Physics, Statistics, Computer Science"
%
% Contribution
%\bibitem{Bro79} C. B. Brosilow. The structure and design of Smith
%predictors from the viewpoint of inferential control.
%In Proceedings of Joint American Control Conference,
%Denver, Colorado, 1979.
%
\bibitem{VK13} V. De Oliveira, A. Karimi. Robust Smith predictor design for time-delay systems with $H_\infty$ performance.  IFAC Joint Conference, Grenoble, France, February 4-6, 2013.
%
%\bibitem{Dep85} A. M. De Paor. A modified Smith predictor and controlled
%for unstable processes with time delay. International
%Journal of Control, 41(4):1025–1036, 1985.
%
\bibitem{DFT92} C. J. Doyle, B. A. Francis, and A. R. Tannenbaum.
Feedback Control Theory. Mc Millan, New York, 1992.
%
\bibitem{GKL10a} G. Galdos, A. Karimi, and R. Longchamp. Robust controller
design by convex optimization based on finite
frequency samples of spectral models. In 49th IEEE
Conference on Decision and Control, Atlanta, USA,
2010a.
%
\bibitem{GKL10b} G. Galdos, A. Karimi, and R. Longchamp. $H_{\infty}$ controller
design for spectral MIMO models by convex optimization.
Journal of Process Control, 20(10):1175 – 1182,
2010b.
%
%\bibitem{Hag92} T. Hagglund. A predictive PI controller for processes with
%long dead times. IEEE Control Systems Magazine, 12
%(1):57–60, 1992.
%
%\bibitem{HWC95} C. C. Hang, Q. Wang, and L. S. Cao. Self-tuning Smith
%predictors for processes with long dead time. International
%journal of adaptive control and signal processing,
%9(3):255–270, 1995.
%
%\bibitem{KG10} A. Karimi and G. Galdos. Fixed-order H∞ controller design
%for nonparametric models by convex optimization.
%Automatica, 46(8):1388–1394, 2010.
%
%\bibitem{Kay01} I. Kaya. Tuning Smith predictors using simple formulas
%derived from optimal responses. Industrial and engineering
%chemistry research, 40(12):2654–2659, 2001.
%
\bibitem{LHW08} C. Lai, P. Hsu, and B. Wang. Design of the adaptive Smith predictor for the time-varying network control system. SICE Annual Conference, The University Electro-Communications, Japan, p. 2933 - 2938, 2008.
%
%\bibitem{LLSL99} D. Lee, M. Lee, S. Sung, and I. Lee. Robust PID tuning
%for Smith predictor in the presence of model uncertainty.
%Journal of Process Control, 9(1):79–85, 1999.
%
%\bibitem{LCGZ05} T. Liu, Y. Z. Cai, D. Y. Gu, and W. D. Zhang. New
%modified Smith predictor scheme for integrating and
%unstable processes with time delay. IEE Proceedings-
%Control Theory and Applications, 152(2):238–246, 2005.
%
%\bibitem{MA98} S. Majhi and D. P. Atherton. A new Smith predictor and
%controller for unstable and integrating processes with
%time delay. In Proceedings of the 37th IEEE Conference
%on Decision and Control, pages 1341–1345, 1998.
%
\bibitem{MZ00} G. Meinsma and H. Zwart. On H∞ control for dead-time
systems. IEEE Transactions on Automatic Control, 45
(2):272–285, 2000.
%
\bibitem{Mir03} L. Mirkin. On the extraction of dead-time controllers
and estimators from delay-free parametrizations. IEEE
Transactions on Automatic Control, 48(4):543–553,
2003.
%
\bibitem{NC00} J. E. Normey-Rico and E. F. Camacho. Multivariable generalised predictive controller based on the Smith predictor. IEEE Proceedings in Control Theory Applications, Vol. 147, No. 5, 2000.
%
\bibitem{NC07} J. E. Normey-Rico and E. F. Camacho. Control of deadtime
processes. Springer Verlag, 2007.
%
%\bibitem{NC09} J. E. Normey-Rico and E. F. Camacho. Unified approach
%for robust dead-time compensator design. Journal of
P%rocess Control, 19(1):38–47, 2009.
%
%\bibitem{Pal80} Z. J. Palmor. Stability properties of Smith dead-time compensator
%controllers. International Journal of Control,
32:937–49, 1980.
%
%\bibitem{Pal96} Z. J. Palmor. Time-delay compensation Smith predictor
%and its modifications. In W. Levine, editor, The Control
%Handbook. CRC Press, Boca Raton, FL, 1996.
%
%\bibitem{PB94} Z. J. Palmor and M. Blau. An auto-tuner for Smith dead
%time compensator. International Journal of Control, 60
%(1):117–135, 1994.
%
\bibitem{SBP09} R. S. Sanchez-Pena, Y. Bolea and V. Puig. MIMO Smith predictor: Global and structured robust performance analysis. Journal of Process Control 19:163-177, 2009.
%
%\bibitem{SS93} C. Santacesaria and R. Scattolini. Easy tuning of Smith
%predictor in presence of delay uncertainty. Automatica,
%29(6):1595–1597, 1993.
%
\bibitem{Sko} S. Skogestad and I. Postlethwaite. Multivariable Feedback Control; Analysis and Design. John Wiley and Sons, England, 1996.
%
\bibitem{Smi57} O. J. M. Smith. Closer control of loops with dead time.
Chemical Engineering Progress, 53(5):217–219, 1957.
%
\bibitem{ZL06} W. Zhang and C. Lin. Multivariable Smith Predictors Design for Nonsquare Plants. IEEE Transactions on Control Systems Technology,
Vol. 14, No. 6, 2006.
%
\bibitem{Zho03a} Q. C. Zhong. On standard H∞ control of processes with a single delay. IEEE Transactions on Automatic Control,
48(6):1097–1103, 2003.
%
%\bibitem{ZhoDoy} K. Zhou and J. Doyle. Essentials of Robust Control. Prentice-Hall, Upper Saddle River, New Jersey, USA, 1998.
%
\bigskip

\end{thebibliography}
\fi

%\begin{IEEEbiographynophoto}
%Author1 Biography
%\end{IEEEbiographynophoto}
%\smallskip{}
%\begin{IEEEbiographynophoto}
%Author2 Biography
%\end{IEEEbiographynophoto}

\bibliography{linear}

\end{document}

### 2017-02-11 Papers/PUBLISHED - RST Torsional System/INITIAL_SUBMISSION.tex
adding files to git (11/2/2017)

\documentclass[a4paper, 10pt, conference]{ieeeconf}
\IEEEoverridecommandlockouts  
\overrideIEEEmargins     
\bibliographystyle{IEEEtran}
\pdfminorversion=4

\usepackage{cite}
%\usepackage{mathptmx}       % selects Times Roman as basic font
\usepackage{helvet}         % selects Helvetica as sans-serif font
\usepackage{courier}        % selects Courier as typewriter font
\usepackage{type1cm}        % activate if the above 3 fonts are
                            % not available on your system
%
\usepackage{makeidx}         % allows index generation
\usepackage{graphicx}        % standard LaTeX graphics tool
%                             % when including figure files
\usepackage{multicol}        % used for the two-column index
\usepackage{times}
\usepackage{xfrac}
%\usepackage{mathabx}
\usepackage[thref]{ntheorem} % Uncomment this in Windows version
\usepackage{amsfonts}%
\usepackage{amssymb}%
\usepackage{color}
%\usepackage{import}
\usepackage{graphicx,psfrag}
\usepackage{float}
\usepackage[cmex10]{amsmath}
%\usepackage{amsthm} % Comment this in Windows version
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem*{remark}{Remark}
\newcommand{\jo}{(e^{-j\omega})}
\newcommand{\jok}{(e^{-j\omega_k})}
\newcommand{\jro}{(e^{-j\omega},\rho)}
\newcommand{\jrok}{(e^{-j\omega_k},\rho)}
%\renewcommand{\IEEEQED}{\IEEEQEDopen}
\renewcommand{\vec}[1]{\mathbf{#1}}
\newcommand{\hilight}[1]{\colorbox{yellow}{#1}}
%\DeclareRobustCommand*{\IEEEauthorrefmark}[1]{%
  %\raisebox{0pt}[0pt][0pt]{\textsuperscript{\footnotesize\ensuremath{#1}}}}

\title{\LARGE \bf A Data-Driven Approach in Designing RST Controllers with $H_{\infty}$ performance via Convex Optimization}

\author{Achille Nicoletti, Zlatko Emedi and Alireza Karimi % <-this % stops a space
\thanks{Automatic Control Laboratory,
Ecole Polytechnique F\'{e}d\'{e}rale de Lausanne (EPFL),
1015 Lausanne, Switzerland}%
%\thanks{$^{3}$ {\tt\small achille.nicoletti@epfl.ch}}%
%\thanks{$^{4}$ {\tt\small michele.martino@cern.ch}}%
\thanks{Corresponding author: {\tt\small alireza.karimi@epfl.ch}}%
}

\begin{document}

\maketitle
\thispagestyle{empty}
\pagestyle{empty}

\begin{abstract}
In this paper, a new method for designing robust fixed-order $\mathcal{H}_{\infty}$ discrete-time controllers is presented. The controller structure is a two-degree of freedom polynomial controller of the RST-type. A data-driven approach is implemented for the design process in order to capture the unmodeled dynamics that may exist with parametric models. The $\mathcal{H}_{\infty}$ robust performance condition can be represented by a set of convex constraints with respect to the parameters of the RST controllers. A convex optimization algorithm can then be implemented to obtain these parameters. The proposed method is applied to a multi-axis torsional system where the goal is to control the position of the disks with variable inertias.
\end{abstract}

\section{Introduction}
In many of today's complex industrial applications, it is difficult to model a process with extreme precision. For such processes, a high-order model is typically required to capture the dynamics of a system; however, high order models lead to high order controllers with numerical implementation problems.  Therefore, in practice, low-order models are preferred in order to simplify the controller design process. However, low-order models possess unmodeled dynamics that can hinder the performance of a controller. Robust controller design methods use the uncertainty models as weighting filters to ensure the stability and performance of the closed-loop system. This in turn increases the controller order which is equal to the order of the plant model and the uncertainty weighting filter. In data-driven methods, the plant model is represented by a set of data; thus there are no unmodeled dynamics and the controller order can be chosen independently of the plant model complexity.  The data-driven approach can be realized in two manners: using time-domain or frequency-domain data. In this paper, the frequency-domain approach will be utilized for the controller design scheme.

The field of frequency-domain controller design techniques continues to spark the interest of many researchers. In \cite{KNN13}, a controller is designed in the frequency-domain by considering a least-squares optimization approach; however, in this method, it is not evident on how to predefine the structure of a stabilizing controller. A data-driven design method that guarantees the stability of a closed-loop system by setting gain and phase margin constraints in the Nyquist diagram has been addressed in \cite{Sae13}. Despite the simplicity and advantages of this method, it cannot be applied to unstable plants. Moreover, the constraints are conservative and may lead to a controller that inhibits the system performance. %A learning algorithm to design a controller in the frequency-domain was examined in \cite{LWZ10}, though it is not clear how the robustness margins are defined. 
A robust frequency-domain control design method has been established in \cite{KNDB13}; this method, however, requires a solution to a non-linear optimization problem.

Robust control methods are continually addressed within the control system community. Many research papers and books have been devoted to developing new algorithms in designing robust controllers that reduce the conservatism associated with uncertainty modeling. Robust controller design methods belonging to the $\mathcal{H}_{\infty}$ control framework minimizes the $\mathcal{H}_{\infty}$ norm of a weighted closed-loop sensitivity function. An $\mathcal{H}_{\infty}$ loop-shaping method to design stabilizing controllers has been examined in \cite{YYH13}. However, a non-convex optimization algorithm is required to obtain a solution. Generally, it is desired to acquire a convex optimization problem since convex problems are computationally tractable. A convex approximation of the $\mathcal{H}_\infty$ criterion has been discussed in \cite{KG10} and \cite{KGL08} where convex constraints are imposed on the Nyquist diagram. The controller is linearly parameterized (the denominator is fixed) and a desired open loop transfer function is used to convexify the $\mathcal{H}_{\infty}$ constraints.  An extension to this method has been presented in \cite{KZ04}, where a single-input-single-output (SISO) controller is represented in a rational form (and thus allowing the numerator and denominator of a controller to be optimized separately). This method gives the necessary and sufficient conditions for the existence of a robust controller for systems represented by a frequency response function.

The RST controller structure is an effective discrete-time two-degree of freedom polynomial controller where the tracking and regulation characteristics of a closed-loop system can be formulated independently \cite{LZ06}. %The general $RST$ controller structure is shown in Fig.\ref{fig:rst_simp}. 
Various methods and applications of the RST controller design methodology have been addressed in \cite{BTA14}, \cite{LHM10}, \cite{KH11}, and \cite{MBH13}. However, in these previous applications, the controllers were devised based on the knowledge of the dynamic model of the physical system. A frequency domain approach in designing the RST controllers has been discussed in \cite{GKL11}. In this approach, a convex optimization algorithm was formulated by considering a convex approximation of the $\mathcal{H}_{\infty}$ criterion. However, in order to preserve convexity, this method required one of the controller terms ($R$) to be fixed a priori.

%\begin{figure}
%\centering
%\resizebox{1.0\columnwidth}{!}{\input{rst_simp.eps_tex}}
%\caption{RST controller structure}
%\label{fig:rst_simp}
%\end{figure}

The proposed method in this paper is an extension of \cite{GKL11} and \cite{KZ04}, where an RST controller will be designed by formulating a convex optimization problem in the frequency domain. In \cite{GKL11}, the controller $R$ was fixed with an integrator\footnote{Note that the variable names for $R$ and $S$ are interchanged in \cite{GKL11}}, while $S$ and $T$ where linearly parameterized. However, with the methodology presented in this paper, the $R$, $S$ and $T$ controllers can each be linearly parameterized, and thus introduces more degrees of freedom which improves the $\mathcal{H}_{\infty}$ performance. Moreover, new convex constraints are imposed in order to guarantee that the closed-loop system remains stable while attaining the desired tracking performance without the need to specify a desired open-loop transfer function.

This paper is organized as follows: In section (\ref{sec:2}), the class of models, controllers and control objectives are defined. Section (\ref{sec:3}) will discuss the control design methodology and stability conditions of the proposed method for the RST controller structure. Convex conditions will be formulated based on the $\mathcal{H}_{\infty}$ criterion. Section (\ref{sec:4}) will demonstrate the effectiveness of the method by applying the proposed design scheme to a multi-axis torsional system. Finally the concluding remarks are given in Section (\ref{sec:5}).

\textbf{Notation}: In order to avoid the risk of any confusion, the notation for the symbols employed in this paper will be defined here.
\begin{align*}
\mathbb{R} &: \ \mbox{the set of all real numbers.} \\
\mathbb{Z} &: \ \mbox{the set of all positive integers including zero.} \\
\mathcal{R}e\{\cdot \} &: \ \mbox{the real part of a complex variable.} \\
\mathcal{I}m\{\cdot \} &: \ \mbox{the imaginary part of a complex variable.} \\
a^{\top} &: \ \mbox{the transpose of the vector }a. \\
z &: \ \parbox[t]{18em}{variable used to represent the complex frequency domain of discrete-time systems.} \\
s &: \ \parbox[t]{18em}{variable used to represent the complex frequency domain of continuous-time systems.}
\end{align*} 
%\section{Notation and Preliminaries}
%Due to the nature of the equations asserted in this paper, it will be convenient express certain equations in a compact manner. A cascade of $q$ frequency response functions $A_1(e^{-j\omega})A_2(e^{-j\omega}) \cdots A_q(e^{-j\omega})$ will be denoted as $[A_1A_2 \cdots A_q](e^{-j\omega})$.

\section{Problem Formulation}
\label{sec:2}

\subsection{Class of models}
\label{sec:21}
Let us begin by considering the frequency response function (FRF) of a discrete-time SISO plant given as
\begin{equation}\label{eq:G_frf}
G(e^{-j\omega}) = N(e^{-j\omega}) M^{-1}(e^{-j\omega}), \qquad \forall \omega \in \Omega
\end{equation}
where $\Omega \in [0,\pi]$. $N(e^{-j\omega})$ and $M(e^{-j\omega})$ must be FRF's of bounded analytic functions outside the unit circle. For stable plants, a trivial choice is $N(e^{-j\omega})=G(e^{-j\omega})$ and $M(e^{-j\omega})=1$. For unstable plants, $N(e^{-j\omega})$ and $M(e^{-j\omega})$ can be obtained, in a data-driven setting, by considering the acquired data of a closed-loop system with a stabilizing controller. If $N(e^{-j\omega})$ represents the FRF of the transfer function from the reference input to the output, and $M(e^{-j\omega})$ represents the FRF of the transfer function from the reference input to the controller output, then the FRF of the plant model can be obtained as asserted in (\ref{eq:G_frf}).
%A discussion on how to formulate $N(e^{-j\omega})$ and $M(e^{-j\omega})$ for systems that are not BIBO stable can be found in \cite{KZ04}.

In general, a set $\mathcal{G}$ that represents a plant model containing $k$ FRF models can be defined:
\begin{equation}
\mathcal{G} = \{G_i(e^{-j\omega}); \quad i=1,\ldots,k; \quad \forall \omega \in \Omega\}
\end{equation} 
These FRF's can be determined by considering the frequency response of a parametric model or from a set of input/output data. For simplicity, one model from the set $\mathcal{G}$ will be considered, and the subscript $i$ will be omitted. However, in general, the design procedures outlined in this paper can be applied to the multi-model case. In section (\ref{sec:4}), the proposed method is applied on a torsional apparatus with multi-model uncertainty.

\subsection{Class of controllers}
The controller structure that will be considered will be of the RST-type, as shown in Fig.\ref{fig:rst}. The RST controllers are linearly parameterized in the variables $r_k$, $s_k$, and $t_k$; they are each polynomials in $z$ which can be expressed as:
\begin{alignat}{2}
R(z^{-1}) &= r_0 + r_1z^{-1} + \cdots + r_{n_r}z^{-n_r} \label{eq:Rc}\\
S(z^{-1}) &= 1 + s_1z^{-1} + \cdots + s_{n_s}z^{-n_s} \label{eq:Sc}\\
T(z^{-1}) &= t_0 + t_1z^{-1} + \cdots + t_{n_t}z^{-n_t} \label{eq:Tc}
\end{alignat}
where $\{n_r,n_s,n_t\} \in \mathbb{Z}$. These controllers can also be represented in vector form as $R(z^{-1},\rho)=\rho_R^\top \phi_R(z^{-1})$, $S(z^{-1},\rho)=\rho_S^\top \phi_S(z^{-1})$ and $T(z^{-1},\rho)=\rho_T^\top \phi_T(z^{-1})$, where 
\begin{alignat}{4}
\rho_R^\top &= [r_0,r_1,\ldots,r_{n_r}]; &&\quad \phi_R^\top(z^{-1}) &&&= [1,z^{-1},\ldots,z^{-n_r}]\\
\rho_S^\top &= [1,s_1,\ldots,s_{n_s}]; &&\quad \phi_S^\top(z^{-1}) &&&= [1,z^{-1},\ldots,z^{-n_s}]\\
\rho_T^\top &= [t_0,t_1,\ldots,t_{n_t}];  &&\quad \phi_T^\top(z^{-1}) &&&= [1,z^{-1},\ldots,z^{-n_t}]
\end{alignat}
%The purpose of parameterizing the controllers in this manner will become apparent in subsequent sections.
%For notation purposes, the dependency on the discrete-time frequency variable $z^{-1}$ will be omitted, and the dependency on the controller parameter $\rho$ will remain. 
\begin{figure}
\centering
\resizebox{1.0\columnwidth}{!}{\input{rst.eps_tex}}
\caption{RST controller structure}
\label{fig:rst}
\end{figure}

\subsection{Process Definitions}
\label{sec:23}
Since the design techniques introduced in this paper belong to the $\mathcal{H}_{\infty}$ framework, it is  appropriate to consider the various sensitivity functions associated with the controller structure shown in Fig.~\ref{fig:rst}. Some of the sensitivity functions for this process can be asserted as follows:
\begin{eqnarray}
\mathcal{S}_0(z^{-1},\rho)&=&\frac{M(z^{-1})S(z^{-1},\rho)}{\psi(z^{-1},\rho)}  \label{eq:S0}\\
\mathcal{S}_i(z^{-1},\rho)&=&\frac{N(z^{-1})S(z^{-1},\rho)}{\psi(z^{-1},\rho)} \\
\mathcal{T}(z^{-1},\rho)&=&\frac{N(z^{-1})T(z^{-1},\rho)}{\psi(z^{-1},\rho)} \label{eq:T} \\
\mathcal{U}(z^{-1},\rho)&=&\frac{M(z^{-1})T(z^{-1},\rho)}{\psi(z^{-1},\rho)} \label{eq:U}\\
\mathcal{V}(z^{-1},\rho)&=& -\frac{N(z^{-1})R(z^{-1},\rho)}{\psi(z^{-1},\rho)} \\
\mathcal{E}(z^{-1},\rho)&=&\frac{\psi(z^{-1},\rho) - N(z^{-1})T(z^{-1},\rho)}{\psi(z^{-1},\rho)} \label{eq:err}
\end{eqnarray}
where $\psi(z^{-1},\rho) = M(z^{-1})S(z^{-1},\rho)+N(z^{-1})R(z^{-1},\rho)$ and $\mathcal{S}_0(z^{-1},\rho)$ is the transfer function between $d_o$ and $y$, $\mathcal{S}_i(z^{-1},\rho)$ is the transfer function between $d_i$ and $y$, $\mathcal{T}(z^{-1},\rho)$ is the transfer function between $r$ and $y$, $\mathcal{U}(z^{-1},\rho)$ is the transfer function between $r$ and $u$, $\mathcal{V}(z^{-1},\rho)$ is the transfer function between $v$ and $y$, and $\mathcal{E}(z^{-1},\rho)$ is the transfer function between $r$ and the tracking error signal $r-y$. Note that all of the sensitivity functions are stable if the zeros of $\psi(z^{-1},\rho)$ lie within the unit circle. Based on the internal model principle, the controller may contain the disturbance model to achieve a zero steady-state error. Therefore, the controllers may be pre-multiplied with any arbitrary function that actualizes the desired performance. For example, if it is desired to reject a step disturbance at the output, then $S(z^{-1},\rho)$ can be pre-multiplied with $(1-z^{-1})$ (which represents the integral action of the controller).

\section{$\mathcal{H}_{\infty}$ Performance via Convex Optimization}
\label{sec:3}
\subsection{Preliminary Design Specifications}
Suppose that it is desired to shape a particular sensitivity function. Consider, for example, the sensitivity function from $d_o$ to $y$, expressed as $\mathcal{S}_0(z^{-1},\rho)$. Given a stable weighting filter $W_1$ with a bounded infinity norm, a necessary and sufficient condition for achieving nominal performance is given by \cite{Zho98}:
\begin{equation} \label{eq:inf1}
\| W_1\mathcal{S}_0 \|_{\infty}<\gamma
\end{equation}
where $\{ \gamma \in \mathbb{R} \mid \gamma > 0 \}$. In general, this condition can be extended to any of the sensitivity functions asserted in section (\ref{sec:23}). This condition can also be expressed as follows:
\begin{equation} \label{eq:inf_f}
 |W_1(e^{-j\omega}) \mathcal{S}_0(e^{-j\omega},\rho)| < \gamma; \quad \forall \omega \in \Omega
\end{equation}
For notation purposes, the dependency in $e^{-j\omega}$ will be omitted, and will only be reiterated when deemed necessary. The dependency on $\rho$ will continue to be highlighted. Notice that (\ref{eq:inf_f}) can also be written as
\begin{equation} \label{eq:circle}
\gamma^{-1}|W_1MS(\rho)| < |\psi(\rho)| ; \quad \forall \omega \in \Omega
\end{equation}
where $\psi(\rho) = MS(\rho) + NR(\rho)$. It is desired to minimize the upper bound $\gamma$ such that the $\mathcal{H}_{\infty}$ performance condition is satisfied. %This phenomenon is known as \textit{optimal $\mathcal{H}_{\infty}$ control}. 
Therefore, the following optimization problem can be considered:
\begin{equation} \label{eq:min1}
\begin{aligned}
& \underset{ \{\rho_R,\rho_S,\rho_T\} \in \mathbb{R}}{\text{minimize}}
& & \gamma  \\
& \text{subject to:} & & \gamma^{-1} |W_1MS(\rho)| < |\psi(\rho)|  \\ 
& & & \forall \omega \in \Omega
\end{aligned}
\end{equation}
Notice that (\ref{eq:min1}) is both a non-linear and non-convex optimization problem. 
\begin{remark}
Note that the controller $T(z^{-1},\rho)$ was not considered in the optimization problem (\ref{eq:min1}) since $\mathcal{S}_0(z^{-1},\rho)$ is independent of $T(z^{-1},\rho)$. One of the benefits of implementing the RST controller is that the tracking performance can be specified independently from the regulation requirements, and thus the controller $T(z^{-1},\rho)$ can be designed once $R(z^{-1},\rho)$ and $S(z^{-1},\rho)$ have been obtained. If tracking performance is crucial for the design, one may consider minimizing $\gamma$ for $\|W_2\mathcal{E} \| _{\infty}<\gamma$, where $W_2$ is also a stable transfer function with a bounded infinity norm. 
\end{remark}

\begin{figure}
\centering
\resizebox{0.8\columnwidth}{!}{\input{nxmy2.eps_tex}}
\caption{The $\mathcal{H}_{\infty}$ constraint in (\ref{eq:inf1}) can be represented as a circle in the complex plane. The constraint ensures that the circle will never encircle the origin for any frequency point in $\Omega$.}
\label{fig:circle}
\end{figure}
Consider a circle in the complex plane which is centered at $MS(\rho) + NR(\rho)$ and has radius $\gamma^{-1}|W_1MS(\rho)|$. The constraint in (\ref{eq:circle}) ensures that for any frequency point in $\Omega$, the circle associated with this frequency point will not encircle the origin. Figure \ref{fig:circle} displays the graphical interpretation of this condition. According to \cite{KZ04}, for each $\omega \in \Omega$ there exists a complex number $f(e^{-j\omega})$ which can rotate the disk in Fig.~\ref{fig:circle} such that it lays on the right hand side of the imaginary axis:
\begin{equation}\label{eq:real}
\mathcal{R}e\{Z(\rho) f(e^{-j\omega}) \} > 0; \quad \forall \omega \in \Omega
\end{equation}
where $Z(\rho) = \psi(\rho) - \gamma^{-1} |W_1MS(\rho)|$. In \cite{RM94}, it is shown that $f(e^{-j\omega})$ can be approximated arbitrarily well by the frequency response of a finite order transfer function if and only if $$[\psi(\rho) - \gamma_0^{-1}|W_1MS(\rho)|]^{-1}$$ is analytic in the right half plane for all $\gamma_0 > \gamma$. Based on (\ref{eq:real}) and on the results established in \cite{KZ04}, the following theorem can be formulated:
\begin{theorem}
Given $\gamma > 0$,  the performance criterion in (\ref{eq:inf1}) is satisfied if and only if there exist polynomials $R(z^{-1},\rho)$ and $S(z^{-1},\rho)$ such that
\begin{equation}
\begin{aligned} \label{eq:con1}
\gamma^{-1} |W_1MS(\rho)| < \mathcal{R}e\{\psi(\rho) \} \qquad 
\forall \omega \in \Omega 
\end{aligned}
\end{equation}
where $\psi(\rho) = MS(\rho) + NR(\rho)$.
\end{theorem}
\begin{proof}
The proof of a similar theorem has been formally documented in \cite{KZ04}\footnote{This proof was established by assuming a unity feedback system with a rational controller structure $K = XY^{-1}$ in the feedforward loop. For the RST controller structure used in this paper, the controller $R$ is equivalent to $X$ and $S$ is equivalent to $Y$.}.
\end{proof}

\iffalse
\begin{proof}
The proof of a similar theorem has been formally documented in \cite{KZ04}\footnote{This proof was established by assuming a unity feedback system with a rational controller structure $K = XY^{-1}$ in the feedforward loop. For the RST controller structure used in this paper, the controller $R$ is equivalent to $X$ and $S$ is equivalent to $Y$.}. By substituting the FRF of (\ref{eq:S0}) into (\ref{eq:inf_f}), the $\mathcal{H}_{\infty}$ constraint can be expressed as follows:
\begin{equation}
\begin{aligned}
\gamma^{-1} |W_1MS(\rho)| < |\psi(\rho) |& \\
\forall \omega \in \Omega &
\end{aligned}
\end{equation}
However, since $\mathcal{R}e\{\psi(\rho) \} \leq |\psi(\rho) |$ (i.e., the real part of a complex number is less than or equal to its magnitude), then the resulting constraint can be expressed as asserted in (\ref{eq:con1}).
\end{proof}
\fi

%%% Part about tracking a ramp
In certain design strategies, it may sometimes be desired to track different reference signals with no steady-state error, such as a step or a ramp input. For the torsional system that will be addressed in this paper, it will be desired to track a step input. Minimization of the error sensitivity function is a soft constraint, and may not lead to the ideal tracking performance. Therefore it is advantageous to consider conditions that ensure proper tracking of a step input by imposing hard convex constraints. Note that in an RST structure, the existence of an integrator in the open-loop transfer function does not guarantee a zero steady-state error for tracking a step input. The necessary and sufficient condition for a zero steady-state error is recalled in the following lemma.

\begin{lemma}
Suppose that the reference signal is a step function given as $r(z^{-1}) = A(1-z^{-1})^{-1}$, where $A$ is the amplitude of the step function. Additionally, suppose that the controller $S(z^{-1},\rho)$ possesses an integrator (i.e., $S(z^{-1},\rho) = (1-z^{-1}) S^{\prime}(z^{-1},\rho)$, where $S^{\prime}(z^{-1},\rho)$ is linearly parameterized). A necessary and sufficient condition to obtain a zero steady-state error for a step input is
\begin{align} \label{eq:step_con}
R(1,\rho) = T(1,\rho) \neq 0
\end{align}
\end{lemma}

\begin{proof}
The proof for this condition can be established by using the final value theorem. For perfect tracking of an arbitrary reference signal $r(k)$, it is required that $\lim_{k \to \infty} [r(k)-y(k)] = 0$, or
\begin{equation}
\lim_{z \to 1}(1-z^{-1})r(z^{-1})[1-\mathcal{T}(z^{-1},\rho)] = 0
\end{equation}
For a step input, the condition for achieving a zero steady-state error can be expressed as
\begin{equation} \label{eq:lim1}
\lim_{z \to 1} [1-\mathcal{T}(z^{-1},\rho)] = 0 
\end{equation}
By substituting (\ref{eq:T}) into (\ref{eq:lim1}) (and noting that $S(z^{-1},\rho) = (1-z^{-1}) S^{\prime}(z^{-1},\rho)$), one can arrive to the following condition:
\begin{eqnarray} \label{eq:limf}
\lim_{z \to 1} \frac{N(z^{-1})[R(z^{-1},\rho) - T(z^{-1},\rho)]}{M(z^{-1})S(z^{-1},\rho) + N(z^{-1})R(z^{-1},\rho)} \nonumber\\
 = \frac{R(1,\rho) - T(1,\rho)}{R(1,\rho)} = 0
\end{eqnarray} 
which evidently leads to the  condition asserted in (\ref{eq:step_con}).
\end{proof}

\subsection{Convex Optimization via Semi-Definite Programming}
Suppose that it is desired to achieve proper tracking performance and zero steady-state error for a step reference input. Moreover, it is desired that the sensitivity function $\mathcal{U}(z^{-1},\rho)$ in (\ref{eq:U}) be shaped to limit the control efforts. As a result, the infinity norm of $W_2\mathcal{E}$ and $W_3\mathcal{U}$ should be minimized where $W_2$ is a lowpass filter with a cut off frequency close to the desired bandwidth and $W_3$ is a high pass filter to attenuate the control efforts at high frequencies. By utilizing the equality constraint in (\ref{eq:step_con}), one can formalize an optimization problem to obtain the admissible $R(\rho)$, $S(\rho)$, and $T(\rho)$ controllers as follows: 
\begin{equation} \label{eq:min2}
\begin{aligned}
& \underset{ \{\rho_R,\rho_S,\rho_T\} \in \mathbb{R}}{\text{minimize}}
& & \gamma  \\
& \text{subject to:} & & \gamma^{-1} |W_2[\psi(\rho) - NT(\rho)]|    < \mathcal{R}e\{\psi(\rho) \}  \\ 
& & & \gamma^{-1} |W_3MT(\rho)|   < \mathcal{R}e\{\psi(\rho) \} \\
& & & R(1,\rho) = T(1,\rho) \neq 0\\
& & & \forall \omega \in \Omega 
\end{aligned}
\end{equation}

%where $ \Pi = \{\Delta \in [0,\pi] \mid \omega \subsetneq \Delta \}$.
The optimization problem in (\ref{eq:min2}) is quasi-convex since the objective function ($\gamma$) is being multiplied with the optimization parameters of $S(\rho)$ in one of the constraints. One solution is to implement an iterative bisection algorithm in order to convexify the optimization problem. In this method, an iterative approach is implemented in order to obtain an asymptotically convergent solution. 
\begin{remark}
In the bisection method, an initial value is assigned for $\gamma$ such that $\gamma_i = 0.5(\gamma_{min} + \gamma_{max})$ to solve the optimization problem, where $\gamma_{min}$ and $\gamma_{max}$ are the minimum and maximum bounds set for $\gamma$. If the problem is feasible for $\gamma_i$, then $\gamma_{i+1} = 0.5(\gamma_{min} + \gamma_i)$, and the solution to the optimization problem in (\ref{eq:min2}) is recalculated with $\gamma_{i+1}$. If the problem is infeasible for $\gamma_i$, then $\gamma_{i+1} = 0.5(\gamma_{max} + \gamma_i)$. This process is repeated until a solution is obtained within a given tolerance. 
\end{remark}

The problem in (\ref{eq:min2}) is known as a semi-infinite programming (SIP) problem since there are a finite number of optimization variables and an infinite number of constraints. To solve this problem, the optimization algorithm can be converted to a semi-definite programming (SDP) problem. A predefined frequency space can be implemented in order to solve a finite number of constraints. This frequency grid can be predefined in a variety of manners (see \cite{SVB11}, \cite{GKL10b}).

\begin{figure}
\centering
\includegraphics[scale=0.2]{pics/torsional_pic}
\caption{Torsional apparatus (ECP model 205a) used for the experimental analysis. The three disks are comprised of block masses which can be added or removed to alter the inertia of each disk (and thus alter the dynamics of the system). Each disk is vertically suspended on a spring with a variable spring constant. The actuator is located on the bottom of the device.}
\label{fig:torsional}
\end{figure}

\section{Experimental Analysis}
\label{sec:4}
In order to demonstrate the effectiveness of the proposed method, an RST controller will be designed for a multi-model torsional apparatus (ECP Model 205a), as shown in Fig.\ref{fig:torsional}. This system contains three disks with variable inertias suspended vertically on anti-friction ball bearings. The disks are connected through a non-rigid cable with an adjustable spring constant. The actuator (a high torque brushless motor with a $2$ Nm rating) is located at the bottom of the apparatus and is directly connected to the bottom disk via a rigid timing belt. The position of the disks are measured with a high resolution encoder ($16,000$ count/rev) and is used as feedback to control the closed-loop system. For this experiment, the dynamics of the apparatus will be altered by varying the inertias of the top disk.

An RST controller will be designed for various inertial configurations. Three different configurations will be considered for this design; the bottom disk and the middle disk will possess fixed inertias, while the inertia for the top disk will be varied. The inertia is varied by altering the number of block masses that are arranged on the disk.

The input to the system is the current of the actuator and the output is the position of the third disk. Therefore, the plant model has an integrator and is not stable; thus it is required to obtain the FRF's of the various configurations in a closed-loop structure. As asserted in Section (\ref{sec:21}), a stabilizing controller must be used to obtain $N(e^{-j\omega})$ and $M(e^{-j\omega})$. For this plant, a PID controller was designed to stabilize the closed-loop system. A reference input with a pseudo-random binary sequence (PRBS) is implemented to excite the closed-loop system with a sampling frequency of $25 \; Hz$. The time-domain signals for the reference input $r(t)$, control output $u(t)$, and output $y(t)$ for this system are depicted in Fig.\ref{fig:iddata} (for brevity, the figure shown is for one of the configurations). The FRF of $N(e^{-j\omega})$ is then obtained with the spectral analysis command in MATLAB (i.e., \texttt{spa($\cdot$)}) by using the time-domain data of $r(t)$ and $y(t)$. Similarly, the FRF of $M(e^{-j\omega})$ is obtained  in a similar fashion by using the time-domain data of $r(t)$ and $u(t)$. The FRF of the plant model can then be described as $G(e^{-j\omega}) = N(e^{-j\omega})M^{-1}(e^{-j\omega})$. The FRF's for each of the three configurations are shown in Fig.~\ref{fig:freq}.
\begin{figure}
\centering
\includegraphics[width=1.1\columnwidth]{pics/id_data_2}
\caption{Time-domain response of the closed-loop system with a PRBS excitation signal (shown only for the system configuration with two block masses on the top disk): the PRBS reference input $r(t)$ with a register length of $511$ (solid-blue); control output $u(t)$ (solid-red); output response $y(t)$ (solid-black).}
\label{fig:iddata}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=\columnwidth]{pics/multi_freq_2}
\caption{FRF's of the plant model obtained from the closed-loop time-domain response of each system configuration. The loads on the bottom and middle disk are fixed while the load on the top disk is varied: FRF with one block mass on the top disk (solid-blue); FRF with two block masses on the top disk (solid-green); FRF with four block masses on the top disk (solid-red). }
\label{fig:freq}
\end{figure}

It will be desired to minimize the tracking error and to reject a step disturbance at the output. In order to achieve these specifications, an integrator will be included in $S^{\star}(z^{-1},\rho)$ (i.e., $S^{\star}(z^{-1},\rho) = (1-z^{-1})S(z^{-1},\rho)$). Additionally, a weight will be designated to limit the control effort. Therefore, the optimization problem formulated in (\ref{eq:min2}) will be implemented for this design scheme. The RST controllers will each be linearly parameterized as in (\ref{eq:Rc}), (\ref{eq:Sc}), (\ref{eq:Tc}) with $n_r = n_s = n_t = 8$. Thus the following optimization problem will be considered:
\iffalse
\begin{equation} \label{eq:min_exp}
\begin{aligned}
& \underset{ \{\rho_R,\rho_S,\rho_T\} \in \mathbb{R}}{\text{minimize}}
& & \gamma  \\
& \text{subject to:} & & \gamma^{-1} |W_2\jok[\psi_i^{\star}\jrok \\ & & &   \hspace{1.5cm} - N_i\jok T\jrok]|  \\ & & & \hspace{1.5cm} - \mathcal{R}e\{\psi_i^{\star}\jrok \}< 0  \\ 
& & & \gamma^{-1} |W_3\jok M_i\jok T\jrok|   \\ & & &   \hspace{1.5cm} - \mathcal{R}e\{\psi_i^{\star}\jrok \}< 0\\
& & & R(1,\rho) = T(1,\rho) \neq 0 \\
& & & \mbox{for }i = 1,2,3 \ \mbox{and }k = 1,\ldots,q
\end{aligned}
\end{equation}
where 
\begin{eqnarray*}
\psi_i^{\star}\jrok = M_i\jok S^{\star}\jrok \\ +N_i\jok R\jrok
\end{eqnarray*}
\fi
\begin{equation} \label{eq:min_exp}
\begin{aligned}
& \underset{ \{\rho_R,\rho_S,\rho_T\} \in \mathbb{R}}{\text{minimize}} \quad \gamma\\
& \text{subject to:} \\
& \gamma^{-1} |W_2\jok[\psi_i^{\star}\jrok - N_i\jok T\jrok]|  \\ & \hspace{4.2cm} - \mathcal{R}e\{\psi_i^{\star}\jrok \}< 0  \\
& \gamma^{-1} |W_3\jok M_i\jok T\jrok|   \\ & \hspace{4.2cm}  - \mathcal{R}e\{\psi_i^{\star}\jrok \}< 0 \\
& R(1,\rho) = T(1,\rho) \neq 0 \\
& \mbox{for }i = 1,2,3 \ \mbox{and }k = 1,\ldots,q
\end{aligned}
\end{equation}
where 
\begin{eqnarray*}
\psi_i^{\star}\jrok = M_i\jok S^{\star}\jrok \\ +N_i\jok R\jrok
\end{eqnarray*}

\subsection{Weighting filter selection}
The weighting filter $W_2$ will be chosen based on the fact that $\mathcal{E}_d + \mathcal{T}_d = 1$, where $\mathcal{E}_d$ is the desired error sensitivity function and $\mathcal{T}_d$ is the desired complementary sensitivity function (i.e., the closed-loop transfer function). $\mathcal{T}_d$ is chosen as a first order transfer function such that the step response will have a time constant of $1 \: s$ (which corresponds to a closed-loop bandwidth of $\omega_b = 1 \; rad/s$). The transfer function which satisfies these requirements can be formulated as
\begin{equation}
\mathcal{T}_d(s) = \frac{\omega_b}{s+\omega_b}
\end{equation}
Since $\mathcal{E}_d  = 1- \mathcal{T}_d$, an appropriate filter for the error sensitivity function can be devised as
\begin{equation}
W_2(s) = \frac{s+\omega_b}{s}
\end{equation}
It will be desired to minimize the control effort at high frequencies; therefore, a viable choice for the control weighting function $W_3$ is
\begin{equation}
W_3(s) = \frac{s + \omega_u / M_u}{\omega_u}
\end{equation}
where $M_u$ is the maximum controller gain, and $\omega_u$ is the controller bandwidth \cite{ZD98}. For the torsional system considered in this paper, an appropriate choice for these parameters are $M_u = 10^3$ and $\omega_u = 3 \; rad/s$. 
\subsection{Experimental results}
The optimization problem in (\ref{eq:min_exp}) is solved by considering a logarithmically spaced frequency grid with $q = 400$ points. The SDPT3 software package is used in conjunction with Matlab to solve the optimization problem. The solution obtained from the bisection algorithm produces the following controllers:

\begin{align*}
R(z^{-1}) &= 34.19 - 113.7 z^{-1} + 160  z^{-2} \\ &\qquad - 100.3 z^{-3} - 10.66 z^{-4} + 60.08 z^{-5} \\ &\qquad - 32.94 z^{-6} - 2.093 z^{-7} + 5.542 z^{-8}  \\
S^{\star}(z^{-1}) &=  1 + 0.3538 z^{-1} + 0.2304 z^{-2} - 0.07627 z^{-3} \\ &\qquad - 0.2845 z^{-4} - 0.2575 z^{-5} - 0.08136 z^{-6} \\ &\qquad - 0.1705 z^{-7} - 0.2921 z^{-8} - 0.422 z^{-9}\\
T(z^{-1}) &= 0.00942 + 0.01295 z^{-1} + 0.01548 z^{-2} \\ &\qquad + 0.01646  z^{-3} + 0.01116 z^{-4} + 0.01683 z^{-5} \\ &\qquad + 0.01491 z^{-6}  + 0.01329 z^{-7} + 0.01008 z^{-8}
\end{align*}

The optimal value of $\gamma$ obtained from the optimization is $\gamma_{opt} = 2.228$. The step responses obtained for each of the inertial configurations are depicted in Fig.~\ref{fig:step}. 
\begin{figure}
\centering
\includegraphics[width=\columnwidth]{pics/step_2}
\caption{Step response for each load configuration: response with one block mass on the top disk (solid-blue); response with two block masses on the top disk (solid-green); response with four block masses on the top disk (solid-red). }
\label{fig:step}
\end{figure}
From the multi-model step responses, it can be observed that the system is stable and robust to the dynamic variations of the torsional apparatus. Moreover, the load variations do not significantly impact the tracking performance (which is expected, since the same weighting filter was used in the multi-model optimization problem). The closed-loop FRF's of all three system configurations are shown in Fig.~\ref{fig:CL}. It can be observed that the achieved closed-loop bandwidth for all three configurations is approximately $1 \ rad/s$, which is the bandwidth that was specified to form the weighting filter $W_2(s)$. This confirms the feasibility of the solution obtained from the optimization problem in (\ref{eq:min_exp}).
\begin{figure}
\centering
\includegraphics[width=\columnwidth]{pics/closed_loop}
\caption{Closed-loop frequency response functions of all three system configurations: closed-loop FRF with one block mass on the top disk (solid-blue); closed-loop FRF with two block masses on the top disk (solid-green); closed-loop FRF with four block masses on the top disk (solid-red).}
\label{fig:CL}
\end{figure}

\section{Conclusion}
\label{sec:5}
In this paper, a new method has been proposed to design robust controllers with $\mathcal{H}_{\infty}$ performance. The RST controller structure possesses many practical advantages, such as its two-degree of freedom design capabilities and the fact that it can be easily implemented. A frequency-domain approach has been used in order to avoid the problem of unmodeled dynamics associated with parametric models. A convex optimization problem is constructed based on the $\mathcal{H}_{\infty}$ criterion thanks to the process of linearly parameterizing the RST controllers. This controller design method has been employed to design a robust RST controller to control the disk position of a coupled torsional apparatus. A multi-model optimization approach was considered to design a controller for various loads; the design proved to be robust to the dynamic variations of the system. For further research, it will be desired to establish an optimal frequency gridding process, and compare how different gridding schemes can improve the solution to the optimization problem.

%\begin{IEEEbiographynophoto}
%Author1 Biography
%\end{IEEEbiographynophoto}
%\smallskip{}
%\begin{IEEEbiographynophoto}
%Author2 Biography
%\end{IEEEbiographynophoto}

\bibliography{linear}

\end{document}

### 2017-02-11 Papers/SUBMITTED - RST Design Current Loop (CERN)/Latex/Draft.tex
adding files to git (11/2/2017)

%\documentclass[12pt,draftcls,onecolumn]{IEEEtran}
\documentclass[journal]{IEEEtran}
%\IEEEoverridecommandlockouts  
%\overrideIEEEmargins     
\bibliographystyle{IEEEtran}
\pdfminorversion=4

\usepackage{cite}
%\usepackage{mathptmx}       % selects Times Roman as basic font
\usepackage{helvet}         % selects Helvetica as sans-serif font
\usepackage{courier}        % selects Courier as typewriter font
\usepackage{type1cm}        % activate if the above 3 fonts are
                            % not available on your system
%
\usepackage{makeidx}         % allows index generation
\usepackage{graphicx}        % standard LaTeX graphics tool
%                             % when including figure files
\usepackage{multicol}        % used for the two-column index
\usepackage{times}
\usepackage{xfrac}
\usepackage{caption}
\usepackage{subcaption}
%\usepackage{mathabx}
%\usepackage[thref]{ntheorem}
\usepackage{amsfonts}%
\usepackage{amssymb}%
\usepackage{amsthm}
\usepackage{mathrsfs}
\usepackage{url}
\usepackage{color}
%\usepackage{import}
\usepackage{graphicx,psfrag}
\usepackage{float}
\usepackage[cmex10]{amsmath}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem*{remark}{Remark}
\newcommand{\jo}{(e^{-j\omega})}
\newcommand{\jok}{(e^{-j\omega_k})}
\newcommand{\jro}{(e^{-j\omega},\rho)}
\newcommand{\jrok}{(e^{-j\omega_k},\rho)}
%\renewcommand{\IEEEQED}{\IEEEQEDopen}
\renewcommand{\vec}[1]{\mathbf{#1}}
\newcommand{\hilight}[1]{\colorbox{yellow}{#1}}
%\DeclareRobustCommand*{\IEEEauthorrefmark}[1]{%
  %\raisebox{0pt}[0pt][0pt]{\textsuperscript{\footnotesize\ensuremath{#1}}}}

\title{\LARGE \bf A Robust Data-driven Controller Design Methodology for Particle Accelerator Power Converters}

%\iffalse
\author{Achille Nicoletti, Michele Martino and Alireza Karimi% <-this % stops a space

\thanks{Achille Nicoletti is with the Technology Department at
European Organization for Nuclear Research (CERN) and the Automatic Control Laboratory at
Ecole Polytechnique F\'{e}d\'{e}rale de Lausanne (EPFL) (email: \tt\small achille.nicoletti@cern.ch)}%
\thanks{Michele Martino is with the Technology Department at
European Organization for Nuclear Research (CERN) (email: \tt\small michele.martino@cern.ch)}%
\thanks{Alireza Karimi is with the Automatic Control Laboratory at
Ecole Polytechnique F\'{e}d\'{e}rale de Lausanne (EPFL) (email: \tt\small alireza.karimi@epfl.ch)}%
}
%\fi

\begin{document}

\maketitle
\thispagestyle{empty}
\pagestyle{empty}

\begin{abstract}
A new data-driven approach using the frequency response function (FRF) of a system is proposed for designing robust $H_{\infty}$ digital controllers for particle accelerators' power converters. This design method ensures that the dynamics of a system are captured and avoids the problem of unmodeled dynamics associated with parametric models. The $H_{\infty}$ robust performance condition can be represented by a set of convex constraints with respect to the parameters of a two-degree of freedom RST controller. This controller is robust with respect to the frequency-dependent uncertainties of the frequency response function. Moreover, constraints will be imposed in order to simultaneously ensure the desired stability margins and the controller stability. A convex optimization algorithm is then implemented to obtain the controller parameters. The effectiveness of the method is illustrated by designing the controller for the Q-STRIP magnet power converter of the PS Booster accelerator upgrade project at CERN. Experimental validation in the time domain is also presented. 
\end{abstract}

\begin{IEEEkeywords}
Convex optimization, data-driven control, H-infinity, power converter control, robust control, RST %uncertainty, Smith predictor, MIMO time delay. 
\end{IEEEkeywords}

\section{Introduction}
\IEEEPARstart{M}{any} of today's  complex systems possess a multitude of uncertainties, and obtaining an accurate parametric model for such systems can be both laborious and impractical for controller synthesis. In industrial schemes, the dynamics of plants are typically approximated by low-order models, since the controller synthesis is easier to implement for lower order processes. However, this approximation can impede the  performance of a controller, since low-order models are subject to model uncertainty. A survey on the differences associated with model-based control and data-driven control has been addressed in \cite{HW13} and \cite{BCE12}; the authors assert that model-based control methods are inherently less robust due to the unmodeled dynamics of a process, and that these controllers are unsafe for practical applications. With the data-driven control scheme, the parametric uncertainties and the unmodeled dynamics are irrelevant and the only source of uncertainty is the measurement noise.

Data-driven controllers can be synthesized either on-line or off-line; the on-line methods such as the classical direct adaptive control (MRAC) \cite{LLMK11}, model-free adaptive control (MFAC) \cite{HJ13}, and the unfalsified control (UC) \cite{ST97} methodologies design controllers using time-domain data. Iterative feedback tuning (IFT) \cite{Hja02}, correlation-based tuning (CBT) \cite{KMB02a}, virtual reference feedback tuning (VRFT) \cite{CLS02}, non-iterative data-driven model reference control \cite{KVB07} methodologies are all off-line time-domain data-driven methods.  The widely used PID controller is usually tuned based on a set of time-domain or frequency-domain data.

Data-driven control methods using frequency-domain data are design schemes that continue to spark the interest of many researchers. The frequency-domain approach offers many advantages compared to time-domain methods :
\begin{itemize}
\item Without knowledge of the transfer function, the dynamics of a system can be captured experimentally through the frequency response.
\item Relative and absolute stability of a closed-loop system can be determined with the knowledge of the open-loop frequency response.
\item Noise disturbance generated in the system can be easily determined using frequency analysis.
\item System uncertainties can be modeled at discrete frequency points (which reduces the conservatism associated with uncertainty modeling). 
\end{itemize}
The authors in \cite{HDAV10} use the frequency response data of a stable system to design an optimal controller through a symmetric root locus technique. A robust frequency-domain control design method has been established in \cite{KNND13b}; this method, however, requires a solution to a non-linear optimization problem. A frequency-domain loop-shaping approach to design fixed-structure controllers is presented in \cite{KNND13c}. In this method, a convex optimization problem can be formulated if a linearly parameterized controller is considered; however, in this method, the closed-loop stability is not guaranteed and should be verified a posteriori. Robust controller design methods belonging to the $\mathcal{H}_{\infty}$ control framework minimizes the $\mathcal{H}_{\infty}$ norm of a weighted closed-loop sensitivity functions. In \cite{DWS09} a frequency-response method is proposed based on the $Q$-parametrization to guarantee the $\mathcal{H}_{\infty}$ performance for fixed-structure controllers. In \cite{KG10}, a frequency domain approach is realized where a convex optimization algorithm is formulated by considering a convex approximation of the $\mathcal{H}_{\infty}$ criterion. In order to obtain convexity, however, the controller is chosen to be linearly parameterized, i.e. the denominator of the controller are fixed. This limits the number of degrees of freedom of the controller, and thus impedes the controller performance. A frequency-domain approach for computing low-order multivariable linearly parameterized controllers is presented in \cite{SOW10}. The $\mathcal{H}_{\infty}$ constraints are convexified around an initial stabilizing controller. An iterative algorithm is used that converges to a local optimal solution of the non-convex problem. The method in \cite{KG10} is extended to data-driven gain-scheduled controller design in \cite{KE13a} and multivariable decoupling controller design in \cite{GKL10b}. A public domain toolbox for Matlab is also available \cite{Kar13}. A similar approach is proposed in  \cite{HAB13}, where a convex-concave approximation of the $\mathcal{H}_{\infty}$ constraints based on an initial stabilizing controller is used. The extension of this method to design multivariable PID controllers for stable systems is presented in \cite{BHA16}. This method uses the same convex approximation as in  \cite{SOW10} but is limited to stable systems and PID structure. The design of controllers that are not linear in parameters (e.g. represented by rational transfer functions) using frequency domain data are studied in \cite{KNZ16}. The necessary and sufficient conditions for the existence of such controllers are developed. This method needs no initial stabilizing controller and converges to the optimal  $\mathcal{H}_{\infty}$ performance when the order of the controller goes to infinity.

%\iffalse
%Generally, it is desired to formulate a convex optimization problem for controller synthesis, since convex problems are computationally tractable. A frequency domain approach in designing the $RST$ controllers has been discussed in \cite{MRS11}, where a convex optimization problem is formulated by bounding a specific sensitivity function and specifying a desired characteristic polynomial. Robust stability, however, is not trivially achieved, since the characteristic polynomial incorporates an observer polynomial which usually needs to be tuned iteratively. With $\mathcal{H}_{\infty}$ control techniques, it is possible to eliminate the necessity of using observer polynomials for achieving proper robustness margins. Robust controller design methods belonging to the $\mathcal{H}_{\infty}$ control framework minimizes the $\mathcal{H}_{\infty}$ norm of a weighted closed-loop sensitivity function. In \cite{GKL11}, a frequency domain approach is realized where a convex optimization algorithm is formulated by considering a convex approximation of the $\mathcal{H}_{\infty}$ criterion. With this method, suitable robustness margins are attainable; however, in order to preserve convexity, this method requires one of the controller terms ($R$) to be fixed a priori\footnote{Note that the variable names for $R$ and $S$ are interchanged in \cite{GKL11}}. This limits the number of degrees of freedom of the controller, and thus impedes the controller performance.

The $RST$ controller structure is an effective discrete-time two-degree of freedom (2DOF) polynomial controller where the tracking and regulation characteristics of a closed-loop system can be formulated independently \cite{LZ06}. 
The $RST$ controller design methodology is usually based on the pole placement technique and uses the dynamic model of the physical system. In \cite{GKL11}, the data-driven frequency-domain approach of \cite{KG10} is extended to $RST$ controller design. However, in order to preserve convexity, this method requires one of the controller terms to be fixed a priori. This problem is fixed in \cite{NEK15}, where an $RST$ controller is designed in the $\mathcal{H}_{\infty}$ framework by formulating a convex optimization problem in a data-driven setting. The necessary and sufficient conditions for the existence of $RST$ controllers that satisfy the  $\mathcal{H}_{\infty}$ constraint only on one sensitivity function are also developed.

The proposed method in this paper is an extension of \cite{NEK15}, where the necessary and sufficient conditions that ensures the $\mathcal{H}_{\infty}$ performance for multiple weighted sensitivity functions is presented. Moreover, the frequency-dependent uncertainties originated from the measurement noise are taken into consideration for robust performance specifications. Additionally, since the parameters of the controller's denominator are the optimization variables, this method can lead to unstable controllers. Therefore, a sufficient condition is presented to ensure that the controller remains stable. The proposed method is then used to design a robust $RST$ controller for power converters in particle accelerators at CERN. The designed controller is implemented in the power converters to control their output current with extremely high precision. The main advantage of the proposed method for this application is to guarantee the robustness margins, high bandwidth and small tracking error by a data-driven convex optimization based approach that does not require the manual tuning of the classical pole-placement model-based approach.

The paper is organized as follows.
The class of models, controllers and control objectives are defined in section (\ref{sec:2}). Section (\ref{sec:3}) discusses the control design methodology and stability conditions of the proposed method for the $RST$ controller structure. Convex conditions are formulated based on the $\mathcal{H}_{\infty}$ criterion. Section (\ref{sec:4}) discusses the framework of the power converter control system and its functionality at CERN. Section (\ref{sec:5}) is dedicated to a case study where the effectiveness of the method is demonstrated by applying the proposed design scheme to a power converter control system for a specific accelerator requirement. Finally, the concluding remarks are given in section (\ref{sec:6}).

%\textbf{Notation}: In order to avoid the risk of any confusion, the notation for the symbols employed in this paper will be defined here.
%\begin{align*}
%\mathbb{R}/ \mathbb{R}^+ &: \ \mbox{the set of all real numbers/positive real numbers.} \\
%\mathbb{Z} &: \ \mbox{the set of non-negative integers.} \\
%\mathcal{R}e\{X \} &: \ \mbox{the real part of a complex variable }X. \\
%\mathcal{I}m\{X \} &: \ \mbox{the imaginary part of a complex variable }X. \\
%a^{\top} &: \ \mbox{the transpose of the vector }a. \\
%z &: \ \parbox[t]{18em}{complex frequency variable used to represent discrete-time systems.} \\
%s &: \ \parbox[t]{18em}{complex frequency variable used to represent continuous-time systems.}
%\end{align*} 
%\section{Notation and Preliminaries}
%Due to the nature of the equations asserted in this paper, it will be convenient express certain equations in a compact manner. A cascade of $q$ frequency response functions $A_1(e^{-j\omega})A_2(e^{-j\omega}) \cdots A_q(e^{-j\omega})$ will be denoted as $[A_1A_2 \cdots A_q](e^{-j\omega})$.

\section{Problem Formulation}
\label{sec:2}
\subsection{Preliminaries}
Let $u[k]$ and $y[k]$ represent the input and output signals of a causal discrete-time system, respectively, where $k$ is a discrete-time instant and $T_s$ is the sampling period. Suppose that these signals are noise-free and have zero initial and final conditions (i.e., $u[k] = y[k] = 0$ for $k \leq 0$ and $k > K_s$). Then, the frequency response function (FRF) of the system can be represented as 
\begin{equation}
G(e^{-j\omega}) = Y(e^{-j\omega}) U^{-1}(e^{-j\omega})
\end{equation}
where
\begin{align}
U(e^{-j\omega}) &= \frac{1}{\sqrt{K_s}} \sum_{k=0}^{K_s} u[k]e^{-j \omega T_s k} \label{eq:U_period}\\
Y(e^{-j\omega}) &= \frac{1}{\sqrt{K_s}} \sum_{k=0}^{K_s} y[k]e^{-j \omega T_s k}
\end{align} 
are the periodograms of the input and output signals and $\omega \in [-\pi/T_s, \pi/T_s]$. Note that due to the symmetry of the periodograms, it is sufficient to consider $\omega \in [0, \pi/T_s]$ for practical applications. Under these assumptions, it is evident that from a set of sampled time-domain data, one is able to obtain a continuous FRF.  If the data is noisy, then $G(e^{-j\omega})$ is characterized as the Empirical Transfer Function Estimate (ETFE) and is asymptotically unbiased \cite{Lju99}. For such systems, a multiplicative uncertainty can be considered to ensure robustness in the presence of noise perturbations.

Let the set $\mathscr{P}$ represent the family of all stable, proper, real-rational discrete-time transfer functions with no pole on the unit circle. It is imperative to note that $\mathscr{P}$ is closed under multiplication and addition; in other words, if $P_1(z^{-1}),P_2(z^{-1}) \in \mathscr{P}$, then 
\begin{equation}
\{ P_1(z^{-1})+P_2(z^{-1}),P_1(z^{-1})P_2(z^{-1})\} \in \mathscr{P}
\end{equation}
Suppose that a single-input-single-output (SISO) feedback control system structure is used where the plant is represented as $G(z^{-1}) = N(z^{-1})M^{-1}(z^{-1})$ such that $\{N(z^{-1}),M(z^{-1})\} \in \mathscr{P}$. As asserted in \cite{ZD98} and \cite{DFT92}, if $\{N(z^{-1}), M(z^{-1})\} \in \mathscr{P}$, then $G(z^{-1}) = N(z^{-1})M^{-1}(z^{-1})$ is called a \textit{coprime factorization} of $G(z^{-1})$ over $\mathscr{P}$.

\subsection{Class of models}
Let the FRF of such a factorized discrete-time SISO plant be defined as follows:
\begin{equation}\label{eq:setpmimo}
G\jo = N\jo M^{-1}\jo, \qquad \forall \omega \in \Omega
\end{equation}
where $\Omega \in [0,\pi/T_s]$. $N\jo$ and $M\jo$ must be FRF's of bounded analytic functions outside the unit circle; for a stable plant, a trivial choice is $N\jo=G\jo$ and $M\jo=1$. A discussion on how to formulate $N\jo$ and $M\jo$ for unstable processes can be found in \cite{KNZ16}. In general, a set $\mathcal{G}$ can be formulated to represent a plant model containing $p$ FRF models:
\begin{equation}
\mathcal{G} = \{G_l\jo; \quad l=1,\ldots,p; \quad \forall \omega \in \Omega\}
\end{equation} 
These FRF's can be determined by considering the frequency response of a parametric model or from a set of input/output data. For simplicity, one model from the set $\mathcal{G}$ will be considered, and the subscript $l$ will be omitted. However, in general, the design procedures outlined in this paper can be applied to the multi-model case. %In fact, in Section (\ref{sec:4}), a multi-model case will be investigated for the controller synthesis of the power converter control system.

\subsection{Frequency-domain uncertainty} \label{sec:freq_uncertain}
Suppose that the uncertainty associated with a given FRF is described by an additive uncertainty:
\begin{equation}
\begin{aligned} \label{eq:frf_uncertainty}
\hat{N}(e^{-j\omega}) &= N(e^{-j\omega}) + |W_n(e^{-j\omega})| \delta_n e^{j\theta_n} \\
\hat{M}(e^{-j\omega}) &= M(e^{-j\omega}) + |W_m(e^{-j\omega})| \delta_m e^{j\theta_m}
\end{aligned}
\end{equation}
where $|\delta_n| \leq 1$, $|\delta_m| \leq 1$; $\{ \theta_n,\theta_m\} \in [0,2\pi]$; $W_n$ and $W_m$ are the uncertainty weighting filters which can be determined from the covariance of the estimates for a given confidence interval.  As previously stated, $N\jo = G\jo$ and $M\jo = 1$ can be selected for stable systems. Therefore, given the periodogram of $G$, the estimates of the real and the imaginary part of $N\jo$ can be formulated; these estimates are asymptotically uncorrelated and normally distributed with a variance of $\Phi_v(\omega)/2|U\jo|^2$, where $\Phi_v(\omega)$ is the spectrum of the disturbance $v[k]$ at the output of the plant (\cite{Lju99}). The additive uncertainty can be described in the complex plane with a disk centered at $N\jo$ having a radius of $|W_n\jo|$. The uncertainty is characterized by the Rayleigh distribution and can be determined for any probability level. For example, if it is desired to construct an uncertainty disk such that the true frequency response lies within the disk with a probability level of $0.95$, then the radius of this disk will be
\begin{equation} \label{eq:uncertainty_radius}
|W_n\jo| = \sqrt{\frac{5.99 \Phi_v(\omega)}{2|U\jo|^2}}
\end{equation}
The output noise spectrum can be estimated as
\begin{equation} \label{eq:noise_spectrum}
\Phi_v(\omega) = \Phi_y(\omega) - \frac{|\Phi_{uy}(\omega)|^2}{\Phi_u(\omega)}
\end{equation}
where $\Phi_u(\omega)$ is the input spectrum, $\Phi_y(\omega)$ is the output spectrum, and $\Phi_{uy}(\omega)$ is the cross-spectral density of the input and output channels.

\subsection{Class of controllers}
\begin{figure}
\centering
\resizebox{1\columnwidth}{!}{\input{rst.eps_tex}}
\caption{$RST$ controller structure}
\label{fig:rst}
\end{figure}
The controller structure that will be considered will be of the $RST$-type. The $RST$ controller is a two-degree of freedom controller which can be used to synthesize the tracking and regulation requirements independently from each other \cite{LZ06}. The general structure of this controller is shown in Fig.~\ref{fig:rst}. Each controller is realized as a polynomial function as follows:
\begin{alignat}{2}
R(z^{-1},\rho) &= r_0 + r_1z^{-1} + \cdots + r_{n_r}z^{-n_r} \label{eq:Rc}\\
S(z^{-1},\rho) &= 1 + s_1z^{-1} + \cdots + s_{n_s}z^{-n_s} \label{eq:Sc}\\
T(z^{-1},\rho) &= t_0 + t_1z^{-1} + \cdots + t_{n_t}z^{-n_t} \label{eq:Tc}
\end{alignat}
where $\{n_s,n_r,n_t\}$ are the orders of the polynomials $R,S$ and $T$, respectively. These controllers can also be represented in a linear regression form as 
\begin{align}
R(z^{-1},\rho)&=\rho_R^\top \phi_{n_r}(z^{-1})= [r_0,r_1,\ldots,r_{n_r}]\phi_{n_r}(z^{-1}); \nonumber \\
S(z^{-1},\rho)&=\rho_S^\top \phi_{n_s}(z^{-1})= [1,s_1,\ldots,s_{n_s}]\phi_{n_s}(z^{-1}); \nonumber \\
T(z^{-1},\rho)&=\rho_T^\top \phi_{n_t}(z^{-1})= [t_0,t_1,\ldots,t_{n_t}]\phi_{n_t}(z^{-1}); \nonumber
\end{align}
where
\begin{align}
\rho^\top &=[\rho_R^\top, \rho_S^\top, \rho_T^\top] \nonumber \\
\phi_x^\top(z^{-1}) &= [1,z^{-1},\ldots,z^{-x}] \nonumber
\end{align}
%The purpose of parameterizing the controllers in this manner will become apparent in subsequent sections. 
where $x \in \{n_r,n_s,n_t \}$.

Based on the internal model principle, the controller may contain the disturbance model to achieve a zero steady-state error. Therefore, the polynomials may be pre-multiplied with any arbitrary function that actualizes the desired action. For example, if it is desired to reject a step disturbance at the output, then $S(z^{-1},\rho)$ can be pre-multiplied with $(1-z^{-1})$ (which represents the integral action of the controller). For sinusoidal disturbances at specific frequencies, the polynomials can be pre-multiplied with the function
\begin{equation*}
\theta (z^{-1}) = 1-2z^{-1} \cos(\omega_z T_s) + z^{-2}
\end{equation*}  
where $\omega_z$ is the frequency in $rad/s$ at which the disturbance occurs. %Suppose that there is noise $v$ at a frequency $\omega_z$, and is it desired to attenuate the effects caused by this disturbance (note that (\ref{eq:V}) represents the sensitivity function of interest for this disturbance). Then the $R$ polynomial can be pre-multiplied with $\theta (z^{-1})$ to achieve the desired noise attenuation at the output. In general, any of the $RST$ polynomials can be pre-multiplied with any polynomial that performs the desired action.
%The purpose of parameterizing the controllers in this manner will become apparent in subsequent sections.
%For notation purposes, the dependency on the discrete-time frequency variable $z^{-1}$ will be omitted, and the dependency on the controller parameter $\rho$ will remain.

\subsection{Sensitivity Functions}
\label{sec:23}
Since the design techniques introduced in this paper belong to the $\mathcal{H}_{\infty}$ framework, it is  appropriate to consider the various sensitivity functions associated with the $RST$ controller structure. Some sensitivity functions for this process can be asserted as follows:
\begin{align}
\mathcal{S}_1(z^{-1},\rho)&= \frac{y}{d_o} = \frac{M(z^{-1})S(z^{-1},\rho)}{\psi(z^{-1},\rho)}  \label{eq:S0}\\
\mathcal{S}_2(z^{-1},\rho)&= \frac{y}{r} =\frac{N(z^{-1})T(z^{-1},\rho)}{\psi(z^{-1},\rho)} \label{eq:T} \\
\mathcal{S}_3(z^{-1},\rho)&= \frac{r-y}{r} =\frac{\psi(z^{-1},\rho)-N(z^{-1})T(z^{-1},\rho)}{\psi(z^{-1},\rho)} 
\end{align}
where $\psi(z^{-1},\rho) = N(z^{-1})R(z^{-1},\rho)+M(z^{-1})S(z^{-1},\rho)$, $y$ is the system output, $r$ is the reference input, and $d_o$ is the output disturbance. For notation purposes, the dependency in $z^{-1}$ will be omitted, and will only be reiterated when deemed necessary. Note that all of the sensitivity functions are stable if the zeros of $\psi(\rho)$ lie within the unit circle. The sensitivity functions defined above (and all other sensitivity functions of interest) all contain the same transfer function  $\psi(\rho)$. Therefore, a general construction of the sensitivity function can be expressed as $\mathcal{S}_q(\rho) = \Delta_q(\rho)/ \psi(\rho)$, where $\Delta_q(\rho)$ is a linear function of $R$, $S$ and/or $T$. The subscript $q \in \{ 1,2,\ldots,c\}$ denotes the $q$-th sensitivity of interest and $c$ is the total number of sensitivity functions.

\section{$\mathcal{H}_{\infty}$ Performance via Convex Optimization}
\label{sec:3}
\subsection{General Design Specifications}
\label{sec:general}
In the general $\mathcal{H}_\infty$ control problem, the objective is to find the controller parameters vector $\rho$ such that
\begin{equation} \label{eq:true_hinf}
\sup_{\omega \in \Omega} |H_q(e^{-j\omega},\rho)| < \gamma
\end{equation}
where $\gamma \in \mathbb{R}^+$, $H_q(e^{-j\omega},\rho) = W_q(e^{-j\omega}) \mathcal{S}_q(e^{-j\omega},\rho)$ and $W_q$ is the FRF of a stable weighting filter such that $H_q(e^{-j\omega},\rho)$ has a bounded infinity norm. For notation purposes, the dependency in $e^{-j\omega}$ will be omitted, and will only be reiterated when deemed necessary. The condition in (\ref{eq:true_hinf}) can also be expressed as follows:
\begin{equation} \label{eq:circle}
\gamma^{-1}|W_q \Delta_q(\rho)| < |\psi(\rho)| ; \quad \forall \omega \in \Omega
\end{equation}

It is desired to minimize the upper bound $\gamma$ such that the $\mathcal{H}_{\infty}$ performance condition is satisfied. 
Therefore, the following optimization problem can be considered:
\begin{equation} \label{eq:min1}
\begin{aligned}
& \underset{\rho}{\text{minimize}}
& & \gamma  \\
& \text{subject to:} & & \gamma^{-1} |W_q\Delta_q(\rho)| < |\psi(\rho)|  \\ 
& & & \forall \omega \in \Omega \quad ; \quad  q \in \mathcal{Q} \subset \{1, 2, \ldots, c\}
\end{aligned}
\end{equation}
Notice that (\ref{eq:min1}) is a non-convex optimization problem.

\begin{figure}
\hspace*{1cm}
\resizebox{0.9\columnwidth}{!}{\input{nxmy2_rad_diff_2.eps_tex}}
\caption{The graphical interpretation of $\mathcal{H}_{\infty}$ constraints in the complex plane}
\label{fig:circle}
\end{figure}

Consider a circle in the complex plane at a specific frequency in $\Omega$ which is centered at $\psi(\rho)$ and has radius $\gamma^{-1}|W_q\Delta_q(\rho)|$. The constraint in (\ref{eq:circle}) ensures that for any frequency point in $\Omega$, the circle associated with this frequency point will not encircle the origin. Fig.~\ref{fig:circle} displays the graphical interpretation of this condition. This geometrical construction will be used to prove the following Lemma:

\begin{lemma}   \label{lem2}
Suppose that $$H_q(\rho,e^{-j\omega})={W_q\jo \Delta_q(\rho,e^{-j\omega})} \psi^{-1}(\rho,e^{-j\omega})$$ is the frequency response of a bounded analytic function outside the unit circle. Then, the following constraint is met
\begin{equation} \label{eq4}
\sup_{\omega \in \Omega}  |H_q(\rho,e^{-j\omega})| < \gamma
\end{equation}
if and only if there exists a finite-impulse-response (FIR) function $F(z^{-1})$ that satisfies
$$
\Re\{\psi(\rho)F(e^{-j\omega})\}>\gamma ^{-1}|W_q\Delta_q(\rho)F(e^{-j\omega})|,  \qquad \forall \omega \in \Omega 
$$
\end{lemma}

{\it Proof :} 
The basic idea is similar to that of  the proof of Theorem~1 in \cite{RM94}. It is clear that (\ref{eq4}) is satisfied if and only if the disk of radius $ \gamma ^{-1}|W_q\Delta_q(\rho)|$ centered at $\psi(\rho)$ does not include the origin for all $\omega \in \Omega$, i.e. $|\psi(\rho)|>\gamma ^{-1}|W_q\Delta_q(\rho)|$. This is equivalent to the existence of a line passing through origin that does not intersect the disk. Therefore, at every given frequency, $\omega$, there exists a complex number $f(e^{-j\omega})$ that can rotate the disk such that it lays inside the right hand side of the imaginary axis. Hence, we have 
\begin{equation}
\label{eq:lem_eq1}
\begin{split}
\Re \left\{ \left[ \psi(\rho) - \gamma ^{-1}|W_q\Delta_q(\rho)|e^{j\theta} \right] f(e^{-j\omega}) \right\}>0 \\
\forall \omega \in \Omega, \forall \theta \in [0 \, , \, 2 \pi [
\end{split}
\end{equation}
where $\Re \{ \cdot \}$ denotes the real part of a complex variable. Since $f(e^{-j\omega}) = |f(e^{-j\omega})|e^{j\theta_f}$, then the above condition can be expressed as
\begin{equation}
\label{eq:lem_eq2}
\begin{split}
\Re\{  \psi(\rho)f(e^{-j\omega}) \}> \gamma ^{-1}|W_q\Delta_q(\rho)f(e^{-j\omega})|\cos(\theta + \theta_f) \\
\forall \omega \in \Omega, \forall \theta \in [0 \, , \, 2 \pi [
\end{split}
\end{equation}
However, (\ref{eq:lem_eq2}) is satisfied if and only if:
\begin{equation}
\label{eq18}
\begin{split}
\Re\{  \psi(\rho)f(e^{-j\omega}) \}> \gamma ^{-1}|W_q\Delta_q(\rho)f(e^{-j\omega})| \\
\forall \omega \in \Omega
\end{split}
\end{equation}
In \cite{RM94}, it is shown that, $f(e^{-j\omega})$ can be approximated arbitrarily well by the frequency response of a stable transfer function or FIR function $F(z^{-1})$ if and only if 
\begin{equation}
Z=\left( \psi(\rho) - \gamma_0 ^{-1}|W_q\Delta_q(\rho)|e^{j\theta} \right)^{-1}
\end{equation}
is analytic in the right half plane for all $\gamma_0>\gamma$ and all $\theta \in [0 \, , \, 2 \pi [$. However, $\psi^{-1}(\rho)$ is stable because of the stability of $H_q(\rho)$. On the other hand, by decreasing $\gamma_0$ from infinity to $\gamma$, the poles of $Z$ move continuously with $\gamma_0$. Therefore, $Z$ is not analytic in the right half plane if and only if $Z^{-1}(e^{-j\omega})=0$ for a given frequency, which is not the case because the origin is not in the interior of the circle $\gamma_0 ^{-1}|W_q\Delta_q(\rho)|e^{j\theta}$.  
{\hfill \ensuremath{\blacksquare}}

The set of all controllers that meet the performance condition defined by the weighted norm of sensitivity functions is asserted in the following theorem.

\begin{theorem}  \label{Th1}
Given the frequency response function $G\jo = N\jo M^{-1}\jo$ and the frequency response of a weighting filter $W_q\jo$, then the following statements are equivalent for a given $q \in \mathcal{Q}$:

{\bf (a)} There exists an $RST$ controller that stabilizes $G$ and

	\begin{equation}
	\label{state_a_single}
	\begin{aligned}
	\sup_{\omega \in \Omega}  | {W_q \mathcal{S}_q(\rho)} | < \gamma 
	\end{aligned}
	\end{equation}

    %\begin{equation}
	%\label{state_a}
	%\sup_{\omega \in \Omega}  | {W_0 (1+GK)^{-1}} | < \gamma
	%\end{equation}

{\bf (b)} There exists an $RST$ controller such that
\begin{equation} \label{state_b_single}
\begin{aligned}
\Re\{\psi(\rho)\}  >\gamma ^{-1}|W_q\Delta_q(\rho)|\quad \forall \omega \in \Omega
 \end{aligned} 
\end{equation}
\end{theorem}
{\it Proof :} ({\bf b} $\Rightarrow$ {\bf a}) 
$\psi(\rho)$ is analytic outside the unit circle and its real part is positive for all $\omega \in \Omega$. Therefore, $\psi(\rho)$ will not encircle the origin when $\omega$ travels along the Nyquist contour, and its inverse is stable. This implies that $R(\rho)$ and $S(\rho)$ stabilizes $G$. On the other hand, we have
\begin{equation}  \nonumber
\begin{aligned}
|\psi(\rho)| \geq \Re\{\psi(\rho)\} \quad 
\forall \omega \in \Omega
\end{aligned}
\end{equation}
which leads to
\begin{equation} \label{eq:the_1_single_2}
\begin{aligned}
|W_q\Delta_q(\rho)| < \gamma |\psi(\rho)| \quad \forall \omega \in \Omega
 \end{aligned}
\end{equation}
Therefore, (\ref{eq:the_1_single_2}) leads to (\ref{state_a_single}) in Statement ({\bf a}).

({\bf a} $\Rightarrow$ {\bf b}) Assume that $R(\rho_0)$,  $S(\rho_0)$, and/or\footnote{The inclusion of $T(\rho_0)$ depends on which sensitivity function $\mathcal{S}_q^0(\rho)$ is being considered} $T(\rho_0)$ satisfies Statement ({\bf a}) but not Statement ({\bf b}). Then, according to Lemma 1, there exists a FIR function $F(z^{-1})$ such that
\begin{equation} \label{eq:the_ineq1}
\Re\{ \psi(\rho_0) F(e^{-j\omega})\} > \gamma^{-1}|F(e^{-j\omega})W_q\Delta_q(\rho_0)| \quad \forall \omega \in \Omega
\end{equation}
Therefore, there exists a higher order $RST$ controller with $R= R(\rho_0)F$, $S = S(\rho_0)F$, and/or $T = T(\rho_0)F$ such that Statement ({\bf b}) holds.
 {\hfill \ensuremath{\blacksquare}}

The above theorem is a necessary and sufficient condition for satisfying the $\mathcal{H}_\infty$ criterion for \textit{one} sensitivity function. However, in typical control system applications, it is desired to shape several sensitivity functions simultaneously and impose multiple constraints on the weighted sensitivity functions. The following theorem ensures necessity and sufficiency of the $\mathcal{H}_\infty$ criterion when multiple sensitivity functions are considered:

\begin{theorem}  \label{Th2}
Given the frequency response function $G\jo = N\jo M^{-1}\jo$ and the frequency response of bounded weighting filters $W_q\jo$ for $\forall q \in \mathcal{Q}$, the following statements are equivalent:

{\bf (a)} There exists an $RST$ controller that stabilizes $G$ and

	\begin{equation}
	\label{state_a}
	\begin{aligned}
	\sup_{\omega \in \Omega}  | {W_q \mathcal{S}_q(\rho)} | < \gamma \quad
	\forall q \in \mathcal{Q}
	\end{aligned}
	\end{equation}

    %\begin{equation}
	%\label{state_a}
	%\sup_{\omega \in \Omega}  | {W_0 (1+GK)^{-1}} | < \gamma
	%\end{equation}

{\bf (b)} There exists an $RST$ controller such that
\begin{equation} \label{state_b}
\begin{aligned}
\Re\{\psi(\rho)\}  >\gamma ^{-1}|W_q\Delta_q(\rho)|\quad \forall \omega \in \Omega
 \end{aligned} 
\end{equation}
and for all $q \in \mathcal{Q}$.
\end{theorem}
{\it Proof :} ({\bf b} $\Rightarrow$ {\bf a}) 
The proof for this condition is equivalent to the proof presented in Theorem \ref{Th1}. By satisfying the constraint in (\ref{state_b}) for all $q \in \mathcal{Q}$, the condition in (\ref{state_a}) for each corresponding $q$ is obtained.

({\bf a} $\Rightarrow$ {\bf b}) Assume that $R(\rho_0)$,  $S(\rho_0)$, and/or $T(\rho_0)$ satisfies Statement ({\bf a}) but not Statement ({\bf b}). Then, according to Lemma 1, there exist FIR transfer functions $F_q(z^{-1})$ such that
\begin{equation} \label{eq:the_ineq1}
\Re\{ F_q\psi(\rho_0)- \gamma ^{-1}|F_qW_q \Delta_q(\rho_0)|\} > 0 
\end{equation} 
for all $\omega \in \Omega$ and for all $q \in \mathcal{Q}$. For Statement ({\bf b}) to hold, there must exist a common $F$  for all $q \in \mathcal{Q}$ such that  $R = R(\rho_0)F$, $S= S(\rho_0)F$, and/or $T = T(\rho_0)F$.

For a given frequency, the constraints in (\ref{state_a}) will represent circles in the complex-plane that are centered exactly at $\psi(\rho_0)$ with varying radii (where the radii depend on each $q$). Let us define the following quantities at every $\omega \in \Omega$:
\begin{equation} 
\begin{aligned}
\mathscr{R}(e^{-j\omega},\rho_0) &= \{ |W_1 \Delta_1(e^{-j\omega},\rho_0)| , \ldots,|W_{c} \Delta_{c}(e^{-j\omega},\rho_0)|\}\\
r(e^{-j\omega},\rho_0) &=  \gamma^{-1}  \max_{q \in \mathcal{Q}}\mathscr{R}(e^{-j\omega},\rho_0) \\
\end{aligned}
\end{equation}
For any $\omega$, the circle with radius $r(\rho_0)$ does not include the origin, and all of the other circles with smaller radii are enclosed in the circle with radius $r(\rho_0)$, i.e. : 
$$\gamma^{-1}|W_q \Delta_q(e^{-j\omega},\rho_0)| \leq r(e^{-j\omega},\rho_0)$$ 
Therefore, for a given frequency, the complex number $f_q$ which is used to rotate the circle associated with radius $r(e^{-j\omega},\rho_0)$ ensures that all of the circles with $\gamma^{-1}|W_q \Delta_q(e^{-j\omega},\rho_0)| \leq r(e^{-j\omega},\rho_0)$ are also rotated such that they all lie in the right-hand side of the imaginary axis. Therefore, there will always exist a common $F$ that interpolates all $f_q$ (different $q$ in different frequencies) such that the conditions in (\ref{eq:the_ineq1}) hold true for all $q \in \mathcal{Q}$.
 {\hfill \ensuremath{\blacksquare}}

\subsection{Robust Design}
\label{sec:rob_con}
With the proposed method, it is possible to design a fixed-structure controller which accounts for the uncertainties of a given FRF (as described in Section \ref{sec:freq_uncertain}). Given this additive uncertainty, a desired performance condition $\|W_q \mathcal{S}_q \|_{\infty}<\gamma$ will be satisfied for all models in the uncertain set (\ref{eq:frf_uncertainty}) if $\| W_q \mathcal{\hat{S}}_q\|_{\infty} < \gamma$, where $\mathcal{\hat{S}}_q =\hat{\Delta}_q/\hat{\psi}(\rho)$ and $\hat{\psi}(\rho) = \hat{N}R(\rho) + \hat{M}S(\rho) $. For example, consider the nominal performance condition $\|W_3 \mathcal{\hat{S}}_3 \|_{\infty}<\gamma$ with $\hat{\Delta}_3(\rho) = \hat{M}S(\rho) + \hat{N}[R(\rho)-T(\rho)]$; as a worst case consideration, $\delta_m$ and $\delta_n$ can be selected to be equal to one  in (\ref{eq:frf_uncertainty}) (which ensures that the uncertainty in the entire disk is taken into account).  By substituting the expressions in (\ref{eq:frf_uncertainty}) into this condition, the following constraint can be devised:
\begin{equation} \label{eq:robust_uncertain}
\begin{split} 
 \bigl|W_3 \left[ \psi(\rho) -NT(\rho)+S(\rho)|W_m|e^{j\theta_m} + C(\rho)|W_n|e^{j\theta_n}\right] \bigr| \\
< \gamma \bigl| \psi(\rho) + R(\rho)|W_n|e^{j\theta_n} + S(\rho)|W_m|e^{j\theta_m} \bigr|\\
\forall \omega \in \Omega, \forall \{\theta_n,\theta_m \} \in [0,2\pi]
\end{split}
\end{equation}
where $C(\rho) = R(\rho) - T(\rho)$. For notation purposes, let us define $\psi\sp{\prime}(\rho,\theta_n) := \psi(\rho) + R(\rho)|W_n|e^{j\theta_n}$. Then for a given $\{\omega,\theta_n,\theta_m \}$, (\ref{eq:robust_uncertain}) represents a circle centered at $\psi\sp{\prime}(\rho,\theta_n) + S(\rho)|W_m|e^{j\theta_m}$ with a radius of 
\begin{equation} \label{eq:robust_ness_suff_1}
\begin{split} 
x_p (\rho,\theta_m,\theta_n)  = \gamma^{-1}|W_3| \bigl| \psi\sp{\prime}(\rho,\theta_n)  + S(\rho)|W_m|e^{j\theta_m} \\ - T(\rho)[N+|W_n|e^{j\theta_n}] \bigr|
\end{split}
\end{equation}
According to Theorem \ref{Th1}, a necessary and sufficient condition for (\ref{eq:robust_uncertain}) can be constructed as follows:
\begin{equation} \label{eq:robust_ness_suff_2}
\begin{split} 
 x_p (\rho,\theta_m,\theta_n) < \Re \{ \psi\sp{\prime}(\rho,\theta_n)+ S(\rho)|W_m|e^{j\theta_m} \} \\
\forall \omega \in \Omega, \forall \{\theta_m,\theta_n\} \in [0,2\pi]
\end{split}
\end{equation}
By gridding in $\omega$, $\theta_m$ and $\theta_n$, then (\ref{eq:robust_ness_suff_1}) becomes a convex constraint (with respect to $\rho$); however, gridding in all of these variables can be computationally expensive. For stable plants (which is the case at CERN), $M = 1$ may be selected. Therefore, the disk uncertainty associated with $M$ is $|W_m| = 0$. From (\ref{eq:robust_ness_suff_1}) and (\ref{eq:robust_ness_suff_2}), it can be observed that with $|W_m| = 0$, the dependency on $\theta_m$ is removed, and no gridding in $\theta_m$ is required. The necessary and sufficient condition then becomes
\begin{equation} \label{eq:robust_ness_suff_3}
\begin{split} 
 x_p (\rho,\theta_n) < \Re \{ \psi\sp{\prime}(\rho,\theta_n)\} \\
\forall \omega \in \Omega, \forall \theta_n \in [0,2\pi]
\end{split}
\end{equation}
where
\begin{equation} \label{eq:robust_ness_suff_4}
\begin{split} 
x_p (\rho,\theta_n)  = \gamma^{-1}|W_3| \bigl| \psi\sp{\prime}(\rho,\theta_n)  - T(\rho)[N+|W_n|e^{j\theta_n}] \bigr|
\end{split}
\end{equation}
In certain applications, gridding in two variables can still be computationally burdensome. Therefore, a sufficient condition for (\ref{eq:robust_uncertain}) can be devised as follows:
\begin{equation} \label{eq:uncertain_condition}
\sup_{\omega \in \Omega} \frac{|W_3|\bigl[|\psi(\rho)-NT(\rho)|  + |C(\rho)W_n | \bigr]}{|\psi(\rho)| -|R(\rho)W_n| } < \gamma
\end{equation}
With this condition, the dependency in $\theta_m$ and $\theta_n$ has been removed, and gridding in only one variable (i.e., $\omega$) is required. Note that the above constraint is sufficient since
\begin{align*}
 & \phantom{{}\leq{}} |W_3|  \bigl| \psi(\rho)  -NT(\rho) + C(\rho)|W_n|e^{j\theta_n} \bigr| \\
 & \leq |W_3|\bigl[|\psi(\rho)-NT(\rho)|  + |C(\rho)W_n | \bigr] \\
 & < \gamma \bigl[ |\psi(\rho)| -|R(\rho)W_n| \bigr] \\
 & \leq \gamma \bigl| \psi(\rho) +R(\rho)|W_n|e^{j\theta_n} \bigr|
\end{align*}
%It can be observed that the quantity $|\psi(\rho)| -|R(\rho)W_n|$ may be less than zero; in this case, the problem simple becomes infeasible for that particular value of $\omega$.

The condition in (\ref{eq:uncertain_condition}) can be represented as a disk in the complex plane which is centered at $\psi(\rho)$ and has radius
\begin{equation} \label{eq:rad_robust_design}
\begin{aligned} 
x_r (\rho) = \gamma^{-1}|W_3| \bigl[|\psi(\rho)-NT(\rho)|  \\ + |C(\rho)W_n | \bigr] +  |R(\rho)W_n| 
\end{aligned}
\end{equation}
%If $|\psi(\rho)| < |W_mS(\rho)|+|W_nR(\rho)|$, then the disk given by (\ref{eq:uncertain_condition}) will become its complement, and the problem will simply be infeasible. 
%In Theorem \ref{Th2}, it was shown that the $\mathcal{H}_\infty$ criterion is satisfied for an arbitrary amount of weighted sensitivity functions (where, for a given frequency, the circles for each sensitivity function were each centered at $\psi(\rho)$). Since the circle associated with (\ref{eq:uncertain_condition}) is also centered at $\psi(\rho)$, then the necessity and sufficiency is also ensured for this constraint (see the proof for the necessary condition in Theorem \ref{Th2}).  
Therefore, a set of convex constraints (with respect to $\rho$) can be devised with the following condition:
\begin{equation}
x_r(\rho) < \Re \{ \psi(\rho)\}, \quad \forall \omega \in \Omega
\end{equation}
This constraint has the same structure as that of the sensitivity functions and so can readily be included in the optimization problem. Note that (\ref{eq:uncertain_condition}) introduces some conservatism; however, this conservatism can always be reduced by imposing (\ref{eq:robust_ness_suff_2}) for unstable plants or (\ref{eq:robust_ness_suff_3}) for stable plants.

\subsection{Convex Optimization via Semi-Definite Programming}
Suppose that it is desired to obtain $\mathcal{H}_{\infty}$ performance for a sensitivity function (i.e., minimize $\gamma$ in $\|W_q\mathcal{S}_q \|_{\infty}<\gamma$). Then according to Theorem \ref{Th2}, one can formalize an optimization problem to obtain the admissible $R(\rho)$, $S(\rho)$, and/or $T(\rho)$ controllers as follows:
\begin{equation} \label{eq:min2}
\begin{aligned}
& \underset{ \rho}{\text{minimize}}
& & \gamma  \\
& \text{subject to:} & & \gamma^{-1} |W_q \Delta_q| < \Re\{\psi(\rho) \}  \\ 
& & & \forall \omega \in \Omega \quad ; \quad  q \in \mathcal{Q}
\end{aligned}
\end{equation}

The optimization problem in (\ref{eq:min2}) is quasi-convex since the objective function ($\gamma$) is being multiplied with the optimization parameters of the controller in the constraints. The classical solution is to implement a bisection algorithm in order to \emph{convexify} the optimization problem. In this method, an iterative approach is implemented in order to obtain an asymptotically convergent solution. 
\begin{remark}
In the bisection method, an initial value is assigned for $\gamma$ such that $\gamma_0 = 0.5(\gamma_{min} + \gamma_{max})$ to solve the optimization problem, where $\gamma_{min}$ and $\gamma_{max}$ are the minimum and maximum bounds set for $\gamma$. In an iterative algorithm, if the problem is feasible for $\gamma_i$, then $\gamma_{i+1} = 0.5(\gamma_{min} + \gamma_i)$, and the solution to the optimization problem in (\ref{eq:min2}) is recalculated with $\gamma_{i+1}$. If the problem is infeasible for $\gamma_i$, then $\gamma_{i+1} = 0.5(\gamma_{max} + \gamma_i)$. This process is repeated until a solution is obtained within a given tolerance. 
\end{remark}

The problem in (\ref{eq:min2}) is known as a semi-infinite programming (SIP) problem since there are a finite number of optimization variables and an infinite number of constraints. To solve this problem, the optimization algorithm can be converted to a semi-definite programming (SDP) problem. A predefined frequency grid can be implemented in order to solve a finite number of constraints. This frequency grid can be predefined in a variety of manners (see \cite{SVBB11}, \cite{GKL10b}).

\section{Power Converter Framework}
\label{sec:4}
Particle accelerators use power converters for many different applications. Some converters are used simply to convert energy in one form to another (to energize special devices); in other cases, power converters are used in a control structure to control particles trajectories (and other \emph{optical} parameters of particle beams) within the accelerator system by modulating the magnetic field produced by specialized (electro-) magnets. These converters will be the focus of this paper. Particle beams usually require extremely precise magnetic fields; in certain cases, accuracy is also crucial for particle accelerators operation \cite{TPMK10}. In most cases, the magnetic fields produced by the magnets cannot be measured in real-time. Therefore, the output current of the power converter (which is injected into the magnets) is used to control the trajectory of particles.

%The CERN LHC Injector Upgrade Project \cite{BHAK14} was implemented to mitigate space-charge effects and to increase the beam brightness in order to fulfill the needs of the High Luminosity LHC. To realize these improvements,  a major upgrade of the PS Booster (PSB) was actualized where the injection energy was increased from $50$ MeV to $160$ MeV. The LINAC4 \cite{LINAC4} hydrogen ions (H$-$) beam must pass through an electron stripping foil in order to inject protons into the Booster. This is done by a magnetic/optical chicane (4 magnets per each ring) which is powered to displace the injected beam in order to strip its electrons. When the injection process is finished, the chicane will be inactive (zero current). This process produces perturbations in the optics of the Booster machine during the injection, and actions to compensate them must be foreseen by adding a correction function to the current of the Q-STRIP magnet. The Q-STRIP system is constituted of two chains of quadrupole magnets for each ring (one for focusing and one for de-focusing); each chain is powered by a single power converter.

\subsection{Power Converters for Particle Accelerators}
The framework of the system discussed in this paper is part of the CERN Large Hadron Collider (LHC) Injector Upgrade Project \cite{BHAK14},  which was implemented to mitigate space-charge effects and to increase the beam brightness in order to fulfill the needs of the High Luminosity LHC. The Q-STRIP magnet (i.e., the load, which is constituted of two chains of quadrupole magnets) is used in this framework to control the particle trajectories via the power converter control system.

Power converters can be seen as systems comprised of three main subsystems: (\textit{i}) a power source (usually a voltage source) (\textit{ii}) a measuring system and (\textit{iii}) a controller unit. 
The current is usually measured with a particularly accurate current transducer called a direct current-current transformer (DCCT) \cite{Kin01}. The current measurement signal is fed back to a digital controller unit which usually includes a high precision analog-to-digital converter that implements the digital control algorithm(\cite{TPMK10}, \cite{BFC07}). 
% The power source is then used as a power amplifier in order to power the magnet through a high bandwidth voltage loop.
%\subsection{Power Converters Control at CERN}

The general configuration of the CERN power converter control system is depicted in Fig.\ref{fig:ident_block}. The control loop consists of a magnet (i.e., the load), a voltage source $V_s$, low-pass anti-aliasing analog and digital filters (ALPF, DLPF), a digital-to-analog converter (DAC), and an analog-to-digital converter (ADC). The DAC (optional) and ADCs are integrated in the control unit labeled as the function generator controller (FGC, \cite{CKS11}) whose main function is to execute the control algorithm; it also implements all the diagnostics and communication functions with higher layers of the control architecture up to the accelerators control rooms. The DLPF may also includes a decimator to reduce the sampling rate of the signal. The COMM block represents the delay associated with the communications link. The $RST$ block represents the discrete-time controller that is used to control the magnet current $i_D$ given a reference current $i_R$.

%The dynamics associated with the filters, the transducer, the DAC, and the ADC are very fast (i.e., they each possess a very large bandwidth), and can usually be approximated arbitrarily well as a positive (real valued) time delay.

\begin{figure}
\centering
\resizebox{1\columnwidth}{!}{\input{pc_drawing_ident2.eps_tex}}
%\caption{A block diagram which depicts the system structure and the identified process. Identified components (red-dashed blocks); unidentified components (blue blocks).}
%\centering
%\resizebox{1\columnwidth}{!}{\input{pc_drawing.eps_tex}}
\caption{Power converter control system}
%\label{fig:pc}
\label{fig:ident_block}
\end{figure}

%on a CANCUN power converter connected to an $RL$ load whose characteristics match those of the Q-STRIP magnets (the magnet used for the experiment has an inductance about $10\%$bigger which can be considered as a worst case for tracking performance evaluation).  The CANCUN is based on a full bridge phase shifted topology followed by a 4 quadrant switching stage to allow 4 quadrant operation. Fig.~\ref{fig:cancun} shows a CANCUN converter which is comprised of a voltage (or power) unit, the control electronics, and the measurement systems in a compact chassis.  The ratings of the CANCUN converter for the Q-STRIP application would be $\pm 100$ $A$ and $\pm 30$ $V$ (the one used for experimental validation is just slightly different: $\pm 50$ $A$ and $\pm 30$ $V$).
%Table.~\ref{tab:cancun} displays the converter ratings and operating characteristics.

%\begin{table}
%\centering
%\caption{Main CANCUN Characteristics}
%\label{tab:cancun}
%\begin{tabular}{l|l}
%\textit{\textbf{Feature}} & \textit{\textbf{Value}}\\ \hline
%Input Power              & $3 \sim \ 240\: V/2.75\: A$                                     \\ \hline
%Output Power              & $\pm 50\: A / \pm 30 \: V$                               \\ \hline
%Converter Type              & 4 Quadrant                                   \\ \hline
%Control Type             & FGC3 / Ethernet+                                \\ \hline
%Current Accuracy             & $20 \: ppm$ in $30 \: mn$                                \\ 
       									%& $20 \: ppm$ in $24 \: h$                                \\    
       									%& $100 \: ppm$ in $1 \: year$                                \\      
       									%& $(1 \: ppm=50\: \mu A=0.05 \: mA)$               \\ \hline
%Voltage Ripple          & $10 \: mV_{rms}$  for  $f \in [20 \: Hz,1 \: kHz)$                                \\ 
%       									& $60 \: mV_{rms}$  for  $f \in [1 \: kHz,130 \: kHz)$                                 \\    
%       									& $7 \: mV_{rms} $  for  $f \in [130 \: kHz,5 \: MHz)$	                                            
%\end{tabular}
%\end{table}

\subsection{Experimental Test Setup}
\label{test_setup}
%on a CANCUN power converter connected to an $RL$ load whose characteristics match those of the Q-STRIP magnets (the magnet used for the experiment has an inductance about $10\%$bigger which can be considered as a worst case for tracking performance evaluation).  The CANCUN is based on a full bridge phase shifted topology followed by a 4 quadrant switching stage to allow 4 quadrant operation. Fig.~\ref{fig:cancun} shows a CANCUN converter which is comprised of a voltage (or power) unit, the control electronics, and the measurement systems in a compact chassis.  The ratings of the CANCUN converter for the Q-STRIP application would be $\pm 100$ $A$ and $\pm 30$ $V$ (the one used for experimental validation is just slightly different: $\pm 50$ $A$ and $\pm 30$ $V$).

The experimental test setup consists of a CANCUN power converter, a dummy load and a proprietary software diagnostics tool:

\begin{itemize}
	\item The CANCUN power converter is based on a full bridge phase shifted topology followed by a 4 quadrant switching stage to allow 4 quadrant operation. Fig.~\ref{fig:cancun} shows a CANCUN converter that incorporates three main parts: $i$) Two high precision current sensors (DCCTs) which are able to measure DC or pulsed current at the required precision; $ii$) A voltage (or power) module; $iii$) A digital controller (FGC3) which implements the digital control loop together with CERN designed control and diagnostics electronics. The ratings of the CANCUN converter for the Q-STRIP application is $\pm 100$ $A$ and $\pm 30$ $V$.
	\item The dummy load is an $RL$ load whose characteristics match those of the Q-STRIP magnets; however, the magnet used for the experiment has an inductance approximately $10\%$ larger, which can be considered as a worst case for tracking performance evaluation.
	\item The software diagnostics tool interfaces with the main digital controller module, the FGC3 \cite{CKS11}, and is able to acquire the relevant signals at a sampling rate of $10$K samples per second. The acquired signals are the reference current and voltage, measured current, and voltage and current error. The length of the record is fixed to $1.2$ $s$, which corresponds to $12000$ samples.
\end{itemize}

\begin{figure}
\centering
\includegraphics[width=0.8\columnwidth]{pics/housing_rack.eps}
\caption{CANCUN power converter. } 
%The FGC also collects and reports all statuses, faults, and measurements from various parts of the system and serves as the interface towards higher levels layers of the complex accelerator control architecture.}
\label{fig:cancun}
\end{figure}

\iffalse
\subsection{Track Delay and Tracking Error}
\label{track_error_definition}
%Before proceeding to the next section, it is imperative to first assert how the error is determined between the reference and the output current. 
In typical control applications, the error is usually calculated as the difference between the reference and the output sampled at a given time $t$. However, for some power converter control applications at CERN, the error is actually calculated as the difference between a delayed version of the reference input and the output at time $t$. 
The delayed reference input (for an arbitrary, positive delay) can be approximated as the output of the following interpolating filter:
\begin{equation}
\label{eq:del_filt}
\begin{aligned}
H(z^{-1})=z^{-\lfloor \tau \rfloor} \left(  1-(\tau - \lfloor \tau \rfloor) + (\tau - \lfloor \tau \rfloor)z^{-1}   \right) \\ \ \tau \in \mathbb{R}
\end{aligned}
\end{equation}
where $\tau$ is a (generally fractional) delay (expressed in units of the sampling time $T_s$), and the $\lfloor \cdot \rfloor$ operator represents the floor function which maps the real number in the argument to the largest integer not greater than that number. The use of (\ref{eq:del_filt}) allows one to interpolate the delayed reference signal between sampling points and calculate a more accurate error signal. For a given reference signal $\tilde{r}(z^{-1})$, the interpolated (causal) discrete-time reference signal will be
\begin{equation}
\label{eq:del_filt_new}
\begin{aligned}
r[n] &= \mathcal{Z}^{-1} \{ H(z^{-1}) \tilde{r}(z^{-1})\} \\
&=(1-\tau_{\text{frac}}) \tilde{r}[n-\lfloor \tau \rfloor]+ \tau_{\text{frac}} \tilde{r}[(n-1) -\lfloor \tau \rfloor]
\end{aligned}
\end{equation}
where $\tau_{\text{frac}} = \tau - \lfloor \tau \rfloor$ and $n \in \mathbb{Z}$. Therefore, for any discrete time instant $n$, the error is determined as $e[n] = r[n] - y[n]$, where $y[n]$ is the output response. For the purposes of this paper, $\tau$ is termed as the `track delay', and its value is related to the group delay of the closed-loop system:
\begin{equation}
\tau_g(\omega) = - \frac{d\phi_T(\omega)}{d\omega}; \quad \tau = \tau_g(0) \\
\label{eq:group_delay_theor}
\end{equation}
where $\phi_T(\omega)$ is the phase response associated with the closed-loop FRF.
%\end{remark}
\fi

\section{Case Study Results}
\label{sec:5}
This case study is devoted to the CANCUN power converter control system, as described in the previous section. The objective is to control the output current $i_D$ that is injected into the particle accelerator magnets in order to ensure proper particle trajectories. The profile of the reference current $i_R$ associated with the Q-STRIP magnet is shown in Fig.~\ref{fig:QCF_ref}.  For this application, the challenging task is to ensure the tracking performance; it is required that the error remains within $\pm 1000$ ppm\footnote{The calculation for obtaining the error in ppm is performed by taking the raw data for the error and scaling it by a factor of $\sfrac{10^6}{100}$. The factor of $100$ represents the nominal current ($100$ $A$) of the power converter for the Q-STRIP magnets.} during the fast transient and remains within $\pm 100$ ppm during steady state. The proposed controller design method was used to synthesize an $RST$ controller for this specific requirement. Experimental validation was performed by means of the test setup presented in \ref{test_setup}. 
\begin{figure}
\centering
\includegraphics[width=\columnwidth]{pics_prbs/reference.eps}
\caption{The reference current associated with the QCF circuit configuration. The blue-dashed line indicates the time when the error must remain within $\pm 1000$ ppm; the red-dashed line indicates the time when the error must remain within $\pm 100$ ppm;}
\label{fig:QCF_ref}
\end{figure}

The Q-STRIP magnet is represented as an $RL$ circuit, and the dynamics of this circuit are dominant over the other components of the system. Thus a first order model with delay (i.e., $G_m(s) = e^{-sT_d}(L_m s + R_m)^{-1}$, where $R_m$ is the circuit resistance, $L_m$ is the circuit inductance, and $T_d$ is the time delay) is appropriate to approximate the dynamics of the plant. For this case study, the model parameters are:
\begin{equation*}
R_m = 164.3 \: m \Omega; \quad L_m = 736.4 \: \mu H; \quad T_d = 275.4 \: \mu s
\end{equation*}
The model is then discretized using the zero-order-hold method and used to design an $RST$ controller based on the model-reference control (MRC) strategy \cite{LZ06}. In this particular implementation of the strategy, the transfer function between the reference signal and output depends on the location of the single zero (which comes from modeling the fractional delay) of the system \cite{KNM15}. According to \cite{LZ06}, if the fractional delay of the system is less than $0.5T_s$, then the zero of the system can be cancelled (which enables the tracking and regulation performances to be achieved without approximation). However, at CERN, this benchmark is modified such that the zero of the system is cancelled if the fractional delay is less than $0.4T_s$. In this case, the reference model is selected such that the transfer function from the reference input to the output will be a pure delay. However, if the fractional delay is greater than $0.4T_s$, then the corresponding zero cannot be cancelled, and the transfer function from the reference input to the output is represented as a fractional delay. The main difficulty of this approach is that the choice of the observer poles that lead to a good robustness margin is not trivial. The current practice at CERN is a trial-and-error approach to meet the control specifications. The main objective of this case study is to propose a systematic optimization based approach to compute the optimal controller parameters and guaranteeing robustness with respect to model uncertainties.

For this type of application, it is a challenging task to achieve tracking and a good robustness margin simultaneously. With the MRC method, the auxilary  poles must be placed in an iterative fashion in order to achieve the desired modulus margin of $0.5$. However, the method proposed in this paper does not need a parametric identification or any iterative tuning scheme. It is a straightforward systematic design methodology that takes also into account the frequency-domain uncertainties, which increases the robustness of the design process.

\subsection{Frequency Response Function Measurement}
A pseudo-random binary sequence (PRBS) signal was used as the input voltage reference of the open-loop system in order to capture the dynamics of the process. The PRBS is a deterministic signal which has characteristics similar to that of white noise and is usually used for system identification. From Fig.~\ref{fig:ident_block}, the measurement process will capture the dynamics from the input of the DAC (with input voltage $v(t)$ representing the reference voltage of the voltage source) to the output of the DLPF (with output current $i(t)$ representing the measured current to be fed back to the $RST$ controller).

Unfortunately, the FGC3 is limited by the amount of input samples that can be programmed to execute the PRBS signal (a maximum of $1023$). Therefore, to maximize the quality of the measurement, a PRBS signal of length $511$ ($9$-bits) with $2$ periods was injected as the input of the open-loop process. Note that a PRBS of length $1023$ ($10$-bits) with one period could also be used as the input; however, the output of such a reference will contain transients and must be considered as an aperiodic signal and thus increasing the truncation errors.

A total of $5$ experiments were performed with the PRBS clock period $T_{cl} = 100 \: \mu s$; the acquired periods (with transients removed in post-processing) could then be merged together. For a signal of length $511$, the frequency resolution is limited to $255$ points. A DC gain was added to this measurement in order to increase the resolution at lower frequencies (due to the low resolution resulting from the PRBS identification). This DC value was determined by simply applying a DC voltage $v(t) = V_{dc} = 1V$ and obtaining the value $i(t) = I_{dc}$. With $95\%$ confidence, the uncertainty associated for this gain can be calculated as 
$$|W_n(e^{-j\omega_0})| = 2\sigma_I / \sqrt{N_s} = 3.51 \times10^{-4}$$ 
where $\omega_0$ is chosen to be arbitrarily small ($\omega_0 = 0.2\pi$), $N_s = 12000$ is the length of the signal, and $\sigma_I = 0.0192 \: A$ is the root-mean-square of the measurement noise. This specific value of the uncertainty is for the DC gain and not for all of the other corresponding frequencies. The uncertainties for the remaining frequencies were determined with (\ref{eq:uncertainty_radius}). The PRBS input signal along with the resulting output response are shown in Fig.~\ref{fig:PRBS}.

\begin{figure}
\centering
\includegraphics[width=\columnwidth]{pics_prbs/prbs_time.eps}
\caption{PRBS signal used for the input voltage $v(t)$ of the open-loop system along with the resulting output current $i(t)$.}
\label{fig:PRBS}
\end{figure}
The FRF of the open-loop plant was then obtained as $G\jo=\mathcal{F}[i(t)]/ \mathcal{F}[v(t)]$ (where the operator $\mathcal{F}$ signifies the Fourier Transform). From (\ref{eq:uncertainty_radius}) and (\ref{eq:noise_spectrum}), the additive uncertainty associated with each frequency can be computed. Fig.~\ref{fig:plant_uncertain} displays a Bode diagram of $G\jo$ with the corresponding uncertainty bounds.

\begin{figure}
\centering
\includegraphics[width=\columnwidth]{pics_prbs/bode.eps}
\caption{Bode diagram of $G\jo$ with additive uncertainty bounds for the corresponding frequency points.}
\label{fig:plant_uncertain}
\end{figure}

%\begin{figure}[!b]
%\centering
%\resizebox{1\columnwidth}{!}{\input{pc_drawing_ident.eps_tex}}
%\caption{A block diagram which depicts the system structure and the identified process. Identified components (red-dashed blocks); unidentified components (blue blocks).}
%\label{fig:ident_block}
%\end{figure}

%\begin{lemma}
%Suppose that a bound is set such that $\| \mathcal{S}_0 \| ^{-1}_{\infty} > m_d$, where $m_d$ is the desired minimum value of the modulus margin. Then a condition for ensuring this constraint can be formulated as follows:
%\begin{equation}
%\begin{aligned}\label{eq:con_mm}
%m_d|MS(\rho)| < \mathcal{R}e\{\psi(\rho) \}& \\
%\forall \omega \in \Omega &
%\end{aligned}
%\end{equation}
%\end{lemma}
%
%\begin{IEEEproof}
%The proof for this condition is very similar to the proof of the constraint in Theorem 1. Here, the radius of the circle in Fig.\ref{fig:circle} is now $m_d|MS(\rho)|$ instead of $\gamma^{-1}|W_q \Delta_q(\rho)|$.
%\end{IEEEproof}
%Since the circle associated with this constraint is centered at $\psi(\rho)$, then the inclusion of this constraint with the $\mathcal{H}_{\infty}$ loop-shaping constraint still guarantees necessity and sufficiency of Theorem \ref{Th2}.
%
%

\subsection{Controller Stability}
\label{sec:con_stab}
Computation of an unstable controller should generally be avoided \cite{LZ06}. The logic behind this assertion has to do with the practical implications involved with a feedback control system.  Suppose that the plant $G(z^{-1}) = N(z^{-1})M^{-1}(z^{-1})$ is analytic outside the unit circle. For the $RST$ structure, it is evident that if the polynomial $S(z^{-1},\rho)$ possesses zeros outside the unit circle, then the open-loop system will become unstable (assuming no zero-pole cancellations occur with $R(z^{-1},\rho)$ and $S(z^{-1},\rho)$). In order to avoid this impairment, it is required to impose a constraint such that the polynomial $S(z^{-1},\rho)$ possesses zeroes inside the unit circle. This rationalization leads to the following lemma:

\begin{lemma}
Suppose that $S(z^{-1},\rho)$ is parameterized as in (\ref{eq:Sc}). Then a sufficient (convex) condition to ensure that the zeros of $S(z^{-1},\rho)$ remain inside the unit circle is
\begin{equation} \label{eq:con_con}
\Re \{S(\rho) \} > 0; \quad \forall \omega \in \Omega
\end{equation}
\end{lemma}
\begin{IEEEproof}
First note that a strictly positive real transfer function (and its inverse) is stable. $\Re \{S(\rho) \} > 0$ implies that the Nyquist diagram of $S(\rho)$ will not encircle the origin. Therefore, $S^{-1}(\rho)$ will not encircle the origin, and $S(\rho)$ is stable.    
\end{IEEEproof}

\subsection{Weighting Filter Design}
\label{sec:weighting_filter}
The $\mathcal{H}_{\infty}$ criterion in (\ref{eq:true_hinf}) is a very powerful design tool, as it provides the capability to shape any sensitivity function $\mathcal{S}_q$ based on the specifications set by a weighting filter. However, in certain design schemes at CERN, it may be desired to bound a sensitivity function to a particular value. For example, it may be desired to simply impose a lower-bound on the modulus margin in order to obtain the intended robust performance of a system. The modulus margin is defined as the minimum distance between the critical point $(-1+j0)$ and the Nyquist plot of the open loop transfer function, and can be expressed as
\begin{equation}
M_m = \| \mathcal{S}_1 \| ^{-1}_{\infty}
\end{equation}
In general, it is desired to obtain a minimum value of the modulus margin in order to ensure a sufficiently robust system. Let $m_d$ denote the minimum value of the desired modulus margin such that $M_m > m_d$. According to \cite{LZ06}, typical values for a good modulus margin are $M_m \geq 0.5 \ (-6 \; dB)$ (which ensures a gain margin of at least $6 \; dB$ and a phase margin of at least $29^{\circ}$). A constraint for ensuring a minimum value of the modulus margin can be constructed as follows:
\begin{equation}
  \| m_d \mathcal{S}_1 \|_\infty < 1 
\end{equation}
This constraint is a special case of the $\mathcal{H}_\infty$ constraints with $W_1(e^{-j\omega})=m_d$ and can be convexified using the results of Theorem \ref{Th2}.

For this particular case study, it is desired to obtain the best tracking performance (i.e., by minimizing $\gamma$ in $\|W_3 \mathcal{S}_3 \|_{\infty} < \gamma$) while ensuring reasonable stability margins. The weighting filter $W_3$ is chosen based on the fact that $\mathcal{S}_2^d + \mathcal{S}_3^d = 1$, where $\mathcal{S}_3^d$ is the desired error sensitivity function and $\mathcal{S}_2^d$ is the desired complementary sensitivity function (i.e., the closed-loop transfer function). $\mathcal{S}_2^d$ was chosen as a standard second order transfer function  with the given form:
\begin{equation}
\mathcal{S}_2^d(s) = \frac{\omega_d^2}{s^2 + 2\zeta \omega_d s + \omega_d^2}
\end{equation}
where $\zeta$ is the damping factor and
\begin{equation*}
\omega_d = \frac{2 \pi f_d}{\sqrt{1-2\zeta^2 + \sqrt{2-4\zeta^2 + 4\zeta^4}}}
\end{equation*}
where $f_d$ is the desired closed-loop bandwidth. Note that it is possible to consider a continuous-time transfer function for this specification since the proposed method implements a frequency-domain approach. Since $\mathcal{S}_2^d = 1- \mathcal{S}_3^d$, an appropriate filter for the error sensitivity function can be devised as
\begin{equation}
W_3(s) = \frac{s^2 + 2\zeta \omega_d s + \omega_d^2}{s(s+2\zeta \omega_d)}
\end{equation}
Due to the fact that $W_3(j\omega_k)$ is evaluated at a finite number of frequency points with $\omega_0 \neq 0$, then the integrator in $W_3$ does not pose problems with boundedness.

%For discrete-time systems, there are limitations with regards to the achievable closed-loop bandwidth of a system. According to \cite{LZ06}, the achievable closed-loop bandwidth is bounded by the following constraint:
%\begin{equation} \label{eq:bandwidth}
%f_s \in [6,25]f_d
%\end{equation}
A simulation was performed to determine the bandwidth that is required in order to satisfy the desired error specifications. At CERN, the error is calculated with respect to a delayed reference input (i.e., $e(t) = r(t-\tau) - y(t)$). By assuming that the closed-loop response behaves as $\mathcal{S}_2^d$, the bandwidth $f_d$ can be selected such that the error between the delayed reference input and output is within $\pm 100$ ppm. For this second order response, this delay was analytically derived as $\tau = 2\zeta/ \omega_d$. It was determined that $f_d = 300 \ Hz$ with $\zeta = 0.8$ satisfies these requirements. 
%Since the sampling frequency for the power converter control system is $3.333 \; kHz$, then $f_s/f_d$ satisfies the constraint in (\ref{eq:bandwidth}).

\subsection{$RST$ Controller Synthesis}
\label{synthesis}
The voltage applied to the magnet by the voltage source and the relative current are both sampled at 10  kHz while the control loop is run $3$ times slower (i.e., $f_s = 3.333$ kHz and $T_s = 300 \  \mu$s, where $f_s$ and $T_s$ are denoted as the sampling frequency and sampling time of the control loop, respectively).  Since the plant is stable, then a possible selection for the coprime factors is $N\jo = G\jo$ and $M\jo = 1$. For proper implementation within the proprietary power converter control software, it is required that all the open-loop poles remain on or within the unit circle, i.e. the controller should be marginally stable. This implies that the zeroes of $S(\rho)$ must lie on or within the unit circle. Since the reference current is close to a ramp signal, to achieve adequate performance, $S(z^{-1},\rho)$ must incorporate a double integrator: $S(z^{-1},\rho) = (1-z^{-1})^2S^\star(z^{-1},\rho)$. With the FRF measured by means of the PRBS excitation, the constraints for the convex optimization problem are formulated. With a minimum value of $m_d=0.5$ set for the modulus margin, the following optimization problem must be solved: 
\begin{equation} \label{eq:min_sim}
\begin{aligned}
& \underset{ \rho \in \mathbb{R}}{\text{minimize}}
& & \gamma  \\
& \text{subject to:} & & \Re\{\psi \jrok \} > x_r \jrok  \\
& & & \Re\{\psi \jrok \} > m_d|S \jrok|  \\
& & & \Re \{S^{\star}\jrok \}  > 0 \\
& & & \mbox{for }k = 0,\ldots,\eta
\end{aligned}
\end{equation}
where 
\begin{equation*}
\psi \jrok = S \jrok  + N\jok R \jrok  
\end{equation*}
and $x_r \jrok$ is defined as in (\ref{eq:rad_robust_design}). The first inequality in (\ref{eq:min_sim}) ensures that $\mathcal{H}_{\infty}$ nominal performance is achieved for the $RST$ structure whilst considering the frequency dependent uncertainties. The second inequality ensures that the modulus margin is at least $0.5$. With the additional low-frequency measurement at $\omega_0$,  there will be a total of $256$ frequency points ($\eta = 255$, $\omega_k \in (0,\pi f_s] \ \forall k$).

\subsection{Optimization Results} 
\label{sec:opt_results}
The SDPT3 open-source optimization package was used in conjunction with Matlab to perform the bisection algorithm \cite{SDPT3}. The solution to the optimization problem in (\ref{eq:min_sim}) leads to a 9-th order stable controller that achieves the desired performance. The main parameters of the bisection algorithm are tabulated in Table.~{\ref{tab:gamma}. 
%Note that the orders of $R$ and $T$ are chosen to be equal. Their orders are larger than $S$ to ensure better tracking performance. All the zeros of $S^{\star}(z^{-1})$ lie inside the unit circle, and thus ensuring that the open-loop system remains marginally stable.

\begin{table}
\centering
\caption{Parameters resulting from the bisection algorithm.}
\label{tab:gamma}
\begin{tabular}{c|cc}
\textit{\textbf{Parameter}} & \textit{\textbf{Value}} & \textit{\textbf{Unit}} \\ \hline
$\gamma_{\max}$              & $2.5$                    & -                      \\
$\gamma_{\min}$              & $0$              & -                      \\
$\gamma_{\text{tol}}$              & $10^{-6}$               & -                      \\
$\gamma_{\text{opt}}$              & $1.202$                & -                      \\
\textit{Optimization time}\footnotemark  & $61.3$                 & $s$                   
\end{tabular}
\end{table}
\footnotetext{This optimization time was calculated based on a computer having the following hardware specifications: Intel-Core i7, 3.4 GHz CPU, 8 GB RAM. The optimization algorithm was run using MATLAB version 8.6.0.267246 (R2015b) on a Windows 7 platform (64-bit).}

%The FRF for the desired and actualized closed-loop response is shown in Fig.~{\ref{fig:cl_freq}. 
%The expected closed-loop bandwidth is approximately equal to the bandwidth chosen for the desired specifications (i.e., $170 \: Hz$). 
The obtained output sensitivity function $| \mathcal{S}_1|$ is depicted in Fig.~{\ref{fig:sens_freq}}. It can be observed that this sensitivity function is indeed bounded by the modulus margin constraint and that a modulus margin of $0.5$ is obtained. %The calculated gain and phase margins are  $11.1 \ dB$ and $66.2^{\circ}$, respectively.

%\begin{figure}
%\centering
%\includegraphics[width=\columnwidth]{pics_prbs/closed_loop.eps}
%\caption{Comparison between the FRF's of the desired and expected closed-loop response. FRF of the desired closed-loop transfer function $\mathcal{T}_d(s)$ (solid-green line); FRF of the actual closed-loop response (solid-blue line). }
%\label{fig:cl_freq}
%\end{figure}

\begin{figure}
\centering
\includegraphics[width=\columnwidth]{pics_prbs/sens_S0.eps}
\caption{FRF of the output sensitivity function $\mathcal{S}_1$ (solid-blue line) and the bound for the modulus margin.}
\label{fig:sens_freq}
\end{figure}

For the reference current applied to this system, the error between the reference and the output current is determined by shifting the reference current such that a minimum peak error is achieved; this will be shown in the next section.
%A plot of the group delay (in units of $T_s$) is shown in Fig.~\ref{fig:track_delay}. 
%For the reference current applied to this system, the track delay $\tau$ can be estimated as the DC value of the group delay (given by (\ref{eq:group_delay_theor})) , which is approximately $829.9 \: \mu s$ (or $\tau = 2.766$ $T_s$). The reference current is delayed by using (\ref{eq:del_filt_new}) in order to calculate the experimental error (which is shown in the next section).

%\begin{figure}
%\centering
%\includegraphics[width=\columnwidth]{pics_prbs/group_delay.eps}
%\caption{A frequency-domain plot of the calculated group delay (in units of the control loop sampling time $T_s$). For the current reference profile, the estimated delay (used for calculating the error) is the DC value of the group delay; this DC value is approximately equal to $10.126 \: [T_s]$.}
%\label{fig:track_delay}
%\end{figure}

%\subsection{Experimental Validation - Frequency Domain}
%The frequency response of the closed-loop system was measured by means of a dedicated experiment. The converter was programmed to produce sinusoidal currents at given frequencies with small amplitudes ($0.4 \: A_{peak}$); both the reference and measured current were recorded with custom software diagnostic tools. The amplitude and phase of both currents were estimated by means of a three-parameter sinefit \cite{1057}, \cite{MLM12}.  
%The main features of the diagnostics tools used for signal acquisition are: 
%\begin{itemize}
	%\item sampling frequency of $10 \: kHz$
	%\item record length of $1.2 \: s$ irrespective of the frequency being probed
%\end{itemize}
%These features posed several limitations on the frequency range that could be probed:
%\begin{itemize}
	%\item \emph{high frequencies} are limited to $1$ $kHz$ by the need of having enough samples per period to properly estimate the amplitude and phase (at $1$ $kHz$, only $10000/1000 = 10$ samples are acquired for each period; furthermore, the first harmonics of $50$ $Hz$ have been discarded for this measurement in order to avoid residual ripple)  
	%\item \emph{low frequencies} are limited to about $1 \: Hz$ by the need of acquiring at least $1$ period to properly estimate both amplitude and phase
%\end{itemize}
%
%The closed-loop frequency response and the group delay (numerically calculated from the measured phase by means of (\ref{eq:group_delay_theor})) are shown in Fig.~\ref{fig:closed_loop_meas} and Fig.~\ref{fig:group_delay_meas}, respectively. From Fig.~\ref{fig:closed_loop_meas}, it can be observed that the actual closed-loop frequency response closely matches that of the desired response. Additionally, the experimental error obtained from the average value of the measured group delay and the value obtained from the DC value of the group delay in the previous section ($\tau_g(0) = 1.0126 \: ms$) is only $0.85 \: \%$.
%
%\begin{figure}
%\centering
%\includegraphics[width=\columnwidth]{pics_prbs/Experimental_Bode.eps}
%\caption{Measured frequency response of the closed-loop system (solid-blue) and the desired closed-loop system (solid-red).}
%\label{fig:closed_loop_meas}
%\end{figure}
%
%\begin{figure}
%\centering
%\includegraphics[width=\columnwidth]{pics_prbs/Experimental_Group_Delay.eps}
%\caption{The measured group delay (solid-blue) along with the group delay calculated from $\mathcal{T}_d$ (solid-red). The track delay is estimated as the average value of the data points shown in solid-black. This value is determined to be $1.042 \: ms$.}
%\label{fig:group_delay_meas}
%\end{figure}

\subsection{Experimental Validation and Comparison}
The reference and measured currents were acquired for the profile required by a specific Q-STRIP magnet (Fig.~\ref{fig:QCF_ref}). As stated in section \ref{sec:weighting_filter}, the error is calculated with respect to a delayed reference input (i.e., $e(t) = r(t-\tau) - y(t)$). For comparison purposes,  the value of $\tau$ was found by shifting the reference profile such that the minimum peak error was achieved. A total of $10$ experiments were performed; the error for both the model-based and data-driven based designs (with the associated error-bars showing the minimum and maximum errors at each sampling instant) are shown in Fig.~\ref{fig:error}. It can be observed that both designs are comfortably within the $\pm 1000$ ppm fast-transient requirement and within the $\pm 100$ ppm steady-state requirement. Indeed, both controllers achieve $\pm 100$ ppm even during the fast-transients. However, the proposed method ensures that all of the design requirements are met while eliminating the iterative process of attaining robust performance from the model-based methodology. Therefore, the proposed data-driven method proves to be superior as it achieves all of the design objectives in a single attempt.

%\begin{figure}
%\centering
%\includegraphics[width=\columnwidth]{pics_prbs/time_comp_2.eps}
%\caption{Comparison between the reference current (solid-red line), the output current resulting from the model-based controller (solid-blue line) and the output current resulting with the proposed method (solid-green line). The accelerator beam is applied at the time indicated with the dashed-blue line ($0.4s$); the error must be calculated after this time. The error after the time indicated with the dashed-red line ($0.4054s$) must be within $\pm 100$ ppm.}
%\label{fig:output}
%\end{figure}

\begin{figure}
\centering
\includegraphics[width=\columnwidth]{pics_prbs/error_comp_shift.eps}
\caption{Comparison between the error resulting from the model-based design (solid-black line with red error-bars) and the error resulting with the proposed method (solid-black line with green error-bars). %The accelerator beam is applied at the time indicated with the dashed-blue line ($0.4s$); the error must be calculated after this time. The error after the time indicated with the dashed-red line ($0.4054s$) must be within $\pm 100$ ppm.}
}
\label{fig:error}
\end{figure}

\section{Conclusion}
\label{sec:6}
A new data-driven method for computing a robust controller that attains $\mathcal{H}_{\infty}$ performance has been presented. A frequency-domain approach has been used in order to avoid the problem of unmodeled dynamics associated with parametric models. The necessary and sufficient conditions for the existence of $RST$ controllers with multiple $\mathcal{H}_\infty$ performance have been developed in terms of a set of convex constraints.  Constraints have been devised in order to design a controller which considers frequency dependent uncertainties, ensures a minimum value for the modulus margin, and to assure the controller stability. This method has been applied to a power converter control system which uses an $RST$ controller structure and is used for experimental purposes at CERN. In the case study presented in this paper, it has been shown that the proposed data-driven method offers an optimization-based systematic approach that leads to low-order $RST$ controllers meeting the challenging specification for particle trajectory tracking. With the proposed methodology, the process of obtaining a model and iteratively tuning the desired closed-loop bandwidth to attain the proper stability margins is eliminated whilst achieving the desired tracking performance.

%For further research, it will be desired to determine the order of the controller polynomials that will produce the optimal tracking performance while attaining adequate disturbance rejection.

%This paper has proposed a new method for computing multivariable SP controllers with $H_\infty$ performance. The method is based on a convex approximation of the $H_\infty$ robust performance criterion in the Nyquist diagram. This approximation relies on the choice of a desired open-loop transfer function $\vec{L}_D$ for the dead-time free model of the plant. With a linearly parameterized controller, one possesses the flexibility to design PI, PID, or higher order controllers for a system. For the industrial processes considered in this paper, the proposed method has been proven to be robust; $H_{\infty}$ performance was achieved for MIMO systems with both multiplicative and time delay uncertainties. Moreover, the solution to the optimization problem generates a controller such that a system becomes decoupled and simultaneously optimizes the single-loop performances of the SISO subsystems.

%\appendix[]
%\begin{table}[H]
%\centering
%\caption{Solution to the optimization problem in (\ref{eq:min_sim}); parameters reported with a reduced number of significant digits.}
%\label{my-label}
%\begin{tabular}{c|c|c}
%$\rho_R$ & $\rho_S^{\star}$ & $\rho_T$ \\ \hline
%$2.064$      & $1$              & $0.9025$      \\ \hline
%$- 0.9093$      & $- 0.4093$              & $- 0.3494$      \\ \hline
%$- 1.08$      & $- 1.014 $              & $- 0.004285$      \\ \hline
%$0.4282$      & $0.05461$              & $- 0.335$      \\ \hline
%$- 1.152$      & $- 0.08757$              & $0.01702$      \\ \hline
%$0.5985$      & $0.1138$              & $- 0.1231$      \\ \hline
%$0.06517$      & $0.3425$              & $0.08679$     \\ \hline
%$0.1158$   &       -       & $- 0.06379$     
%\end{tabular}
%\end{table}

\iffalse
\section*{Acknowledgement}
The authors of this paper would like to thank Louis de Mallac for his contribution to the experimental setup of the power converter control system and Quentin King (both with the TE department at CERN) for providing support for the controller implementation within the FGC software environment.
\fi

%\begin{IEEEbiographynophoto}
%Author1 Biography
%\end{IEEEbiographynophoto}
%\smallskip{}
%\begin{IEEEbiographynophoto}
%Author2 Biography
%\end{IEEEbiographynophoto}

%\bibliography{/Users/anicolet/Google Drive/EPFL Research/Publications/linear}
\bibliography{linear}

\iffalse
\vspace*{-2\baselineskip}

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{pics/bib_achille.eps}}]{Achille Nicoletti} was born in Quebec, Canada on June 20, 1983. He received both his B.Sc. in Physics and B.E.E degrees at Cleveland State University (USA) in 2011 (summa cum laude). He also received his M.Sc. in Electrical Engineering at the same university in 2012. During his studies in receiving his M.Sc. degree, he was recruited by Philips in Highland Heights, Ohio, where he was employed as an Electrical Design Engineer (II) and was responsible for designing the control system for the next generation computed tomography (CT) products. During this time at Philips, he received his Six Sigma Green Belt certification. In 2014, he decided to pursue a PhD in the field of control systems at the Swiss Federal Institute of Technology in Lausanne (EPFL), Switzerland. In the same year, he had been accepted to a doctoral fellowship program at CERN. His main research interests include robust data-driven control methods (frequency domain), and optimization in systems and control.
\end{IEEEbiography}

\vspace*{-2\baselineskip}

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{pics/bib_michele.eps}}]{Michele Martino}
was born in Napoli, Italy, on July 23, 1975. He received the M.Sc. in Electronics Engineering (magna cum laude) and the Ph.D. in Electrical Engineering at the University of Napoli Federico II. PhD research was carried out at CERN on the high precision position survey of the Large Hadron Collider collimators. In 2004 he was with FIAT as control algorithm designer on Traction Control and then, in 2005, he joined I.N.F.N (Italian National Institute of Nuclear Physics) as fellow to work on the LHCb muon detector front end electronics test. Since June 2006 he is at CERN and in 2010 joined the Electrical Power Converter group to work on the high precision measurement and control of the power converters of CERN accelerators. His main research subjects are LVDT sensors characterization, high precision pulsed current and voltage measurements, digital control for power converters.
\end{IEEEbiography}

\vspace*{-2\baselineskip}

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{pics/bib_alireza.eps}}]{Alireza Karimi} received his B. Sc. and M. Sc. degrees in Electrical Engineering in 1987 and 1990 from Amir Kabir University (Tehran Polytechnic). After 3 years of industrial experience he joined Institut National Polytechnique de Grenoble (INPG) in France and received his DEA and Ph. D. degrees both on Automatic Control in 1994 and 1997, respectively. He was Assistant Professor at Electrical Engineering Department of Sharif University of Technology in Teheran from 1998 to 2000. He is currently Senior Scientist at the Automatic Laboratory of Swiss Federal Institute of Technology in Lausanne (EPFL), Switzerland. He was an Associate Editor of European Journal of Control from 2004 to 2013. His research interests include closed-loop identification, data-driven controller tuning approaches and robust control.
\end{IEEEbiography}
\fi
\end{document}

### 2017-02-11 Theory and Notes/CERN_objectives/Discussion.tex
adding files to git (11/2/2017)

\documentclass[12pt]{article}
%\usepackage[a4paper, total={6.5in, 8in}]{geometry}
\usepackage{graphicx}  % Add graphics capabilities
 \usepackage{color}

\usepackage{amsmath} % assumes amsmath package installed
\usepackage{amssymb}  % assumes amsmath package installed
\usepackage{amsthm}
\usepackage{epstopdf}
\usepackage{float}

\title{\LARGE \bf Discussion of CERN Objectives}
\begin{document}
\maketitle

\hrule
\begin{flushright}
Date: 27/06/2016
\end{flushright}
\textbf{Discussion 1: Optimal gains for voltage loop}

We are now trying to design controllers for the inner-loop of the power converter control system. Upper management has insisted that they want to control the inner loop with gains only. We are able to analytically derive the solutions for the gains such that a desired bandwidth is achieved, but there are some limitations to the amount of bandwidth that you ask for.

We know that for bandwidths of less that $100 \: Hz$, the analytical solution gives us very goods results. I am now trying to use the data-driven method to obtain the solution for the gains, but the resulting solution from the optimization problem does not give good results. To obtain the gains, I am using the $H_\infty$ weighted sensitivity method. The closed-loop transfer function is given as follows:
\begin{equation}
T(s) = \frac{k_wG(s)}{1+k_iG(s)H(s) + k_uG(s)}
\end{equation} 
where $k_i, k_u, k_w$ are the gains to be found. $G(s)$ and $H(s)$ are stable transfer functions ($G$ is strictly proper, $H$ is proper, $H^{-1}$ is marginally stable). The sensitivity function that I shaped is:
\begin{equation}
S = 1-T =\frac{1+k_iGH+G(k_u-k_w)}{1+k_iGH+k_uG} 
\end{equation}
What is nice is that the numerators and denominators of these sensitivity functions are linearly parameterized in the gains, so the SPR condition can be used to formulate the convex optimization problem for $\| W_1S\|_\infty < \gamma$:
\begin{equation}
\Re \{ 1+k_iGH+k_uG\} > \gamma^{-1} |W_1(1+k_iGH+G(k_u-k_w))| 
\end{equation}
where $W_1 = (1-T_{des})^{-1}$ and $T_{des}$ is the desired closed loop transfer function. We have been selecting $T_{des}$ as a typical second order damped transfer function ($T_{des} = \omega_n^2(s^2+2\zeta\omega_n s + \omega_n^2 )^{-1}$). For $\zeta = 0.8$ and a desired bandwidth of $100 \: Hz$, the analytical solution produces satisfactory results; but the convex optimization problem does not produce gains that give good results. In fact, I get $\gamma_{opt} = 32.5$. Fig.~\ref{fig:volt_comp} shows the FRF comparison between the responses obtained.
\begin{figure}
\centering
\includegraphics[width=\columnwidth]{pics/voltage_loop.eps}
\caption{Closed-loop FRF comparison between solutions obtained.}
\label{fig:volt_comp}
\end{figure}

What do you think the issue is? Am I shaping the wrong sensitivity function? Is there a limitation with the $H_\infty$ method by using strict gains?

{\bf Answer AK:} The convexification for fixed low order controllers is too conservative. In fact there exists a multiplier F that reduces the conservatism but make the problem non-convex (that can be solved by PSO).

Another solution is to use the linearization method that I sent you sometimes ago by H2 control, which I believe has less conservatism for your problem. The similar linearization can be used also for H infinity if you wish.

{\bf Answer AN:} I will now attempt to derive the convex optimization problem (using the Shur complement lemma) for the specific controller configuration that we have for the damping loop. Below is a figure of the damping loop, where it is desired to find the gains $k_i$ and $k_u$ such that the desired bandwidth (with desired damping) is achieved. 
\begin{figure}
\centering
\resizebox{1\columnwidth}{!}{\input{damping_loop.pdf_tex}}
\caption{Damping loop}
%\label{fig:pc}
\label{fig:damping_loop}
\end{figure}

The closed-loop TF is:
\begin{equation}
T(s) = \frac{(1+k_u)G(s)}{1+k_iG(s)H(s) + k_uG(s)}
\end{equation} 
The error sensitivity function will be:
\begin{equation}
S =1-T =  \frac{1+k_iGH - G}{1+k_iGH + k_uG}
\end{equation} 
Using the sufficient condition you present in your paper with Christoph, we can formulate the loop-shaping constraint. But instead of shaping the open-loop TF $L(s)$, we can shape the closed-loop TF directly. In the $H_\infty$ sense, the optimization problem to solve is:
\begin{equation} \label{eq:min_loopshape}
\begin{aligned}
& {\text{minimize}}
& & \gamma  \\
& \text{subject to:} & & (T-T_d)^*(T-T_d) < \gamma
\end{aligned}
\end{equation}
where $T_d$ is the desired closed-loop TF. Let $P = 1+k_iGH + k_uG$; then the above constraint can be written as:
\begin{equation}
(G(1+k_u)-PT_d)^*\gamma^{-1}(G(1+k_u)-PT_d) - P^*P<0
\end{equation} 
By using the linearization constraint in your paper $(P^*P \geq P^*P_0 + P_0^*P - P_0^*P_0)$, then we can write the following convex optimization problem:
\begin{equation} \label{eq:min_loopshape}
\begin{aligned}
& {\text{minimize}}
& & \gamma  \\
& \text{subject to:} \\
& & &
\begin{bmatrix}
P^*P_0 + P_0^*P - P_0^*P_0 & [G(1+k_u)-PT_d]^* \\ 
G(1+k_u)-PT_d & \gamma
\end{bmatrix} > 0
\end{aligned}
\end{equation}
where $P_0 = 1+k_i^0GH + k_u^0G$; $k_i^0$ and $k_u^0$ are the initializing gains.

{\bf Remark:} \textit{As a side note, the linearization constraint can actually be written in a more compact form: 
\begin{equation}
P^*P_0 + P_0^*P - P_0^*P_0 = \Re \{2PP_0^* - |P_0|^2 \}
\end{equation}
This will eliminate the error you had stated that MATLAB was giving (not removing the small complex part of the equation).}

Now, to analyze the stability, I had to derive it for this specific problem. I used your draft paper as a reference. The open-loop TF is given as $L = k_uG(1+k_iGH)^{-1}$. Let $F = k_u(1+k_iGH)^{-1}$, so that $L = GF$. By the Nyquist stability criterion, the closed-loop system is stable if $1+GF$ makes $N_G+N_F$ counter-clockwise encirclements of the origin (where $N_G$ and $N_F$ are respectively the number of RHP poles of $G$ and $F$). The Nyquist plot of $1+GF$ must also not pass through the origin.

For initial stabilizing gains $k_i^0$ and $k_u^0$, and for feasible solutions $k_u$ and $k_i$ to the constraint $P^*P_0+P_0^*P > 0$, I claim that the closed-loop system is stable if $k_u \neq 0$. Here is the proof:

The winding number of $P^*P_0$ is given as follows:
\begin{equation} \label{eq:winding_proof}
\begin{aligned}
\underset{D}{\mbox{wno}} \{ P^*P_0\} &= \underset{D}{\mbox{wno}} \{ P^*\} + \underset{D}{\mbox{wno}} \{ P_0\} \\
&= -\underset{D}{\mbox{wno}} \{ 1+k_iGH+k_uG\} + \underset{D}{\mbox{wno}} \{ 1+k_i^0GH+k_u^0G\} \\
&=-\underset{D}{\mbox{wno}} \{ (1+k_iGH)(1+GF)\} + \underset{D}{\mbox{wno}} \{ (1+k_i^0GH)(1+GF_0)\}
\end{aligned}
\end{equation}
where $F_0 = k_u^0(1+k_i^0GH)^{-1}$. Note that $G$ is strictly proper and $H$ is proper, which means that $F$ is proper and $GF$ is strictly proper. So the winding number of $P^*P_0$ can be evaluated over $\Omega$ instead of the $D$-contour. We can write $1+k_iGH = k_uF^{-1}$ and $1+k_i^0GH = k_u^0F_0^{-1}$; therefore, we will have the following:
\begin{equation} \label{eq:winding_proof2}
\begin{aligned}
\mbox{wno} \{ P^*P_0\} &= -\mbox{wno} \{ k_uF^{-1}(1+GF)\} + \mbox{wno} \{ k_u^0F_0^{-1}(1+GF_0)\} \\
&= -\mbox{wno} \{F^{-1}\} - \mbox{wno} \{1+GF\} +\mbox{wno} \{F_0^{-1}\} + \mbox{wno} \{1+GF_0\} 
\end{aligned}
\end{equation}
$P^*P_0+P_0^*P > 0$ implies that $\Re\{ P^*P_0\} > 0$, which means that the Nyquist of $P^*P_0$ will not pass through or encircle the origin. So $\mbox{wno} \{ P^*P_0\} = 0$. From (\ref{eq:winding_proof2}), we will then get the following equation:
\begin{equation} \label{eq:winding_proof3}
\begin{aligned}
\mbox{wno} \{ 1+GF\} &= -\mbox{wno} \{ F^{-1}\} + \mbox{wno} \{ F_0^{-1}\} + \mbox{wno} \{ 1+GF_0\}\\
&= \mbox{wno} \{ F\} - \mbox{wno} \{ F_0\} + \mbox{wno} \{ 1+GF_0\} \\
&= N_F - N_{F_0} + N_G + N_{F_0} \\
&= N_G+N_F
\end{aligned}
\end{equation}
Since $k_u \neq 0$, then $F\neq 0$ for all $\omega$. In other words, for $k_u \neq 0$, the Nyquist theorem is met. This looks like condition 1 in Theorem 2 of your paper ($det(Y) \neq 0$). The other 2 conditions in the theorem don't seem to apply for this particular controller structure.

\hrule
\begin{flushright}
Date: 16/09/2016
\end{flushright}
\textbf{Discussion 2: Optimal Delayed Performance}

I would like to now discuss the best way to formulate an optimization problem to ensure that the closed-loop transfer function is a delay (or fractional delay). I have discussed with you in the past that I was able to achieve great performance when I performed a 2-step optimization method (first design $R$ and $S$ to ensure modulus margin, and then design $T$ for performance). However, I believe that I can formulate a problem to design all of the RST controllers in one step.

So suppose that we are interested in minimizing the following objective function:
\begin{equation} \label{eq:min_for_delay_inf}
\|N(j\omega)T(j\omega) - e^{-j\omega \tau }[NR+MS](j\omega)\|_2
\end{equation}
Note that in the RST structure, the closed-loop transfer function is defined as
\begin{equation}
H = \frac{NT}{NR+MS}
\end{equation}
Therefore, minimizing (\ref{eq:min_for_delay_inf}) will ensure that the closed-loop system is a pure delay (delayed by a value of $\tau$), which is what they want here at CERN. With the RST controller linearly parameterized, this becomes a convex problem. In fact, this optimization problem is convex for any norm; so we can consider minimizing the following objective (removing the $j\omega$ notation):
\begin{equation} \label{eq:min_for_delay}
\|NT - e^{-j\omega \tau }(NR+MS)\|_n
\end{equation}
where $n \in [1,\infty]$.

I tried some simulations using the above objective function (and adding a constraint for stability) and the results seem to be very promising! The only problem is knowing how to choose $\tau$ to ensure a feasible problem. But as long as $\tau$ is greater than the delay of the open-loop system, then feasibility can be achieved.

One thing to also note is that if the plant has stable zeroes, then $\tau$ can be chosen such that it is an integer multiple of the sampling time (and simultaneously larger than the plant delay); this will guarantee that the closed-loop transfer function will be a pure delay (as the optimization algorithm will design an RST such that the stable zeroes are cancelled). However, if the plant has unstable zeroes, then $\tau$ can simply be chosen to be larger than the plant delay, and the optimization algorithm will design a controller to get as close to $\tau$ as possible. But with unstable zeroes, you can never get the closed-loop transfer function to be a pure delay, since you cannot cancel the unstable zeroes. I noticed that with unstable zeroes, minimizing the 1-norm seems to produce the best results; with stable zeroes, minimizing any norm gives the desired results.

{\bf Remark:} \textit{This optimization problem is essentially equivalent to minimizing $\gamma$ in $\| W \mathcal{S}\|_\infty < \gamma$, where $\mathcal{S}$ is the error sensitivity function and $W = (1-e^{j\omega \tau})^{-1}$. But in (\ref{eq:min_for_delay}), we remove the process of performing the bisection iteration, and get a solution much faster. Another advantage of this method is that you can consider minimizing the 1-norm or 2-norm, and not necessarily the $\infty$-norm (as in $\| W \mathcal{S}\|_\infty < \gamma$).}

\vspace{1cm}
EXAMPLE: Suppose the plant model is given as:
\begin{equation}
G(z^{-1}) = z^{-2} \frac{0.48 + 0.36 z^{-1} + 0.06 z^{-2}}{ 1 - 0.3 z^{-1} + 0.8 z^{-2}}
\end{equation} 
 This plant model has stable zeroes, so we should be able to get the closed loop transfer function such that it is a pure delay. It is a stable plant, so $N = G$ and $M=1$ can be selected. According to CERN, we must also put a constraint to ensure a modulus margin of at least 0.5 and have another constraint to have the controller $S$ stable (i.e., $\Re \{ S\} > 0$ for all $\omega$). The above plant model has a pure delay of $2T_s$ with two additional zeroes; so lets choose $\tau = 3T_s$ (with $T_s = 100 \: \mu s$). Below is the step response for the RST designed by minimizing (\ref{eq:min_for_delay}) for $n \in \{1,2,\infty \}$:

\begin{figure}[H]
\centering
\includegraphics[width=\columnwidth]{pics/stable_zero_resp}
\caption{Step response of closed-loop system. 1-norm, 2-norm, and $\infty$-norm give all the same response.}
\label{fig:stable_zero_resp}
\end{figure}

The second example will consider the following system (which has an unstable zero):
\begin{equation}
G(z^{-1}) = z^{-2} \frac{0.18  + 0.51 z^{-1} + 0.21 z^{-2}}{ 1 - 0.3 z^{-1} + 0.8 z^{-2}}
\end{equation} 
Since this plant model has an unstable zero, a pure-delay cannot be achieved for the closed-loop transfer function. The best we can do is a fractional delay. Since we don't know what the value of the fractional delay should be for optimal performance, then we can simply select a pure delay for $\tau$ and let the optimization algorithm determine the best RST to get to this value. With an unstable zero in the plant, we can increase the delay to $\tau = 6T_s$ to improve the results. Below is the step response for the RST designed by minimizing (\ref{eq:min_for_delay}) for $n \in \{1,2,\infty \}$

\begin{figure}[H]
\centering
\includegraphics[width=\columnwidth]{pics/unstable_zero_resp}
\caption{Step response of closed-loop system for different norm minimizations.}
\label{fig:unstable_zero_resp}
\end{figure}

\begin{figure}[H]
\centering
\includegraphics[width=\columnwidth]{pics/step_close_up}
\caption{Zoomed version of the step response for the plant with unstable zeroes (from plot above).}
\label{fig:unstable_zero_resp}
\end{figure}

From the figure above, the $\mathcal{H}_\infty$ norm optimization seems to give the worst performance, since it does not converge to unity. The 1- and 2- norms seem to both give similar results. It can be seen that there are some oscillations and that the closed-loop transfer function is not a pure delay (due to the unstable zero).

{\bf Remark:} \textit{The results for the plant with the unstable zeroes can be further improved by increasing the controller order and increasing the delay (for example, $\tau = 10T_s$).}

\end{document}

### 2017-02-11 Theory and Notes/H2_Control_Problem/Discussion.tex
adding files to git (11/2/2017)

\documentclass[12pt]{article}
\bibliographystyle{IEEEtran}
%\usepackage[a4paper, total={6.5in, 8in}]{geometry}
\usepackage{graphicx}  % Add graphics capabilities
 \usepackage{color}

\usepackage{amsmath} % assumes amsmath package installed
\usepackage{amssymb}  % assumes amsmath package installed
\usepackage{amsthm}
\usepackage{epstopdf}

\title{\LARGE \bf Discussion of $H_2$ Control Problem}
\begin{document}
\maketitle

\hrule
\begin{flushright}
Date: 13/04/2016 \\
Written by: Achille Nicoletti
\end{flushright}
\textbf{Discussion 1: Defining the optimality for the $H_2$ problem}

You define the $H_2^2$ optimization problem (in page 3 of your note) to be the following:

\begin{equation} \label{eq:opt_prob_1}
\begin{aligned}
& \underset{ \{X,Y,\gamma\}}{\text{minimize}}
& & \sum_{k=1}^Q \gamma (\omega_k)  \\
& \text{subject to:} & & |W_1MY(\omega_k)|^2 < \gamma(\omega_k) |NX(\omega_k)+MY(\omega_k)|^2  \\ 
& & & k = 1,\ldots,N
\end{aligned}
\end{equation}

Suppose that there exist optimal controllers $X_0$, $Y_0 \in \bf{RH_{\infty}}$ which satisfy the $H_2^2$ control problem. Then is it correct to state that the optimal solution $\gamma_0(\omega)$ is

\begin{equation}
\gamma_0(\omega) =  \left\lvert\frac{W_1MY_0(\omega)}{NX_0(\omega) + MY_0(\omega)} \right\rvert ^2
\end{equation}

{\bf Answer by AK:} Yes

{\bf Answer by AN:}

In this case, I think that the proof for convergence is very similar to the one you presented in the journal paper sent to International Journal of Robust and Nonlinear Control (for the $H_\infty$ criterion).

Let $X_n^*$ and $Y_n^*$ be the projections of $X_0$ and $Y_0$ into the subspace spanned by an $n$ dimensional orthogonal basis functions and define $\gamma_n^*$ as:
\begin{equation}
\gamma_n^*(\omega) =  \left\lvert\frac{W_1MY_n^*(\omega)}{NX_n^*(\omega) + MY_n^*(\omega)} \right\rvert ^2
\end{equation}
Assume that $\gamma_n^*(\omega)$ is bounded and that $NX_n^* + MY_n^*$ has no zeros on the imaginary axis (which you proved in the journal paper). Since $\gamma_0(\omega_k) > 0$ and $\gamma_n^*(\omega_k) > 0$ for every $k$, then it is convenient to investigate the convergence of $|\sqrt{\gamma_n^*(\omega_k)} - \sqrt{\gamma_0(\omega_k)}|$ instead of $|\gamma_n^*(\omega_k) - \gamma_0(\omega_k)|$ as $n \rightarrow \infty$. By using the reverse triangle inequality, we will have the following condition:

\begin{equation} \label{eq:gamma_bound}
\begin{aligned}
\left\lvert \sqrt{\gamma_n^*(\omega_k)} - \sqrt{\gamma_0(\omega_k)} \right\rvert  &\leq  \left\lvert  \frac{W_1MY_n^*(\omega_k)}{NX_n^*(\omega_k) + MY_n^*(\omega_k)} - \frac{W_1MY_0(\omega_k)}{NX_0(\omega_k) + MY_0(\omega_k)}   \right\rvert \\  &\leq \left\lvert  \frac{W_1MN[X_n^*(Y_0-Y_n^*)(\omega_k) - Y_n^*(X_0-X_n^*)(\omega_k)]}{[NX_n^*(\omega_k) + MY_n^*(\omega_k)][NX_0(\omega_k)+MY_0(\omega_k)]} \right\rvert \\ & \hspace{6.3cm} \mbox{for } k=1,\ldots,Q
 \end{aligned}
\end{equation}

$X_n^*$ and $Y_n^*$ are the projections of $X_0$ and $Y_0$, respectively, into the subspace spanned by orthogonal basis functions; therefore, according to \cite{AN99b},
\begin{equation} 
\begin{aligned}
\lim_{n \to \infty} \|X_0 - X_n^* \|_p &=0\\
\lim_{n \to \infty} \|Y_0 - Y_n^* \|_p &=0
 \end{aligned}
\end{equation}
where $p \in (1,\infty)$. Therefore, since the frequency functions in (\ref{eq:gamma_bound}) are bounded for every $k$, and the denominator has no zero on the imaginary axis, then
\begin{equation} 
\begin{aligned}
\lim_{n \to \infty} \left\lvert \sqrt{\gamma_n^*(\omega_k)} - \sqrt{\gamma_0(\omega_k)} \right\rvert =0 \Longleftrightarrow \lim_{n \to \infty} \sqrt{\gamma_n^*(\omega_k)} = \sqrt{\gamma_0(\omega_k)} \\
\mbox{for } k = 1,\ldots,Q
 \end{aligned}
\end{equation}
Since $\sqrt{\gamma_n^*(\omega_k)}$ is a convergent sequence, then so is $\gamma_n^*(\omega_k)$; therefore, it is evident that
\begin{equation} 
\begin{aligned}
\lim_{n \to \infty} \gamma_n^*(\omega_k) =   \lim_{n \to \infty}  \left[ \sqrt{\gamma_n^*(\omega_k)}\right] ^2 = \left[ \lim_{n \to \infty}  \sqrt{\gamma_n^*(\omega_k)}\right] ^2 = \left[ \sqrt{\gamma_0(\omega_k)}\right] ^2 = \gamma_0(\omega_k)\\
\mbox{for } k = 1,\ldots,Q
 \end{aligned}
\end{equation}
The above condition shows that as $n \rightarrow \infty$, the solution obtained with projections $X_n^*$ and $Y_n^*$ converges to the optimal solution.

{\bf Answer by AK:} The problem is that the optimization in (1) is not convex, while for the $H_\infty$ case we could make the optimization quasi-convex and solve it by bisection algorithm. In fact we should have two properties: first the convexity of the optimization problem and second the convergence to the optimal solution by increasing the order. What you did was to show the convergence for a non convex problem. This result is not useful because in a non-convex optimization you cannot show that the local optimal solution is monotonically non-increasing.

\hrule
\begin{flushright}
Date: 21/04/2016 \\
Written by: Achille Nicoletti
\end{flushright}
\textbf{Discussion 2: Proving the optimality for the $H_\infty$ problem}

So now we must re-prove the theorem for converging to the optimal solution for the $H_\infty$ case. I have one mathematical question I would like to pose. Suppose we have 2 real numbers $x$ and $y$. Then we know that
\begin{equation}
|x - y| =0 \ \mbox{if and only if } x = y
\end{equation}
Now suppose that $X_0$ is an optimal controller for the $H_\infty$ problem and that $X_n$ is the controller with an $n$-dimensional orthogonal basis function (for the convex problem). Then we know that
\begin{equation} \label{eq:converge_cond}
\lim_{n \to \infty} \|X_0 - X_n \|_p =0
\end{equation}
where $p \in (1,\infty)$. Can the above equation be equivalently stated as
\begin{equation}
\lim_{n \to \infty} \|X_0 - X_n \|_p =0 \ \mbox{if and only if } X_0 = X_{n \to \infty}  
\end{equation}

{\bf Answer by AK:} $X_0$ cannot be equal to $X_n$ because they do not have the same structure.

{\bf Answer by AN:} Ah yes, sorry I forgot to put the norm in the statement:
\begin{equation}
\lim_{n \to \infty} \|X_0 - X_n \|_p =0 \ \mbox{if and only if } \|X_0\|_p = \|X_{n \to \infty}\|_p  
\end{equation}
$X_0$ and $X_n$ in (\ref{eq:converge_cond}) are both functions of $\omega$, right? So is structure important? I believe that in \cite{AN99b}, they prove this convergence based on the  Fourier series of the basis functions.

{\bf Answer by AK:} The left hand side is much stronger. You may have $\|X_0\|_p = \|X_{n \to \infty}\|_p$ while  $X_0$ and $X_n$  are completely different. In other words $\|X_0\|_p = \|X_{n \to \infty}\|_p$ is a sufficient condition for $\lim_{n \to \infty} \|X_0 - X_n \|_p =0$ but it is not necessary.

{\bf Answer by AN:} Here is the analysis I performed for proving the convergence for the $H_\infty$ problem. The optimal solution for the true $H_\infty$ optimization problem is 
\begin{equation}
\gamma_0 = \sup_{\omega \in \Omega} \left \lvert \frac{W_1MY_0}{ NX_0 + MY_0} \right \rvert
\end{equation}
Now define 
\begin{equation} \label{convexopt}
\gamma_n^* = \sup_{\omega \in \Omega} \left \lvert \frac{W_1MY_n^*}{\Re\{ NX_n^* + MY_n^*\}} \right \rvert
\end{equation}
where $X_n^*$ and $Y_n^*$ are the projections of $X_0$ and $Y_0$ into the subspace spanned by an n dimensional orthogonal basis function. We assume that $\gamma_n^*$ is bounded (i.e., $NX_n^* + MY_n^*$ has no zero on the imaginary axis, which you have already proved in the journal paper). By using the fact that for two real functions $f$ and $g$, $\sup (f) - \sup (g) \leq \sup(f-g)$, we get the following condition:

\begin{equation} \label{eq:H_inf_ineq}
\begin{aligned}
\gamma_0-\gamma_n^*  =& \sup_{\omega \in \Omega} \left \lvert \frac{W_1MY_0}{ NX_0 + MY_0} \right \rvert  - \sup_{\omega \in \Omega} \left \lvert \frac{W_1MY_n^*}{\Re\{ NX_n^* + MY_n^*\}} \right \rvert  \\
\leq & \sup_{\omega \in \Omega} \left[ \left \lvert \frac{W_1MY_0}{ NX_0 + MY_0} \right \rvert  - \left \lvert \frac{W_1MY_n^*}{\Re\{ NX_n^* + MY_n^*\}} \right \rvert \right] \\
 =&   \sup_{\omega \in \Omega} \left[ \frac{|W_1MY_0 \Re\{ NX_n^*+MY_n^*\}| - |W_1MY_n^*(NX_0+MY_0)| }{|F|} \right] \\
 \leq & \sup_{\omega \in \Omega} \left[ \frac{|W_1MY_0 (NX_n^*+MY_n^*)| - |W_1MY_n^*(NX_0+MY_0)| }{|F|} \right]  \\
  \leq & \sup_{\omega \in \Omega} \left \lvert \frac{W_1MY_0 (NX_n^*+MY_n^*) - W_1MY_n^*(NX_0+MY_0) }{F} \right \rvert \\
  = & \sup_{\omega \in \Omega} \left \lvert \frac{W_1MNX_n^*(Y_0-Y_n^*) - W_1MNY_n^*(X_0-X_n^*) }{F} \right \rvert 
\end{aligned}
\end{equation}
where $F = (NX_0+MY_0) \Re\{ NX_n^*+MY_n^*\}$. But according to \cite{AN99b},
\begin{equation} 
\begin{aligned}
\lim_{n \to \infty} \|X_0 - X_n^* \|_p &=0\\
\lim_{n \to \infty} \|Y_0 - Y_n^* \|_p &=0
 \end{aligned}
\end{equation}
where $p \in (1,\infty)$. Therefore, since (\ref{eq:H_inf_ineq}) is bounded, and the denominator has no zero in the imaginary axis,
\begin{equation}
\lim_{n\to\infty} \gamma_n^* = \gamma_0
\end{equation} 
On the other hand, $\gamma_n$ (i.e., the solution to the convex optimization problem) is always less than or equal to $\gamma_n^*$ and greater than the optimal solution $\gamma_0$. Thus $\gamma_n$ converges from above to $\gamma_0$ and this convergence is monotonic because the basis functions of order $n$ are a subset of those of order $n + 1$, which ensures that $\gamma_{n+1} \leq \gamma_n$.

{\bf Answer by AK:} It's nice but it is not clear if $X_n$ and $Y_n$ are the projection of $X_0$ and $Y_0$ or they are the solutions of the convexified optimization problem in (\ref{convexopt}). In the paper we use two different notation for that leading to $X^*_n$ and $Y_n^*$. If you suppose that these are the same you should prove it.

{\bf Answer by AN:} Yes, I should have made it more clear. I modified the solution (see above).

{\bf Answer by AK:} It's now perfect.
\bibliography{linear2}
\end{document}

### 2017-02-11 Theory and Notes/Nonlinear_Uncertainty/Discussion.tex
adding files to git (11/2/2017)

\documentclass[12pt]{article}
\bibliographystyle{IEEEtran}
%\usepackage[a4paper, total={6.5in, 8in}]{geometry}
\usepackage{graphicx}  % Add graphics capabilities
 \usepackage{color}

\usepackage{amsmath} % assumes amsmath package installed
\usepackage{amssymb}  % assumes amsmath package installed
\usepackage{amsthm}
\usepackage{epstopdf}
\newtheorem{theorem}{Theorem}

\title{\LARGE \bf Discussion of Nonlinear Control Problem}
\begin{document}
\maketitle

\hrule
\begin{flushright}
Date: 9/05/2016
\end{flushright}
\textbf{Discussion 1: Using describing function as an uncertainty}

Suppose that the nominal plant transfer function is $G$ with the perturbed transfer function of the form $\hat{G} = G(1+\Delta W_2)$ ($W_2$ is fixed, stable transfer function). If $\| \Delta\|_{\infty}<1$, then as described in \cite{DFT92}, $W_2$ can be chosen such that
\begin{equation} \label{eq:uncertain_profile}
\left \lvert \frac{\hat{G}(j\omega)}{G(j\omega)} - 1 \right \rvert \leq |W_2(j\omega)|, \quad \forall \omega
\end{equation}
so that $W_2(j\omega)$ provides the uncertainty profile.

Let us consider the saturation describing function (with a slope of $1$) given as follows:
\begin{equation}
N(A) = 
\begin{cases}
1, & \text{if }A \leq \delta \vspace{0.6em}\\
\frac{2}{\pi}\left[\sin^{-1}\frac{\delta }{A} + \frac{\delta }{A}\sqrt{1-\left(\frac{\delta }{A}\right)^2}\right], & \text{if }A>\delta 
\end{cases}
\end{equation}
where $A$ is the amplitude of the sine signal that enters the saturation, $\delta $ is the value at which saturation occurs. Notice that $N(A)\in [0,1]$; this means that $N(A)$ can be modeled as an uncertainty. If the saturation block is in series with the plant (as is usually the case), then the perturbed model can be described as $\hat{G} = GN(A)$, where $G$ is the nominal model. In other words, $N(A)$ can be treated as a multiplicative perturbation of the nominal plant. By using the condition in (\ref{eq:uncertain_profile}), we will get the following constraint:
\begin{equation}
|N(A)-1|\leq |W_2(j\omega)|, \quad \forall \omega
\end{equation}
However, since $N(A) \in [0,1]$, then we can consider $W_2(j\omega) \geq 1$ for all $\omega$. Therefore, to reduce the conservatism, we can simply choose $W_2(j\omega) = 1$.

\vspace{1cm}
\textbf{Discussion 2: Stability using circle criterion}

I will now be deriving the conditions to achieve stability given a time-variant memoryless nonlinearity (in the frequency domain). As we had already spoken about, I will use the the circle criterion for this.

Suppose we have a closed-loop system with a nonlinearity $\Phi$, a plant $G(s)$ and controller $C(s)$, as depicted in Fig.~\ref{fig:nl_block}. 
\begin{figure}
\centering
\resizebox{1\columnwidth}{!}{\input{nl_block.pdf_tex}}
\caption{Block diagram with nonlinear component.}
%\label{fig:pc}
\label{fig:nl_block}
\end{figure}

The type of nonlinearity that will be addressed here is of the sector type. The sector condition can be expressed as follows:
\begin{equation} \label{eq:sector_cond}
k_1 u \leq \Phi(t,u) \leq k_2 u, \quad \forall t \geq 0, \forall u \in [a,b] 
\end{equation}
where $k_1, k_2, a$ and $b$ are constants (with $k_2 > k_1$ and $a < 0 < b$). This condition can be interpreted as a nonlinearity which is bounded by two straight lines with slopes $k_1$ and $k_2$ that pass through the origin. Fig.~\ref{fig:nl_graph} depicts this sector nonlinearity when (\ref{eq:sector_cond}) holds globally.  
\begin{figure}
\centering
\resizebox{1\columnwidth}{!}{\input{nl_graph.pdf_tex}}
\caption{Nonlinear sector}
%\label{fig:pc}
\label{fig:nl_graph}
\end{figure}

In order to analyze the stability, let us consider the autonomous form of the block diagram in Fig.~\ref{fig:nl_block}, which is shown in Fig.~\ref{fig:nl_block_reform}. 
\begin{figure}
\centering
\resizebox{1\columnwidth}{!}{\input{nl_block_reform.pdf_tex}}
\caption{Equivalent block diagram in autonomous form}
%\label{fig:pc}
\label{fig:nl_block_reform}
\end{figure}
Let us define the open-loop system as $L(s) = C(s)G(s)$. The circle criterion states that given the sector nonlinearity in (\ref{eq:sector_cond}), then the closed-loop system is globally asymptotically stable at the origin if $L(j\omega)$ satisfies the Nyquist criterion and 
\begin{equation} \label{eq:sector_stability_cond}
\Re \left[  \frac{1+k_2L(j\omega)}{1+k_1L(j\omega)} \right] > 0, \quad \forall \omega
\end{equation}
For $L(j\omega)$ to satisfy the Nyquist criterion, it must encircle the point $-1/k_1 + j0$ $m$ times in the counterclockwise direction, where $m$ is the number poles of $L(s)$ in the RHP.  Let us first consider the case when $0< k_1 < k_2$; then the condition in (\ref{eq:sector_stability_cond}) can be interpreted as a disk $D(k_1,k_2)$ in the complex plane that is centered at $k = (k_1+k_2)(2k_1k_2)^{-1}$ with radius $r_k = k - 1/k_2$ that does not include or intersect with $L(j\omega)$. In other words, the Nyquist plot of $L(j\omega)$ must be strictly outside the disk $D(k_1,k_2)$. Fig.~\ref{fig:complex_circ} displays a graphical interpretation of this condition. 
\begin{figure}
\centering
\resizebox{1\columnwidth}{!}{\input{popov_circ.pdf_tex}}
\caption{Absolute stability condition for sector nonlinearity in (\ref{eq:sector_cond}) (for $0 < k_1 < k_2$)}
%\label{fig:pc}
\label{fig:complex_circ}
\end{figure}

\textbf{Definition 1:} \textit{Consider an open-loop system $L(s)$ with $\Phi(\cdot,\cdot)$ that satisfies the sector condition in (\ref{eq:sector_cond}) globally. Then the system is absolutely stable for $0 < k_1 < k_2 $ if the Nyquist plot of $L(j\omega)$ does not enter the disk $D(k_1,k_2)$ and encircles it $m$ times in the counterclockwise direction, where m is the number of poles of $L(s)$ with positive real parts.}

This condition can be expressed as follows:
\begin{equation} \label{eq:stab_ineq_1}
\sup_\omega \left\lvert \frac{r_k}{k+L(j\omega)} \right\lvert < 1
\end{equation}
This inequality will ensure that the Nyquist plot of $L(j\omega)$ will never intersect the disk $D(k_1,k_2)$. Notice that this condition looks similar to the $H_\infty$ norm of the weighted sensitivity function (i.e., when the weight $W = r_k$ and $k = 1$).

\begin{theorem}
Suppose that $C(s)$ is linearly parameterized. A convex constraint which ensures the absolute stability of the autonomous system with the sector nonlinearity in (\ref{eq:sector_cond}) can be asserted as follows:
\begin{equation} \label{eq:the_cons}
r_k|k+L_d(j\omega)|  -  \Re \{[k+L_d(-j\omega)][k+L(j\omega)]\} < 0, \quad \forall \omega
\end{equation}
where $L_d(j\omega)$ is the FRF of the desired open-loop transfer function.
\end{theorem}

{\it Proof :}\\
We know that
\begin{equation}
\Re \{[k+L_d(-j\omega)][k+L(j\omega)]\} \leq |[k+L_d(-j\omega)][k+L(j\omega)]|
\end{equation}
Therefore, noting that $|k+L_d(-j\omega)| = |k+L_d(j\omega)|$, we can conclude the following:
\begin{equation}
r_k -  |k+L(j\omega)| < 0, \quad \forall \omega
\end{equation}
which leads directly to (\ref{eq:stab_ineq_1}). To ensure stability, we must show that the Nyquist criterion is met for $L(j\omega)$. Notice that (\ref{eq:the_cons}) implies that
\begin{equation}
\Re \{[k+L_d(-j\omega)][k+L(j\omega)]\} > 0
\end{equation}
which in turn implies the following:
\begin{equation}
\mbox{wno} \{[k+L_d(-j\omega)][k+L(j\omega)]\} = 0
\end{equation}
where ``wno'' stands for the winding number of the Nyquist plot around the origin. Therefore, we can conclude that 
\begin{equation}
\mbox{wno} [k+L_d(j\omega)] = \mbox{wno} [k+L(j\omega)] 
\end{equation}
Thus if $L_d$ meets the Nyquist stability requirement, then so will $L$.
 {\hfill \ensuremath{\blacksquare}}

\vspace{1cm}
\textbf{$H_\infty$ Performance for Sector Nonlinearity}

The constraint in Theorem 1 guarantees that the system is globally asymptotically stable at the origin for the sector nonlinearity. We will now investigate how we can achieve $H_\infty$ performance with the sector nonlinearity. In one of the papers with Gorka, you derived a sufficient condition to guarantee $H_\infty$ performance by loop-shaping $L(j\omega)$ around a desired $L_d$:
\begin{equation} \label{eq:h_inf_cond}
\gamma^{-1}|W_1(j\omega)(1+L_d(j\omega))|  -  \Re \{[1+L_d(-j\omega)][1+L(j\omega)]\} < 0, \quad \forall \omega
\end{equation}
where $\gamma$ is minimized. Let us replace the nonlinearity $\Phi(\cdot)$ in Fig.~\ref{fig:nl_block} with a simple gain $Q > 0$. We can define the modified plant as $G_2 = QG$. The output can then be expressed as $x = Qu$, which is a line in the $u-x$ plane in Fig.~\ref{fig:nl_graph} that passes through the origin and has slope $Q$. Notice that (\ref{eq:h_inf_cond}) is convex in $Q$. Therefore, if (\ref{eq:h_inf_cond}) is satisfied for $Q = k_1$ AND $Q = k_2$, and because it is convex in $Q$, then (\ref{eq:h_inf_cond}) will be satisfied for all $Q \in [k_1,k_2]$. If this is the case, then $H_\infty$ performance is guaranteed for the nonlinearity sector defined in (\ref{eq:sector_cond}) because the performance is ensured for all slopes between $k_1$ and $k_2$. In other words, you can always select a slope $Q \in [k_1,k_2]$ such that it intersects with the sector nonlinearity in (\ref{eq:sector_cond}). Therefore, one can impose the following optimization problem to guarantee the performance for the nonlinear sector in (\ref{eq:sector_cond}):
\begin{equation}  \label{eq-14}
\begin{aligned}
& \underset{ \{C,\gamma\}}{\text{minimize}}
& & \gamma  \\
& \text{subject to:} & & \gamma^{-1}|W_1(j\omega)(1+L_d(j\omega))|  -  \Re \{[1+L_d(-j\omega)][1+QL(j\omega)]\} < 0  \\ 
& & & Q \in \{ k_1,k_2\} \\
& & & \forall \omega
\end{aligned}
\end{equation}

{\bf Comments by AK for the second discussion:} 
\begin{itemize}
	\item Although the stability constraint in Theorem 1 seems to be fine the performance constraint in (\ref{eq-14}) is unlikely valid for time-varying sector non-linearilty. It should be fine with time-invariant sector non-linearity. 
	\item The condition in Theorem 1 is a sufficient condition. You could develop a necessary and sufficient condition using your formulation instead of that of Gorka.
\end{itemize}

\bibliography{linear2}
\end{document}

### 2017-02-11 Theory and Notes/Other/Discussion.tex
adding files to git (11/2/2017)

\documentclass[12pt]{article}
%\usepackage[a4paper, total={6.5in, 8in}]{geometry}
\usepackage{graphicx}  % Add graphics capabilities
 \usepackage{color}

\usepackage{amsmath} % assumes amsmath package installed
\usepackage{amssymb}  % assumes amsmath package installed
\usepackage{amsthm}
\usepackage{epstopdf}
\newtheorem{lemma}{Lemma}

\title{\LARGE \bf Other Discussions}
\begin{document}
\maketitle

\hrule
\begin{flushright}
Date: 26/07/2016
\end{flushright}
\textbf{Discussion 1: Theory for Positive Realness}

I would like to investigate the necessary condition of Theorem 1 in the journal sent to ``Robust and Nonlinear Control.'' In this theorem (going from a to b), it is stated the following:
\vspace{0.2cm} \hrule

Assume that $K = X_0Y_0^{-1}$ satisfies Statement (a) but not Statement (b). Then, according to Lemma 1, there exists a stable proper rational transfer function $F(s)$ such that
\begin{equation}
\Re \{ F(j\omega)[NX_0+MY_0-\gamma^{-1}|W_1MY_0|]\} > 0, \quad \forall \omega \in \Omega
\end{equation}
Therefore, there exists $X = X_0F$ and $Y = Y_0F$ with $K = XY^{-1} = X_0Y_0^{-1}$ such that Statement (b) holds. 
\hrule \vspace{0.2cm}

Now, there is a little concern with this proof that Michele and I have (which was spawned by the CDC review comments). First, notice that the equation above implies the following:
\begin{equation} \label{eq:cons_2}
\Re \{ NX+MY-\gamma^{-1}|W_1MY_0|F\} > 0, \quad \forall \omega \in \Omega
\end{equation}
But $F$ can be written as $F = |F|e^{j\theta_F}$. Therefore, (\ref{eq:cons_2}) can be expressed as 
\begin{equation} \label{eq:cons_3}
\Re \{ NX+MY-\gamma^{-1}|W_1MY|e^{j\theta_F}\}  > 0, \quad \forall \omega \in \Omega
\end{equation}
After rearranging, we get
\begin{equation} \label{eq:cons_4}
\Re \{ NX+MY\}>\gamma^{-1}|W_1MY|\cos (\theta_F) , \quad \forall \omega \in \Omega
\end{equation}
In other words, we only arrive to the condition in Statement (b) of the theorem if $\theta_F = 2\pi k$ for $k = 0,1,\ldots,n$, which implies that $F$ must be a positive real number. But if this is the case, then you cannot guarantee that you rotate the disk such that it lies to the right of the $j\omega$ axis.

Is there an underlying explanation that I am not seeing in the proof? Or is there something we are missing to prove the theorem properly?
\vspace{0.2cm} \hrule

Michele and I have been looking for another solution to this problem. The control objective is to find a stabilizing controller $K$ such that
\begin{equation} \label{eq:inf1}
\sup_{\omega \in \Omega} |H(j\omega)| < \gamma
\end{equation}
where $H = W_1(1+GK)^{-1} = W_1MY\psi^{-1}$ and $\psi = NX+MY$. For our solution to the theorem, we will need to change Lemma 1 slightly. 
\begin{lemma} 
Suppose that $H = W_1 MY\psi^{-1}$ is a bounded analytic function in the right-half plane. Then the condition in (\ref{eq:inf1}) is satisfied if and only if there exists an angle $\theta(\omega)$ such that
\begin{equation} \label{eq:lem_mod}
\Re \{ e^{-j\theta(\omega)}\psi - \gamma^{-1}|W_1MY|\}>0 , \quad \forall \omega \in \Omega
\end{equation}
where $\psi = NX+MY$.
\end{lemma}

\textit{Proof:}
The condition in (\ref{eq:inf1}) implies that there is a circle centered at $\psi$ with a radius of $\gamma^{-1}|W_1MY|$ (that does not include the origin). At every frequency, there is a function $f(j\omega)$ that can rotate the point $\psi$ such that it lays on the right hand side of the $j\omega$ axis. Hence we have
\begin{equation}
\Re \{ f(j\omega)\psi\}>\gamma^{-1}|W_1MY|\geq 0, \quad \forall \omega \in \Omega
\end{equation}
$f(j\omega)$ can be approximated arbitrarily well by the frequency response of a rational stable transfer function $F(s)$ if and only if $\psi^{-1}$ is analytic in the RHP, which is the case because of the stability of $H$. Therefore, $F(s) = e^{-s\theta(\omega)/\omega}$ can be selected for such a function since
\begin{equation} \label{eq:pade}
e^{-s\theta(\omega)/\omega} \approx \frac{\sum_{i=0}^n \binom ni \frac{(2n-i)!}{(2n)!} \left(-\frac{s\theta(\omega)}{\omega}\right)^i}{\sum_{i=0}^n \binom ni \frac{(2n-i)!}{(2n)!} \left(\frac{s\theta(\omega)}{\omega}\right)^i}
\end{equation}
where $\theta(\omega) > 0$.  Note that (\ref{eq:pade}) represents the Pad\'{e} approximant and is stable for any $n$. As $n \to \infty$, the Pad\'{e} approximant converges to the original function. The frequency response of this function is given by $F(j\omega) = e^{-j\theta(\omega)}$. Therefore, the condition in (\ref{eq:lem_mod}) can be expressed as follows:
\begin{equation} \label{eq:cos_cons}
\cos (\theta_\psi - \theta(\omega)) > \frac{\gamma^{-1}|W_1MY|}{|\psi|}, \quad \forall \omega \in \Omega
\end{equation} 
where $\theta_\psi$ is the phase angle associated with $\psi$. However, based on (\ref{eq:inf1}), we know that the right-hand side of the above constraint is less than one (since (\ref{eq:inf1}) implies that $|\psi| > \gamma^{-1}|W_1MY|$). Therefore, there will always exists a $\theta(\omega)$ such that (\ref{eq:cos_cons}) is satisfied. 
{\hfill \ensuremath{\blacksquare}}

Based on this modified lemma, we have proposed the following necessary condition for the theorem:
\vspace{0.2cm} \hrule

Assume that $K = X_0Y_0^{-1}$ satisfies Statement (a) but not Statement (b). Then, according to (modified) Lemma 1, there exists a function $F(j\omega) = e^{-j\theta(\omega)}$ such that
\begin{equation}
\Re \{ e^{-j\theta(\omega)}\psi_0-\gamma^{-1}|W_1MY_0|\} > 0, \quad \forall \omega \in \Omega
\end{equation}
where $\psi_0 = NX_0 + MY_0$. Therefore, there exists $X = X_0e^{-j\theta(\omega)}$ and $Y = Y_0e^{-j\theta(\omega)}$ with $|Y| = |Y_0|$ and with $K = XY^{-1} = X_0Y_0^{-1}$ such that Statement (b) holds. 
\hrule \vspace{0.2cm}

Geometrically, what we have done is rotate only the point $\psi$ and keep the radius constant through the rotation. Of course, simply rotating the point $\psi$ will not satisfy (\ref{eq:inf1}) (because the point $\psi - \gamma^{-1}|W_1MY|$ may still lie to the left of the $j\omega$ axis); but in the Lemma, we showed that there exists an angle $\theta(\omega)$ such that the disk lays completely on the right-hand side of the $j\omega$ axis, and thus satisfying (\ref{eq:inf1}).

{\bf Comments by AK:} Thank you for your work and comment of the reviewer for mentioning this problem in the paper. Unfortunately, we cannot change anymore the journal paper. So, I tried to modify just the Lemma slightly and keep the theorem unchanged. The main problem in Lemma one was the fact that the disk was represented just by one point (you mentioned this problem one time, I believe). The idea is to represent the disk by the whole circle as it should be. The new Lemma will be like that:

\begin{lemma}   \label{lem2}
Suppose that $H(j\omega)={W_1MY} (NX+MY)^{-1}$ is the frequency response of a bounded analytic function in the right half plane. Then, the following constraint is met
\begin{equation} \label{eq4}
\sup_{\omega \in \Omega}  |H(j\omega )| < \gamma
\end{equation}
if and only if there exists a stable proper rational transfer function $F(s)$ that satisfies
$$
\Re\{(NX + MY)F(j\omega)\}>\gamma ^{-1}|W_1MYF|,  \qquad \forall \omega \in \Omega 
$$
\end{lemma}

{\it Proof :} 
The basic idea is similar to that of  the proof of Theorem~1 in \cite{RM94}. It is clear that (\ref{eq4}) is satisfied if and only if the disk of radius $ \gamma ^{-1}|W_1MY|$ centered at $NX+MY$ does not include the origin for all $\omega \in \Omega$, i.e. $|NX+MY|>\gamma ^{-1}|W_1MY|$. This is equivalent to the existence of a line passing through origin that does not intersect the disk. Therefore, at every given frequency, $\omega$, there exists a complex number $f(j\omega)$ that can rotate the disk such that it lays inside the right hand side of the imaginary axis. Hence, we have 
\begin{equation}
\label{eq18}
\Re\{ (NX + MY - \gamma ^{-1}|W_1MY|e^{j\theta})f(j\omega)\}>0
\end{equation}
for all $\omega \in \Omega$ and for all $\theta \in [0 \, , \, 2 \pi [$. The above condition is satisfied if and only if:
\begin{equation}
\label{eq18}
\Re\{ (NX + MY)f(j\omega) \} > \gamma ^{-1}|W_1MYf(j\omega)| \qquad \forall \omega \in \Omega 
\end{equation}
In \cite{RM94}, it is shown that, $f(j\omega)$ can be approximated arbitrarily well by the frequency response of a rational stable transfer function $F(s)$ if and only if 
\begin{equation}
Z=(NX + MY - \gamma_0 ^{-1}|W_1MY|e^{j\theta})^{-1}
\end{equation}
is analytic in the right half plane for all $\gamma_0>\gamma$ and all $\theta \in [0 \, , \, 2 \pi [$. However, $(NX + MY )^{-1}$ is stable because of the stability of $H$. On the other hand, by decreasing $\gamma_0$ from infinity to $\gamma$, the poles of $Z$ move continuously with $\gamma_0$. Therefore, $Z$ is not analytic in the right half plane if and only if $Z^{-1}(j\omega)=0$ for a given frequency, which is not the case because the origin is not in the interior of the circle  $\gamma_0 ^{-1}|W_1MY|e^{j\theta}$.  
{\hfill \ensuremath{\blacksquare}}

{\bf Comments by AN:} 
Actually, I realized that the Lemma you present is exactly the same as the one I presented. Since $F = |F|e^{j\theta_F}$, then 
\begin{equation}
\Re\{(NX + MY)F - \gamma ^{-1}|W_1MYF| \}>0
\end{equation}
can be expressed as
\begin{equation}
\Re\{|F| \left[ (NX + MY)e^{j\theta_F} - \gamma ^{-1}|W_1MY| \right] \}>0
\end{equation}
But you can factor $|F|$ out of the real part of the argument, since it is real. So you can write the above constraint as
\begin{equation}
\Re\{ (NX + MY)e^{j\theta_F} - \gamma ^{-1}|W_1MY| \}>0
\end{equation}
This is exactly the condition I derived in (\ref{eq:lem_mod}). So in essence, we are simply rotating the point $NX+MY$ such that the entire disk lies in the right-hand side of the $j\omega$ axis.

\end{document}

### 2017-02-11 IPAC Abstract/Abstract.tex
testing

--- 2017-02-11 Papers/SUBMITTED - RST Design Current Loop (CERN)/Latex/Draft.tex
@@
-%\documentclass[12pt,draftcls,onecolumn]{IEEEtran}
-\documentclass[journal]{IEEEtran}
-%\IEEEoverridecommandlockouts  
-%\overrideIEEEmargins     
+\documentclass[11pt,english]{article}
+\usepackage[T1]{fontenc}
+\usepackage{babel}
 \bibliographystyle{IEEEtran}
-\pdfminorversion=4
 
-\usepackage{cite}
-%\usepackage{mathptmx}       % selects Times Roman as basic font
-\usepackage{helvet}         % selects Helvetica as sans-serif font
-\usepackage{courier}        % selects Courier as typewriter font
-\usepackage{type1cm}        % activate if the above 3 fonts are
-                            % not available on your system
-%
-\usepackage{makeidx}         % allows index generation
-\usepackage{graphicx}        % standard LaTeX graphics tool
-%                             % when including figure files
-\usepackage{multicol}        % used for the two-column index
-\usepackage{times}
-\usepackage{xfrac}
-\usepackage{caption}
-\usepackage{subcaption}
-%\usepackage{mathabx}
-%\usepackage[thref]{ntheorem}
-\usepackage{amsfonts}%
-\usepackage{amssymb}%
-\usepackage{amsthm}
-\usepackage{mathrsfs}
-\usepackage{url}
-\usepackage{color}
-%\usepackage{import}
-\usepackage{graphicx,psfrag}
-\usepackage{float}
-\usepackage[cmex10]{amsmath}
-\newtheorem{theorem}{Theorem}
-\newtheorem{lemma}{Lemma}
-\newtheorem*{remark}{Remark}
-\newcommand{\jo}{(e^{-j\omega})}
-\newcommand{\jok}{(e^{-j\omega_k})}
-\newcommand{\jro}{(e^{-j\omega},\rho)}
-\newcommand{\jrok}{(e^{-j\omega_k},\rho)}
-%\renewcommand{\IEEEQED}{\IEEEQEDopen}
-\renewcommand{\vec}[1]{\mathbf{#1}}
-\newcommand{\hilight}[1]{\colorbox{yellow}{#1}}
-%\DeclareRobustCommand*{\IEEEauthorrefmark}[1]{%
-  %\raisebox{0pt}[0pt][0pt]{\textsuperscript{\footnotesize\ensuremath{#1}}}}
+\author{
+  Achille Nicoletti and Michele Martino\\ \\
+  \textit{\small The European Organization for Nuclear Research (CERN)} \\
+  \textit{\small Technology Department, Electrical Power Converters group,} \\
+  \textit{\small High Precision Measurements section}
+}
 
-\title{\LARGE \bf A Robust Data-driven Controller Design Methodology for Particle Accelerator Power Converters}
-
-%\iffalse
-\author{Achille Nicoletti, Michele Martino and Alireza Karimi% <-this % stops a space
-
-\thanks{Achille Nicoletti is with the Technology Department at
-European Organization for Nuclear Research (CERN) and the Automatic Control Laboratory at
-Ecole Polytechnique F\'{e}d\'{e}rale de Lausanne (EPFL) (email: \tt\small achille.nicoletti@cern.ch)}%
-\thanks{Michele Martino is with the Technology Department at
-European Organization for Nuclear Research (CERN) (email: \tt\small michele.martino@cern.ch)}%
-\thanks{Alireza Karimi is with the Automatic Control Laboratory at
-Ecole Polytechnique F\'{e}d\'{e}rale de Lausanne (EPFL) (email: \tt\small alireza.karimi@epfl.ch)}%
-}
-%\fi
+\title{Data-driven Controller Design for a Fast-Pulsed Power Converter Control Application}
+\date{}
 
 \begin{document}
+  \maketitle
 
-\maketitle
-\thispagestyle{empty}
-\pagestyle{empty}
+  \begin{center}
+  \LARGE{\bf{Abstract}}
+  \end{center}
 
-\begin{abstract}
-A new data-driven approach using the frequency response function (FRF) of a system is proposed for designing robust $H_{\infty}$ digital controllers for particle accelerators' power converters.
-This design method ensures that the dynamics of a system are captured and avoids the problem of unmodeled dynamics associated with parametric models.
-The $H_{\infty}$ robust performance condition can be represented by a set of convex constraints with respect to the parameters of a two-degree of freedom RST controller.
-This controller is robust with respect to the frequency-dependent uncertainties of the frequency response function.
-Moreover, constraints will be imposed in order to simultaneously ensure the desired stability margins and the controller stability.
-A convex optimization algorithm is then implemented to obtain the controller parameters.
-The effectiveness of the method is illustrated by designing the controller for the Q-STRIP magnet power converter of the PS Booster accelerator upgrade project at CERN.
-Experimental validation in the time domain is also presented.
-\end{abstract}
-
-\begin{IEEEkeywords}
-Convex optimization, data-driven control, H-infinity, power converter control, robust control, RST %uncertainty, Smith predictor, MIMO time delay. 
-\end{IEEEkeywords}
-
-\section{Introduction}
-\IEEEPARstart{M}{any} of today's  complex systems possess a multitude of uncertainties, and obtaining an accurate parametric model for such systems can be both laborious and impractical for controller synthesis.
-In industrial schemes, the dynamics of plants are typically approximated by low-order models, since the controller synthesis is easier to implement for lower order processes.
-However, this approximation can impede the  performance of a controller, since low-order models are subject to model uncertainty.
+The complex structures of today's systems create challenging tasks for the control engineer in designing a viable controller.
+In order to simplify the controller design process, these systems are approximated with low-order models; this reduces both time and effort in synthesizing a controller.
+However, this approximation can create stability and performance problems since these low-order models are subject to model uncertainty.
+Data-driven control methods seek to alleviate this problem by synthesizing controllers based on time-domain or frequency-domain data (i.e., synthesis is model independant).
 A survey on the differences associated with model-based control and data-driven control has been addressed in \cite{HW13} and \cite{BCE12}; the authors assert that model-based control methods are inherently less robust due to the unmodeled dynamics of a process, and that these controllers are unsafe for practical applications.
-With the data-driven control scheme, the parametric uncertainties and the unmodeled dynamics are irrelevant and the only source of uncertainty is the measurement noise.
-
-Data-driven controllers can be synthesized either on-line or off-line; the on-line methods such as the classical direct adaptive control (MRAC) \cite{LLMK11}, model-free adaptive control (MFAC) \cite{HJ13}, and the unfalsified control (UC) \cite{ST97} methodologies design controllers using time-domain data.
-Iterative feedback tuning (IFT) \cite{Hja02}, correlation-based tuning (CBT) \cite{KMB02a}, virtual reference feedback tuning (VRFT) \cite{CLS02}, non-iterative data-driven model reference control \cite{KVB07} methodologies are all off-line time-domain data-driven methods.
-The widely used PID controller is usually tuned based on a set of time-domain or frequency-domain data.
+In other words, the parametric uncertainties and the unmodeled dynamics associated with the data-driven scheme are irrelevant, and the only source of uncertainty is the measurement noise.
 
@@
 \end{itemize}
-The authors in \cite{HDAV10} use the frequency response data of a stable system to design an optimal controller through a symmetric root locus technique.
-A robust frequency-domain control design method has been established in \cite{KNND13b}; this method, however, requires a solution to a non-linear optimization problem.
-A frequency-domain loop-shaping approach to design fixed-structure controllers is presented in \cite{KNND13c}.
-In this method, a convex optimization problem can be formulated if a linearly parameterized controller is considered; however, in this method, the closed-loop stability is not guaranteed and should be verified a posteriori.
-Robust controller design methods belonging to the $\mathcal{H}_{\infty}$ control framework minimizes the $\mathcal{H}_{\infty}$ norm of a weighted closed-loop sensitivity functions.
-In \cite{DWS09} a frequency-response method is proposed based on the $Q$-parametrization to guarantee the $\mathcal{H}_{\infty}$ performance for fixed-structure controllers.
-In \cite{KG10}, a frequency domain approach is realized where a convex optimization algorithm is formulated by considering a convex approximation of the $\mathcal{H}_{\infty}$ criterion.
-In order to obtain convexity, however, the controller is chosen to be linearly parameterized, i.e.
-the denominator of the controller are fixed.
-This limits the number of degrees of freedom of the controller, and thus impedes the controller performance.
-A frequency-domain approach for computing low-order multivariable linearly parameterized controllers is presented in \cite{SOW10}.
-The $\mathcal{H}_{\infty}$ constraints are convexified around an initial stabilizing controller.
-An iterative algorithm is used that converges to a local optimal solution of the non-convex problem.
-The method in \cite{KG10} is extended to data-driven gain-scheduled controller design in \cite{KE13a} and multivariable decoupling controller design in \cite{GKL10b}.
-A public domain toolbox for Matlab is also available \cite{Kar13}.
-A similar approach is proposed in  \cite{HAB13}, where a convex-concave approximation of the $\mathcal{H}_{\infty}$ constraints based on an initial stabilizing controller is used.
-The extension of this method to design multivariable PID controllers for stable systems is presented in \cite{BHA16}.
-This method uses the same convex approximation as in  \cite{SOW10} but is limited to stable systems and PID structure.
-The design of controllers that are not linear in parameters (e.g.
-represented by rational transfer functions) using frequency domain data are studied in \cite{KNZ16}.
-The necessary and sufficient conditions for the existence of such controllers are developed.
-This method needs no initial stabilizing controller and converges to the optimal  $\mathcal{H}_{\infty}$ performance when the order of the controller goes to infinity.
 
-%\iffalse
-%Generally, it is desired to formulate a convex optimization problem for controller synthesis, since convex problems are computationally tractable.
-A frequency domain approach in designing the $RST$ controllers has been discussed in \cite{MRS11}, where a convex optimization problem is formulated by bounding a specific sensitivity function and specifying a desired characteristic polynomial.
-Robust stability, however, is not trivially achieved, since the characteristic polynomial incorporates an observer polynomial which usually needs to be tuned iteratively.
-With $\mathcal{H}_{\infty}$ control techniques, it is possible to eliminate the necessity of using observer polynomials for achieving proper robustness margins.
-Robust controller design methods belonging to the $\mathcal{H}_{\infty}$ control framework minimizes the $\mathcal{H}_{\infty}$ norm of a weighted closed-loop sensitivity function.
-In \cite{GKL11}, a frequency domain approach is realized where a convex optimization algorithm is formulated by considering a convex approximation of the $\mathcal{H}_{\infty}$ criterion.
-With this method, suitable robustness margins are attainable; however, in order to preserve convexity, this method requires one of the controller terms ($R$) to be fixed a priori\footnote{Note that the variable names for $R$ and $S$ are interchanged in \cite{GKL11}}.
-This limits the number of degrees of freedom of the controller, and thus impedes the controller performance.
+For this specific application, an $RST$ controller structure was implemented to control the dynamics of the power converter control system.
+The $RST$ controller structure is an effective discrete-time two-degree of freedom (2DOF) polynomial controller where the tracking and regulation characteristics of a closed-loop system can be formulated independently \cite{LZ06}.
+To design this controller, a $\mathcal{H}_\infty$ loop-shaping method was used to shape a desired sensitivity function.
+Robust controller design methods belonging to the $\mathcal{H}_{\infty}$ control framework minimizes the $\mathcal{H}_{\infty}$ norm of a weighted closed-loop sensitivity function \cite{ZD98}.
+In this method, a convex optimization problem can be formulated if each of the $RST$ polynomials are linearly parameterized \cite{NEK15}.
 
-The $RST$ controller structure is an effective discrete-time two-degree of freedom (2DOF) polynomial controller where the tracking and regulation characteristics of a closed-loop system can be formulated independently \cite{LZ06}.
-The $RST$ controller design methodology is usually based on the pole placement technique and uses the dynamic model of the physical system.
-In \cite{GKL11}, the data-driven frequency-domain approach of \cite{KG10} is extended to $RST$ controller design.
-However, in order to preserve convexity, this method requires one of the controller terms to be fixed a priori.
-This problem is fixed in \cite{NEK15}, where an $RST$ controller is designed in the $\mathcal{H}_{\infty}$ framework by formulating a convex optimization problem in a data-driven setting.
-The necessary and sufficient conditions for the existence of $RST$ controllers that satisfy the  $\mathcal{H}_{\infty}$ constraint only on one sensitivity function are also developed.
-
-The proposed method in this paper is an extension of \cite{NEK15}, where the necessary and sufficient conditions that ensures the $\mathcal{H}_{\infty}$ performance for multiple weighted sensitivity functions is presented.
-Moreover, the frequency-dependent uncertainties originated from the measurement noise are taken into consideration for robust performance specifications.
-Additionally, since the parameters of the controller's denominator are the optimization variables, this method can lead to unstable controllers.
-Therefore, a sufficient condition is presented to ensure that the controller remains stable.
-The proposed method is then used to design a robust $RST$ controller for power converters in particle accelerators at CERN.
-The designed controller is implemented in the power converters to control their output current with extremely high precision.
-The main advantage of the proposed method for this application is to guarantee the robustness margins, high bandwidth and small tracking error by a data-driven convex optimization based approach that does not require the manual tuning of the classical pole-placement model-based approach.
-
-The paper is organized as follows.
-The class of models, controllers and control objectives are defined in section (\ref{sec:2}).
-Section (\ref{sec:3}) discusses the control design methodology and stability conditions of the proposed method for the $RST$ controller structure.
-Convex conditions are formulated based on the $\mathcal{H}_{\infty}$ criterion.
-Section (\ref{sec:4}) discusses the framework of the power converter control system and its functionality at CERN.
-Section (\ref{sec:5}) is dedicated to a case study where the effectiveness of the method is demonstrated by applying the proposed design scheme to a power converter control system for a specific accelerator requirement.
-Finally, the concluding remarks are given in section (\ref{sec:6}).
-
-%\textbf{Notation}: In order to avoid the risk of any confusion, the notation for the symbols employed in this paper will be defined here.
-%\begin{align*}
-%\mathbb{R}/ \mathbb{R}^+ &: \ \mbox{the set of all real numbers/positive real numbers.} \\
-%\mathbb{Z} &: \ \mbox{the set of non-negative integers.} \\
-%\mathcal{R}e\{X \} &: \ \mbox{the real part of a complex variable }X. \\
-%\mathcal{I}m\{X \} &: \ \mbox{the imaginary part of a complex variable }X. \\
-%a^{\top} &: \ \mbox{the transpose of the vector }a. \\
-%z &: \ \parbox[t]{18em}{complex frequency variable used to represent discrete-time systems.} \\
-%s &: \ \parbox[t]{18em}{complex frequency variable used to represent continuous-time systems.}
-%\end{align*} 
-%\section{Notation and Preliminaries}
-%Due to the nature of the equations asserted in this paper, it will be convenient express certain equations in a compact manner.
-A cascade of $q$ frequency response functions $A_1(e^{-j\omega})A_2(e^{-j\omega}) \cdots A_q(e^{-j\omega})$ will be denoted as $[A_1A_2 \cdots A_q](e^{-j\omega})$.
-
-\section{Problem Formulation}
-\label{sec:2}
-\subsection{Preliminaries}
-Let $u[k]$ and $y[k]$ represent the input and output signals of a causal discrete-time system, respectively, where $k$ is a discrete-time instant and $T_s$ is the sampling period.
-Suppose that these signals are noise-free and have zero initial and final conditions (i.e., $u[k] = y[k] = 0$ for $k \leq 0$ and $k > K_s$).
-Then, the frequency response function (FRF) of the system can be represented as
-\begin{equation}
-G(e^{-j\omega}) = Y(e^{-j\omega}) U^{-1}(e^{-j\omega})
-\end{equation}
-where
-\begin{align}
-U(e^{-j\omega}) &= \frac{1}{\sqrt{K_s}} \sum_{k=0}^{K_s} u[k]e^{-j \omega T_s k} \label{eq:U_period}\\
-Y(e^{-j\omega}) &= \frac{1}{\sqrt{K_s}} \sum_{k=0}^{K_s} y[k]e^{-j \omega T_s k}
-\end{align} 
-are the periodograms of the input and output signals and $\omega \in [-\pi/T_s, \pi/T_s]$.
-Note that due to the symmetry of the periodograms, it is sufficient to consider $\omega \in [0, \pi/T_s]$ for practical applications.
-Under these assumptions, it is evident that from a set of sampled time-domain data, one is able to obtain a continuous FRF.
-If the data is noisy, then $G(e^{-j\omega})$ is characterized as the Empirical Transfer Function Estimate (ETFE) and is asymptotically unbiased \cite{Lju99}.
-For such systems, a multiplicative uncertainty can be considered to ensure robustness in the presence of noise perturbations.
-
-Let the set $\mathscr{P}$ represent the family of all stable, proper, real-rational discrete-time transfer functions with no pole on the unit circle.
-It is imperative to note that $\mathscr{P}$ is closed under multiplication and addition; in other words, if $P_1(z^{-1}),P_2(z^{-1}) \in \mathscr{P}$, then
-\begin{equation}
-\{ P_1(z^{-1})+P_2(z^{-1}),P_1(z^{-1})P_2(z^{-1})\} \in \mathscr{P}
-\end{equation}
-Suppose that a single-input-single-output (SISO) feedback control system structure is used where the plant is represented as $G(z^{-1}) = N(z^{-1})M^{-1}(z^{-1})$ such that $\{N(z^{-1}),M(z^{-1})\} \in \mathscr{P}$.
-As asserted in \cite{ZD98} and \cite{DFT92}, if $\{N(z^{-1}), M(z^{-1})\} \in \mathscr{P}$, then $G(z^{-1}) = N(z^{-1})M^{-1}(z^{-1})$ is called a \textit{coprime factorization} of $G(z^{-1})$ over $\mathscr{P}$.
-
-\subsection{Class of models}
-Let the FRF of such a factorized discrete-time SISO plant be defined as follows:
-\begin{equation}\label{eq:setpmimo}
-G\jo = N\jo M^{-1}\jo, \qquad \forall \omega \in \Omega
-\end{equation}
-where $\Omega \in [0,\pi/T_s]$.
-$N\jo$ and $M\jo$ must be FRF's of bounded analytic functions outside the unit circle; for a stable plant, a trivial choice is $N\jo=G\jo$ and $M\jo=1$.
-A discussion on how to formulate $N\jo$ and $M\jo$ for unstable processes can be found in \cite{KNZ16}.
-In general, a set $\mathcal{G}$ can be formulated to represent a plant model containing $p$ FRF models:
-\begin{equation}
-\mathcal{G} = \{G_l\jo; \quad l=1,\ldots,p; \quad \forall \omega \in \Omega\}
-\end{equation} 
-These FRF's can be determined by considering the frequency response of a parametric model or from a set of input/output data.
-For simplicity, one model from the set $\mathcal{G}$ will be considered, and the subscript $l$ will be omitted.
-However, in general, the design procedures outlined in this paper can be applied to the multi-model case.
-%In fact, in Section (\ref{sec:4}), a multi-model case will be investigated for the controller synthesis of the power converter control system.
-
-\subsection{Frequency-domain uncertainty} \label{sec:freq_uncertain}
-Suppose that the uncertainty associated with a given FRF is described by an additive uncertainty:
-\begin{equation}
-\begin{aligned} \label{eq:frf_uncertainty}
-\hat{N}(e^{-j\omega}) &= N(e^{-j\omega}) + |W_n(e^{-j\omega})| \delta_n e^{j\theta_n} \\
-\hat{M}(e^{-j\omega}) &= M(e^{-j\omega}) + |W_m(e^{-j\omega})| \delta_m e^{j\theta_m}
-\end{aligned}
-\end{equation}
-where $|\delta_n| \leq 1$, $|\delta_m| \leq 1$; $\{ \theta_n,\theta_m\} \in [0,2\pi]$; $W_n$ and $W_m$ are the uncertainty weighting filters which can be determined from the covariance of the estimates for a given confidence interval.
-As previously stated, $N\jo = G\jo$ and $M\jo = 1$ can be selected for stable systems.
-Therefore, given the periodogram of $G$, the estimates of the real and the imaginary part of $N\jo$ can be formulated; these estimates are asymptotically uncorrelated and normally distributed with a variance of $\Phi_v(\omega)/2|U\jo|^2$, where $\Phi_v(\omega)$ is the spectrum of the disturbance $v[k]$ at the output of the plant (\cite{Lju99}).
-The additive uncertainty can be described in the complex plane with a disk centered at $N\jo$ having a radius of $|W_n\jo|$.
-The uncertainty is characterized by the Rayleigh distribution and can be determined for any probability level.
-For example, if it is desired to construct an uncertainty disk such that the true frequency response lies within the disk with a probability level of $0.95$, then the radius of this disk will be
-\begin{equation} \label{eq:uncertainty_radius}
-|W_n\jo| = \sqrt{\frac{5.99 \Phi_v(\omega)}{2|U\jo|^2}}
-\end{equation}
-The output noise spectrum can be estimated as
-\begin{equation} \label{eq:noise_spectrum}
-\Phi_v(\omega) = \Phi_y(\omega) - \frac{|\Phi_{uy}(\omega)|^2}{\Phi_u(\omega)}
-\end{equation}
-where $\Phi_u(\omega)$ is the input spectrum, $\Phi_y(\omega)$ is the output spectrum, and $\Phi_{uy}(\omega)$ is the cross-spectral density of the input and output channels.
-
-\subsection{Class of controllers}
-\begin{figure}
-\centering
-\resizebox{1\columnwidth}{!}{\input{rst.eps_tex}}
-\caption{$RST$ controller structure}
-\label{fig:rst}
-\end{figure}
-The controller structure that will be considered will be of the $RST$-type.
-The $RST$ controller is a two-degree of freedom controller which can be used to synthesize the tracking and regulation requirements independently from each other \cite{LZ06}.
-The general structure of this controller is shown in Fig.~\ref{fig:rst}.
-Each controller is realized as a polynomial function as follows:
-\begin{alignat}{2}
-R(z^{-1},\rho) &= r_0 + r_1z^{-1} + \cdots + r_{n_r}z^{-n_r} \label{eq:Rc}\\
-S(z^{-1},\rho) &= 1 + s_1z^{-1} + \cdots + s_{n_s}z^{-n_s} \label{eq:Sc}\\
-T(z^{-1},\rho) &= t_0 + t_1z^{-1} + \cdots + t_{n_t}z^{-n_t} \label{eq:Tc}
-\end{alignat}
-where $\{n_s,n_r,n_t\}$ are the orders of the polynomials $R,S$ and $T$, respectively. These controllers can also be represented in a linear regression form as 
-\begin{align}
-R(z^{-1},\rho)&=\rho_R^\top \phi_{n_r}(z^{-1})= [r_0,r_1,\ldots,r_{n_r}]\phi_{n_r}(z^{-1}); \nonumber \\
-S(z^{-1},\rho)&=\rho_S^\top \phi_{n_s}(z^{-1})= [1,s_1,\ldots,s_{n_s}]\phi_{n_s}(z^{-1}); \nonumber \\
-T(z^{-1},\rho)&=\rho_T^\top \phi_{n_t}(z^{-1})= [t_0,t_1,\ldots,t_{n_t}]\phi_{n_t}(z^{-1}); \nonumber
-\end{align}
-where
-\begin{align}
-\rho^\top &=[\rho_R^\top, \rho_S^\top, \rho_T^\top] \nonumber \\
-\phi_x^\top(z^{-1}) &= [1,z^{-1},\ldots,z^{-x}] \nonumber
-\end{align}
-%The purpose of parameterizing the controllers in this manner will become apparent in subsequent sections. 
-where $x \in \{n_r,n_s,n_t \}$.
-
-Based on the internal model principle, the controller may contain the disturbance model to achieve a zero steady-state error.
-Therefore, the polynomials may be pre-multiplied with any arbitrary function that actualizes the desired action.
-For example, if it is desired to reject a step disturbance at the output, then $S(z^{-1},\rho)$ can be pre-multiplied with $(1-z^{-1})$ (which represents the integral action of the controller).
-For sinusoidal disturbances at specific frequencies, the polynomials can be pre-multiplied with the function
-\begin{equation*}
-\theta (z^{-1}) = 1-2z^{-1} \cos(\omega_z T_s) + z^{-2}
-\end{equation*}  
-where $\omega_z$ is the frequency in $rad/s$ at which the disturbance occurs.
-%Suppose that there is noise $v$ at a frequency $\omega_z$, and is it desired to attenuate the effects caused by this disturbance (note that (\ref{eq:V}) represents the sensitivity function of interest for this disturbance).
-Then the $R$ polynomial can be pre-multiplied with $\theta (z^{-1})$ to achieve the desired noise attenuation at the output.
-In general, any of the $RST$ polynomials can be pre-multiplied with any polynomial that performs the desired action.
-%The purpose of parameterizing the controllers in this manner will become apparent in subsequent sections.
-%For notation purposes, the dependency on the discrete-time frequency variable $z^{-1}$ will be omitted, and the dependency on the controller parameter $\rho$ will remain.
-
-\subsection{Sensitivity Functions}
-\label{sec:23}
-Since the design techniques introduced in this paper belong to the $\mathcal{H}_{\infty}$ framework, it is  appropriate to consider the various sensitivity functions associated with the $RST$ controller structure.
-Some sensitivity functions for this process can be asserted as follows:
-\begin{align}
-\mathcal{S}_1(z^{-1},\rho)&= \frac{y}{d_o} = \frac{M(z^{-1})S(z^{-1},\rho)}{\psi(z^{-1},\rho)}  \label{eq:S0}\\
-\mathcal{S}_2(z^{-1},\rho)&= \frac{y}{r} =\frac{N(z^{-1})T(z^{-1},\rho)}{\psi(z^{-1},\rho)} \label{eq:T} \\
-\mathcal{S}_3(z^{-1},\rho)&= \frac{r-y}{r} =\frac{\psi(z^{-1},\rho)-N(z^{-1})T(z^{-1},\rho)}{\psi(z^{-1},\rho)} 
-\end{align}
-where $\psi(z^{-1},\rho) = N(z^{-1})R(z^{-1},\rho)+M(z^{-1})S(z^{-1},\rho)$, $y$ is the system output, $r$ is the reference input, and $d_o$ is the output disturbance.
-For notation purposes, the dependency in $z^{-1}$ will be omitted, and will only be reiterated when deemed necessary.
-Note that all of the sensitivity functions are stable if the zeros of $\psi(\rho)$ lie within the unit circle.
-The sensitivity functions defined above (and all other sensitivity functions of interest) all contain the same transfer function  $\psi(\rho)$.
-Therefore, a general construction of the sensitivity function can be expressed as $\mathcal{S}_q(\rho) = \Delta_q(\rho)/ \psi(\rho)$, where $\Delta_q(\rho)$ is a linear function of $R$, $S$ and/or $T$.
-The subscript $q \in \{ 1,2,\ldots,c\}$ denotes the $q$-th sensitivity of interest and $c$ is the total number of sensitivity functions.
-
-\section{$\mathcal{H}_{\infty}$ Performance via Convex Optimization}
-\label{sec:3}
-\subsection{General Design Specifications}
-\label{sec:general}
-In the general $\mathcal{H}_\infty$ control problem, the objective is to find the controller parameters vector $\rho$ such that
-\begin{equation} \label{eq:true_hinf}
-\sup_{\omega \in \Omega} |H_q(e^{-j\omega},\rho)| < \gamma
-\end{equation}
-where $\gamma \in \mathbb{R}^+$, $H_q(e^{-j\omega},\rho) = W_q(e^{-j\omega}) \mathcal{S}_q(e^{-j\omega},\rho)$ and $W_q$ is the FRF of a stable weighting filter such that $H_q(e^{-j\omega},\rho)$ has a bounded infinity norm.
-For notation purposes, the dependency in $e^{-j\omega}$ will be omitted, and will only be reiterated when deemed necessary.
-The condition in (\ref{eq:true_hinf}) can also be expressed as follows:
-\begin{equation} \label{eq:circle}
-\gamma^{-1}|W_q \Delta_q(\rho)| < |\psi(\rho)| ; \quad \forall \omega \in \Omega
-\end{equation}
-
-It is desired to minimize the upper bound $\gamma$ such that the $\mathcal{H}_{\infty}$ performance condition is satisfied. 
-Therefore, the following optimization problem can be considered:
-\begin{equation} \label{eq:min1}
-\begin{aligned}
-& \underset{\rho}{\text{minimize}}
-& & \gamma  \\
-& \text{subject to:} & & \gamma^{-1} |W_q\Delta_q(\rho)| < |\psi(\rho)|  \\ 
-& & & \forall \omega \in \Omega \quad ; \quad  q \in \mathcal{Q} \subset \{1, 2, \ldots, c\}
-\end{aligned}
-\end{equation}
-Notice that (\ref{eq:min1}) is a non-convex optimization problem.
-
-\begin{figure}
-\hspace*{1cm}
-\resizebox{0.9\columnwidth}{!}{\input{nxmy2_rad_diff_2.eps_tex}}
-\caption{The graphical interpretation of $\mathcal{H}_{\infty}$ constraints in the complex plane}
-\label{fig:circle}
-\end{figure}
-
-Consider a circle in the complex plane at a specific frequency in $\Omega$ which is centered at $\psi(\rho)$ and has radius $\gamma^{-1}|W_q\Delta_q(\rho)|$.
-The constraint in (\ref{eq:circle}) ensures that for any frequency point in $\Omega$, the circle associated with this frequency point will not encircle the origin.
-Fig.~\ref{fig:circle} displays the graphical interpretation of this condition.
-This geometrical construction will be used to prove the following Lemma:
-
-\begin{lemma}   \label{lem2}
-Suppose that $$H_q(\rho,e^{-j\omega})={W_q\jo \Delta_q(\rho,e^{-j\omega})} \psi^{-1}(\rho,e^{-j\omega})$$ is the frequency response of a bounded analytic function outside the unit circle.
-Then, the following constraint is met
-\begin{equation} \label{eq4}
-\sup_{\omega \in \Omega}  |H_q(\rho,e^{-j\omega})| < \gamma
-\end{equation}
-if and only if there exists a finite-impulse-response (FIR) function $F(z^{-1})$ that satisfies
-$$
-\Re\{\psi(\rho)F(e^{-j\omega})\}>\gamma ^{-1}|W_q\Delta_q(\rho)F(e^{-j\omega})|,  \qquad \forall \omega \in \Omega 
-$$
-\end{lemma}
-
-{\it Proof :} 
-The basic idea is similar to that of  the proof of Theorem~1 in \cite{RM94}.
-It is clear that (\ref{eq4}) is satisfied if and only if the disk of radius $ \gamma ^{-1}|W_q\Delta_q(\rho)|$ centered at $\psi(\rho)$ does not include the origin for all $\omega \in \Omega$, i.e.
-$|\psi(\rho)|>\gamma ^{-1}|W_q\Delta_q(\rho)|$.
-This is equivalent to the existence of a line passing through origin that does not intersect the disk.
-Therefore, at every given frequency, $\omega$, there exists a complex number $f(e^{-j\omega})$ that can rotate the disk such that it lays inside the right hand side of the imaginary axis.
-Hence, we have
-\begin{equation}
-\label{eq:lem_eq1}
-\begin{split}
-\Re \left\{ \left[ \psi(\rho) - \gamma ^{-1}|W_q\Delta_q(\rho)|e^{j\theta} \right] f(e^{-j\omega}) \right\}>0 \\
-\forall \omega \in \Omega, \forall \theta \in [0 \, , \, 2 \pi [
-\end{split}
-\end{equation}
-where $\Re \{ \cdot \}$ denotes the real part of a complex variable. Since $f(e^{-j\omega}) = |f(e^{-j\omega})|e^{j\theta_f}$, then the above condition can be expressed as
-\begin{equation}
-\label{eq:lem_eq2}
-\begin{split}
-\Re\{  \psi(\rho)f(e^{-j\omega}) \}> \gamma ^{-1}|W_q\Delta_q(\rho)f(e^{-j\omega})|\cos(\theta + \theta_f) \\
-\forall \omega \in \Omega, \forall \theta \in [0 \, , \, 2 \pi [
-\end{split}
-\end{equation}
-However, (\ref{eq:lem_eq2}) is satisfied if and only if:
-\begin{equation}
-\label{eq18}
-\begin{split}
-\Re\{  \psi(\rho)f(e^{-j\omega}) \}> \gamma ^{-1}|W_q\Delta_q(\rho)f(e^{-j\omega})| \\
-\forall \omega \in \Omega
-\end{split}
-\end{equation}
-In \cite{RM94}, it is shown that, $f(e^{-j\omega})$ can be approximated arbitrarily well by the frequency response of a stable transfer function or FIR function $F(z^{-1})$ if and only if 
-\begin{equation}
-Z=\left( \psi(\rho) - \gamma_0 ^{-1}|W_q\Delta_q(\rho)|e^{j\theta} \right)^{-1}
-\end{equation}
-is analytic in the right half plane for all $\gamma_0>\gamma$ and all $\theta \in [0 \, , \, 2 \pi [$.
-However, $\psi^{-1}(\rho)$ is stable because of the stability of $H_q(\rho)$.
-On the other hand, by decreasing $\gamma_0$ from infinity to $\gamma$, the poles of $Z$ move continuously with $\gamma_0$.
-Therefore, $Z$ is not analytic in the right half plane if and only if $Z^{-1}(e^{-j\omega})=0$ for a given frequency, which is not the case because the origin is not in the interior of the circle $\gamma_0 ^{-1}|W_q\Delta_q(\rho)|e^{j\theta}$.
-{\hfill \ensuremath{\blacksquare}}
-
-The set of all controllers that meet the performance condition defined by the weighted norm of sensitivity functions is asserted in the following theorem.
-
-\begin{theorem}  \label{Th1}
-Given the frequency response function $G\jo = N\jo M^{-1}\jo$ and the frequency response of a weighting filter $W_q\jo$, then the following statements are equivalent for a given $q \in \mathcal{Q}$:
-
-{\bf (a)} There exists an $RST$ controller that stabilizes $G$ and
+For this power converter application, it was desired to track a desired reference signal while maintaining sufficient stability margins. Therefore,
 
 \begin{equation}
-	\label{state_a_single}
-	\begin{aligned}
-	\sup_{\omega \in \Omega}  | {W_q \mathcal{S}_q(\rho)} | < \gamma 
-	\end{aligned}
+\int f(t)e^{-st}dt
 \end{equation}
-
-    %\begin{equation}
-	%\label{state_a}
-	%\sup_{\omega \in \Omega}  | {W_0 (1+GK)^{-1}} | < \gamma
-	%\end{equation}
-
-{\bf (b)} There exists an $RST$ controller such that
-\begin{equation} \label{state_b_single}
-\begin{aligned}
-\Re\{\psi(\rho)\}  >\gamma ^{-1}|W_q\Delta_q(\rho)|\quad \forall \omega \in \Omega
- \end{aligned} 
-\end{equation}
-\end{theorem}
-{\it Proof :} ({\bf b} $\Rightarrow$ {\bf a}) 
-$\psi(\rho)$ is analytic outside the unit circle and its real part is positive for all $\omega \in \Omega$.
-Therefore, $\psi(\rho)$ will not encircle the origin when $\omega$ travels along the Nyquist contour, and its inverse is stable.
-This implies that $R(\rho)$ and $S(\rho)$ stabilizes $G$.
-On the other hand, we have
-\begin{equation}  \nonumber
-\begin{aligned}
-|\psi(\rho)| \geq \Re\{\psi(\rho)\} \quad 
-\forall \omega \in \Omega
-\end{aligned}
-\end{equation}
-which leads to
-\begin{equation} \label{eq:the_1_single_2}
-\begin{aligned}
-|W_q\Delta_q(\rho)| < \gamma |\psi(\rho)| \quad \forall \omega \in \Omega
- \end{aligned}
-\end{equation}
-Therefore, (\ref{eq:the_1_single_2}) leads to (\ref{state_a_single}) in Statement ({\bf a}).
-
-({\bf a} $\Rightarrow$ {\bf b}) Assume that $R(\rho_0)$,  $S(\rho_0)$, and/or\footnote{The inclusion of $T(\rho_0)$ depends on which sensitivity function $\mathcal{S}_q^0(\rho)$ is being considered} $T(\rho_0)$ satisfies Statement ({\bf a}) but not Statement ({\bf b}).
-Then, according to Lemma 1, there exists a FIR function $F(z^{-1})$ such that
-\begin{equation} \label{eq:the_ineq1}
-\Re\{ \psi(\rho_0) F(e^{-j\omega})\} > \gamma^{-1}|F(e^{-j\omega})W_q\Delta_q(\rho_0)| \quad \forall \omega \in \Omega
-\end{equation}
-Therefore, there exists a higher order $RST$ controller with $R= R(\rho_0)F$, $S = S(\rho_0)F$, and/or $T = T(\rho_0)F$ such that Statement ({\bf b}) holds.
- {\hfill \ensuremath{\blacksquare}}
-
-The above theorem is a necessary and sufficient condition for satisfying the $\mathcal{H}_\infty$ criterion for \textit{one} sensitivity function.
-However, in typical control system applications, it is desired to shape several sensitivity functions simultaneously and impose multiple constraints on the weighted sensitivity functions.
-The following theorem ensures necessity and sufficiency of the $\mathcal{H}_\infty$ criterion when multiple sensitivity functions are considered:
-
-\begin{theorem}  \label{Th2}
-Given the frequency response function $G\jo = N\jo M^{-1}\jo$ and the frequency response of bounded weighting filters $W_q\jo$ for $\forall q \in \mathcal{Q}$, the following statements are equivalent:
-
-{\bf (a)} There exists an $RST$ controller that stabilizes $G$ and
-
-	\begin{equation}
-	\label{state_a}
-	\begin{aligned}
-	\sup_{\omega \in \Omega}  | {W_q \mathcal{S}_q(\rho)} | < \gamma \quad
-	\forall q \in \mathcal{Q}
-	\end{aligned}
-	\end{equation}
-
-    %\begin{equation}
-	%\label{state_a}
-	%\sup_{\omega \in \Omega}  | {W_0 (1+GK)^{-1}} | < \gamma
-	%\end{equation}
-
-{\bf (b)} There exists an $RST$ controller such that
-\begin{equation} \label{state_b}
-\begin{aligned}
-\Re\{\psi(\rho)\}  >\gamma ^{-1}|W_q\Delta_q(\rho)|\quad \forall \omega \in \Omega
- \end{aligned} 
-\end{equation}
-and for all $q \in \mathcal{Q}$.
-\end{theorem}
-{\it Proof :} ({\bf b} $\Rightarrow$ {\bf a}) 
-The proof for this condition is equivalent to the proof presented in Theorem \ref{Th1}.
-By satisfying the constraint in (\ref{state_b}) for all $q \in \mathcal{Q}$, the condition in (\ref{state_a}) for each corresponding $q$ is obtained.
-
-({\bf a} $\Rightarrow$ {\bf b}) Assume that $R(\rho_0)$,  $S(\rho_0)$, and/or $T(\rho_0)$ satisfies Statement ({\bf a}) but not Statement ({\bf b}).
-Then, according to Lemma 1, there exist FIR transfer functions $F_q(z^{-1})$ such that
-\begin{equation} \label{eq:the_ineq1}
-\Re\{ F_q\psi(\rho_0)- \gamma ^{-1}|F_qW_q \Delta_q(\rho_0)|\} > 0 
-\end{equation} 
-for all $\omega \in \Omega$ and for all $q \in \mathcal{Q}$.
-For Statement ({\bf b}) to hold, there must exist a common $F$  for all $q \in \mathcal{Q}$ such that  $R = R(\rho_0)F$, $S= S(\rho_0)F$, and/or $T = T(\rho_0)F$.
-
-For a given frequency, the constraints in (\ref{state_a}) will represent circles in the complex-plane that are centered exactly at $\psi(\rho_0)$ with varying radii (where the radii depend on each $q$).
-Let us define the following quantities at every $\omega \in \Omega$:
-\begin{equation} 
-\begin{aligned}
-\mathscr{R}(e^{-j\omega},\rho_0) &= \{ |W_1 \Delta_1(e^{-j\omega},\rho_0)| , \ldots,|W_{c} \Delta_{c}(e^{-j\omega},\rho_0)|\}\\
-r(e^{-j\omega},\rho_0) &=  \gamma^{-1}  \max_{q \in \mathcal{Q}}\mathscr{R}(e^{-j\omega},\rho_0) \\
-\end{aligned}
-\end{equation}
-For any $\omega$, the circle with radius $r(\rho_0)$ does not include the origin, and all of the other circles with smaller radii are enclosed in the circle with radius $r(\rho_0)$, i.e. : 
-$$\gamma^{-1}|W_q \Delta_q(e^{-j\omega},\rho_0)| \leq r(e^{-j\omega},\rho_0)$$ 
-Therefore, for a given frequency, the complex number $f_q$ which is used to rotate the circle associated with radius $r(e^{-j\omega},\rho_0)$ ensures that all of the circles with $\gamma^{-1}|W_q \Delta_q(e^{-j\omega},\rho_0)| \leq r(e^{-j\omega},\rho_0)$ are also rotated such that they all lie in the right-hand side of the imaginary axis.
-Therefore, there will always exist a common $F$ that interpolates all $f_q$ (different $q$ in different frequencies) such that the conditions in (\ref{eq:the_ineq1}) hold true for all $q \in \mathcal{Q}$.
- {\hfill \ensuremath{\blacksquare}}
-
-\subsection{Robust Design}
-\label{sec:rob_con}
-With the proposed method, it is possible to design a fixed-structure controller which accounts for the uncertainties of a given FRF (as described in Section \ref{sec:freq_uncertain}).
-Given this additive uncertainty, a desired performance condition $\|W_q \mathcal{S}_q \|_{\infty}<\gamma$ will be satisfied for all models in the uncertain set (\ref{eq:frf_uncertainty}) if $\| W_q \mathcal{\hat{S}}_q\|_{\infty} < \gamma$, where $\mathcal{\hat{S}}_q =\hat{\Delta}_q/\hat{\psi}(\rho)$ and $\hat{\psi}(\rho) = \hat{N}R(\rho) + \hat{M}S(\rho) $.
-For example, consider the nominal performance condition $\|W_3 \mathcal{\hat{S}}_3 \|_{\infty}<\gamma$ with $\hat{\Delta}_3(\rho) = \hat{M}S(\rho) + \hat{N}[R(\rho)-T(\rho)]$; as a worst case consideration, $\delta_m$ and $\delta_n$ can be selected to be equal to one  in (\ref{eq:frf_uncertainty}) (which ensures that the uncertainty in the entire disk is taken into account).
-By substituting the expressions in (\ref{eq:frf_uncertainty}) into this condition, the following constraint can be devised:
-\begin{equation} \label{eq:robust_uncertain}
-\begin{split} 
- \bigl|W_3 \left[ \psi(\rho) -NT(\rho)+S(\rho)|W_m|e^{j\theta_m} + C(\rho)|W_n|e^{j\theta_n}\right] \bigr| \\
-< \gamma \bigl| \psi(\rho) + R(\rho)|W_n|e^{j\theta_n} + S(\rho)|W_m|e^{j\theta_m} \bigr|\\
-\forall \omega \in \Omega, \forall \{\theta_n,\theta_m \} \in [0,2\pi]
-\end{split}
-\end{equation}
-where $C(\rho) = R(\rho) - T(\rho)$.
-For notation purposes, let us define $\psi\sp{\prime}(\rho,\theta_n) := \psi(\rho) + R(\rho)|W_n|e^{j\theta_n}$.
-Then for a given $\{\omega,\theta_n,\theta_m \}$, (\ref{eq:robust_uncertain}) represents a circle centered at $\psi\sp{\prime}(\rho,\theta_n) + S(\rho)|W_m|e^{j\theta_m}$ with a radius of
-\begin{equation} \label{eq:robust_ness_suff_1}
-\begin{split} 
-x_p (\rho,\theta_m,\theta_n)  = \gamma^{-1}|W_3| \bigl| \psi\sp{\prime}(\rho,\theta_n)  + S(\rho)|W_m|e^{j\theta_m} \\ - T(\rho)[N+|W_n|e^{j\theta_n}] \bigr|
-\end{split}
-\end{equation}
-According to Theorem \ref{Th1}, a necessary and sufficient condition for (\ref{eq:robust_uncertain}) can be constructed as follows:
-\begin{equation} \label{eq:robust_ness_suff_2}
-\begin{split} 
- x_p (\rho,\theta_m,\theta_n) < \Re \{ \psi\sp{\prime}(\rho,\theta_n)+ S(\rho)|W_m|e^{j\theta_m} \} \\
-\forall \omega \in \Omega, \forall \{\theta_m,\theta_n\} \in [0,2\pi]
-\end{split}
-\end{equation}
-By gridding in $\omega$, $\theta_m$ and $\theta_n$, then (\ref{eq:robust_ness_suff_1}) becomes a convex constraint (with respect to $\rho$); however, gridding in all of these variables can be computationally expensive.
-For stable plants (which is the case at CERN), $M = 1$ may be selected.
-Therefore, the disk uncertainty associated with $M$ is $|W_m| = 0$.
-From (\ref{eq:robust_ness_suff_1}) and (\ref{eq:robust_ness_suff_2}), it can be observed that with $|W_m| = 0$, the dependency on $\theta_m$ is removed, and no gridding in $\theta_m$ is required.
-The necessary and sufficient condition then becomes
-\begin{equation} \label{eq:robust_ness_suff_3}
-\begin{split} 
- x_p (\rho,\theta_n) < \Re \{ \psi\sp{\prime}(\rho,\theta_n)\} \\
-\forall \omega \in \Omega, \forall \theta_n \in [0,2\pi]
-\end{split}
-\end{equation}
-where
-\begin{equation} \label{eq:robust_ness_suff_4}
-\begin{split} 
-x_p (\rho,\theta_n)  = \gamma^{-1}|W_3| \bigl| \psi\sp{\prime}(\rho,\theta_n)  - T(\rho)[N+|W_n|e^{j\theta_n}] \bigr|
-\end{split}
-\end{equation}
-In certain applications, gridding in two variables can still be computationally burdensome. Therefore, a sufficient condition for (\ref{eq:robust_uncertain}) can be devised as follows:
-\begin{equation} \label{eq:uncertain_condition}
-\sup_{\omega \in \Omega} \frac{|W_3|\bigl[|\psi(\rho)-NT(\rho)|  + |C(\rho)W_n | \bigr]}{|\psi(\rho)| -|R(\rho)W_n| } < \gamma
-\end{equation}
-With this condition, the dependency in $\theta_m$ and $\theta_n$ has been removed, and gridding in only one variable (i.e., $\omega$) is required. Note that the above constraint is sufficient since
-\begin{align*}
- & \phantom{{}\leq{}} |W_3|  \bigl| \psi(\rho)  -NT(\rho) + C(\rho)|W_n|e^{j\theta_n} \bigr| \\
- & \leq |W_3|\bigl[|\psi(\rho)-NT(\rho)|  + |C(\rho)W_n | \bigr] \\
- & < \gamma \bigl[ |\psi(\rho)| -|R(\rho)W_n| \bigr] \\
- & \leq \gamma \bigl| \psi(\rho) +R(\rho)|W_n|e^{j\theta_n} \bigr|
-\end{align*}
-%It can be observed that the quantity $|\psi(\rho)| -|R(\rho)W_n|$ may be less than zero; in this case, the problem simple becomes infeasible for that particular value of $\omega$.
-
-The condition in (\ref{eq:uncertain_condition}) can be represented as a disk in the complex plane which is centered at $\psi(\rho)$ and has radius
-\begin{equation} \label{eq:rad_robust_design}
-\begin{aligned} 
-x_r (\rho) = \gamma^{-1}|W_3| \bigl[|\psi(\rho)-NT(\rho)|  \\ + |C(\rho)W_n | \bigr] +  |R(\rho)W_n| 
-\end{aligned}
-\end{equation}
-%If $|\psi(\rho)| < |W_mS(\rho)|+|W_nR(\rho)|$, then the disk given by (\ref{eq:uncertain_condition}) will become its complement, and the problem will simply be infeasible. 
-%In Theorem \ref{Th2}, it was shown that the $\mathcal{H}_\infty$ criterion is satisfied for an arbitrary amount of weighted sensitivity functions (where, for a given frequency, the circles for each sensitivity function were each centered at $\psi(\rho)$).
-Since the circle associated with (\ref{eq:uncertain_condition}) is also centered at $\psi(\rho)$, then the necessity and sufficiency is also ensured for this constraint (see the proof for the necessary condition in Theorem \ref{Th2}).
-Therefore, a set of convex constraints (with respect to $\rho$) can be devised with the following condition:
-\begin{equation}
-x_r(\rho) < \Re \{ \psi(\rho)\}, \quad \forall \omega \in \Omega
-\end{equation}
-This constraint has the same structure as that of the sensitivity functions and so can readily be included in the optimization problem.
-Note that (\ref{eq:uncertain_condition}) introduces some conservatism; however, this conservatism can always be reduced by imposing (\ref{eq:robust_ness_suff_2}) for unstable plants or (\ref{eq:robust_ness_suff_3}) for stable plants.
-
-\subsection{Convex Optimization via Semi-Definite Programming}
-Suppose that it is desired to obtain $\mathcal{H}_{\infty}$ performance for a sensitivity function (i.e., minimize $\gamma$ in $\|W_q\mathcal{S}_q \|_{\infty}<\gamma$).
-Then according to Theorem \ref{Th2}, one can formalize an optimization problem to obtain the admissible $R(\rho)$, $S(\rho)$, and/or $T(\rho)$ controllers as follows:
-\begin{equation} \label{eq:min2}
-\begin{aligned}
-& \underset{ \rho}{\text{minimize}}
-& & \gamma  \\
-& \text{subject to:} & & \gamma^{-1} |W_q \Delta_q| < \Re\{\psi(\rho) \}  \\ 
-& & & \forall \omega \in \Omega \quad ; \quad  q \in \mathcal{Q}
-\end{aligned}
-\end{equation}
-
-The optimization problem in (\ref{eq:min2}) is quasi-convex since the objective function ($\gamma$) is being multiplied with the optimization parameters of the controller in the constraints.
-The classical solution is to implement a bisection algorithm in order to \emph{convexify} the optimization problem.
-In this method, an iterative approach is implemented in order to obtain an asymptotically convergent solution.
-\begin{remark}
-In the bisection method, an initial value is assigned for $\gamma$ such that $\gamma_0 = 0.5(\gamma_{min} + \gamma_{max})$ to solve the optimization problem, where $\gamma_{min}$ and $\gamma_{max}$ are the minimum and maximum bounds set for $\gamma$.
-In an iterative algorithm, if the problem is feasible for $\gamma_i$, then $\gamma_{i+1} = 0.5(\gamma_{min} + \gamma_i)$, and the solution to the optimization problem in (\ref{eq:min2}) is recalculated with $\gamma_{i+1}$.
-If the problem is infeasible for $\gamma_i$, then $\gamma_{i+1} = 0.5(\gamma_{max} + \gamma_i)$.
-This process is repeated until a solution is obtained within a given tolerance.
-\end{remark}
-
-The problem in (\ref{eq:min2}) is known as a semi-infinite programming (SIP) problem since there are a finite number of optimization variables and an infinite number of constraints.
-To solve this problem, the optimization algorithm can be converted to a semi-definite programming (SDP) problem.
-A predefined frequency grid can be implemented in order to solve a finite number of constraints.
-This frequency grid can be predefined in a variety of manners (see \cite{SVBB11}, \cite{GKL10b}).
-
-\section{Power Converter Framework}
-\label{sec:4}
-Particle accelerators use power converters for many different applications.
-Some converters are used simply to convert energy in one form to another (to energize special devices); in other cases, power converters are used in a control structure to control particles trajectories (and other \emph{optical} parameters of particle beams) within the accelerator system by modulating the magnetic field produced by specialized (electro-) magnets.
-These converters will be the focus of this paper.
-Particle beams usually require extremely precise magnetic fields; in certain cases, accuracy is also crucial for particle accelerators operation \cite{TPMK10}.
-In most cases, the magnetic fields produced by the magnets cannot be measured in real-time.
-Therefore, the output current of the power converter (which is injected into the magnets) is used to control the trajectory of particles.
-
-%The CERN LHC Injector Upgrade Project \cite{BHAK14} was implemented to mitigate space-charge effects and to increase the beam brightness in order to fulfill the needs of the High Luminosity LHC.
-To realize these improvements,  a major upgrade of the PS Booster (PSB) was actualized where the injection energy was increased from $50$ MeV to $160$ MeV.
-The LINAC4 \cite{LINAC4} hydrogen ions (H$-$) beam must pass through an electron stripping foil in order to inject protons into the Booster.
-This is done by a magnetic/optical chicane (4 magnets per each ring) which is powered to displace the injected beam in order to strip its electrons.
-When the injection process is finished, the chicane will be inactive (zero current).
-This process produces perturbations in the optics of the Booster machine during the injection, and actions to compensate them must be foreseen by adding a correction function to the current of the Q-STRIP magnet.
-The Q-STRIP system is constituted of two chains of quadrupole magnets for each ring (one for focusing and one for de-focusing); each chain is powered by a single power converter.
-
-\subsection{Power Converters for Particle Accelerators}
-The framework of the system discussed in this paper is part of the CERN Large Hadron Collider (LHC) Injector Upgrade Project \cite{BHAK14},  which was implemented to mitigate space-charge effects and to increase the beam brightness in order to fulfill the needs of the High Luminosity LHC.
-The Q-STRIP magnet (i.e., the load, which is constituted of two chains of quadrupole magnets) is used in this framework to control the particle trajectories via the power converter control system.
-
-Power converters can be seen as systems comprised of three main subsystems: (\textit{i}) a power source (usually a voltage source) (\textit{ii}) a measuring system and (\textit{iii}) a controller unit.
-The current is usually measured with a particularly accurate current transducer called a direct current-current transformer (DCCT) \cite{Kin01}.
-The current measurement signal is fed back to a digital controller unit which usually includes a high precision analog-to-digital converter that implements the digital control algorithm(\cite{TPMK10}, \cite{BFC07}).
-% The power source is then used as a power amplifier in order to power the magnet through a high bandwidth voltage loop.
-%\subsection{Power Converters Control at CERN}
-
-The general configuration of the CERN power converter control system is depicted in Fig.\ref{fig:ident_block}.
-The control loop consists of a magnet (i.e., the load), a voltage source $V_s$, low-pass anti-aliasing analog and digital filters (ALPF, DLPF), a digital-to-analog converter (DAC), and an analog-to-digital converter (ADC).
-The DAC (optional) and ADCs are integrated in the control unit labeled as the function generator controller (FGC, \cite{CKS11}) whose main function is to execute the control algorithm; it also implements all the diagnostics and communication functions with higher layers of the control architecture up to the accelerators control rooms.
-The DLPF may also includes a decimator to reduce the sampling rate of the signal.
-The COMM block represents the delay associated with the communications link.
-The $RST$ block represents the discrete-time controller that is used to control the magnet current $i_D$ given a reference current $i_R$.
-
-%The dynamics associated with the filters, the transducer, the DAC, and the ADC are very fast (i.e., they each possess a very large bandwidth), and can usually be approximated arbitrarily well as a positive (real valued) time delay.
-
-\begin{figure}
-\centering
-\resizebox{1\columnwidth}{!}{\input{pc_drawing_ident2.eps_tex}}
-%\caption{A block diagram which depicts the system structure and the identified process. Identified components (red-dashed blocks); unidentified components (blue blocks).}
-%\centering
-%\resizebox{1\columnwidth}{!}{\input{pc_drawing.eps_tex}}
-\caption{Power converter control system}
-%\label{fig:pc}
-\label{fig:ident_block}
-\end{figure}
-
-%on a CANCUN power converter connected to an $RL$ load whose characteristics match those of the Q-STRIP magnets (the magnet used for the experiment has an inductance about $10\%$bigger which can be considered as a worst case for tracking performance evaluation).
-The CANCUN is based on a full bridge phase shifted topology followed by a 4 quadrant switching stage to allow 4 quadrant operation.
-Fig.~\ref{fig:cancun} shows a CANCUN converter which is comprised of a voltage (or power) unit, the control electronics, and the measurement systems in a compact chassis.
-The ratings of the CANCUN converter for the Q-STRIP application would be $\pm 100$ $A$ and $\pm 30$ $V$ (the one used for experimental validation is just slightly different: $\pm 50$ $A$ and $\pm 30$ $V$).
-%Table.~\ref{tab:cancun} displays the converter ratings and operating characteristics.
-
-%\begin{table}
-%\centering
-%\caption{Main CANCUN Characteristics}
-%\label{tab:cancun}
-%\begin{tabular}{l|l}
-%\textit{\textbf{Feature}} & \textit{\textbf{Value}}\\ \hline
-%Input Power              & $3 \sim \ 240\: V/2.75\: A$                                     \\ \hline
-%Output Power              & $\pm 50\: A / \pm 30 \: V$                               \\ \hline
-%Converter Type              & 4 Quadrant                                   \\ \hline
-%Control Type             & FGC3 / Ethernet+                                \\ \hline
-%Current Accuracy             & $20 \: ppm$ in $30 \: mn$                                \\ 
-       									%& $20 \: ppm$ in $24 \: h$                                \\    
-       									%& $100 \: ppm$ in $1 \: year$                                \\      
-       									%& $(1 \: ppm=50\: \mu A=0.05 \: mA)$               \\ \hline
-%Voltage Ripple          & $10 \: mV_{rms}$  for  $f \in [20 \: Hz,1 \: kHz)$                                \\ 
-%       									& $60 \: mV_{rms}$  for  $f \in [1 \: kHz,130 \: kHz)$                                 \\    
-%       									& $7 \: mV_{rms} $  for  $f \in [130 \: kHz,5 \: MHz)$	                                            
-%\end{tabular}
-%\end{table}
-
-\subsection{Experimental Test Setup}
-\label{test_setup}
-%on a CANCUN power converter connected to an $RL$ load whose characteristics match those of the Q-STRIP magnets (the magnet used for the experiment has an inductance about $10\%$bigger which can be considered as a worst case for tracking performance evaluation).
-The CANCUN is based on a full bridge phase shifted topology followed by a 4 quadrant switching stage to allow 4 quadrant operation.
-Fig.~\ref{fig:cancun} shows a CANCUN converter which is comprised of a voltage (or power) unit, the control electronics, and the measurement systems in a compact chassis.
-The ratings of the CANCUN converter for the Q-STRIP application would be $\pm 100$ $A$ and $\pm 30$ $V$ (the one used for experimental validation is just slightly different: $\pm 50$ $A$ and $\pm 30$ $V$).
-
-The experimental test setup consists of a CANCUN power converter, a dummy load and a proprietary software diagnostics tool:
-
-\begin{itemize}
-	\item The CANCUN power converter is based on a full bridge phase shifted topology followed by a 4 quadrant switching stage to allow 4 quadrant operation.
-Fig.~\ref{fig:cancun} shows a CANCUN converter that incorporates three main parts: $i$) Two high precision current sensors (DCCTs) which are able to measure DC or pulsed current at the required precision; $ii$) A voltage (or power) module; $iii$) A digital controller (FGC3) which implements the digital control loop together with CERN designed control and diagnostics electronics.
-The ratings of the CANCUN converter for the Q-STRIP application is $\pm 100$ $A$ and $\pm 30$ $V$.
-	\item The dummy load is an $RL$ load whose characteristics match those of the Q-STRIP magnets; however, the magnet used for the experiment has an inductance approximately $10\%$ larger, which can be considered as a worst case for tracking performance evaluation.
-	\item The software diagnostics tool interfaces with the main digital controller module, the FGC3 \cite{CKS11}, and is able to acquire the relevant signals at a sampling rate of $10$K samples per second.
-The acquired signals are the reference current and voltage, measured current, and voltage and current error.
-The length of the record is fixed to $1.2$ $s$, which corresponds to $12000$ samples.
-\end{itemize}
-
-\begin{figure}
-\centering
-\includegraphics[width=0.8\columnwidth]{pics/housing_rack.eps}
-\caption{CANCUN power converter. } 
-%The FGC also collects and reports all statuses, faults, and measurements from various parts of the system and serves as the interface towards higher levels layers of the complex accelerator control architecture.}
-\label{fig:cancun}
-\end{figure}
-
-\iffalse
-\subsection{Track Delay and Tracking Error}
-\label{track_error_definition}
-%Before proceeding to the next section, it is imperative to first assert how the error is determined between the reference and the output current. 
-In typical control applications, the error is usually calculated as the difference between the reference and the output sampled at a given time $t$.
-However, for some power converter control applications at CERN, the error is actually calculated as the difference between a delayed version of the reference input and the output at time $t$.
-The delayed reference input (for an arbitrary, positive delay) can be approximated as the output of the following interpolating filter:
-\begin{equation}
-\label{eq:del_filt}
-\begin{aligned}
-H(z^{-1})=z^{-\lfloor \tau \rfloor} \left(  1-(\tau - \lfloor \tau \rfloor) + (\tau - \lfloor \tau \rfloor)z^{-1}   \right) \\ \ \tau \in \mathbb{R}
-\end{aligned}
-\end{equation}
-where $\tau$ is a (generally fractional) delay (expressed in units of the sampling time $T_s$), and the $\lfloor \cdot \rfloor$ operator represents the floor function which maps the real number in the argument to the largest integer not greater than that number.
-The use of (\ref{eq:del_filt}) allows one to interpolate the delayed reference signal between sampling points and calculate a more accurate error signal.
-For a given reference signal $\tilde{r}(z^{-1})$, the interpolated (causal) discrete-time reference signal will be
-\begin{equation}
-\label{eq:del_filt_new}
-\begin{aligned}
-r[n] &= \mathcal{Z}^{-1} \{ H(z^{-1}) \tilde{r}(z^{-1})\} \\
-&=(1-\tau_{\text{frac}}) \tilde{r}[n-\lfloor \tau \rfloor]+ \tau_{\text{frac}} \tilde{r}[(n-1) -\lfloor \tau \rfloor]
-\end{aligned}
-\end{equation}
-where $\tau_{\text{frac}} = \tau - \lfloor \tau \rfloor$ and $n \in \mathbb{Z}$.
-Therefore, for any discrete time instant $n$, the error is determined as $e[n] = r[n] - y[n]$, where $y[n]$ is the output response.
-For the purposes of this paper, $\tau$ is termed as the `track delay', and its value is related to the group delay of the closed-loop system:
-\begin{equation}
-\tau_g(\omega) = - \frac{d\phi_T(\omega)}{d\omega}; \quad \tau = \tau_g(0) \\
-\label{eq:group_delay_theor}
-\end{equation}
-where $\phi_T(\omega)$ is the phase response associated with the closed-loop FRF.
-%\end{remark}
-\fi
-
-\section{Case Study Results}
-\label{sec:5}
-This case study is devoted to the CANCUN power converter control system, as described in the previous section.
-The objective is to control the output current $i_D$ that is injected into the particle accelerator magnets in order to ensure proper particle trajectories.
-The profile of the reference current $i_R$ associated with the Q-STRIP magnet is shown in Fig.~\ref{fig:QCF_ref}.
-For this application, the challenging task is to ensure the tracking performance; it is required that the error remains within $\pm 1000$ ppm\footnote{The calculation for obtaining the error in ppm is performed by taking the raw data for the error and scaling it by a factor of $\sfrac{10^6}{100}$.
-The factor of $100$ represents the nominal current ($100$ $A$) of the power converter for the Q-STRIP magnets.} during the fast transient and remains within $\pm 100$ ppm during steady state.
-The proposed controller design method was used to synthesize an $RST$ controller for this specific requirement.
-Experimental validation was performed by means of the test setup presented in \ref{test_setup}.
-\begin{figure}
-\centering
-\includegraphics[width=\columnwidth]{pics_prbs/reference.eps}
-\caption{The reference current associated with the QCF circuit configuration.
-The blue-dashed line indicates the time when the error must remain within $\pm 1000$ ppm; the red-dashed line indicates the time when the error must remain within $\pm 100$ ppm;}
-\label{fig:QCF_ref}
-\end{figure}
-
-The Q-STRIP magnet is represented as an $RL$ circuit, and the dynamics of this circuit are dominant over the other components of the system.
-Thus a first order model with delay (i.e., $G_m(s) = e^{-sT_d}(L_m s + R_m)^{-1}$, where $R_m$ is the circuit resistance, $L_m$ is the circuit inductance, and $T_d$ is the time delay) is appropriate to approximate the dynamics of the plant.
-For this case study, the model parameters are:
-\begin{equation*}
-R_m = 164.3 \: m \Omega; \quad L_m = 736.4 \: \mu H; \quad T_d = 275.4 \: \mu s
-\end{equation*}
-The model is then discretized using the zero-order-hold method and used to design an $RST$ controller based on the model-reference control (MRC) strategy \cite{LZ06}.
-In this particular implementation of the strategy, the transfer function between the reference signal and output depends on the location of the single zero (which comes from modeling the fractional delay) of the system \cite{KNM15}.
-According to \cite{LZ06}, if the fractional delay of the system is less than $0.5T_s$, then the zero of the system can be cancelled (which enables the tracking and regulation performances to be achieved without approximation).
-However, at CERN, this benchmark is modified such that the zero of the system is cancelled if the fractional delay is less than $0.4T_s$.
-In this case, the reference model is selected such that the transfer function from the reference input to the output will be a pure delay.
-However, if the fractional delay is greater than $0.4T_s$, then the corresponding zero cannot be cancelled, and the transfer function from the reference input to the output is represented as a fractional delay.
-The main difficulty of this approach is that the choice of the observer poles that lead to a good robustness margin is not trivial.
-The current practice at CERN is a trial-and-error approach to meet the control specifications.
-The main objective of this case study is to propose a systematic optimization based approach to compute the optimal controller parameters and guaranteeing robustness with respect to model uncertainties.
-
-For this type of application, it is a challenging task to achieve tracking and a good robustness margin simultaneously.
-With the MRC method, the auxilary  poles must be placed in an iterative fashion in order to achieve the desired modulus margin of $0.5$.
-However, the method proposed in this paper does not need a parametric identification or any iterative tuning scheme.
-It is a straightforward systematic design methodology that takes also into account the frequency-domain uncertainties, which increases the robustness of the design process.
-
-\subsection{Frequency Response Function Measurement}
-A pseudo-random binary sequence (PRBS) signal was used as the input voltage reference of the open-loop system in order to capture the dynamics of the process.
-The PRBS is a deterministic signal which has characteristics similar to that of white noise and is usually used for system identification.
-From Fig.~\ref{fig:ident_block}, the measurement process will capture the dynamics from the input of the DAC (with input voltage $v(t)$ representing the reference voltage of the voltage source) to the output of the DLPF (with output current $i(t)$ representing the measured current to be fed back to the $RST$ controller).
-
-Unfortunately, the FGC3 is limited by the amount of input samples that can be programmed to execute the PRBS signal (a maximum of $1023$).
-Therefore, to maximize the quality of the measurement, a PRBS signal of length $511$ ($9$-bits) with $2$ periods was injected as the input of the open-loop process.
-Note that a PRBS of length $1023$ ($10$-bits) with one period could also be used as the input; however, the output of such a reference will contain transients and must be considered as an aperiodic signal and thus increasing the truncation errors.
-
-A total of $5$ experiments were performed with the PRBS clock period $T_{cl} = 100 \: \mu s$; the acquired periods (with transients removed in post-processing) could then be merged together.
-For a signal of length $511$, the frequency resolution is limited to $255$ points.
-A DC gain was added to this measurement in order to increase the resolution at lower frequencies (due to the low resolution resulting from the PRBS identification).
-This DC value was determined by simply applying a DC voltage $v(t) = V_{dc} = 1V$ and obtaining the value $i(t) = I_{dc}$.
-With $95\%$ confidence, the uncertainty associated for this gain can be calculated as
-$$|W_n(e^{-j\omega_0})| = 2\sigma_I / \sqrt{N_s} = 3.51 \times10^{-4}$$ 
-where $\omega_0$ is chosen to be arbitrarily small ($\omega_0 = 0.2\pi$), $N_s = 12000$ is the length of the signal, and $\sigma_I = 0.0192 \: A$ is the root-mean-square of the measurement noise.
-This specific value of the uncertainty is for the DC gain and not for all of the other corresponding frequencies.
-The uncertainties for the remaining frequencies were determined with (\ref{eq:uncertainty_radius}).
-The PRBS input signal along with the resulting output response are shown in Fig.~\ref{fig:PRBS}.
-
-\begin{figure}
-\centering
-\includegraphics[width=\columnwidth]{pics_prbs/prbs_time.eps}
-\caption{PRBS signal used for the input voltage $v(t)$ of the open-loop system along with the resulting output current $i(t)$.}
-\label{fig:PRBS}
-\end{figure}
-The FRF of the open-loop plant was then obtained as $G\jo=\mathcal{F}[i(t)]/ \mathcal{F}[v(t)]$ (where the operator $\mathcal{F}$ signifies the Fourier Transform).
-From (\ref{eq:uncertainty_radius}) and (\ref{eq:noise_spectrum}), the additive uncertainty associated with each frequency can be computed.
-Fig.~\ref{fig:plant_uncertain} displays a Bode diagram of $G\jo$ with the corresponding uncertainty bounds.
-
-\begin{figure}
-\centering
-\includegraphics[width=\columnwidth]{pics_prbs/bode.eps}
-\caption{Bode diagram of $G\jo$ with additive uncertainty bounds for the corresponding frequency points.}
-\label{fig:plant_uncertain}
-\end{figure}
-
-%\begin{figure}[!b]
-%\centering
-%\resizebox{1\columnwidth}{!}{\input{pc_drawing_ident.eps_tex}}
-%\caption{A block diagram which depicts the system structure and the identified process. Identified components (red-dashed blocks); unidentified components (blue blocks).}
-%\label{fig:ident_block}
-%\end{figure}
-
-%\begin{lemma}
-%Suppose that a bound is set such that $\| \mathcal{S}_0 \| ^{-1}_{\infty} > m_d$, where $m_d$ is the desired minimum value of the modulus margin.
-Then a condition for ensuring this constraint can be formulated as follows:
-%\begin{equation}
-%\begin{aligned}\label{eq:con_mm}
-%m_d|MS(\rho)| < \mathcal{R}e\{\psi(\rho) \}& \\
-%\forall \omega \in \Omega &
-%\end{aligned}
-%\end{equation}
-%\end{lemma}
-%
-%\begin{IEEEproof}
-%The proof for this condition is very similar to the proof of the constraint in Theorem 1.
-Here, the radius of the circle in Fig.\ref{fig:circle} is now $m_d|MS(\rho)|$ instead of $\gamma^{-1}|W_q \Delta_q(\rho)|$.
-%\end{IEEEproof}
-%Since the circle associated with this constraint is centered at $\psi(\rho)$, then the inclusion of this constraint with the $\mathcal{H}_{\infty}$ loop-shaping constraint still guarantees necessity and sufficiency of Theorem \ref{Th2}.
-%
-%
-
-\subsection{Controller Stability}
-\label{sec:con_stab}
-Computation of an unstable controller should generally be avoided \cite{LZ06}.
-The logic behind this assertion has to do with the practical implications involved with a feedback control system.
-Suppose that the plant $G(z^{-1}) = N(z^{-1})M^{-1}(z^{-1})$ is analytic outside the unit circle.
-For the $RST$ structure, it is evident that if the polynomial $S(z^{-1},\rho)$ possesses zeros outside the unit circle, then the open-loop system will become unstable (assuming no zero-pole cancellations occur with $R(z^{-1},\rho)$ and $S(z^{-1},\rho)$).
-In order to avoid this impairment, it is required to impose a constraint such that the polynomial $S(z^{-1},\rho)$ possesses zeroes inside the unit circle.
-This rationalization leads to the following lemma:
-
-\begin{lemma}
-Suppose that $S(z^{-1},\rho)$ is parameterized as in (\ref{eq:Sc}). Then a sufficient (convex) condition to ensure that the zeros of $S(z^{-1},\rho)$ remain inside the unit circle is
-\begin{equation} \label{eq:con_con}
-\Re \{S(\rho) \} > 0; \quad \forall \omega \in \Omega
-\end{equation}
-\end{lemma}
-\begin{IEEEproof}
-First note that a strictly positive real transfer function (and its inverse) is stable.
-$\Re \{S(\rho) \} > 0$ implies that the Nyquist diagram of $S(\rho)$ will not encircle the origin.
-Therefore, $S^{-1}(\rho)$ will not encircle the origin, and $S(\rho)$ is stable.
-\end{IEEEproof}
-
-\subsection{Weighting Filter Design}
-\label{sec:weighting_filter}
-The $\mathcal{H}_{\infty}$ criterion in (\ref{eq:true_hinf}) is a very powerful design tool, as it provides the capability to shape any sensitivity function $\mathcal{S}_q$ based on the specifications set by a weighting filter.
-However, in certain design schemes at CERN, it may be desired to bound a sensitivity function to a particular value.
-For example, it may be desired to simply impose a lower-bound on the modulus margin in order to obtain the intended robust performance of a system.
-The modulus margin is defined as the minimum distance between the critical point $(-1+j0)$ and the Nyquist plot of the open loop transfer function, and can be expressed as
-\begin{equation}
-M_m = \| \mathcal{S}_1 \| ^{-1}_{\infty}
-\end{equation}
-In general, it is desired to obtain a minimum value of the modulus margin in order to ensure a sufficiently robust system.
-Let $m_d$ denote the minimum value of the desired modulus margin such that $M_m > m_d$.
-According to \cite{LZ06}, typical values for a good modulus margin are $M_m \geq 0.5 \ (-6 \; dB)$ (which ensures a gain margin of at least $6 \; dB$ and a phase margin of at least $29^{\circ}$).
-A constraint for ensuring a minimum value of the modulus margin can be constructed as follows:
-\begin{equation}
-  \| m_d \mathcal{S}_1 \|_\infty < 1 
-\end{equation}
-This constraint is a special case of the $\mathcal{H}_\infty$ constraints with $W_1(e^{-j\omega})=m_d$ and can be convexified using the results of Theorem \ref{Th2}.
-
-For this particular case study, it is desired to obtain the best tracking performance (i.e., by minimizing $\gamma$ in $\|W_3 \mathcal{S}_3 \|_{\infty} < \gamma$) while ensuring reasonable stability margins.
-The weighting filter $W_3$ is chosen based on the fact that $\mathcal{S}_2^d + \mathcal{S}_3^d = 1$, where $\mathcal{S}_3^d$ is the desired error sensitivity function and $\mathcal{S}_2^d$ is the desired complementary sensitivity function (i.e., the closed-loop transfer function).
-$\mathcal{S}_2^d$ was chosen as a standard second order transfer function  with the given form:
-\begin{equation}
-\mathcal{S}_2^d(s) = \frac{\omega_d^2}{s^2 + 2\zeta \omega_d s + \omega_d^2}
-\end{equation}
-where $\zeta$ is the damping factor and
-\begin{equation*}
-\omega_d = \frac{2 \pi f_d}{\sqrt{1-2\zeta^2 + \sqrt{2-4\zeta^2 + 4\zeta^4}}}
-\end{equation*}
-where $f_d$ is the desired closed-loop bandwidth.
-Note that it is possible to consider a continuous-time transfer function for this specification since the proposed method implements a frequency-domain approach.
-Since $\mathcal{S}_2^d = 1- \mathcal{S}_3^d$, an appropriate filter for the error sensitivity function can be devised as
-\begin{equation}
-W_3(s) = \frac{s^2 + 2\zeta \omega_d s + \omega_d^2}{s(s+2\zeta \omega_d)}
-\end{equation}
-Due to the fact that $W_3(j\omega_k)$ is evaluated at a finite number of frequency points with $\omega_0 \neq 0$, then the integrator in $W_3$ does not pose problems with boundedness.
-
-%For discrete-time systems, there are limitations with regards to the achievable closed-loop bandwidth of a system.
-According to \cite{LZ06}, the achievable closed-loop bandwidth is bounded by the following constraint:
-%\begin{equation} \label{eq:bandwidth}
-%f_s \in [6,25]f_d
-%\end{equation}
-A simulation was performed to determine the bandwidth that is required in order to satisfy the desired error specifications.
-At CERN, the error is calculated with respect to a delayed reference input (i.e., $e(t) = r(t-\tau) - y(t)$).
-By assuming that the closed-loop response behaves as $\mathcal{S}_2^d$, the bandwidth $f_d$ can be selected such that the error between the delayed reference input and output is within $\pm 100$ ppm.
-For this second order response, this delay was analytically derived as $\tau = 2\zeta/ \omega_d$.
-It was determined that $f_d = 300 \ Hz$ with $\zeta = 0.8$ satisfies these requirements.
-%Since the sampling frequency for the power converter control system is $3.333 \; kHz$, then $f_s/f_d$ satisfies the constraint in (\ref{eq:bandwidth}).
-
-\subsection{$RST$ Controller Synthesis}
-\label{synthesis}
-The voltage applied to the magnet by the voltage source and the relative current are both sampled at 10  kHz while the control loop is run $3$ times slower (i.e., $f_s = 3.333$ kHz and $T_s = 300 \  \mu$s, where $f_s$ and $T_s$ are denoted as the sampling frequency and sampling time of the control loop, respectively).
-Since the plant is stable, then a possible selection for the coprime factors is $N\jo = G\jo$ and $M\jo = 1$.
-For proper implementation within the proprietary power converter control software, it is required that all the open-loop poles remain on or within the unit circle, i.e.
-the controller should be marginally stable.
-This implies that the zeroes of $S(\rho)$ must lie on or within the unit circle.
-Since the reference current is close to a ramp signal, to achieve adequate performance, $S(z^{-1},\rho)$ must incorporate a double integrator: $S(z^{-1},\rho) = (1-z^{-1})^2S^\star(z^{-1},\rho)$.
-With the FRF measured by means of the PRBS excitation, the constraints for the convex optimization problem are formulated.
-With a minimum value of $m_d=0.5$ set for the modulus margin, the following optimization problem must be solved:
-\begin{equation} \label{eq:min_sim}
-\begin{aligned}
-& \underset{ \rho \in \mathbb{R}}{\text{minimize}}
-& & \gamma  \\
-& \text{subject to:} & & \Re\{\psi \jrok \} > x_r \jrok  \\
-& & & \Re\{\psi \jrok \} > m_d|S \jrok|  \\
-& & & \Re \{S^{\star}\jrok \}  > 0 \\
-& & & \mbox{for }k = 0,\ldots,\eta
-\end{aligned}
-\end{equation}
-where 
-\begin{equation*}
-\psi \jrok = S \jrok  + N\jok R \jrok  
-\end{equation*}
-and $x_r \jrok$ is defined as in (\ref{eq:rad_robust_design}).
-The first inequality in (\ref{eq:min_sim}) ensures that $\mathcal{H}_{\infty}$ nominal performance is achieved for the $RST$ structure whilst considering the frequency dependent uncertainties.
-The second inequality ensures that the modulus margin is at least $0.5$.
-With the additional low-frequency measurement at $\omega_0$,  there will be a total of $256$ frequency points ($\eta = 255$, $\omega_k \in (0,\pi f_s] \ \forall k$).
-
-\subsection{Optimization Results} 
-\label{sec:opt_results}
-The SDPT3 open-source optimization package was used in conjunction with Matlab to perform the bisection algorithm \cite{SDPT3}.
-The solution to the optimization problem in (\ref{eq:min_sim}) leads to a 9-th order stable controller that achieves the desired performance.
-The main parameters of the bisection algorithm are tabulated in Table.~{\ref{tab:gamma}.
-%Note that the orders of $R$ and $T$ are chosen to be equal.
-Their orders are larger than $S$ to ensure better tracking performance.
-All the zeros of $S^{\star}(z^{-1})$ lie inside the unit circle, and thus ensuring that the open-loop system remains marginally stable.
-
-\begin{table}
-\centering
-\caption{Parameters resulting from the bisection algorithm.}
-\label{tab:gamma}
-\begin{tabular}{c|cc}
-\textit{\textbf{Parameter}} & \textit{\textbf{Value}} & \textit{\textbf{Unit}} \\ \hline
-$\gamma_{\max}$              & $2.5$                    & -                      \\
-$\gamma_{\min}$              & $0$              & -                      \\
-$\gamma_{\text{tol}}$              & $10^{-6}$               & -                      \\
-$\gamma_{\text{opt}}$              & $1.202$                & -                      \\
-\textit{Optimization time}\footnotemark  & $61.3$                 & $s$                   
-\end{tabular}
-\end{table}
-\footnotetext{This optimization time was calculated based on a computer having the following hardware specifications: Intel-Core i7, 3.4 GHz CPU, 8 GB RAM.
-The optimization algorithm was run using MATLAB version 8.6.0.267246 (R2015b) on a Windows 7 platform (64-bit).}
-
-%The FRF for the desired and actualized closed-loop response is shown in Fig.~{\ref{fig:cl_freq}. 
-%The expected closed-loop bandwidth is approximately equal to the bandwidth chosen for the desired specifications (i.e., $170 \: Hz$). 
-The obtained output sensitivity function $| \mathcal{S}_1|$ is depicted in Fig.~{\ref{fig:sens_freq}}.
-It can be observed that this sensitivity function is indeed bounded by the modulus margin constraint and that a modulus margin of $0.5$ is obtained.
-%The calculated gain and phase margins are  $11.1 \ dB$ and $66.2^{\circ}$, respectively.
-
-%\begin{figure}
-%\centering
-%\includegraphics[width=\columnwidth]{pics_prbs/closed_loop.eps}
-%\caption{Comparison between the FRF's of the desired and expected closed-loop response.
-FRF of the desired closed-loop transfer function $\mathcal{T}_d(s)$ (solid-green line); FRF of the actual closed-loop response (solid-blue line).
-}
-%\label{fig:cl_freq}
-%\end{figure}
-
-\begin{figure}
-\centering
-\includegraphics[width=\columnwidth]{pics_prbs/sens_S0.eps}
-\caption{FRF of the output sensitivity function $\mathcal{S}_1$ (solid-blue line) and the bound for the modulus margin.}
-\label{fig:sens_freq}
-\end{figure}
-
-For the reference current applied to this system, the error between the reference and the output current is determined by shifting the reference current such that a minimum peak error is achieved; this will be shown in the next section.
-%A plot of the group delay (in units of $T_s$) is shown in Fig.~\ref{fig:track_delay}. 
-%For the reference current applied to this system, the track delay $\tau$ can be estimated as the DC value of the group delay (given by (\ref{eq:group_delay_theor})) , which is approximately $829.9 \: \mu s$ (or $\tau = 2.766$ $T_s$).
-The reference current is delayed by using (\ref{eq:del_filt_new}) in order to calculate the experimental error (which is shown in the next section).
-
-%\begin{figure}
-%\centering
-%\includegraphics[width=\columnwidth]{pics_prbs/group_delay.eps}
-%\caption{A frequency-domain plot of the calculated group delay (in units of the control loop sampling time $T_s$).
-For the current reference profile, the estimated delay (used for calculating the error) is the DC value of the group delay; this DC value is approximately equal to $10.126 \: [T_s]$.}
-%\label{fig:track_delay}
-%\end{figure}
-
-%\subsection{Experimental Validation - Frequency Domain}
-%The frequency response of the closed-loop system was measured by means of a dedicated experiment.
-The converter was programmed to produce sinusoidal currents at given frequencies with small amplitudes ($0.4 \: A_{peak}$); both the reference and measured current were recorded with custom software diagnostic tools.
-The amplitude and phase of both currents were estimated by means of a three-parameter sinefit \cite{1057}, \cite{MLM12}.
-%The main features of the diagnostics tools used for signal acquisition are: 
-%\begin{itemize}
-	%\item sampling frequency of $10 \: kHz$
-	%\item record length of $1.2 \: s$ irrespective of the frequency being probed
-%\end{itemize}
-%These features posed several limitations on the frequency range that could be probed:
-%\begin{itemize}
-	%\item \emph{high frequencies} are limited to $1$ $kHz$ by the need of having enough samples per period to properly estimate the amplitude and phase (at $1$ $kHz$, only $10000/1000 = 10$ samples are acquired for each period; furthermore, the first harmonics of $50$ $Hz$ have been discarded for this measurement in order to avoid residual ripple)
-	%\item \emph{low frequencies} are limited to about $1 \: Hz$ by the need of acquiring at least $1$ period to properly estimate both amplitude and phase
-%\end{itemize}
-%
-%The closed-loop frequency response and the group delay (numerically calculated from the measured phase by means of (\ref{eq:group_delay_theor})) are shown in Fig.~\ref{fig:closed_loop_meas} and Fig.~\ref{fig:group_delay_meas}, respectively.
-From Fig.~\ref{fig:closed_loop_meas}, it can be observed that the actual closed-loop frequency response closely matches that of the desired response.
-Additionally, the experimental error obtained from the average value of the measured group delay and the value obtained from the DC value of the group delay in the previous section ($\tau_g(0) = 1.0126 \: ms$) is only $0.85 \: \%$.
-%
-%\begin{figure}
-%\centering
-%\includegraphics[width=\columnwidth]{pics_prbs/Experimental_Bode.eps}
-%\caption{Measured frequency response of the closed-loop system (solid-blue) and the desired closed-loop system (solid-red).}
-%\label{fig:closed_loop_meas}
-%\end{figure}
-%
-%\begin{figure}
-%\centering
-%\includegraphics[width=\columnwidth]{pics_prbs/Experimental_Group_Delay.eps}
-%\caption{The measured group delay (solid-blue) along with the group delay calculated from $\mathcal{T}_d$ (solid-red).
-The track delay is estimated as the average value of the data points shown in solid-black.
-This value is determined to be $1.042 \: ms$.}
-%\label{fig:group_delay_meas}
-%\end{figure}
-
-\subsection{Experimental Validation and Comparison}
-The reference and measured currents were acquired for the profile required by a specific Q-STRIP magnet (Fig.~\ref{fig:QCF_ref}).
-As stated in section \ref{sec:weighting_filter}, the error is calculated with respect to a delayed reference input (i.e., $e(t) = r(t-\tau) - y(t)$).
-For comparison purposes,  the value of $\tau$ was found by shifting the reference profile such that the minimum peak error was achieved.
-A total of $10$ experiments were performed; the error for both the model-based and data-driven based designs (with the associated error-bars showing the minimum and maximum errors at each sampling instant) are shown in Fig.~\ref{fig:error}.
-It can be observed that both designs are comfortably within the $\pm 1000$ ppm fast-transient requirement and within the $\pm 100$ ppm steady-state requirement.
-Indeed, both controllers achieve $\pm 100$ ppm even during the fast-transients.
-However, the proposed method ensures that all of the design requirements are met while eliminating the iterative process of attaining robust performance from the model-based methodology.
-Therefore, the proposed data-driven method proves to be superior as it achieves all of the design objectives in a single attempt.
-
-%\begin{figure}
-%\centering
-%\includegraphics[width=\columnwidth]{pics_prbs/time_comp_2.eps}
-%\caption{Comparison between the reference current (solid-red line), the output current resulting from the model-based controller (solid-blue line) and the output current resulting with the proposed method (solid-green line).
-The accelerator beam is applied at the time indicated with the dashed-blue line ($0.4s$); the error must be calculated after this time.
-The error after the time indicated with the dashed-red line ($0.4054s$) must be within $\pm 100$ ppm.}
-%\label{fig:output}
-%\end{figure}
-
-\begin{figure}
-\centering
-\includegraphics[width=\columnwidth]{pics_prbs/error_comp_shift.eps}
-\caption{Comparison between the error resulting from the model-based design (solid-black line with red error-bars) and the error resulting with the proposed method (solid-black line with green error-bars).
-%The accelerator beam is applied at the time indicated with the dashed-blue line ($0.4s$); the error must be calculated after this time.
-The error after the time indicated with the dashed-red line ($0.4054s$) must be within $\pm 100$ ppm.}
-}
-\label{fig:error}
-\end{figure}
-
-\section{Conclusion}
-\label{sec:6}
-A new data-driven method for computing a robust controller that attains $\mathcal{H}_{\infty}$ performance has been presented.
-A frequency-domain approach has been used in order to avoid the problem of unmodeled dynamics associated with parametric models.
-The necessary and sufficient conditions for the existence of $RST$ controllers with multiple $\mathcal{H}_\infty$ performance have been developed in terms of a set of convex constraints.
-Constraints have been devised in order to design a controller which considers frequency dependent uncertainties, ensures a minimum value for the modulus margin, and to assure the controller stability.
-This method has been applied to a power converter control system which uses an $RST$ controller structure and is used for experimental purposes at CERN.
-In the case study presented in this paper, it has been shown that the proposed data-driven method offers an optimization-based systematic approach that leads to low-order $RST$ controllers meeting the challenging specification for particle trajectory tracking.
-With the proposed methodology, the process of obtaining a model and iteratively tuning the desired closed-loop bandwidth to attain the proper stability margins is eliminated whilst achieving the desired tracking performance.
-
-%For further research, it will be desired to determine the order of the controller polynomials that will produce the optimal tracking performance while attaining adequate disturbance rejection.
-
-%This paper has proposed a new method for computing multivariable SP controllers with $H_\infty$ performance.
-The method is based on a convex approximation of the $H_\infty$ robust performance criterion in the Nyquist diagram.
-This approximation relies on the choice of a desired open-loop transfer function $\vec{L}_D$ for the dead-time free model of the plant.
-With a linearly parameterized controller, one possesses the flexibility to design PI, PID, or higher order controllers for a system.
-For the industrial processes considered in this paper, the proposed method has been proven to be robust; $H_{\infty}$ performance was achieved for MIMO systems with both multiplicative and time delay uncertainties.
-Moreover, the solution to the optimization problem generates a controller such that a system becomes decoupled and simultaneously optimizes the single-loop performances of the SISO subsystems.
-
-%\appendix[]
-%\begin{table}[H]
-%\centering
-%\caption{Solution to the optimization problem in (\ref{eq:min_sim}); parameters reported with a reduced number of significant digits.}
-%\label{my-label}
-%\begin{tabular}{c|c|c}
-%$\rho_R$ & $\rho_S^{\star}$ & $\rho_T$ \\ \hline
-%$2.064$      & $1$              & $0.9025$      \\ \hline
-%$- 0.9093$      & $- 0.4093$              & $- 0.3494$      \\ \hline
-%$- 1.08$      & $- 1.014 $              & $- 0.004285$      \\ \hline
-%$0.4282$      & $0.05461$              & $- 0.335$      \\ \hline
-%$- 1.152$      & $- 0.08757$              & $0.01702$      \\ \hline
-%$0.5985$      & $0.1138$              & $- 0.1231$      \\ \hline
-%$0.06517$      & $0.3425$              & $0.08679$     \\ \hline
-%$0.1158$   &       -       & $- 0.06379$     
-%\end{tabular}
-%\end{table}
-
-\iffalse
-\section*{Acknowledgement}
-The authors of this paper would like to thank Louis de Mallac for his contribution to the experimental setup of the power converter control system and Quentin King (both with the TE department at CERN) for providing support for the controller implementation within the FGC software environment.
-\fi
-
-%\begin{IEEEbiographynophoto}
-%Author1 Biography
-%\end{IEEEbiographynophoto}
-%\smallskip{}
-%\begin{IEEEbiographynophoto}
-%Author2 Biography
-%\end{IEEEbiographynophoto}
-
-%\bibliography{/Users/anicolet/Google Drive/EPFL Research/Publications/linear}
 \bibliography{linear}
-
-\iffalse
-\vspace*{-2\baselineskip}
-
-\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{pics/bib_achille.eps}}]{Achille Nicoletti} was born in Quebec, Canada on June 20, 1983.
-He received both his B.Sc.
-in Physics and B.E.E degrees at Cleveland State University (USA) in 2011 (summa cum laude).
-He also received his M.Sc.
-in Electrical Engineering at the same university in 2012.
-During his studies in receiving his M.Sc.
-degree, he was recruited by Philips in Highland Heights, Ohio, where he was employed as an Electrical Design Engineer (II) and was responsible for designing the control system for the next generation computed tomography (CT) products.
-During this time at Philips, he received his Six Sigma Green Belt certification.
-In 2014, he decided to pursue a PhD in the field of control systems at the Swiss Federal Institute of Technology in Lausanne (EPFL), Switzerland.
-In the same year, he had been accepted to a doctoral fellowship program at CERN.
-His main research interests include robust data-driven control methods (frequency domain), and optimization in systems and control.
-\end{IEEEbiography}
-
-\vspace*{-2\baselineskip}
-
-\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{pics/bib_michele.eps}}]{Michele Martino}
-was born in Napoli, Italy, on July 23, 1975.
-He received the M.Sc.
-in Electronics Engineering (magna cum laude) and the Ph.D.
-in Electrical Engineering at the University of Napoli Federico II.
-PhD research was carried out at CERN on the high precision position survey of the Large Hadron Collider collimators.
-In 2004 he was with FIAT as control algorithm designer on Traction Control and then, in 2005, he joined I.N.F.N (Italian National Institute of Nuclear Physics) as fellow to work on the LHCb muon detector front end electronics test.
-Since June 2006 he is at CERN and in 2010 joined the Electrical Power Converter group to work on the high precision measurement and control of the power converters of CERN accelerators.
-His main research subjects are LVDT sensors characterization, high precision pulsed current and voltage measurements, digital control for power converters.
-\end{IEEEbiography}
-
-\vspace*{-2\baselineskip}
-
-\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{pics/bib_alireza.eps}}]{Alireza Karimi} received his B.
-Sc.
-and M.
-Sc.
-degrees in Electrical Engineering in 1987 and 1990 from Amir Kabir University (Tehran Polytechnic).
-After 3 years of industrial experience he joined Institut National Polytechnique de Grenoble (INPG) in France and received his DEA and Ph.
-D.
-degrees both on Automatic Control in 1994 and 1997, respectively.
-He was Assistant Professor at Electrical Engineering Department of Sharif University of Technology in Teheran from 1998 to 2000.
-He is currently Senior Scientist at the Automatic Laboratory of Swiss Federal Institute of Technology in Lausanne (EPFL), Switzerland.
-He was an Associate Editor of European Journal of Control from 2004 to 2013.
-His research interests include closed-loop identification, data-driven controller tuning approaches and robust control.
-\end{IEEEbiography}
-\fi
 \end{document}

### 2017-02-12 Dissertation/Latex/head/acknowledgements.tex
updated files

\chapter*{Acknowledgements}
\markboth{Acknowledgements}{Acknowledgements}
\addcontentsline{toc}{chapter}{Acknowledgements}

The writing and completion of this dissertation would not have been possible without the assistance, support, and guidance of the many special people in my life. Firstly, I would like to thank God for giving me the capability to contribute to the engineering world and hopefully assist the future civilizations in creating technologies for the good of mankind. Technology has been abused by the powers that be, and I hope that, someday, ethical values will be the priorities of our future leaders in order to sustain peace and harmony in this planet.

Secondly, I would like to thank my EPFL advisor, Dr. Alireza Karimi. 
I have learned many things from him since starting my Ph.D, and I thank him for accepting me into his program. His contributions and patience were key factors in the successful completion of this dissertation.
I would also like to thank my CERN supervisor, Dr. Michele Martino. 
He has been very helpful during my Ph.D studies, and I have enjoyed the numerous technical discussions I had with him; I always learned something from each discussion, and am very appreciative for that. 
Among my other CERN colleagues, I would like to also thank Miguel Cerqueira Bastos, Quentin King, Olivier Michele, Davide Aguglia, Todor Todorvic, Ivan Jovetic, Olivier Founier, and Louis De Mallac. 
The knowledge that I have acquired from Michele and my numerous colleagues will be something that I will foster and cherish for the rest of my life.

In addition to my work colleagues, I would also like to thank Zlatko Emedji and Jose Manuel De Paco Soto for being good friends and providing the emotional support I needed. Also a thank you to Predrag Milosavljevic and Christoph Kammer for being good competitors at Foosball during my time at EPFL. Additionally, I would like to thank Michael Davis, Hugo Lebreton, Miguel Hermo Serans, and Timm Faulwasser for our random technical and non-technical discussions.

Finally, I would like to thank my family for their support during this endeavour. 
My sisters Carmen, Marie, and Elizabeth have been great inspirations to me; they shaped me into the person I am today and can honestly say that without them, I may not have been so successful. 
To my mother, I thank you for everything you have done for me during my 33 years on this planet. 
I will always carry your love in my heart. 
And finally, to my father, I wish you could have still been with us to witness this moment in my life. 
I know that you would have been proud of me, and am very grateful for all of the sacrifices you made for the family.

\bigskip

\noindent\textit{Geneva, 12 March 2017}
\hfill A.~N.

### 2017-02-12 Dissertation/Latex/head/settings_epfl_template.tex
updated files

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%		Thesis Settings
%
%		EDOC Template
%		2011
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[a4paper,11pt,fleqn]{book}

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[french,english]{babel}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% EDOC THESIS TEMPLATE: Variant 1.0 -> Latin modern, large text width&height
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\usepackage{lmodern}
%\usepackage[a4paper,top=22mm,bottom=28mm,inner=35mm,outer=25mm]{geometry}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% EDOC THESIS TEMPLATE: Variant 2.0 -> Utopia, Gabarrit A (lighter pages)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{fourier} % Utopia font-typesetting including mathematical formula compatible with newer TeX-Distributions (>2010)
%\usepackage{utopia} % on older systems -> use this package instead of fourier in combination with mathdesign for better looking results
%\usepackage[adobe-utopia]{mathdesign}
\setlength{\textwidth}{146.8mm} % = 210mm - 37mm - 26.2mm
\setlength{\oddsidemargin}{11.6mm} % 37mm - 1in (from hoffset)
\setlength{\evensidemargin}{0.8mm} % = 26.2mm - 1in (from hoffset)
\setlength{\topmargin}{-2.2mm} % = 0mm -1in + 23.2mm 
\setlength{\textheight}{221.9mm} % = 297mm -29.5mm -31.6mm - 14mm (12 to accomodate footline with pagenumber)
\setlength{\headheight}{14pt}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\setlength{\parindent}{0pt}

\usepackage{setspace} % increase interline spacing slightly
\setstretch{1.1}

\makeatletter
\setlength{\@fptop}{0pt}  % for aligning all floating figures/tables etc... to the top margin
\makeatother

\usepackage{graphicx,xcolor}
\graphicspath{{images/}}

\usepackage{subfig}
\usepackage{booktabs}
\usepackage{lipsum}
\usepackage{microtype}
\usepackage{url}
\usepackage[final]{pdfpages}

\usepackage{fancyhdr}
\renewcommand{\sectionmark}[1]{\markright{\thesection\ #1}}
\pagestyle{fancy}
	\fancyhf{}
	\renewcommand{\headrulewidth}{0.4pt}
	\renewcommand{\footrulewidth}{0pt}
	\fancyhead[OR]{\bfseries \nouppercase{\rightmark}}
	\fancyhead[EL]{\bfseries \nouppercase{\leftmark}}
	\fancyfoot[EL,OR]{\thepage}
\fancypagestyle{plain}{
	\fancyhf{}
	\renewcommand{\headrulewidth}{0pt}
	\renewcommand{\footrulewidth}{0pt}
	\fancyfoot[EL,OR]{\thepage}}
\fancypagestyle{addpagenumbersforpdfimports}{
	\fancyhead{}
	\renewcommand{\headrulewidth}{0pt}
	\fancyfoot{}
	\fancyfoot[RO,LE]{\thepage}
}

\usepackage{listings}
\lstset{language=[LaTeX]Tex,tabsize=4, basicstyle=\scriptsize\ttfamily, showstringspaces=false, numbers=left, numberstyle=\tiny, numbersep=10pt, breaklines=true, breakautoindent=true, breakindent=10pt}

\usepackage{hyperref}
\hypersetup{pdfborder={0 0 0},
	colorlinks=true,
	linkcolor=black,
	citecolor=black,
	urlcolor=black}
\urlstyle{same}

\makeatletter
\def\cleardoublepage{\clearpage\if@twoside \ifodd\c@page\else
    \hbox{}
    \thispagestyle{empty}
    \newpage
    \if@twocolumn\hbox{}\newpage\fi\fi\fi}
\makeatother \clearpage{\pagestyle{plain}\cleardoublepage}

%%%%% CHAPTER HEADER %%%%
\usepackage{color}
\usepackage{tikz}
\usepackage[explicit]{titlesec}
\newcommand*\chapterlabel{}
%\renewcommand{\thechapter}{\Roman{chapter}}
\titleformat{\chapter}[display]  % type (section,chapter,etc...) to vary,  shape (eg display-type)
	{\normalfont\bfseries\Huge} % format of the chapter
	{\gdef\chapterlabel{\thechapter\ }}     % the label 
 	{0pt} % separation between label and chapter-title
 	  {\begin{tikzpicture}[remember picture,overlay]
    \node[yshift=-8cm] at (current page.north west)
      {\begin{tikzpicture}[remember picture, overlay]
        \draw[fill=black] (0,0) rectangle(35.5mm,15mm);
        \node[anchor=north east,yshift=-7.2cm,xshift=34mm,minimum height=30mm,inner sep=0mm] at (current page.north west)
        {\parbox[top][30mm][t]{15mm}{\raggedleft $\phantom{\textrm{l}}$\color{white}\chapterlabel}};  %the black l is just to get better base-line alingement
        \node[anchor=north west,yshift=-7.2cm,xshift=37mm,text width=\textwidth,minimum height=30mm,inner sep=0mm] at (current page.north west)
              {\parbox[top][30mm][t]{\textwidth}{\color{black}#1}};
       \end{tikzpicture}
      };
   \end{tikzpicture}
   \gdef\chapterlabel{}
  } % code before the title body

\titlespacing*{\chapter}{0pt}{50pt}{30pt}
\titlespacing*{\section}{0pt}{13.2pt}{*0}  % 13.2pt is line spacing for a text with 11pt font size
\titlespacing*{\subsection}{0pt}{13.2pt}{*0}
\titlespacing*{\subsubsection}{0pt}{13.2pt}{*0}

\newcounter{myparts}
\newcommand*\partlabel{}
\titleformat{\part}[display]  % type (section,chapter,etc...) to vary,  shape (eg display-type)
	{\normalfont\bfseries\Huge} % format of the part
	{\gdef\partlabel{\thepart\ }}     % the label 
 	{0pt} % separation between label and part-title
 	  {\setlength{\unitlength}{20mm}
	  \addtocounter{myparts}{1}
	  \begin{tikzpicture}[remember picture,overlay]
    \node[anchor=north west,xshift=-65mm,yshift=-6.9cm-\value{myparts}*20mm] at (current page.north east) % for unknown reasons: 3mm missing -> 65 instead of 62
      {\begin{tikzpicture}[remember picture, overlay]
        \draw[fill=black] (0,0) rectangle(62mm,20mm);   % -\value{myparts}\unitlength
        \node[anchor=north west,yshift=-6.1cm-\value{myparts}*20mm,xshift=-60.5mm,minimum height=30mm,inner sep=0mm] at (current page.north east)
        {\parbox[top][30mm][t]{55mm}{\raggedright \color{white}Part \partlabel $\phantom{\textrm{l}}$}};  %the phantom l is just to get better base-line alingement
        \node[anchor=north east,yshift=-6.1cm-\value{myparts}*20mm,xshift=-63.5mm,text width=\textwidth,minimum height=30mm,inner sep=0mm] at (current page.north east)
              {\parbox[top][30mm][t]{\textwidth}{\raggedleft \color{black}#1}};
       \end{tikzpicture}
      };
   \end{tikzpicture}
   \gdef\partlabel{}
  } % code before the title body

\usepackage{amsmath}
% Fix the problem with delimiter size caused by fourier and amsmath packages.
\makeatletter
\def\resetMathstrut@{%
  \setbox\z@\hbox{%
    \mathchardef\@tempa\mathcode`\(\relax
      \def\@tempb##1"##2##3{\the\textfont"##3\char"}%
      \expandafter\@tempb\meaning\@tempa \relax
  }%
  \ht\Mathstrutbox@1.2\ht\z@ \dp\Mathstrutbox@1.2\dp\z@
}
\makeatother

### 2017-02-12 Dissertation/Latex/head/acknowledgements.tex
updated acknowledgement

@@
 Firstly, I would like to thank God for giving me the capability to contribute to the engineering world and hopefully assist the future civilizations in creating technologies for the good of mankind.
-Technology has been abused by the powers that be, and I hope that, someday, ethical values will be the priorities of our future leaders in order to sustain peace and harmony in this planet.
+I hope that ethical values will be exercised and that the technologies arising from the new frontiers of science are used in conscientious manners.
 

### 2017-02-13 Papers/Nonlinear Optimization/Latex/Draft/Draft.tex
Update Draft.tex
updated file

@@
 \section{Conclusion} \label{sec:conclusion}
-Robust performance can be accomplished by considering the $\mathcal{H}_{\infty}$ control problem.
-By presetting a frequency grid, an optimization problem can be formulated to minimize the upper-bound of the robust performance condition and solve a finite amount of constraints in the frequency-domain.
-In this paper, a Non-Death-Penalty approach has been implemented to solve an unconstrained $\mathcal{H}_{\infty}$ problem; the solution to this problem was obtained by realizing a PSO algorithm.
-From the examples considered in this paper, it is evident that the solutions obtained from the PSO algorithm generate favorable closed-loop responses (with respect to the other methods considered in this paper).
-In terms of performance, the convex optimization algorithm produces a solution that is comparable to that of the PSO.
-From the simulation examples, it can be deduced that the solution obtained from the convex optimization algorithm is a good approximation to the solution obtained from the original problem.
-For further research, it will be desired to investigate how the solution obtained from the PSO algorithm with the $\epsilon$-level comparisons correlates with the solutions obtained in this work.
+A frequency-domain approach has been implemented in order to design robust controllers that achieve $\mathcal{H}_{\infty}$ performance.
+With the proposed method, it has been shown that the solution to the $\mathcal{H}_{\infty}$ problem converges monotonically to the optimal solution with the order of the basis function $F$ approaches infinity.
+This solution is obtained by considering an optimization problem which guarantees the stability of the closed-loop system.
+The optimization problem is converted from an SIP problem to an SDP problem by gridding the frequency vector over a finite interval.
+The simulation examples show that the proposed approach achieves the optimal performance for a given controller order without any conservatism.
+For future work, it will be desired to implement this method for multi-input-multi-output (MIMO) systems and systems with controllers that possess multiple degrees-of-freedom.
 

### 2017-02-13 Papers/Nonlinear Optimization/Latex/Draft/Draft.tex
updated file

@@
 
-\subsection{Example 1: Robust Performance}
+\subsection{Example 1: Convergence to Optimal Solution}
+Consider the following discrete time SISO system:
+\begin{equation}
+G(z) = \frac{z-0.186}{z^3 - 1.116z^2 + 0.465z-0.093}
+\end{equation}
+Note that since this system is stable, then the coprimes can be selected as $N(z) = G(z)$ and $M(z) = 1$.
+The control objective of this case study is to design a controller (with integral action) that minimizes the nominal performance condition $\|W_1S \|_{\infty}$ (i.e., minimize $\gamma$ in $\|W_1S \|_{\infty} < \gamma$), where
+\begin{equation}
+W_1(z) = \frac{0.4902(z^2-1.0431z+0.3263)}{(z-1)(z-0.282)}
+\end{equation}
+For this controller synthesis, we can simply select the basis functions in (\ref{eq:Laguerre_z}) to be FIR filters (i.e., $\rho_d = 0$) for $X(\bm{\rho})$ and $Y(\bm{\rho})$.
+In order to avoid unboundedness of $W_1$ at $\omega = 0$ and have integral action, the basis functions for $Y(\bm{\rho})$ will be multiplied by $(z-1)/z$.
+It will be shown that as the order of $F(\bm{\rho})$ increases, the optimal solution $\gamma$ will decrease monotonically and converge to the optimal solution.
+
+\subsubsection{Simulation Results}
+The \texttt{mixsyn} command from \texttt{MATLAB}'s Robust Control toolbox yields an optimal value of $\gamma^* = 0.5522$ with a fifth-order controller.
+Therefore, according to Theorem.\ref{thm_1}, a fifth-order controller was also implemented with the proposed method (i.e., to ensure convergence to the optimal solution).
+Additionally, two simulations were performed with the proposed method; one simulation with $F(\bm{\rho})$ selected such that the basis function is an FIR filter (i.e., Laguerre basis functions in (\ref{eq:Laguerre_z}) with $\rho_d = 0$) and one simulation with $F(\bm{\rho})$ selected such that $\rho_d$ is a decision variable.
+Let $F_{n_f}(\bm{\rho})$ denote the function $F(\bm{\rho})$ of $n_f$-th order and $\gamma_{n_f}$ denote the optimal solution of the nominal performance condition for a given order of $F_{n_f}(\bm{\rho})$.
+Figure.~\ref{fig:ex1_1} shows the convergence of the optimal solution $\gamma_{n_f}$ as a function $n_f$; it can be observed that with the proposed frequency-domain method, the optimal solution to the $\mathcal{H}_{\infty}$ problem converges monotonically as the order of $F(\bm{\rho})$ increases.
+Additionally, when the parameter $\rho_d$ is a decision variable, the convergence time is reduced.
+
+\begin{figure}
+\centering
+\includegraphics[width=\columnwidth]{../pics/gamma_convergence_F_var.eps}
+\caption{Optimal solution obtained from \texttt{mixsyn} command (straight-red line); $\gamma_{n_f}$ for $F(\bm{\rho})$ as an FIR filter ({\color{red}{- -$\square$- -}});  $\gamma_{n_f}$ for $F(\bm{\rho})$ with $\rho_d$ as a decision variable ({\color{red}{- -$*$- -}}); the value of $\rho_d$ when used as a decision variable  ({\color{blue}{- -$\circ$- -}}) }
+\label{fig:ex1_1}
+\end{figure}
+
+Note that the controller order was fixed in this case study, since it was known (from the \texttt{mixsyn} command) that the optimal controller order was $5$.
+However, suppose that the order and structure of the optimal controller $K = XY^{-1}$ was unknown.
+In the case, one can simply fix the structure of the basis function of $F(\bm{\rho})$ with a large order and solve the optimization problem as the order of the controller is varied.
+The lowest order controller that achieves convergence can then be selected as the optimal controller.
+Figure.~\ref{fig:ex1_2} shows the convergence of the optimal solution then the order of the basis function $F(\bm{\rho})$ is fixed to $20$ (as an FIR filter) and the controller order is varied; it can be observed that convergence to the optimal solution does indeed occur with a $5$-th order controller.
+
+\begin{figure}
+\centering
+\includegraphics[width=\columnwidth]{../pics/gamma_convergence_F_var.eps}
+\caption{Optimal solution obtained from \texttt{mixsyn} command (straight-red line); $\gamma_{n_f}$ for $F(\bm{\rho})$ as an FIR filter ({\color{red}{- -$\square$- -}});  $\gamma_{n_f}$ for $F(\bm{\rho})$ with $\rho_d$ as a decision variable ({\color{red}{- -$*$- -}}); the value of $\rho_d$ when used as a decision variable  ({\color{blue}{- -$\circ$- -}}) }
+\label{fig:ex1_2}
+\end{figure}
+
+\subsection{Example 2: Robust Performance}
 Consider the unstable non-minimum phase system analyzed in \cite{Zhe10}  and \cite{Ho03} (which is subject to multiplicative uncertainty):
@@
 
-Table.\ref{tab:ex1_1} shows the values of the optimal solutions obtained from various methods.
+Table.\ref{tab:ex2_1} shows the values of the optimal solutions obtained from various methods.
 The convex problem in (\ref{eq:convex_con}) was solved with $\rho_g = \rho_c^{\prime} = 1$.
@@
 However, with a simple PID controller, the proposed method yields the best performance for the \textit{true} robust performance criteria in (\ref{eq:inf_norm}).
-The optimal value for the the decision variable of $F(\bm{\rho})$ was obtained as $\rho_o^{\star} = 0.933$, while the optimal values of the remaining decision variables (for both the convex and proposed optimization methods) are shown in Table.\ref{tab:ex1_2}.
+The optimal value for the the decision variable of $F(\bm{\rho})$ was obtained as $\rho_o^{\star} = 0.933$, while the optimal values of the remaining decision variables (for both the convex and proposed optimization methods) are shown in Table.\ref{tab:ex2_2}.
 
@@
 \caption{My caption}
-\label{tab:ex1_1}
+\label{tab:ex2_1}
 \begin{tabular}{c|c|c}
@@
 \caption{My caption}
-\label{tab:ex1_2}
+\label{tab:ex2_2}
 \begin{tabular}{c|c|cccc}
@@
 \end{table}
-
-\subsection{Example 2: Convergence to Optimal Solution}
-Consider the following discrete time SISO system:
-\begin{equation}
-G(z) = \frac{z-0.186}{z^3 - 1.116z^2 + 0.465z-0.093}
-\end{equation}
-Note that since this system is stable, then the coprimes can be selected as $N(z) = G(z)$ and $M(z) = 1$.
-The control objective of this case study is to design a controller (with integral action) that minimizes the nominal performance condition $\|W_1S \|_{\infty}$ (i.e., minimize $\gamma$ in $\|W_1S \|_{\infty} < \gamma$), where
-\begin{equation}
-W_1(z) = \frac{0.4902(z^2-1.0431z+0.3263)}{(z-1)(z-0.282)}
-\end{equation}
-For this controller synthesis, we can simply select the basis functions in (\ref{eq:Laguerre_z}) to be FIR filters (i.e., $\rho_d = 0$) for $X(\bm{\rho})$ and $Y(\bm{\rho})$.
-In order to avoid unboundedness of $W_1$ at $\omega = 0$ and have integral action, the basis functions for $Y(\bm{\rho})$ will be multiplied by $(z-1)/z$.
-It will be shown that as the order of $F(\bm{\rho})$ increases, the optimal solution $\gamma$ will decrease monotonically and converge to the optimal solution.
-
-\subsubsection{Simulation Results}
-The \texttt{mixsyn} command from \texttt{MATLAB}'s Robust Control toolbox yields an optimal value of $\gamma^* = 0.5522$ with a fifth-order controller.
-Therefore, according to Theorem.\ref{thm_1}, a fifth-order controller was also implemented with the proposed method (i.e., to ensure convergence to the optimal solution).
-Additionally, two simulations were performed with the proposed method; one simulation with $F(\bm{\rho})$ selected such that the basis function is an FIR filter (i.e., Laguerre basis functions in (\ref{eq:Laguerre_z}) with $\rho_d = 0$) and one simulation with $F(\bm{\rho})$ selected such that $\rho_d$ is a decision variable.
-Let $F_{n_f}(\bm{\rho})$ denote the function $F(\bm{\rho})$ of $n_f$-th order and $\gamma_{n_f}$ denote the optimal solution of the nominal performance condition for a given order of $F_{n_f}(\bm{\rho})$.
-Figure.~\ref{fig:ex2} shows the convergence of the optimal solution $\gamma_{n_f}$ as a function $n_f$; it can be observed that with the proposed frequency-domain method, the optimal solution to the $\mathcal{H}_{\infty}$ problem converges monotonically as the order of $F(\bm{\rho})$ increases.
-Additionally, when the parameter $\rho_d$ is a decision variable, the convergence time is reduced.
-
-\begin{figure}
-\centering
-\includegraphics[width=\columnwidth]{../pics/gamma_convergence.eps}
-\caption{Optimal solution obtained from \texttt{mixsyn} command (straight-red line); $\gamma_{n_f}$ for $F(\rho)$ as an FIR filter ({\color{red}{- -$\square$- -}});  $\gamma_{n_f}$ for $F(\rho)$ with $\rho_d$ as a decision variable ({\color{red}{- -$*$- -}}); the value of $\rho_d$ when used as a decision variable  ({\color{blue}{- -$\circ$- -}}) }
-\label{fig:ex2}
-\end{figure}
 

### 2017-02-13 Papers/Nonlinear Optimization/Latex/Draft/Draft.tex
updated files

@@
 
-\author{Achille Nicoletti$^{1}$, and Alireza Karimi$^{1}$
-\thanks{$^{1}$A. Nicoletti and A. Karimi are with the Automatic Control Laboratory at Ecole Polytechnique F\'ed\'erale de Lausanne (EPFL), Switzerland.
+\author{Achille Nicoletti and Alireza Karimi
+\thanks{The authors A. Nicoletti and A. Karimi are with the Automatic Control Laboratory at Ecole Polytechnique F\'ed\'erale de Lausanne (EPFL), Switzerland.
        Corresponding author: Alireza Karimi: {\tt\small alireza.karimi@epfl.ch}}
@@
 Note that since this system is stable, then the coprimes can be selected as $N(z) = G(z)$ and $M(z) = 1$. 
+\begin{remark*}
+Discrete-time systems can also be considered since the proposed method uses the FRF of a system for the controller synthesis.
+The FRF between continuous-time and discrete-time systems are nearly identical when the Shannon sampling condition is met.
+\end{remark*}
 The control objective of this case study is to design a controller (with integral action) that minimizes the nominal performance condition $\|W_1S \|_{\infty}$ (i.e., minimize $\gamma$ in $\|W_1S \|_{\infty} < \gamma$), where
@@
 Additionally, two simulations were performed with the proposed method; one simulation with $F(\bm{\rho})$ selected such that the basis function is an FIR filter (i.e., Laguerre basis functions in (\ref{eq:Laguerre_z}) with $\rho_d = 0$) and one simulation with $F(\bm{\rho})$ selected such that $\rho_d$ is a decision variable.
-Let $F_{n_f}(\bm{\rho})$ denote the function $F(\bm{\rho})$ of $n_f$-th order and $\gamma_{n_f}$ denote the optimal solution of the nominal performance condition for a given order of $F_{n_f}(\bm{\rho})$.
+Let $\gamma_{n_f}$ denote the optimal solution of the nominal performance condition for a given $n_f$-th order of $F(\bm{\rho})$.
 Figure.~\ref{fig:ex1_1} shows the convergence of the optimal solution $\gamma_{n_f}$ as a function $n_f$; it can be observed that with the proposed frequency-domain method, the optimal solution to the $\mathcal{H}_{\infty}$ problem converges monotonically as the order of $F(\bm{\rho})$ increases.
@@
 \includegraphics[width=\columnwidth]{../pics/gamma_convergence_F_var.eps}
-\caption{Optimal solution obtained from \texttt{mixsyn} command (straight-red line); $\gamma_{n_f}$ for $F(\bm{\rho})$ as an FIR filter ({\color{red}{- -$\square$- -}});  $\gamma_{n_f}$ for $F(\bm{\rho})$ with $\rho_d$ as a decision variable ({\color{red}{- -$*$- -}}); the value of $\rho_d$ when used as a decision variable  ({\color{blue}{- -$\circ$- -}}) }
+\caption{Optimal solution obtained from \texttt{mixsyn} command (straight-red line); $\gamma_{n_f}$ for $F(\bm{\rho})$ as an FIR filter ({\color{red}{- -$\square$- -}});  $\gamma_{n_f}$ for $F(\bm{\rho})$ with $\rho_d$ as a decision variable ({\color{red}{- -$*$- -}}); the value of $\rho_d$ when used as a decision variable  ({\color{blue}{- -$\circ$- -}}).
+$n_f = 0$ signifies the solution to the problem when $F(\bm{\rho})=1$.}
 \label{fig:ex1_1}
@@
 However, suppose that the order and structure of the optimal controller $K = XY^{-1}$ was unknown.
-In the case, one can simply fix the structure of the basis function of $F(\bm{\rho})$ with a large order and solve the optimization problem as the order of the controller is varied.
+In this case, one can simply fix the structure of the basis function of $F(\bm{\rho})$ with a large order and solve the optimization problem as the order of the controller is varied.
 The lowest order controller that achieves convergence can then be selected as the optimal controller.
-Figure.~\ref{fig:ex1_2} shows the convergence of the optimal solution then the order of the basis function $F(\bm{\rho})$ is fixed to $20$ (as an FIR filter) and the controller order is varied; it can be observed that convergence to the optimal solution does indeed occur with a $5$-th order controller.
+Let $n_k$ denote the order of the controller $K(\bm{\rho})$ and $\gamma_{n_k}$ the optimal solution to the $\mathcal{H}_{\infty}$ problem for a given $n_k$.
+Figure.~\ref{fig:ex1_2} shows the convergence to the optimal solution when the order of the basis function $F(\bm{\rho})$ is fixed to $20$ (with $F(\bm{\rho})$ selected as an FIR filter) and the controller order $n_k$ is varied; it can be observed that convergence to the optimal solution does indeed occur with a 5\textsuperscript{th}  order controller.
+In fact, according to Fig.~\ref{fig:ex1_2}, a 3\textsuperscript{rd} order controller generates the performance similar to that of the 5\textsuperscript{th} order optimal controller that \texttt{MATLAB}'s Robust Control toolbox provides.
 
@@
 \centering
-\includegraphics[width=\columnwidth]{../pics/gamma_convergence_F_var.eps}
-\caption{Optimal solution obtained from \texttt{mixsyn} command (straight-red line); $\gamma_{n_f}$ for $F(\bm{\rho})$ as an FIR filter ({\color{red}{- -$\square$- -}});  $\gamma_{n_f}$ for $F(\bm{\rho})$ with $\rho_d$ as a decision variable ({\color{red}{- -$*$- -}}); the value of $\rho_d$ when used as a decision variable  ({\color{blue}{- -$\circ$- -}}) }
+\includegraphics[width=\columnwidth]{../pics/gamma_convergence_F_fixed.eps}
+\caption{Optimal solution obtained from \texttt{mixsyn} command (straight-blue line); $\gamma_{n_k}$ for $F(\bm{\rho})$ selected as a 20\textsuperscript{th} order FIR filter ({\color{blue}{- -X- -}}).}
 \label{fig:ex1_2}
@@
 
-Table.\ref{tab:ex2_1} shows the values of the optimal solutions obtained from various methods.
+Table.\ref{tab:ex2_1} shows the values of the optimal solutions obtained from various methods\footnote{The method proposed in \cite{Zhe10} produced a set of PID controllers.
+A random solution from the set was used for comparative purposes.}.
 The convex problem in (\ref{eq:convex_con}) was solved with $\rho_g = \rho_c^{\prime} = 1$.
@@
 \centering
-\caption{My caption}
+\caption{Comparison of optimal solutions to the $\mathcal{H}_\infty$ problem (robust performance vs. mixed sensitivity)}
 \label{tab:ex2_1}
@@
                                                                                                           & $\| |W_1S| + |W_2T| \|_{\infty}$ & $\left\| \begin{matrix} W_1S \\[2pt] W_2T \end{matrix} \right\|_{\infty} $ \\ \hline
+\begin{tabular}[c]{@{}c@{}}Convex method (\ref{eq:convex_con})\end{tabular}  & $1.327$                          & $1.223$  \\ \hline
+\begin{tabular}[c]{@{}c@{}}$\mathcal{H}_\infty$ parametric\\ approach in \cite{Zhe10}\end{tabular}                                                                                     & $1.205$                          & $0.923$                                                     \\ \hline
 \texttt{MATLAB\textsuperscript{\tiny{\textregistered}}} (\texttt{mixsyn})                                                                           & $1.111$                          & $0.789$                                                     \\ \hline
-\begin{tabular}[c]{@{}c@{}}$\mathcal{H}_\infty$ parametric\\ approach in \cite{Kar13}\end{tabular}                                                                                     & $1.205$                          & $0.923$                                                     \\ \hline
-\begin{tabular}[c]{@{}c@{}}Proposed method\end{tabular}  & $1.019$                          & $0.966$ \\ \hline
-\begin{tabular}[c]{@{}c@{}}Convex method (\ref{eq:convex_con})\end{tabular}  & $1.327$                          & $1.223$
+\begin{tabular}[c]{@{}c@{}}Proposed method (\ref{eq:opt_true})\end{tabular}  & $1.019$                          & $0.966$
 \end{tabular}
@@
 \centering
-\caption{My caption}
+\caption{Optimal values of PID controllers obtained from the convex and nonlinear optimization problems}
 \label{tab:ex2_2}
@@
 \includegraphics[width=\columnwidth]{../pics/step_multi_optimal.eps}
-\caption{Closed-loop step responses with the PID controller parameters asserted in Table.~2 (with $\tau = \tau_n$).
-Response associated with the proposed PSO algorithm (solid-blue); response associated with the convex optimization algorithm (solid-green); response associated with the robust stability method in \cite{EW09} (solid-red).}
+\caption{Step response of $S(s)$ for all seven models using the proposed optimization algorithm.}
 \label{fig:ex3_2}

### 2017-02-14 Dissertation/Latex/head/titlepage.tex
updated files

\begin{titlepage}
\begin{center}
%\large
\sffamily

\null\vspace{2cm}
%{\huge A Data-Driven Robust Controller Design Method\\[12pt] Using Frequency-Domain Data} \\[24pt] 
{\huge Robust Controller Design with $\hinf$ Performance: \\[12pt] A Data-Driven Frequency-Domain Approach} \\[24pt] 
\textcolor{gray}{\small{THIS IS A TEMPORARY TITLE PAGE \\ It will be replaced for the final print by a version \\ provided by the service academique.}}

\vfill

\begin{tabular} {cc}
\parbox{0.3\textwidth}{\includegraphics[width=4cm]{images/epfl}}
&
\parbox{0.7\textwidth}{%
	Thèse n. 1234 2011\\
	présenté le 15 Octobre 2017\\
	à la Faculté des Sciences et Techniques de L'ingénieur\\
	laboratoire d'automatique \\
	programme doctoral en Génie Electrique\\
%
%	ÉCOLE POLYTECHNIQUE FÉDÉRALE DE LAUSANNE\\
	École Polytechnique Fédérale de Lausanne\\[6pt]
	pour l'obtention du grade de Docteur ès Sciences\\
	par\\ [4pt]
	\null \hspace{3em} Achille Nicoletti\\[9pt]
%
\small
acceptée sur proposition du jury:\\[4pt]
%
    Colin Jones, président du jury\\
    MER Alireza Karimi, directeur de thèse\\
    Michele Martino, co-directeur de thèse\\
    Dominique Bonvin, rapporteur\\
    Quentin King, rapporteur\\
    Davide Aguglia, rapporteur\\[12pt]
%
Lausanne, EPFL, 2017}
\end{tabular}
\end{center}
\vspace{2cm}
\end{titlepage}

### 2017-02-14 Papers/Loop Shaping Voltage Loop (CERN)/Latex/Draft/Draft.tex
updated files

@@
 \usepackage{mathrsfs}
-%\usepackage{amsthm}
+
+\let\proof\relax
+\let\endproof\relax
+\usepackage{amsthm}
+
 \usepackage{epstopdf}
@@
 \newtheorem{lemma}{Lemma}
+\newtheorem*{remark}{Remark}
 \newtheorem{definition}{Definition}
+
 \newcommand{\jo}{(j\omega)}
@@
 
-\title{A Data-Driven Loop-Shaping Approach to Design Controllers for Power Converters} 
+\title{A Data-Driven Loop-Shaping Approach to Design Controllers for Power Converters via Convex Optimization} 
 % Title, preferably not more than 10 words.
@@
 \end{figure}
-$G_0(s)$ represents the TF from $v_i$ to $v_0$ in Fig.~\ref{fig:circuit}; $H(s)$ represents the TF from $v_0$ to $i_c$; $P_1(s)$ and $P_2(s)$ are sensors (i.e., low-pass filters); $k_i$ and $k_u$ are the control variable gains; $T_\alpha \: [s]$ is an actuation delay; and $C(s)$ is a PI controller (i.e., $C(s) = k_{p_1} + s^{-1}k_{p_2}$).
+$G_0(s)$ represents the TF from $v_i$ to $v_0$ in Fig.~\ref{fig:circuit}; $H(s)$ represents the TF from $v_0$ to $i_c$; $P_1(s)$ and $P_2(s)$ are sensors (i.e., low-pass filters); $k_i$ and $k_u$ are the control variable gains; $\tau \: [s]$ is an actuation delay; and $C(s)$ is a PI controller (i.e., $C(s) = k_{p_1} + s^{-1}k_{p_2}$).
 From this framework, it can be observed that the inner feedback loops are reminiscent of a state-feedback control architecture while the system (as a whole) is a common unity feedback structure with feedforward action.
@@
 H_1(s,k) &:= k_iP_1(s)H(s);  &H_2(s,k) &:= k_uP_2(s) \\
-G_d(s) &:= G_0(s)e^{-sT_\alpha}; &C_m(s,k) &:= k_{m_1}+s^{-1}k_{m_2}\\ 
+G_d(s) &:= G_0(s)e^{-s\tau}; &C_m(s,k) &:= k_{m_1}+s^{-1}k_{m_2}\\ 
 \end{aligned}
@@
 
-{\bf Remark:} 
+\begin{remark}
 \textit{Note that the choice of the initializing gains in $k_0$ may affect the stability of the closed-loop system (for either the optimization problems concerning the $\mathcal{H}_\infty$ or $\mathcal{H}_2$ norms).
@@
 Additionally, note that these optimization problems are considering the gains for $C_m(k)$; however, once an optimal solution is obtained for the gains in $k$, then the definitions in (\ref{eq:new_var}) can be used to revert back to the original gains (i.e., $k_{p_1}$ and $k_{p_2}$.)}
+\end{remark}
 
@@
 \begin{definition}
-Let wno$\{ A(s)\}$ refer to the winding number; in the counterclockwise sense, wno$\{ A(s)\}$ represents the image of $A(s)$ around the origin when $s$ traverses the Nyquist contour (with small detours around the poles of $A(s)$ on the imaginary axis).
+Let \emph{wno}$\{ A(s)\}$ refer to the winding number; in the counterclockwise sense, \emph{wno}$\{ A(s)\}$ represents the image of $A(s)$ around the origin when $s$ traverses the Nyquist contour (with small detours around the poles of $A(s)$ on the imaginary axis).
 Then the following properties hold:
 \begin{align}
-\text{wno}\bigl\{ A_1(s)A_2(s) \bigr\} &= \text{wno}\bigl\{ A_1(s) \bigr\} + \text{wno}\bigl\{ A_2(s) \bigr\}  \label{eq:wno_add}\\ 
-\text{wno}\bigl\{ A(s)\bigr\} &= -\text{wno}\bigl\{ A^{\star}(s)\bigr\} \label{eq:wno_conj} \\ 
-\text{wno}\bigl\{ A(s)\bigr\} &= -\text{wno}\bigl\{ A^{-1}(s)\bigr\} \label{eq:wno_inv}
+\emph{wno}\bigl\{ A_1(s)A_2(s) \bigr\} &= \emph{wno}\bigl\{ A_1(s) \bigr\} + \emph{wno}\bigl\{ A_2(s) \bigr\}  \label{eq:wno_add}\\ 
+\emph{wno}\bigl\{ A(s)\bigr\} &= -\emph{wno}\bigl\{ A^{\star}(s)\bigr\} \label{eq:wno_conj} \\ 
+\emph{wno}\bigl\{ A(s)\bigr\} &= -\emph{wno}\bigl\{ A^{-1}(s)\bigr\} \label{eq:wno_inv}
 \end{align}
@@
 For this application, it was desired to shape $T^{\prime}(k)$ and $T(k)$ such that a bandwidth of $300 \: Hz$ and $500 \: Hz$ is attained, respectively (where both achieve a damping of $\zeta = 0.8$).
-Note that in both of these TF's, a pure delay appears in the numerator; therefore, the performance of the loop-shape algorithm can be improved by specifying a desired loop-shape $T_d = T_d^*e^{-sT_\alpha}$ where $T_d^*$ was selected as a standard second order process, i.e.,
+Note that in both of these TF's, a pure delay appears in the numerator; therefore, the performance of the loop-shape algorithm can be improved by specifying a desired loop-shape $T_d(s) = T_d^*(s) e^{-s\tau}$ where $T_d^*(s)$ was selected as a standard second order process, i.e.,
 \begin{equation}
@@
 \end{equation*}
-where $f_d$ is the desired closed-loop bandwidth. In other words, $T_d$ is simply a delayed version of the second order process.
+where $f_d$ is the desired closed-loop bandwidth.
+In other words, $T_d$ is simply a delayed version of the second order process.
+There is some uncertainty associated with the delay $\tau$; the range of this delay is $\tau \in [0,200]\mu s$ with a nominal value of $100 \mu s$.
+Therefore, for tracking purposes, $\tau = 100 \mu s$ in $T_d(s)$ can be selected as a viable performance criteria.
+Note that selecting $\tau$ to be another value within the uncertain range will not significantly impact the response.
+The critical values in the desired response are $f_d$ and $\zeta$.
 
-Although the delay in $G_d$ was captured in the frequency response measurement, it is known that there also exists an additional measurement delay $T_\beta$ that was not captured in the identification experiment.
+Although the delay in $G_d$ was captured in the frequency response measurement, it is known that there also exists an additional measurement delay $\tau_e$ that was not captured in the identification experiment.
 This delay occurs after digitization of the analog signals at the outputs of $P_1$ and $P_2$.
-The value of the delay is uncertain and is known to be in the range of $T_\beta \in [0,30]\mu s$.
+The value of the delay is uncertain and is known to be in the range of $\tau_e \in [0,30]\mu s$.
 Therefore, a multi-model design can be considered where the additional delay can be gridded in this range and incorporated into the closed-loop TF's.
-The grid was established in intervals of $5 \: \mu s$ (i.e., $T_{\beta_i} = [0,5,\ldots30] \mu s$, $i = 1,\ldots,7$).
+The grid was established in intervals of $5 \: \mu s$ (i.e., $\tau_{e_i} = [0,5,\ldots30] \mu s$, $i = 1,\ldots,7$).
 
@@
 \end{equation}
-where $T_i(k)$ and $T_i^{\prime}(k)$ are the closed-loop TF's that incorporate the additional $i$-th delay in $T_{\beta_i}$; $T_d$ is the desired closed-loop TF for loop-shaping $T(k)$ (with a desired bandwidth of $f_d = 500 \: Hz$ and damping $\zeta = 0.8$); $T_d^{\prime}$ is the desired closed-loop TF for loop-shaping $T^{\prime}(k)$ (with a desired bandwidth of $f_d^{\prime} = 300 \: Hz$ and damping $\zeta^{\prime} = \zeta$).
-A similar optimization problem can be considered for minimizing the $\mathcal{H}_2$ norm of the process.
-This optimization problem can be transformed to the convex problem by implementing the methods outlined in section \ref{sec:loop_shape}.
+where $T_i(k)$ and $T_i^{\prime}(k)$ are the closed-loop TF's that incorporate the additional $i$-th delay in $\tau_{e_i}$; $T_d$ is the desired closed-loop TF for loop-shaping $T(k)$ (with a desired bandwidth of $f_d = 500 \: Hz$ and damping $\zeta = 0.8$); $T_d^{\prime}$ is the desired closed-loop TF for loop-shaping $T^{\prime}(k)$ (with a desired bandwidth of $f_d^{\prime} = 300 \: Hz$ and damping $\zeta^{\prime} = \zeta$).
+In the $\mathcal{H}_2$ sense, the optimization problem to consider is as follows:
+\begin{equation} \label{eq:case_study_opt_2}
+\begin{aligned}
+& \underset{ k \in \mathbb{R}}{\text{minimize}}
+& & \int_0^{\infty} \gamma(\omega) d\omega  \\
+& \text{subject to:} & & \|T_i(k)-T_d\|_2^2< \gamma(\omega) \\
+& &  &\|T_i^{\prime}(k)-T_d^{\prime}\|_2^2< \gamma(\omega) \\ 
+& & & i = 1,\ldots,7
+\end{aligned}
+\end{equation}
+These optimization problems can be transformed to convex problems by implementing the methods outlined in section \ref{sec:loop_shape}. 
 \subsection{Experimental Results}
-The constraints in the optimization problem in (\ref{eq:case_study_opt}) were first converted to LMI constraints; the problem was then converted to an SDP problem (since the transfer function analyzer provides the gain and phase at discrete frequency points).
-For solving the $\mathcal{H}_2$ problem in SDP form, the objective function in (\ref{eq:loop_shape_LMI_2}) must be discretized where $\int \gamma(\omega) d\omega \rightarrow \sum_i \gamma(\omega_i)$.
+The constraints in the optimization problem in (\ref{eq:case_study_opt}) and (\ref{eq:case_study_opt_2}) were first converted to LMI constraints.
+Since the transfer function analyzer provides the gain and phase at discrete frequency points, the optimization problem then becomes an SDP problem.
+For solving the $\mathcal{H}_2$ problem in SDP form, the objective function in (\ref{eq:case_study_opt_2}) must be discretized where $\int \gamma(\omega) d\omega \rightarrow \sum_i \gamma(\omega_i)$.
 
 For comparative purposes, controllers were designed by considering the model of the process.
-There is uncertainty associated with the delay $T_\alpha$; the range of this uncertainty is $T_\alpha \in [0,200]\mu s$.
-Therefore, for the model-based design, the problem in (\ref{eq:case_study_opt}) was solved by gridding in both $T_\alpha$ and $T_\beta$.
+Since there is uncertainty associated with the delay $\tau$, a multi-model approach can be implemented to ensure that the performance is attained for the uncertain values.
+Therefore, for the model-based design, the problem in (\ref{eq:case_study_opt}) and (\ref{eq:case_study_opt_2}) was solved by gridding in both $\tau$ and $\tau_e$.
 
@@
 The performance achieved by the data-driven method (in both the $\mathcal{H}_{\infty}$ and $\mathcal{H}_2$ minimization cases) are comparable.
+
+\begin{remark}
+Note that the solutions obtained for the model-based design were nearly identical for both the $\mathcal{H}_2$ and $\mathcal{H}_\infty$ problems.
+Hence the single result shown for the model-based design in Fig.~\ref{fig:d_loop} and Fig.~\ref{fig:v_loop}.
+\end{remark}
+
+Table.~\ref{tab:case_study} displays the optimal solutions for all criteria considered in this case study.
+
 \begin{figure}
@@
 \includegraphics[width=\columnwidth]{../pics/d_loop_mag.eps}
-\caption{The closed-loop response of $|T^{\prime}(j\omega)|$; data-driven method with $\mathcal{H}_{\infty}$ performance (red line); data-driven method with $\mathcal{H}_2$ performance (blue line); model-based approach with $\mathcal{H}_{\infty}$ performance (yellow line); $-3 \: dB$ point representing $300 \: Hz$ bandwidth (dashed-black line).}
+\caption{The closed-loop response of $|T^{\prime}(j\omega)|$; data-driven method with $\mathcal{H}_{\infty}$ performance (red line); data-driven method with $\mathcal{H}_2$ performance (blue line); model-based approach with $\mathcal{H}_2 / \mathcal{H}_\infty$ performance (yellow line); $-3 \: dB$ point representing $300 \: Hz$ bandwidth (dashed-black line).}
 \label{fig:d_loop}
@@
 \includegraphics[width=\columnwidth]{../pics/v_loop_mag.eps}
-\caption{The closed-loop response of $|T(j\omega)|$; data-driven method with $\mathcal{H}_{\infty}$ performance (red line); data-driven method with $\mathcal{H}_2$ performance (blue line); model-based approach with $\mathcal{H}_{\infty}$ performance (yellow line); $-3 \: dB$ point representing $500 \: Hz$ bandwidth (dashed-black line).}
+\caption{The closed-loop response of $|T(j\omega)|$; data-driven method with $\mathcal{H}_{\infty}$ performance (red line); data-driven method with $\mathcal{H}_2$ performance (blue line); model-based approach with $\mathcal{H}_2 / \mathcal{H}_\infty$ performance (yellow line); $-3 \: dB$ point representing $500 \: Hz$ bandwidth (dashed-black line).}
 \label{fig:v_loop}
 \end{figure}
+
+\begin{table}[]
+\centering
+\caption{Comparison of optimal solutions between data-driven and model-based methodology}
+\label{tab:case_study}
+\begin{tabular}{c|c|c|c|c|c}
+                                                                             & $k_i^*$ & $k_u^*$ & $k_{p_1}^*$ & $k_{p_2}^*$       & $\gamma^*$                                                     \\ \hline
+\begin{tabular}[c]{@{}c@{}}$\mathcal{H}_\infty$\\ (data-driven)\end{tabular} & $1.29$  & $3.80$  & $0.42$      & $2 \cdot 10^{-6}$ & $0.057$                                                        \\ \hline
+\begin{tabular}[c]{@{}c@{}}$\mathcal{H}_2$\\ (data-driven)\end{tabular}      & $1.39$  & $3.82$  & $0.60$      & $7 \cdot 10^{-7}$ & \begin{tabular}[c]{@{}c@{}}$0.108$\\ (peak value)\end{tabular} \\ \hline
+\begin{tabular}[c]{@{}c@{}}$\mathcal{H}_\infty$\\ (model-based)\end{tabular} & $0.95$  & $1.70$  & $0.48$      & $3 \cdot 10^{-7}$ & $0.149$                                                        \\ \hline
+\begin{tabular}[c]{@{}c@{}}$\mathcal{H}_2$\\ (model-based)\end{tabular}      & $0.95$  & $1.70$  & $0.48$      & $3 \cdot 10^{-7}$ & \begin{tabular}[c]{@{}c@{}}$0.191$\\ (peak value)\end{tabular}
+\end{tabular}
+\end{table}
 

### 2017-02-14 Papers/Nonlinear Optimization/Latex/Draft/Draft.tex
updated files

@@
 A frequency-domain approach has been implemented in order to design robust controllers that achieve $\mathcal{H}_{\infty}$ performance.
-With the proposed method, it has been shown that the solution to the $\mathcal{H}_{\infty}$ problem converges monotonically to the optimal solution with the order of the basis function $F$ approaches infinity.
+With the proposed method, it has been shown that the solution to the $\mathcal{H}_{\infty}$ problem converges monotonically to the optimal solution when the order of the basis function $F$ approaches infinity.
 This solution is obtained by considering an optimization problem which guarantees the stability of the closed-loop system.

### 2017-02-14 Papers/Nonlinear Optimization/Latex/Draft/Draft.tex
updated files

@@
 
-\title{Designing Robust Controllers With $H_{\infty}$ Performance Using Frequency-Domain Data}
+\title{Designing Robust Controllers With Optimal $H_{\infty}$ Performance Using Frequency-Domain Data}
 
@@
 A nonlinear optimization problem is formulated which guarantees the stability of the closed-loop system whilst ensuring robust performance.
+It is shown that the optimal solution to the $\mathcal{H}_\infty$ problem is attained for a fixed-structure controller without any conservatism.
 A convexified version of the $\mathcal{H}_{\infty}$ criterion has been established in many works and have utilized a similar frequency gridding process; therefore, it is of interest to determine the definiteness of the solution produced by this convex optimization method with respect to the solution of the optimal $\mathcal{H}_{\infty}$ problem proposed in this work.
@@
 This method uses the same convex approximation as in  \cite{SOW10} but is limited to stable systems and PID structure.
+More recent works that implement an iterative loop-shaping method that ensures $\mathcal{H}_{\infty}$ performance have been devised in \cite{UYY16} and \cite{KK16}.
+These methods use the concepts from \cite{BHA16} to linearize non-convex constraints around an operating point.
 
-In the works asserted above, it has been proved that a convex approximation of the $\mathcal{H}_{\infty}$ problem yields favorable results; however, these approximations do not yield the true global optimal solution to the $\mathcal{H}_{\infty}$ problem.
+In some of the works asserted above, it has been proved that a convex approximation of the $\mathcal{H}_{\infty}$ problem yields favorable results; however, these approximations do not yield the true global optimal solution to the $\mathcal{H}_{\infty}$ problem.
 This paper presents an extension of the work in \cite{KNZ16}, and its purpose is to devise a new frequency-domain approach for obtaining the optimal solution to the $\mathcal{H}_{\infty}$ problem.
-In \cite{KNZ16}, it was shown that the optimal solution is obtained when the order of the controller increases to infinity; in the proposed method, the optimal solution can be obtained for a fixed low-order controller (which has desirable practical implications).
+In \cite{KNZ16}, it was shown that the optimal solution is obtained when the order of the controller increases to infinity; in the proposed method, the optimal solution can be obtained for a fixed low-order fully-parameterized controller (which has desirable practical implications).
 A nonlinear optimization problem is formulated to guarantee stability of the closed-loop system while ensuring robust performance (without any approximation).
@@
 A preset frequency grid will be used to satisfy the robust performance condition and solve for a finite number of constraints.
-It is desired to compare the solutions produced from the convex optimization algorithms in \cite{KNZ16} with the proposed algorithm and correlate the .
+It is desired to compare the solutions produced from the convex optimization algorithms in \cite{KNZ16} with the proposed algorithm and correlate the results.
 
-This paper is organized as follows: In Section \ref{sec:pre}, the class of models, controllers and control objectives are defined.
-Section \ref{sec:problem_form} will address the conditions required for robust performance and the optimization methods used to obtain a solution to the $\mathcal{H}_{\infty}$ problem.
+This paper is organized as follows: In section \ref{sec:pre}, the class of models and controllers are defined.
+Section \ref{sec:problem_form} will address the control objectives and the conditions required for robust performance; an optimization problem will be formulated to obtain a solution to the $\mathcal{H}_{\infty}$ problem.
 Section \ref{sec:sim} will demonstrate the effectiveness of the proposed method and establish the efficacy for the convex approximation of the $\mathcal{H}_{\infty}$ criterion.
@@
 \subsection{Class of Models}
-The set of all linear time-invariant (LTI) single-input-signal-output (SISO) stable strictly proper models belonging to the family of perturbed plants with multiplicative uncertainty can be defined as follows:
+The set of all linear time-invariant (LTI) single-input-signal-output (SISO) strictly proper models belonging to the family of perturbed plants with multiplicative uncertainty can be defined as follows:
 \begin{equation}\label{eq:uncert_set}
@@
 \end{equation}
-for $q = 2,\ldots,n$, where $\rho_c \in \mathbb{R}_+$. For discrete-time systems, the Laguerre basis function can be expressed as follows:
+for $q = 2,\ldots,\{n_x,n_y\}$, where $\rho_c \in \mathbb{R}_+$. For discrete-time systems, the Laguerre basis function can be expressed as follows:
 \begin{equation} \label{eq:Laguerre_z}
@@
 \end{equation}
-where $L(s) = G(s)K(s)$; $r$ is the reference input; $y$ is the system output; $e$ is the tracking error signal (i.e., $e = r-y$).
+where $L(\bm{\rho},s) = G(s)K(\bm{\rho},s)$; $r$ is the reference input; $y$ is the system output; $e$ is the tracking error signal (i.e., $e = r-y$).
 From the above definitions of the sensitivity functions, it can be observed that $S(s)+T(s)=1$.
@@
 \end{figure}
-
 where $\psi(\bm{\rho}) = NX(\bm{\rho})+MY(\bm{\rho})$.
@@
 This problem can be solved by presetting a frequency grid $\omega$ and solving a finite number of constraints.
-This frequency grid can be predefined in a variety of manners (see \cite{SVBB11}, \cite{GKL10b}).
+This frequency grid can be predefined in a variety of manners (see \cite{SVBB11}, \cite{GKL10b}, and \cite{FR05}).
 
-\subsection{Optimal Performance via Nonlinear Programming}
+\subsection{Optimal $\mathcal{H}_{\infty}$ Performance}
 In \cite{KNZ16}, it is shown that when the orders of $X(\bm{\rho})$ and $Y(\bm{\rho})$ approach infinity, then $\gamma$ from (\ref{eq:convex_con}) approaches the optimal solution to the $\mathcal{H}_{\infty}$ problem.
@@
 where $\rho_o \in \mathbb{R}_+$.
-It will now be shown that the solution to the optimization problem in (\ref{eq:opt_true}) converges to the optimal solution of the $\mathcal{H}_\infty$ problem as the order of $F(\bm{\rho})$ increases.
+It should be noted that the optimal solution to the $\mathcal{H}_\infty$ problem is achieved when $K(\bm{\rho}) = X(\bm{\rho})Y^{-1}(\bm{\rho})$ has the same structure as the optimal controller.
+However, if the structure of the optimal controller is unknown a priori, then one can simply fix the order of the basis $F(\bm{\rho})$ and vary the orders of the controllers $X(\bm{\rho})$ and $Y(\bm{\rho})$ until $\gamma$ converges to a constant value.
+The concept of this method will be shown in one of the examples in section \ref{sec:sim}.
+
+It will now be shown that the solution to the optimization problem in (\ref{eq:opt_true}) converges monotonically to the optimal solution of the $\mathcal{H}_\infty$ problem as the order of $F(\bm{\rho})$ increases.
 The proof will omit the dependence on $\bm{\rho}$ since the result is independent on the parameterization of the basis functions.
@@
 \end{equation}
-However, $\gamma_n$ (the solution to the optimization problem in (\ref{eq:opt_true})) is always less than or equal to $\gamma_n^*$ and greater that the optimal solution $\gamma_o$ if the structures of $X$ and $Y$ are the same as $X_o$ and $Y_o$, respectively.
+However, $\gamma_n$ (the solution to the optimization problem in (\ref{eq:opt_true})) is always less than or equal to $\gamma_n^*$ and greater that the optimal solution $\gamma_o$ if the structures of $X$ and $Y$ are the same as $X_o$ and $Y_o$, respectively (which is the case, as postulated in the Theorem).
 Therefore, $\gamma_n$ converges from above to $\gamma_o$, and this convergence is monotonic because the basis functions $F_n$ of order $n$ are a subset of those of order $n+1$, which ensures that $\gamma_{n+1} \leq \gamma_n$.
@@
 \subsection{Example 1: Convergence to Optimal Solution}
-Consider the following discrete time SISO system:
+Consider the following discrete time SISO system (with a sampling time of $T_s = 1s$):
 \begin{equation}
@@
 \subsubsection{Simulation Results}
-The \texttt{mixsyn} command from \texttt{MATLAB}'s Robust Control toolbox yields an optimal value of $\gamma^* = 0.5522$ with a fifth-order controller.
-Therefore, according to Theorem.\ref{thm_1}, a fifth-order controller was also implemented with the proposed method (i.e., to ensure convergence to the optimal solution).
+The \texttt{mixsyn} command from \texttt{MATLAB}'s Robust Control toolbox yields an optimal value of $\gamma^* = 0.5522$ with a 5\textsuperscript{th} order controller.
+Therefore, according to Theorem.\ref{thm_1}, a 5\textsuperscript{th} order controller was also implemented with the proposed method (i.e., to ensure convergence to the optimal solution).
 Additionally, two simulations were performed with the proposed method; one simulation with $F(\bm{\rho})$ selected such that the basis function is an FIR filter (i.e., Laguerre basis functions in (\ref{eq:Laguerre_z}) with $\rho_d = 0$) and one simulation with $F(\bm{\rho})$ selected such that $\rho_d$ is a decision variable.
@@
 Note that the controller order was fixed in this case study, since it was known (from the \texttt{mixsyn} command) that the optimal controller order was $5$.
-However, suppose that the order and structure of the optimal controller $K = XY^{-1}$ was unknown.
+However, suppose that the order and structure of the optimal controller $K_o = X_oY_o^{-1}$ was unknown.
 In this case, one can simply fix the structure of the basis function of $F(\bm{\rho})$ with a large order and solve the optimization problem as the order of the controller is varied.
@@
 A $20$-th order basis function for $F(\bm{\rho})$ is selected (as defined in (\ref{eq:Laguerre_sum_c})).
-For comparative purposes, the \texttt{MATLAB} \texttt{mixsyn} function from the Robust Control Toolbox is used to compute a controller with the given weighting filters; the toolbox yields a $4$-th order controller.
+For comparative purposes, the \texttt{MATLAB} \texttt{mixsyn} function from the Robust Control Toolbox is used to compute a controller with the given weighting filters; the toolbox yields a 4\textsuperscript{th} order controller.
 
@@
 \centering
-\caption{Optimal values of PID controllers obtained from the convex and nonlinear optimization problems}
+\caption{Optimal values of PID controllers obtained from the convex and proposed optimization problems}
 \label{tab:ex2_2}
@@
 In this approach, a multiplicative uncertainty is considered and an appropriate weighting filter is designed to ensure that the condition in (\ref{eq:mixed_syn}) is satisfied for all seven models.
-The controller produced by \texttt{MATLAB} with this $\mu$-synthesis approach yields an $18$-th order controller and satisfies the control objective for all models.
+The controller produced by \texttt{MATLAB} with this $\mu$-synthesis approach yields an 18\textsuperscript{th} order controller and satisfies the control objective for all models.
 
@@
 To further simplify the design, the same $\rho_p$ can be selected for each $\ell$-th coprime.
-To solve the convex optimization problem in (\ref{eq:convex_con}), $\rho_p$ must be fixed a priori; however, with the proposed method, $\rho_p$ need not be fixed.
+To solve the convex optimization problem proposed in \cite{KNZ16}, $\rho_p$ must be fixed a priori; however, with the proposed method, $\rho_p$ need not be fixed.
 
@@
 
-The optimal solutions from several optimization algorithms for satisfying the criteria in (\ref{eq:mixed_syn}) are tabulated in Table.\ref{tab:ex3} (where $n$ is the controller order of the respective method).
-The table also shows the solutions when the convex optimization problem in \cite{KNZ16} is solved when the variables $\rho_c$ and $\rho_p$ are decision variables (thus making the problem non-convex).
-It can be observed that the proposed method produces the best performance.
-
 \begin{table}[]
@@
 \begin{tabular}{c|c|c|c|c||c}
-                                                                              & \begin{tabular}[c]{@{}c@{}} $n$ \end{tabular} & $\rho_c$ & $\rho_p$ & $\rho_o$ & $\gamma$ \\ \hline
+                                                                              & \begin{tabular}[c]{@{}c@{}} $n$ \end{tabular} & $\rho_c^{\star}$ & $\rho_p^{\star}$ & $\rho_o^{\star}$ & $\gamma^{\star}$ \\ \hline
 \texttt{MATLAB} $\mu$-Synthesis                                               & $18$                                                        & $-$      & $-$      & $-$      & $1.024$  \\ \hline
@@
 
+The optimal solutions from several optimization algorithms for satisfying the criteria in (\ref{eq:mixed_syn}) are tabulated in Table.\ref{tab:ex3} (where $n$ is the controller order of the respective method).
+The table also shows the solutions when the convex optimization problem in \cite{KNZ16} is solved when the variables $\rho_c$ and $\rho_p$ are decision variables (thus making the problem non-convex).
+It can be observed that the proposed method produces the best performance.
+
 Figure.~\ref{fig:ex3_1} shows the step response of $S(s)$ (disturbance response) for all seven models using the convex optimization algorithm, while Figure.~\ref{fig:ex3_2} shows the step response of $S(s)$ using the proposed method.
 It can be observed that the proposed method produces shorter settling times and reduced overshoot.
+
+\begin{remark*}
+The $\mu$-synthesis approach by \texttt{MATLAB} introduces some conservatism in determining the optimal controller.
+Additionally, with the $\mu$-synthesis approach, the plant $G_4(s)$ was approximated with a first-order Pade function, since pure delay's cannot be used for synthesis.
+In the proposed approach, the true delay function can be considered in the design while eliminating the conservatism associated with modeling the multi-model uncertainties.
+\end{remark*}
+
 \begin{figure}
@@
 
-\begin{remark*}
-The $\mu$-synthesis approach by \texttt{MATLAB} introduces some conservatism in determining the optimal controller.
-Additionally, with the $\mu$-synthesis approach, the plant $G_4(s)$ was approximated with a first-order Pade function, since pure delay's cannot be used for synthesis.
-In the proposed approach, the true delay function can be considered in the design while eliminating the conservatism associated with modeling the multi-model uncertainties.
-\end{remark*}
-
 \section{Conclusion} \label{sec:conclusion}
-A frequency-domain approach has been implemented in order to design robust controllers that achieve $\mathcal{H}_{\infty}$ performance.
+A frequency-domain approach has been implemented in order to design robust controllers that achieve optimal $\mathcal{H}_{\infty}$ performance.
 With the proposed method, it has been shown that the solution to the $\mathcal{H}_{\infty}$ problem converges monotonically to the optimal solution when the order of the basis function $F$ approaches infinity.
@@
 The simulation examples show that the proposed approach achieves the optimal performance for a given controller order without any conservatism.
+Although the proposed approach does yield the best solution for the robust performance condition, it should be emphasized that the convex problem proposed in \cite{KNZ16} generates a solution that is comparable with the methods proposed in this paper.
 For future work, it will be desired to implement this method for multi-input-multi-output (MIMO) systems and systems with controllers that possess multiple degrees-of-freedom.

### 2017-02-15 Papers/Loop Shaping Voltage Loop (CERN)/Latex/Draft/Draft.tex
updated files

@@
 The effectiveness of the method is illustrated by designing a controller for the SATURN power converter which is used in the Large Hadron Collider, in injector machines, and for pulsed applications at CERN.
-Experimental validation in the time domain is also presented.
+Experimental validation in the frequency-domain is also presented.
 \end{abstract}
@@
 Frequency-domain based controller synthesis methods are design schemes that continue to spark the interest of many researchers.
-The authors in \cite{KNND13b} establish a robust frequency-domain controller design methods that requires a solution to a non-linear optimization problem.
+The authors in \cite{KNND13b} establish a robust frequency-domain controller design method that requires a solution to a non-linear optimization problem.
 A frequency-domain loop-shaping method for fixed-structure controllers is proposed in \cite{KNND13c}; however, stability is not guaranteed with this method and must be verified a posteriori.
@@
 The proposed method in this paper invokes a new data-driven control design scheme for a specific power converter application at CERN.
-Currently, the load (i.e., the magnet of the particle accelerator) is approximated as a simple first-order system (series $RL$ circuit); however, as shown in \cite{GB65}, the parameters of the magnet are frequency dependent.
-Additionally, it has been shown in \cite{KZ98} that the vacuum chamber of the magnet is also frequency dependent (due to the skin depth effect and the chamber geometry).
+Currently, the load (i.e., the magnet of the particle accelerator) is approximated as a simple first-order system (series $RL$ circuit); however, it has been shown in \cite{KZ98}, \cite{NW95} and \cite{NS79} that the vacuum chamber of the magnet is also frequency dependent (mainly due to the coupling effects of the beam and deformations in the chamber geometry).
+In fact, the authors in \cite{NW95} assert that even small deformations in the beam pipe can drastically change the impedance of the system and create stability issues.
 Therefore, it is appropriate to consider a data-driven based design to regulate the power converter control system.
 In this work, it is shown that a loop-shaping design in the $\mathcal{H}_\infty$ or $\mathcal{H}_2$ sense can be formulated through a convex optimization problem; however, the methods described in this paper can also be applied to mixed $\mathcal{H}_2$ and $\mathcal{H}_\infty$ problems (i.e., minimizing the norm of weighted sensitivity functions).
-Additionally, with certain conditions on the controller parameters, it is shown that the closed-loop stability is guaranteed.
+Additionally, with certain trivial conditions on the controller parameters, it is shown that the closed-loop stability is guaranteed.
 
@@
 For simplicity, one model from the set $\mathcal{G}$ will be considered, and the subscript $l$ will be omitted.
-However, in general, the design procedures outlined in this paper can be applied to the multi-model case.
+However, in general, the design procedures outlined in this paper can be applied to the multi-model case (as will be seen in the case study).
 
@@
 In this section, it will be demonstrated that the performance specification of the control problem will be achieved by formulating a convex optimization problem.
-The controllers will be synthesized by only considering the FRF of the system components.
+The controllers will be synthesized by only considering the FRF of the system.
 
 \subsection{Convex Approximation}
-The type of optimization problem that will be considered in the paper will have the following form:
+The type of optimization problem that will be considered in this paper will have the following form:
 
@@
 \end{equation}
-
 where $y(x)$ and $z(x)$ are both convex functions of $x$ and $\{ \gamma \in \mathbb{R} : \gamma > 0\}$.
@@
 \end{equation}
-
 where $\nabla z(x_0)$ is the gradient of $z(x)$ evaluated at $x_0$.
@@
 \end{equation} 
-
 where $y(x)$ and $z(x)$ are complex affine functions of the decision variable $x$ and $(\cdot)^{\star}$ denotes the complex conjugate of the argument.
 Let $f(x) = z^{\star}(x)z(x)$ with $z(x)$ defined as
-
 $$z(x) = a_0 + a_1x_1 + a_2x_2 + ,\ldots , + a_nx_n$$
-
 where $z:\mathbb{R}^n \rightarrow \mathbb{C}$ and $f:\mathbb{R}^n \rightarrow \mathbb{R}$. A first order Taylor series of $f(x)$ around an operating point $x_0$ can be formulated as follows:
@@
 \end{equation}
-
 where
@@
 \subsection{Control Performance}
-Since the control methods discussed in this paper are based on the $\mathcal{H}_\infty$ criterion, it is appropriate to first define this criterion in the context of this work.
+Since the control methods discussed in this paper are based on the $\mathcal{H}_\lambda$ criterion ($\lambda \in \{2,\infty \}$), it is appropriate to first define this criterion in the context of this work.
 A typical control objective is to design a controller such that the following constraint is satisfied:
@@
 where $\mathcal{S}_q$ is the $q$-th sensitivity function of interest, and $W_q$ is a stable weighting function such that $\| W_q \mathcal{S}_q\|$ is bounded.
-The norm considered in (\ref{eq:WS_lt1}) can be either the 2- or infinity-norm.
+The norm considered in (\ref{eq:WS_lt1}) can be either the $\mathcal{H}_\infty$ or $\mathcal{H}_2$ norm.
 
-For SISO systems, and for a stable system $X(s)$, the 2- and infinity-norms are defined as follows:
+For SISO systems, and for a stable system $X(s)$, the $\mathcal{H}_2$ and $\mathcal{H}_\infty$ norms are defined as follows:
 \begin{align*}
@@
 A loop-shaping criterion can also be considered as a form of control performance.
-If $T$ is the closed-loop FRF and $T_d$ is the desired FRF, then one can consider minimizing $(T-T_d)$ in either the 2- or infinity-norm sense in order to shape $T$.
+If $T$ is the closed-loop FRF and $T_d$ is the desired FRF, then one can consider minimizing $(T-T_d)$ in either the $\mathcal{H}_2$ or $\mathcal{H}_\infty$ sense in order to shape $T$.
 The next section will discuss how an optimization problem can be formulated for this type of control methodology.
@@
 As asserted in section \ref{sec:system}, the objective of this control problem is to shape the FRF of $T(k)$.
-Suppose that a desired loop-shape is specified as $T_d$; the objective is to design gains in $k$ such that the closed-loop system $T(k)$ coincides with $T_d$ in the $\mathcal{H}_\infty$ or $\mathcal{H}_2$ sense.
+Suppose that a desired loop-shape is specified as $T_d$; the objective is to design the controllers in $k$ such that the closed-loop system $T(k)$ coincides with $T_d$ in the $\mathcal{H}_\infty$ or $\mathcal{H}_2$ sense.
 In the $\mathcal{H}_\infty$ sense, the objective is to minimize $ \|T(k) - T_d \|_\infty$; an equivalent representation of this objective is to minimize $\gamma$ such that $ \|T(k) - T_d \|_\infty < \gamma$.
@@
 \\
-Additionally, note that these optimization problems are considering the gains for $C_m(k)$; however, once an optimal solution is obtained for the gains in $k$, then the definitions in (\ref{eq:new_var}) can be used to revert back to the original gains (i.e., $k_{p_1}$ and $k_{p_2}$.)}
+Additionally, note that these optimization problems are considering the gains for $C_m(k)$; however, once an optimal solution is obtained for the controllers in $k$, then the definitions in (\ref{eq:new_var}) can be used to revert back to the original gains (i.e., $k_{p_1}$ and $k_{p_2}$.)}
 \end{remark}
@@
 
-The initializing gains in $k_0$ play an important role in guaranteeing the stability of the closed-loop system.
+The initializing controllers in $k_0$ play an important role in guaranteeing the stability of the closed-loop system.
 By using the Nyquist criterion for continuous-time systems, the stability of the closed-loop system can be ensured if certain conditions are met for these initializing gains.
@@
 
-The open-loop FRF from the system in Fig.~\ref{fig:damping_loop} is given as $$L(k) = G_d[H_1(k)+H_2(k)+C_m(k)].$$ Let $F(k) = H_1(k)+H_2(k)+C_m(k)$ such that $L(k) = G_dF(k)$; by the Nyquist stability criterion, the closed-loop system is stable if and only if $1+G_dF$ makes $n_{G_d}+n_F$ counter-clockwise encirclements of the origin (where $n_{G_d}$ and $n_F$ are, respectively, the number of RHP poles of $G_d$ and $F$).
+The open-loop FRF of the system $T(k)$ in Fig.~\ref{fig:damping_loop} is given as $$L(k) = G_d[H_1(k)+H_2(k)+C_m(k)].$$ Let $F(k) = H_1(k)+H_2(k)+C_m(k)$ such that $L(k) = G_dF(k)$; by the Nyquist stability criterion, the closed-loop system is stable if and only if $1+G_dF$ makes $n_{G_d}+n_F$ counter-clockwise encirclements of the origin (where $n_{G_d}$ and $n_F$ are, respectively, the number of RHP poles of $G_d$ and $F$).
 The Nyquist plot of $1+G_dF$ must also not pass through the origin.
@@
 \subsection{Initializing Controller}
-For the given structure in Figure.~\ref{fig:damping_loop} , it remains to show how to select the initial stabilizing controllers in order to guarantee the stability of the closed-loop system.
+For the given structure in Figure.~\ref{fig:damping_loop}, it remains to show how to select the initial stabilizing controllers in order to guarantee the stability of the closed-loop system.
 From the control structure of the power converter control system, it can be observed that if all the gains in Figure.~\ref{fig:damping_loop} are set to zero, then the system will be in open-loop.
@@
 A schematic of the SATURN modules are shown in Fig.~ \ref{fig:schematic}.
-A complete assembly of the SATURN power converter is shown in Fig.~\ref{fig:saturn_pc} while the load (i.e., the $RL$ circuit representing the magnet) is shown in Fig.~\ref{fig:load}.
+A complete assembly of the SATURN power converter is shown in Fig.~\ref{fig:saturn_pc} while the load (i.e., the magnet) is shown in Fig.~\ref{fig:load}.
 
@@
 \includegraphics[width=\columnwidth]{../pics/schematic}
-\caption{Schematic of the SATURN modules set in series.}
+\caption{Schematic of the SATURN modules assembled in series.}
 \label{fig:schematic}
@@
 \subsection{Frequency Response Measurement}
-Since the proposed method uses a data-driven methodology with frequency-domain data, the frequency response of each subsystem within the power converter control system must be obtained.
-In other words, we must obtain the frequency responses of $G_d$, $H$, $P_1$, and $P_2$.
-The signals that are accessible for the measurements are the inputs to the capacitor banks ($U_{dc}$ in Fig.~\ref{fig:schematic}), and the outputs of the sensors $P_1$ and $P_2$.
+Since the proposed method uses a data-driven methodology with frequency-domain data, the FRF of each subsystem within the power converter control system must be obtained.
+In other words, we must obtain the FRF of $G_d$, $H$, $P_1$, and $P_2$.
+The signals that are accessible for the measurements are the inputs to the capacitor banks ($U_{dc}$ in Fig.~\ref{fig:schematic}, which is approximately equal to $v_r$ in Fig.~\ref{fig:damping_loop}), and the outputs of the sensors $P_1$ and $P_2$.
 Therefore, when all of the controller gains are set to zero, we are able to obtain the frequency responses of $G_dHP_1$ and $G_dP_2$.
@@
 Although the delay in $G_d$ was captured in the frequency response measurement, it is known that there also exists an additional measurement delay $\tau_e$ that was not captured in the identification experiment.
-This delay occurs after digitization of the analog signals at the outputs of $P_1$ and $P_2$.
+This delay occurs after digitization of the analog signals at the outputs of $P_1$ and $P_2$ (when the system is operating in closed-loop mode).
 The value of the delay is uncertain and is known to be in the range of $\tau_e \in [0,30]\mu s$.
@@
 Fig.~\ref{fig:d_loop} shows the closed-loop frequency response of $|T^{\prime}(j\omega)|$ while Fig.~\ref{fig:v_loop} shows the closed-loop frequency response of $|T(j\omega)|$ for the solutions obtained by minimizing both the $\mathcal{H}_{\infty}$ and $\mathcal{H}_2$ norms of the process.
-From these figures, it can be observed that that model-based design produces the worst performance while the data-driven based design achieves the desired performance for both TF's.
+From these figures, it can be observed that the model-based design produces the worst performance while the data-driven based design achieves the desired performance for both $T(j\omega)$ and $T^{\prime}(j\omega)$.
 The performance achieved by the data-driven method (in both the $\mathcal{H}_{\infty}$ and $\mathcal{H}_2$ minimization cases) are comparable.
@@
 Table.~\ref{tab:case_study} displays the optimal solutions for all criteria considered in this case study.
+It can be observed that the optimal solutions $\gamma^*$ obtained with the data-driven method are less than the solutions obtained with the model-based approach.
+This is due to the fact that the uncertainty in the delay $\tau$ for the model-based design was too conservative.
+This conservativeness was significantly reduced in the data-driven approach since the delay $\tau$ was captured in the FRF identification experiment.
 
@@
 In the case study presented in this paper, it has been shown that the proposed data-driven method offers a systematic optimization-based approach that meets the challenging specifications required for the application.
-In future work, it would be
+The experiments have confirmed that the data-driven approach significantly reduces the conservativeness associated with the modeling process.
+For future work, it will be desired to develop a method that ensures feasibility (given a set of initializing controllers) without applying relaxation techniques.
 

### 2017-02-15 Papers/Nonlinear Optimization/Latex/Draft/Draft.tex
updated files

@@
 This method uses the same convex approximation as in  \cite{SOW10} but is limited to stable systems and PID structure.
-More recent works that implement an iterative loop-shaping method that ensures $\mathcal{H}_{\infty}$ performance have been devised in \cite{UYY16} and \cite{KK16}.
+More recent works that implement an iterative loop-shaping method that ensures $\mathcal{H}_{\infty}$ performance have been devised in \cite{UYY16} and \cite{KK16_2}.
 These methods use the concepts from \cite{BHA16} to linearize non-convex constraints around an operating point.

### 2017-02-15 Papers/Loop Shaping Voltage Loop (CERN)/Latex/Draft/Draft.tex
updated files

@@
 A survey on the differences associated with model-based control and data-driven control has been addressed in \cite{HW13} and \cite{BCE12}; the authors assert that model-based control methods are inherently less robust due to the unmodeled dynamics of a process, and that these controllers are unsafe for practical applications.
-In other words, the parametric uncertainties and the unmodeled dynamics associated with the data-driven scheme are irrelevant, and the only source of uncertainty is the measurement noise.
+In other words, the parametric uncertainties and the unmodeled dynamics associated with the data-driven scheme are irrelevant, and the only source of uncertainty is the measurement uncertainty.
 
@@
 
-The proposed method in this paper invokes a new data-driven control design scheme for a specific power converter application at CERN.
+The method proposed in this paper invokes a new data-driven control design scheme for specific power converter applications at CERN.
 Currently, the load (i.e., the magnet of the particle accelerator) is approximated as a simple first-order system (series $RL$ circuit); however, it has been shown in \cite{KZ98}, \cite{NW95} and \cite{NS79} that the vacuum chamber of the magnet is also frequency dependent (mainly due to the coupling effects of the beam and deformations in the chamber geometry).
@@
 The power converter voltage source filter has the structure shown in Fig.~\ref{fig:circuit}.
-The input voltage $v_i$ is the output of a pulse-width modulated signal (which will be discussed in more detail in section \ref{sec:case}).
-The TF from $v_i$ to $v_0$ describes the filter of the power converter.
+The input voltage $v_i$ is the output of a pulse-width modulated system (which will be discussed in more detail in section \ref{sec:case}).
+The TF from $v_i$ to $v_0$ describes the output filter of the power converter.
 The magnet (i.e., the load) is connected to the output of the converter.
@@
 However, the objective of this paper is to design and implement a controller to shape the FRF between the reference voltage and $v_0$.
-This intermediate control is performed due to the fact that the power converter typically possesses large resonances, and a controller is required to attenuate these resonances in order to ensure better performance in the current loop.
+This intermediate control is performed due to the fact that the output typically possesses large resonances, and a controller is required to attenuate these resonances in order to ensure better performance in the current loop.
+These large resonances are present because the values of the filter resistances are small (in order to reduce the power losses).
+Large resistance values can attenuate the resonances at the price of larger power losses.
 Another reason for implementing this type of control structure at CERN is for commissioning purposes; if/when faults occur in the system, each loop can be verified one at a time to ensure quality operation.
@@
 From this framework, it can be observed that the inner feedback loops are reminiscent of a state-feedback control architecture while the system (as a whole) is a common unity feedback structure with feedforward action.
-For this application, note that $\{G_0,P_1,P_2 \} \in \mathscr{S}$ and $H \in \mathscr{P}$.
-The objective of this application is to design controllers such the TF from $v_d$ to $v_0$ and $v_r$ to $v_0$ both achieve the desired loop-shapes.
+For this application, note that $\{G_0,P_1,P_2 \} \in \mathscr{S}$ and $H \in \mathscr{P}$ (where $H$ possesses a zero at zero).
+The objective of this application is to design controllers such the TFs from $v_d$ to $v_0$ and $v_r$ to $v_0$ both achieve the desired loop-shapes.
 
@@
 H_1(s,k) &:= k_iP_1(s)H(s);  &H_2(s,k) &:= k_uP_2(s) \\
-G_d(s) &:= G_0(s)e^{-s\tau}; &C_m(s,k) &:= k_{m_1}+s^{-1}k_{m_2}\\ 
+G(s) &:= G_0(s)e^{-s\tau}; &C_m(s,k) &:= k_{m_1}+s^{-1}k_{m_2}\\ 
 \end{aligned}
 \end{equation}
-where $k \in \{k_i,k_u,k_{m_1},k_{m_2}\}$.
+where $k = [k_i,k_u,k_{m_1},k_{m_2}]$.
 Let the TF from $v_d$ to $v_0$ be denoted as $T^{\prime}(s,k)$ and the TF from $v_r$ to $v_0$ be denoted as $T(s,k)$.
-Then these closed-loop TF's can easily be derived as follows:
+These closed-loop TFs can easily be derived as follows:
 
 \begin{align}
-T^{\prime}(s,k) &= \frac{G_d(s)(1+k_u)}{1+G_d(s)[H_1(s,k)+H_2(s,k)]} \label{eq:Tclp}  \\ 
-T(s,k) &= \frac{G_d(s)[1+k_u+C_m(s,k)]}{1+G_d(s)[H_1(s,k)+H_2(s,k)+C_m(s,k)]}  \label{eq:Tcl} 
+T^{\prime}(s,k) &= \frac{G(s)(1+k_u)}{1+G(s)[H_1(s,k)+H_2(s,k)]} \label{eq:Tclp}  \\ 
+T(s,k) &= \frac{G(s)[1+k_u+C_m(s,k)]}{1+G(s)[H_1(s,k)+H_2(s,k)+C_m(s,k)]}  \label{eq:Tcl} 
 \end{align}
@@
 \subsection{Convex Approximation}
-The type of optimization problem that will be considered in this paper will have the following form:
+The type of optimization problem that will be considered will have the following form:
 
@@
 
-The control methodology in this paper is based on minimizing a control objective in the $\mathcal{H}_\infty$ or $\mathcal{H}_2$ sense.
+The control methodology is based on minimizing a control objective in the $\mathcal{H}_\infty$ or $\mathcal{H}_2$ sense.
 In subsequent sections, it will be shown that these performance constraints will have the following quadratic form:
@@
 \begin{equation} \label{eq:WS_lt1}
-\| W_q \mathcal{S}_q\| < 1
+\| W \mathcal{S}\| < 1
 \end{equation}
-where $\mathcal{S}_q$ is the $q$-th sensitivity function of interest, and $W_q$ is a stable weighting function such that $\| W_q \mathcal{S}_q\|$ is bounded.
+where $\mathcal{S}$ is the sensitivity function of interest, and $W$ is a stable weighting function such that $\| W \mathcal{S}\|$ is bounded.
 The norm considered in (\ref{eq:WS_lt1}) can be either the $\mathcal{H}_\infty$ or $\mathcal{H}_2$ norm.
@@
 If $T$ is the closed-loop FRF and $T_d$ is the desired FRF, then one can consider minimizing $(T-T_d)$ in either the $\mathcal{H}_2$ or $\mathcal{H}_\infty$ sense in order to shape $T$.
-The next section will discuss how an optimization problem can be formulated for this type of control methodology.
+The next section will discuss how such an optimization problem can be formulated for this type of control methodology.
 
@@
 \end{equation}
-for all $\omega \in \Omega$.
-It can be observed that the constraint in (\ref{eq:min_loopshape}) is not convex.
-Let $z(k) = 1+G_d[H_1(k)+H_2(k)+C_m(k)]$ and $N(k) = G_d[1+k_u+C_m(k)]$; then the above constraint can be written as:
+for all $\omega \in \Omega$. It can be observed that the constraint in (\ref{eq:min_loopshape}) is not convex. Let us now define the following quantities:
+\begin{equation} 
+\begin{aligned}
+w(k) &= G[1+k_u+C_m(k)] \\
+z(k) &= 1+G[H_1(k)+H_2(k)+C_m(k)]
+\end{aligned}
+\end{equation}
+where it is evident that $T(k) = w(k)z^{-1}(k)$; then the constraint in (\ref{eq:min_loopshape}) can be written as:
 
 \begin{equation}
-\bigl[N(k)-z(k)T_d \bigr]^{\star}\gamma^{-1} \bigl[N(k)-z(k)T_d \bigr] - z^{\star}(k)z(k)<0
+\bigl[w(k)-z(k)T_d \bigr]^{\star}\gamma^{-1} \bigl[w(k)-z(k)T_d \bigr] - z^{\star}(k)z(k)<0
 \end{equation}
@@
 \begin{bmatrix}
-z^{\star}(k)z_0 + z_0^{\star}z(k) - z_0^{\star}z_0 & \phantom{xx}[N(k)-z(k)T_d]^{\star} \\ 
-N(k)-z(k)T_d & \phantom{xx}\gamma
+z^{\star}(k)z_0 + z_0^{\star}z(k) - z_0^{\star}z_0 & \phantom{xx}[w(k)-z(k)T_d]^{\star} \\ 
+w(k)-z(k)T_d & \phantom{xx}\gamma
 \end{bmatrix} \succ 0
@@
 \end{equation}
-for all $\omega \in \Omega$, where $z_0 = 1+G_d[H_1(k_0) + H_2(k_0)+C_m(k_0)]$ and $k_0 \in \{k_{i,0},k_{u,0},k_{m_1,0},k_{m_2,0}  \}$ are the initializing gains.
+for all $\omega \in \Omega$, where $z_0 = 1+G[H_1(k_0) + H_2(k_0)+C_m(k_0)]$ and $k_0 =[k_{i,0},k_{u,0},k_{m_1,0},k_{m_2,0}  ]$ are the initializing gains.
 In a similar manner, the following convex optimization problem can be considered for minimizing  $ \|T(k)- T_d \|_2^2$, as follows:
@@
 \begin{bmatrix}
-z^{\star}(k)z_0 + z_0^{\star}z(k) - z_0^{\star}z_0 & \phantom{xx}[N(k)-z(k)T_d]^{\star} \\ 
-N(k)-z(k)T_d & \phantom{xx}\gamma(\omega)
+z^{\star}(k)z_0 + z_0^{\star}z(k) - z_0^{\star}z_0 & \phantom{xx}[w(k)-z(k)T_d]^{\star} \\ 
+w(k)-z(k)T_d & \phantom{xx}\gamma(\omega)
 \end{bmatrix} \succ 0
@@
 
-The open-loop FRF of the system $T(k)$ in Fig.~\ref{fig:damping_loop} is given as $$L(k) = G_d[H_1(k)+H_2(k)+C_m(k)].$$ Let $F(k) = H_1(k)+H_2(k)+C_m(k)$ such that $L(k) = G_dF(k)$; by the Nyquist stability criterion, the closed-loop system is stable if and only if $1+G_dF$ makes $n_{G_d}+n_F$ counter-clockwise encirclements of the origin (where $n_{G_d}$ and $n_F$ are, respectively, the number of RHP poles of $G_d$ and $F$).
-The Nyquist plot of $1+G_dF$ must also not pass through the origin.
+The open-loop FRF of the system $T(k)$ in Fig.~\ref{fig:damping_loop} is given as $$L(k) = G[H_1(k)+H_2(k)+C_m(k)].$$ Let $F(k) = H_1(k)+H_2(k)+C_m(k)$ such that $L(k) = GF(k)$; by the Nyquist stability criterion, the closed-loop system is stable if and only if $1+GF$ makes $n_{G}+n_F$ counter-clockwise encirclements of the origin (where $n_{G}$ and $n_F$ are, respectively, the number of RHP poles of $G$ and $F$).
+The Nyquist plot of $1+GF$ must also not pass through the origin.
 
@@
 \begin{align*}
-z(k) &= 1+G_d[H_1(k)+H_2(k)+C_m(k)] \\
-z_0 &= 1+G_d[H_1(k_0)+H_2(k_0)+C_m(k_0)]
+z(k) &= 1+G[H_1(k)+H_2(k)+C_m(k)] \\
+z_0 &= 1+G[H_1(k_0)+H_2(k_0)+C_m(k_0)]
 \end{align*}
-with $\{G_d,H_1,H_2\} \in \mathscr{S}$. Then the closed-loop system $T$ is stable if the parameters in the set $k_0$ are stabilizing initial gains.
+with $\{G,H_1,H_2\} \in \mathscr{S}$. Then the closed-loop system $T$ is stable if the parameters in the set $k_0$ are stabilizing initial gains.
 \end{theorem}
@@
 {\mbox{wno}} \{ z^{\star}(k)z_0\} &= {\mbox{wno}} \{ z^{\star}\} + {\mbox{wno}} \{ z_0\} \\
-&= -{\mbox{wno}} \{ 1+G_dF(k)\} \\
-&\phantom{=} + {\mbox{wno}} \{ 1+G_dF(k_0)\} \\
+&= -{\mbox{wno}} \{ 1+GF(k)\} \\
+&\phantom{=} + {\mbox{wno}} \{ 1+GF(k_0)\} \\
 \end{aligned}
@@
 where $F(k_0) = H_1(k_0) + H_2(k_0) + C_m(k_0)$.
-Note that $F(k)$ is strictly proper and $G_dF(k)$ is strictly proper; therefore, the winding number of $z^{\star}(k)z_0$ can be evaluated over $\Omega$ instead of the $D$-contour.
+Note that $F(k)$ is strictly proper and $GF(k)$ is strictly proper; therefore, the winding number of $z^{\star}(k)z_0$ can be evaluated over $\Omega$ instead of the $D$-contour.
 Additionally, the constraint in (\ref{eq:theorem1_cond}) implies that $\Re\{ z^{\star}(k)z_0\} > 0$ (where $\Re\{ \cdot \}$ indicates the real part of the argument), which signifies that the Nyquist plot of $z^{\star}(k)z_0$ will not pass through or encircle the origin.
@@
 \begin{equation} \label{eq:winding_proof3}
-\mbox{wno} \{ 1+G_dF(k)\} = {\mbox{wno}} \{ 1+G_dF(k_0)\}
+\mbox{wno} \{ 1+GF(k)\} = {\mbox{wno}} \{ 1+GF(k_0)\}
 \end{equation}
-The condition in (\ref{eq:winding_proof3}) implies that if the initializing controllers $k_0$ are stabilizing (i.e., the open-loop system $G_dF(k_0)$ meets the Nyquist stability criterion), then the closed-loop system will be stable.
+The condition in (\ref{eq:winding_proof3}) implies that if the initializing controllers $k_0$ are stabilizing (i.e., the open-loop system $GF(k_0)$ meets the Nyquist stability criterion), then the closed-loop system will be stable.
 {\hfill \ensuremath{\blacksquare}}
@@
 \subsection{Initializing Controller}
-For the given structure in Figure.~\ref{fig:damping_loop}, it remains to show how to select the initial stabilizing controllers in order to guarantee the stability of the closed-loop system.
+For the given structure in Figure.~\ref{fig:damping_loop}, it remains to be shown how to select the initial stabilizing controllers in order to guarantee the stability of the closed-loop system.
 From the control structure of the power converter control system, it can be observed that if all the gains in Figure.~\ref{fig:damping_loop} are set to zero, then the system will be in open-loop.
-However, since $G_d \in \mathscr{S}$, then selecting $k_0 = 0$ will guarentee the stability of the closed-loop system.
+However, since $G \in \mathscr{S}$, then selecting $k_0 = 0$ will guarentee the stability of the closed-loop system.
 
 If the initializing controllers are selected such that the performance with these controllers is far from the desired performance, then it is possible that either the optimization problem yields no feasible solution, or that the solver runs into numerical problems (which leads to infeasible solutions).
-One method to resolve this problem is to apply relaxation techniques where a relaxed optimization problem is solved; the solution to the relaxed problem is then used as the initializing controllers for the non-relaxed problem.
+One method to resolve this problem is to apply relaxation techniques where a relaxed optimization problem is solved; the solution to the relaxed problem can then be used as the initializing controllers for the non-relaxed problem.
 
@@
 In other words, for a finite number of frequency points $n$ selected in $\omega \in [0,\infty)$, then $n$ constraints must be satisfied.
-This frequency grid can be predefined in a variety of manners (see \cite{SVBB11}, \cite{GKL10b}, \cite{FR05}).
+This frequency grid can be predefined in a variety of manners (see \cite{GKL10b}, \cite{SVBB11}, \cite{FR05}).
 
@@
 A complete assembly of the SATURN power converter is shown in Fig.~\ref{fig:saturn_pc} while the load (i.e., the magnet) is shown in Fig.~\ref{fig:load}.
+
+\begin{table}[]
+\centering
+\caption{My caption}
+\label{my-label}
+\begin{tabular}{c|c|c}
+                                                                               & Value                      & Units \\ \hline
+\begin{tabular}[c]{@{}c@{}}$U_0$\\ (Output Voltage)\end{tabular}               & $700$                      & V     \\ \hline
+\begin{tabular}[c]{@{}c@{}}$I_0$\\ (Output Current)\end{tabular}               & $850$                      & A     \\ \hline
+Input Power                                                                    & $18$                       & kV    \\ \hline
+Input Frequency                                                                & $50$                       & Hz    \\ \hline
+\begin{tabular}[c]{@{}c@{}}IGBT equivalent \\ switching frequency\end{tabular} & $5000$                     & Hz    \\ \hline
+Transformer Weight                                                             & $4500$                     & kg    \\ \hline
+Control Type                                                                   & RegFGC3 Type 10 / Ethernet \cite{CKS11} & $-$  
+\end{tabular}
+\end{table}
 
@@
 Since the proposed method uses a data-driven methodology with frequency-domain data, the FRF of each subsystem within the power converter control system must be obtained.
-In other words, we must obtain the FRF of $G_d$, $H$, $P_1$, and $P_2$.
+In other words, we must obtain the FRF of $G$, $H$, $P_1$, and $P_2$.
 The signals that are accessible for the measurements are the inputs to the capacitor banks ($U_{dc}$ in Fig.~\ref{fig:schematic}, which is approximately equal to $v_r$ in Fig.~\ref{fig:damping_loop}), and the outputs of the sensors $P_1$ and $P_2$.
-Therefore, when all of the controller gains are set to zero, we are able to obtain the frequency responses of $G_dHP_1$ and $G_dP_2$.
-However, note that $G_d$ appears independently of $P_2$ in (\ref{eq:Tclp}) and (\ref{eq:Tcl}); since $P_1$ and $P_2$ are sensors with very high bandwidths relative to $G_d$ (approximately $10 \: kHz$), then $G_d \approx G_dP_2$  at frequencies less than $1 \: kHz$.
+Therefore, when all of the controller gains are set to zero, we are able to obtain the frequency responses of $GHP_1$ and $GP_2$.
+However, note that $G$ appears independently of $P_2$ in (\ref{eq:Tclp}) and (\ref{eq:Tcl}); since $P_1$ and $P_2$ are sensors with very high bandwidths relative to $G$ (approximately $10 \: kHz$), then $G \approx GP_2$  at frequencies less than $1 \: kHz$.
 
@@
 The appropriate scaling factors were taken into account for the measurements (due to the series connection of the SATURN modules) in order to coincide with the structure used in Fig.~\ref{fig:damping_loop}.
-The frequency responses of $G_dP_2$ and $G_dHP_1$ are shown in Fig.~\ref{fig:G} and Fig.~\ref{fig:GHP1}, respectively.
+The frequency responses of $GP_2$ and $GHP_1$ are shown in Fig.~\ref{fig:G} and Fig.~\ref{fig:GHP1}, respectively.
 
@@
 
-Although the delay in $G_d$ was captured in the frequency response measurement, it is known that there also exists an additional measurement delay $\tau_e$ that was not captured in the identification experiment.
+Although the delay in $G$ was captured in the frequency response measurement, it is known that there also exists an additional measurement delay $\tau_e$ that was not captured in the identification experiment.
 This delay occurs after digitization of the analog signals at the outputs of $P_1$ and $P_2$ (when the system is operating in closed-loop mode).

### 2017-02-27 Papers/Loop Shaping Voltage Loop (CERN)/Latex/Draft_2/Draft_2.tex
updated files

--- 2017-02-15 Papers/Loop Shaping Voltage Loop (CERN)/Latex/Draft/Draft.tex
@@
 
-\title{A Data-Driven Loop-Shaping Approach to Design Controllers for Power Converters via Convex Optimization} 
+\title{A Data-Driven Approach to Power Converter Control via Convex Optimization} 
 % Title, preferably not more than 10 words.
@@
 \begin{abstract}                % Abstract of not more than 250 words.
-A new loop-shaping data-driven approach is presented for synthesizing controllers for the CERN power converter control system.
-This method uses the frequency response function (FRF) of a system in order to avoid the problem of unmodeled dynamics associated with parametric models.
+A new model reference data-driven approach is presented for synthesizing controllers for the CERN power converter control system.
+This method uses the frequency response function (FRF) of a system in order to avoid the problem of unmodeled dynamics associated with low-order parametric models.
 For this particular application, it is shown that a convex optimization problem can be formulated (in either the $H_\infty$ or $H_2$ sense) to shape the closed-loop FRF while guaranteeing the closed-loop stability.
@@
 Today's industrial processes pose challenging problems to control engineers due to the increasing complexities of system structures.
-In order to simplify the controller design process, these systems are approximated with low-order models; this reduces both time and effort in synthesizing a controller.
+In order to simplify the controller design process, these systems are approximated with low-order parameteric models; this reduces both time and effort in synthesizing a controller.
 However, this approximation can create stability and performance problems since these low-order models are subject to model uncertainty.
 Data-driven control methods seek to alleviate this problem by synthesizing controllers based on time-domain or frequency-domain data (i.e., synthesis is model independant).
-A survey on the differences associated with model-based control and data-driven control has been addressed in \cite{HW13} and \cite{BCE12}; the authors assert that model-based control methods are inherently less robust due to the unmodeled dynamics of a process, and that these controllers are unsafe for practical applications.
-In other words, the parametric uncertainties and the unmodeled dynamics associated with the data-driven scheme are irrelevant, and the only source of uncertainty is the measurement uncertainty.
+A survey on the differences associated with model-based control and data-driven control has been addressed in \cite{HW13} and \cite{FK13a}; the authors assert that model-based control methods are inherently less robust due to the unmodeled dynamics of a process, and that these controllers are unsafe for practical applications.
+In other words, the parametric uncertainties and the unmodeled dynamics associated with the data-driven scheme are irrelevant, and the only source of uncertainty is the measurement error.
 
-Data-driven controllers can be synthesized either on-line or off-line; the on-line methods such as the classical direct adaptive control (MRAC) \cite{LLMK11}, model-free adaptive control (MFAC) \cite{HJ13}, and the unfalsified control (UC) \cite{ST97} methodologies design controllers using time-domain data.
+%Data-driven controllers can be synthesized either on-line or off-line; the on-line methods such as the classical direct adaptive control (MRAC) \cite{LLMK11}, model-free adaptive control (MFAC) \cite{HJ13}, and the unfalsified control (UC) \cite{ST97} methodologies design controllers using time-domain data.
 Iterative feedback tuning (IFT) \cite{Hja02}, correlation-based tuning (CBT) \cite{KMB02a}, virtual reference feedback tuning (VRFT) \cite{CLS02}, non-iterative data-driven model reference control \cite{KVB07} methodologies are all off-line time-domain data-driven methods.
@@
 Controller synthesis methods belonging to the $\mathcal{H}_{\infty}$ control framework minimizes the $\mathcal{H}_{\infty}$ norm of a weighted closed-loop sensitivity function.
-A convex optimization approach is used to design linearly-parameterized (LP) controllers with loop shaping and $\mathcal{H}_{\infty}$ performance in \cite{KG10}.
-This method is extended to multiple-input multiple-output (MIMO) systems for computing decoupling LP-MIMO controllers in \cite{GKL10b}.
-In \cite{NK14}, this method of designing LP controllers was further extended to MIMO systems with delay.
+A convex optimization approach is used to design linearly-parameterized (LP) controllers with loop-shaping and $\mathcal{H}_{\infty}$ performance in \cite{KG10}.
+The constraints are convexified around a desired open-loop transfer function.
+A frequency-domain approach for computing low-order multivariable LP controllers is presented in \cite{SOW10}.
+The $\mathcal{H}_{\infty}$ constraints are convexified around an initial stabilizing controller.
+An iterative algorithm is used that converges to a local optimal solution of the non-convex problem.
+Moreover, in \cite{HAB13},  a convex-concave approximation of the $\mathcal{H}_{\infty}$ constraint is used which leads to the same constraints as \cite{KG10} for PID controllers.
+This method is then generalized to MIMO PID controller design in \cite{BHA16} for stable systems.
+More recent works that implement an iterative loop-shaping method that ensures $\mathcal{H}_{\infty}$ performance have been devised in \cite{KK16}.
+This method is not limited to LP controllers and stable systems and can consider $H_2$ performance as well.
 Recently, the necessary and sufficient conditions for the existence of $\mathcal{H}_{\infty}$ controllers for SISO systems represented by their frequency response has been proposed in \cite{KNZ16}.
+The advantage of this method is that it does not require an initial stabilizing controller and converges to the global optimal solution if the controller order goes to infinity.
 
-The method proposed in this paper invokes a new data-driven control design scheme for specific power converter applications at CERN.
+The method proposed in this paper is an extension of \cite{KK16} to the model reference control problem and invokes a new data-driven control design scheme for specific power converter applications at CERN.
 Currently, the load (i.e., the magnet of the particle accelerator) is approximated as a simple first-order system (series $RL$ circuit); however, it has been shown in \cite{KZ98}, \cite{NW95} and \cite{NS79} that the vacuum chamber of the magnet is also frequency dependent (mainly due to the coupling effects of the beam and deformations in the chamber geometry).
@@
 Therefore, it is appropriate to consider a data-driven based design to regulate the power converter control system.
-In this work, it is shown that a loop-shaping design in the $\mathcal{H}_\infty$ or $\mathcal{H}_2$ sense can be formulated through a convex optimization problem; however, the methods described in this paper can also be applied to mixed $\mathcal{H}_2$ and $\mathcal{H}_\infty$ problems (i.e., minimizing the norm of weighted sensitivity functions).
+In this work, it is shown that a model reference design in the $\mathcal{H}_\infty$ or $\mathcal{H}_2$ sense can be formulated through a convex optimization problem; however, the methods described in this paper can also be applied to mixed $\mathcal{H}_2$ and $\mathcal{H}_\infty$ problems (i.e., minimizing the norm of weighted sensitivity functions).
 Additionally, with certain trivial conditions on the controller parameters, it is shown that the closed-loop stability is guaranteed.
@@
 The paper is organized as follows.
-The class of models represented by FRF's are addressed in section \ref{sec:prelim}.
+The class of models represented by FRF's are addressed in Section \ref{sec:prelim}.
 Section \ref{sec:system} discusses the framework of the power converter control system and its functionality at CERN.
-The main results and theoretical bases are addressed in section \ref{sec:main}; in this section, loop-shaping constraints are formulated for the power converter control system.
+The main results and theoretical bases are addressed in Section \ref{sec:main}; in this section, loop-shaping constraints are formulated for the power converter control system.
 Section \ref{sec:case} is dedicated to a case study where the effectiveness of the method is demonstrated by applying the proposed design scheme to a power converter control system for a specific accelerator requirement.
@@
 The FRF can be obtained directly with a given transfer function (TF) model, or through an identification experiment using the Fourier analysis method.
-Let $U\jo$ and $Y\jo$ represent the FRF's of the system input and output signals, respectively.
+Let $U\jo$ and $Y\jo$ represent the FRFs of the system input and output signals, respectively.
 Then the FRF of the system can be represented as
@@
 \end{equation}
-If the data is noisy, then $G\jo$ is characterized as the Empirical Transfer Function Estimate (ETFE) and is asymptotically unbiased \cite{Lju99}.
-For such systems, a multiplicative uncertainty can be considered to ensure robustness in the presence of noise perturbations.
 In general, a set $\mathcal{G}$ can be formulated to represent a plant model containing $p$ FRF models:
@@
 
+\begin{remark}
+In this work, the control structure will contain both discrete-time and continuous time systems.
+However, the proposed method synthesizes controllers based on the FRF of the system (i.e., the design method is not based on the parametric model); therefore, if the Nyquist-Shannon sampling rate is met, then the FRF of discrete-time systems will be nearly identical to that of the continuous-time system.
+\end{remark}
+
 \section{System Framework}
 \label{sec:system}
-\begin{figure}
+\begin{figure*}
 \centering
-\includegraphics[width=\columnwidth]{../pics/circuit_partial_a}
-\caption{Power converter filter schematic (from $v_i$ to $v_0$). The magnet represents the load of the process.}
+\includegraphics[width=1.7\columnwidth]{../pics/voltage_loop_schematic_color_coded}
+\caption{Power converter control system schematic.
+The magnet represents the load of the process while the DSP implements the control strategy.
+The blue portion represents the power electronics of the converter; the yellow portion represents the analog process of the converter with the load; the red portion represents the digital-signal processor (DSP) which implements the control strategy; and the green block represents the measurement board which reads the desired control variables and sends the information to the DSP for processing.}
 \label{fig:circuit}
-\end{figure}
-The power converter voltage source filter has the structure shown in Fig.~\ref{fig:circuit}.
-The input voltage $v_i$ is the output of a pulse-width modulated system (which will be discussed in more detail in section \ref{sec:case}).
-The TF from $v_i$ to $v_0$ describes the output filter of the power converter.
-The magnet (i.e., the load) is connected to the output of the converter.
-For general applications at CERN, the objective is to control the current in the magnet (through $L_m$) such that the error between this output current and a delayed version of the reference current is minimized.
+\end{figure*}
+A schematic of the power converter control system is shown in Fig.~\ref{fig:circuit}.
+Specific portions of the schematic are color-coded in order to construct the associated block diagram.
+Note that there are two power converter branches assembled in series in this schematic; however, both branches possess the same components with identical values.
+Therefore, the analysis and control strategy can be performed in one branch and then scale the controller parameters accordingly (i.e., by a factor of 2).
+The input voltage for one of the high frequency (HF) filters will be denoted as $v_i$ while the output voltage of the filter (for one branch) will be denoted as $v_0$.
+The TF from $v_i$ to $v_0$ describes the output filter of the power converter for one branch.
+For general applications at CERN, the objective is to control the current in the magnet such that the error between this output current and a delayed version of the reference current is minimized.
 However, the objective of this paper is to design and implement a controller to shape the FRF between the reference voltage and $v_0$.
@@
 
-The system structure for this application is shown in Fig.~\ref{fig:damping_loop}. 
-\begin{figure}
+The block diagram of the control strategy is shown in Fig.~\ref{fig:damping_loop}.
+This block diagram is color-coded to correlate with the structure of the schematic in Fig.~\ref{fig:circuit}.
+The analog-to-digital converter (ADC) is used to process the information from the analog system to the DSP; $G_0(s)$ represents the TF from $v_i$ to $v_0$; $H(s)$ represents the TF from $v_0$ to $i_c$ (the current through the capacitor in the HF filter); $P_1(s)$ and $P_2(s)$ are sensors (i.e., low-pass filters); $k_i$ and $k_u$ are the control variable gains; $\tau \: [s]$ is an actuation delay that is used to approximate the dynamics of the power electronics; and $C(s)$ is a PI controller, i.e., $$C(z^{-1}) = k_{p_1} + k_{p_2}\frac{t_s z^{-1}}{1-z^{-1}}$$ where $t_s \: [s]$ is the sampling rate of the DSP.
+The ADCs have very fast dynamics relative to the other subsystems in the loop; for this reason, it is appropriate to consider the ADCs as pure time delays (which will be denoted with a delay $\tau_{a} \: [s]$).
+The transfer function analyzer (TFA) is used for identification purposes, and will be discussed in the case study.
+As stated in the Remark in the previous section, the FRFs of continuous-time and discrete-time systems are nearly identical when the Nyquist-Shannon sampling theorem is met.
+Since the proposed method invokes a data-driven method using the FRF of a system, all functions discussed hereafter will be FRFs.
+
+From this framework, it can be observed that the inner feedback loops are reminiscent of a state-feedback control architecture.
+For this application, note that $\{G_0,P_1,P_2 \} \in \mathscr{S}$ and $H \in \mathscr{P}$ (where $H$ possesses a zero at zero).
+The objective of this application is to design controller's gains such that the FRFs from $v_d$ to $v_0$ and $v_r$ to $v_0$ both achieve the desired reference models.
+\begin{figure*}
 \centering
-\includegraphics[width=\columnwidth]{../pics/damping_loop_full}
-\caption{Interconnection of the power converter control system. }
+\includegraphics[width=1.6\columnwidth]{../pics/voltage_loop_color_coded}
+\caption{Interconnection of the power converter control system. During normal operation, the TFA along with the connections indicated with a dashed-black line are not present.}
 \label{fig:damping_loop}
-\end{figure}
-$G_0(s)$ represents the TF from $v_i$ to $v_0$ in Fig.~\ref{fig:circuit}; $H(s)$ represents the TF from $v_0$ to $i_c$; $P_1(s)$ and $P_2(s)$ are sensors (i.e., low-pass filters); $k_i$ and $k_u$ are the control variable gains; $\tau \: [s]$ is an actuation delay; and $C(s)$ is a PI controller (i.e., $C(s) = k_{p_1} + s^{-1}k_{p_2}$).
-From this framework, it can be observed that the inner feedback loops are reminiscent of a state-feedback control architecture while the system (as a whole) is a common unity feedback structure with feedforward action.
-For this application, note that $\{G_0,P_1,P_2 \} \in \mathscr{S}$ and $H \in \mathscr{P}$ (where $H$ possesses a zero at zero).
-The objective of this application is to design controllers such the TFs from $v_d$ to $v_0$ and $v_r$ to $v_0$ both achieve the desired loop-shapes.
+\end{figure*}
 
@@
 k_{m_1} &:= k_{p_1}(1+k_u) ;  &k_{m_2} &:= k_{p_2}(1+k_u)  \\
-H_1(s,k) &:= k_iP_1(s)H(s);  &H_2(s,k) &:= k_uP_2(s) \\
-G(s) &:= G_0(s)e^{-s\tau}; &C_m(s,k) &:= k_{m_1}+s^{-1}k_{m_2}\\ 
+H_1(k) &:= k_iP_1H;  &H_2(k) &:= k_uP_2e^{-j\omega \tau_{a}} \\
+G &:= G_0e^{-j\omega\tau}; &C_m(k) &:= k_{m_1}+k_{m_2}\frac{t_se^{-j\omega}}{1-e^{-j\omega}}\\ 
 \end{aligned}
@@
 where $k = [k_i,k_u,k_{m_1},k_{m_2}]$.
-Let the TF from $v_d$ to $v_0$ be denoted as $T^{\prime}(s,k)$ and the TF from $v_r$ to $v_0$ be denoted as $T(s,k)$.
-These closed-loop TFs can easily be derived as follows:
+Let the FRF from $v_d$ to $v_0$ be denoted as $T^{\prime}(k)$ and the FRF from $v_r$ to $v_0$ be denoted as $T(k)$.
+These closed-loop FRFs can easily be derived as follows:
 
 \begin{align}
-T^{\prime}(s,k) &= \frac{G(s)(1+k_u)}{1+G(s)[H_1(s,k)+H_2(s,k)]} \label{eq:Tclp}  \\ 
-T(s,k) &= \frac{G(s)[1+k_u+C_m(s,k)]}{1+G(s)[H_1(s,k)+H_2(s,k)+C_m(s,k)]}  \label{eq:Tcl} 
+T^{\prime}(k) &= \frac{G(1+k_u)}{1+G[H_1(k)+H_2(k)]} \label{eq:Tclp}  \\ 
+T(k) &= \frac{G[1+k_u+C_m(k)]}{1+G[H_1(k)+H_2(k)+e^{-\tau_{a}s} P_2C_m(k)]}  \label{eq:Tcl} 
 \end{align}
 
-For the remaining theoretical portions of this document, the loop-shaping technique will only be shown for $T(s,k)$, since the same procedures can also be applied to $T^{\prime}(s,k)$.
-Additionally, for notation purposes, the dependency in $s$ will be omitted and reiterated when deemed necessary.
-Additionally, all functions discussed hereafter will be FRF's with $s = j\omega$.
-For example, the denotation $T(k)$ represents $T(j\omega,k)$.
+For the remaining theoretical portions of this document, the model reference control will only be shown for $T(k)$, since the same procedures can also be applied to $T^{\prime}(k)$.
 
@@
 \subsection{Convex Approximation}
-The type of optimization problem that will be considered will have the following form:
+In subsequent sections, it will be shown that the type of optimization problem that will be considered will have the following form:
 
@@
 \begin{aligned}
-& \underset{ x }{\text{minimize}}
+& \underset{ k }{\text{minimize}}
 & & \gamma  \\
-& \text{subject to:} & & y(x)-z(x) < \gamma 
+& \text{subject to:} & & y^{\star}(k) \gamma^{-1} y(k) - z^{\star}(k)z(k) < 0 
 \end{aligned}
 \end{equation}
-where $y(x)$ and $z(x)$ are both convex functions of $x$ and $\{ \gamma \in \mathbb{R} : \gamma > 0\}$.
-This type of problem is convex-concave (due to the $-z(x)$ term); one solution to convexify this problem is to linearize $z(x)$ around an operating point $x_0$ and obtain the following optimization problem:
-
-\begin{equation} \label{eq:con_lin}
-\begin{aligned}
-& \underset{ x }{\text{minimize}}
-& & \gamma  \\
-& \text{subject to:} & & y(x)-\bigl[ \nabla z(x_0) \bigr]^{\top} (x-x_0) < \gamma 
-\end{aligned}
-\end{equation}
-where $\nabla z(x_0)$ is the gradient of $z(x)$ evaluated at $x_0$.
-
-The control methodology is based on minimizing a control objective in the $\mathcal{H}_\infty$ or $\mathcal{H}_2$ sense.
-In subsequent sections, it will be shown that these performance constraints will have the following quadratic form:
-
-\begin{equation} \label{eq:basic_ineq}
-y^{\star}(x) \gamma^{-1} y(x) - z^{\star}(x)z(x) < 0 
-\end{equation} 
-where $y(x)$ and $z(x)$ are complex affine functions of the decision variable $x$ and $(\cdot)^{\star}$ denotes the complex conjugate of the argument.
-Let $f(x) = z^{\star}(x)z(x)$ with $z(x)$ defined as
-$$z(x) = a_0 + a_1x_1 + a_2x_2 + ,\ldots , + a_nx_n$$
-where $z:\mathbb{R}^n \rightarrow \mathbb{C}$ and $f:\mathbb{R}^n \rightarrow \mathbb{R}$. A first order Taylor series of $f(x)$ around an operating point $x_0$ can be formulated as follows:
-
-\begin{equation} \label{eq:lin_fx}
-f(x) \approx f(x_0) + D_f(x_0)[x-x_0]
-\end{equation}
-where
-$$D_f(x_0) = \left[ \frac{\partial f(x)}{x_1}\Bigr|_{x=x_0}, \frac{\partial f(x)}{x_2}\Bigr|_{x=x_0},\ldots, \frac{\partial f(x)}{x_n}\Bigr|_{x=x_0}\right]$$
-
-Without loss of generality, it can be shown that the left-hand side of (\ref{eq:lin_fx}) will always be greater than or equal to the right-hand side, i.e.,
+where $y(k)$ and $z(k)$ are linear functions of the decision variable $k$ and $(\cdot)^{\star}$ denotes the complex conjugate of the argument.
+This type of problem is convex-concave (due to the $-z^{\star}(k)z(k)$ term).
+To convexify this constraint, the term $z^{\star}(k)z(k)$ can be linearized around an operating point $k_0$; without loss of generality, it can be shown that the linearization of $z^{\star}(k)z(k)$ leads to the following constraint:
 
 \begin{equation} \label{eq:lin_inequality}
-z^{\star}(x)z(x) \geq z^{\star}(x)z_0 + z(x)z_0^{\star} - z_0^{\star}z_0
+z^{\star}(k)z(k) \geq z^{\star}(k)z_0 + z(k)z_0^{\star} - z_0^{\star}z_0
 \end{equation} 
-
-where $z_0 = z(x_0)$. The condition in (\ref{eq:lin_inequality}) can easily be established by realizing the following inequality:
+where $z_0 = z(k_0)$. The condition in (\ref{eq:lin_inequality}) can easily be established by realizing the following inequality:
 
 \begin{equation}
-[z(x)-z_0]^{\star}[z(x)-z_0] \geq 0
+[z(k)-z_0]^{\star}[z(k)-z_0] \geq 0
 \end{equation}
-
-With this linearization, a sufficient condition for the inequality in (\ref{eq:basic_ineq}) can be developed as follows:
+With this linearization, a sufficient condition for the inequality in (\ref{eq:con_cav}) can be developed as follows:
 
 \begin{equation}
-y^{\star}(x) \gamma^{-1} y(x) - [z^{\star}(x)z_0 + z(x)z_0^{\star} - z_0^{\star}z_0]< 0 
+y^{\star}(k) \gamma^{-1} y(k) - [z^{\star}(k)z_0 + z(k)z_0^{\star} - z_0^{\star}z_0]< 0 
 \end{equation}
-
 By using the Shur Complement Lemma \cite{BEN09}, the above condition can be expressed in terms of a Linear-Matrix-Inequality (LMI):
@@
 \begin{bmatrix}
-z^{\star}(x)z_0 + z(x)z_0^{\star} - z_0^{\star}z_0 & \phantom{xx} y^{\star}(x) \\
-y(x) & \phantom{xx} \gamma
+z^{\star}(k)z_0 + z(k)z_0^{\star} - z_0^{\star}z_0 & \phantom{kk} y^{\star}(k) \\
+y(k) & \phantom{kk} \gamma
 \end{bmatrix}
@@
 \end{equation}
+This type of formulation will be used in the next section in order to construct a model reference control objective.
 
-This type of formulation will be used in section \ref{sec:loop_shape} in order to construct a loop-shaping constraint on the closed-loop FRF.
-
-\subsection{Control Performance}
-Since the control methods discussed in this paper are based on the $\mathcal{H}_\lambda$ criterion ($\lambda \in \{2,\infty \}$), it is appropriate to first define this criterion in the context of this work.
-A typical control objective is to design a controller such that the following constraint is satisfied:
-\begin{equation} \label{eq:WS_lt1}
-\| W \mathcal{S}\| < 1
-\end{equation}
-where $\mathcal{S}$ is the sensitivity function of interest, and $W$ is a stable weighting function such that $\| W \mathcal{S}\|$ is bounded.
-The norm considered in (\ref{eq:WS_lt1}) can be either the $\mathcal{H}_\infty$ or $\mathcal{H}_2$ norm.
-
+\subsection{Control Performance}  \label{sec:controlperformance}
 For SISO systems, and for a stable system $X(s)$, the $\mathcal{H}_2$ and $\mathcal{H}_\infty$ norms are defined as follows:
@@
 
-A loop-shaping criterion can also be considered as a form of control performance.
+A model reference criterion can be considered as a form of control performance.
 If $T$ is the closed-loop FRF and $T_d$ is the desired FRF, then one can consider minimizing $(T-T_d)$ in either the $\mathcal{H}_2$ or $\mathcal{H}_\infty$ sense in order to shape $T$.
-The next section will discuss how such an optimization problem can be formulated for this type of control methodology.
 
-\subsection{Loop-Shaping Design}
-\label{sec:loop_shape}
-As asserted in section \ref{sec:system}, the objective of this control problem is to shape the FRF of $T(k)$.
-Suppose that a desired loop-shape is specified as $T_d$; the objective is to design the controllers in $k$ such that the closed-loop system $T(k)$ coincides with $T_d$ in the $\mathcal{H}_\infty$ or $\mathcal{H}_2$ sense.
 In the $\mathcal{H}_\infty$ sense, the objective is to minimize $ \|T(k) - T_d \|_\infty$; an equivalent representation of this objective is to minimize $\gamma$ such that $ \|T(k) - T_d \|_\infty < \gamma$.
-This criterion is satisfied if the the following optimization problem is considered:
+This criterion is satisfied if the following optimization problem is considered:
 
@@
 w(k) &= G[1+k_u+C_m(k)] \\
-z(k) &= 1+G[H_1(k)+H_2(k)+C_m(k)]
+z(k) &= 1+G[H_1(k)+H_2(k)+e^{-j\omega \tau_{a}}P_2C_m(k)]
 \end{aligned}
@@
 where it is evident that $T(k) = w(k)z^{-1}(k)$; then the constraint in (\ref{eq:min_loopshape}) can be written as:
+$$
+\bigl[w(k)-z(k)T_d \bigr]^{\star}\gamma^{-1} \bigl[w(k)-z(k)T_d \bigr] - z^{\star}(k)z(k)<0
+$$
 
-\begin{equation}
-\bigl[w(k)-z(k)T_d \bigr]^{\star}\gamma^{-1} \bigl[w(k)-z(k)T_d \bigr] - z^{\star}(k)z(k)<0
-\end{equation}
-
-Note that this constraint has the exact form as in (\ref{eq:basic_ineq}); therefore, the convex constraint in (\ref{eq:LMI_1}) can be utilized to construct the loop-shaping optimization problem as follows:
-
+Note that this constraint has the exact form as in (\ref{eq:con_cav}); therefore, the convex constraint in (\ref{eq:LMI_1}) can be utilized to construct the model-reference optimization problem as follows:
 \begin{equation} \label{eq:loop_shape_LMI_inf}
@@
 \end{equation}
-for all $\omega \in \Omega$, where $z_0 = 1+G[H_1(k_0) + H_2(k_0)+C_m(k_0)]$ and $k_0 =[k_{i,0},k_{u,0},k_{m_1,0},k_{m_2,0}  ]$ are the initializing gains.
+for all $\omega \in \Omega$, where $$z_0 = 1+G[H_1(k_0) + H_2(k_0)+e^{-j\omega \tau_{a}}P_2C_m(k_0)]$$ and $k_0 =[k_{i,0},k_{u,0},k_{m_1,0},k_{m_2,0}  ]$ are the initializing gains.
+
 In a similar manner, the following convex optimization problem can be considered for minimizing  $ \|T(k)- T_d \|_2^2$, as follows:
-
 \begin{equation} \label{eq:loop_shape_LMI_2}
@@
 \textit{Note that the choice of the initializing gains in $k_0$ may affect the stability of the closed-loop system (for either the optimization problems concerning the $\mathcal{H}_\infty$ or $\mathcal{H}_2$ norms).
-The next section will discuss how to select these gains in order to ensure stability.
-\\
-Additionally, note that these optimization problems are considering the gains for $C_m(k)$; however, once an optimal solution is obtained for the controllers in $k$, then the definitions in (\ref{eq:new_var}) can be used to revert back to the original gains (i.e., $k_{p_1}$ and $k_{p_2}$.)}
+}
 \end{remark}
 
+The next section will discuss how to select these gains in order to ensure stability.
+
 \subsection{Stability Analysis}
-The loop-shaping constraints developed in the previous section do not guarantee the closed-loop stability of the closed-loop system.
+The model reference constraints developed in the previous section do not guarantee the stability of the closed-loop system.
 Setting a desired FRF to shape a closed-loop FRF is analogous to bounding the closed-loop FRF; it can be shown that unstable systems can still possess bounded FRF's.
 
-The initializing controllers in $k_0$ play an important role in guaranteeing the stability of the closed-loop system.
-By using the Nyquist criterion for continuous-time systems, the stability of the closed-loop system can be ensured if certain conditions are met for these initializing gains.
+The initializing controller gains in $k_0$ play an important role in guaranteeing the stability of the closed-loop system.
+By using the Nyquist criterion, the stability of the closed-loop system can be ensured if certain conditions are met for these initializing gains.
+In this paper, it is assumed that the Nyquist contour has some small detours around the poles of the open-loop system on the imaginary axis.
+
+\iffalse
 Let us first recall the Nyquist stability criterion with the following Lemma:
@@
 \end{lemma}
-Note that in this Nyquist stability criterion, the term $GC$ refers to the open-loop system.
-In this paper, it is assumed that the Nyquist contour has some small detours around the poles of $G$ and $C$ on the imaginary axis.
+\fi
 
@@
 \begin{definition}
-Let \emph{wno}$\{ A(s)\}$ refer to the winding number; in the counterclockwise sense, \emph{wno}$\{ A(s)\}$ represents the image of $A(s)$ around the origin when $s$ traverses the Nyquist contour (with small detours around the poles of $A(s)$ on the imaginary axis).
+Let \emph{wno}$\{ A(s)\}$ refer to the winding number around the origin, in the counterclockwise sense, of the image of $A(s)$  when $s$ traverses the Nyquist contour (with small detours around the poles of $A(s)$ on the imaginary axis).
 Then the following properties hold:
@@
 \end{definition}
-
-The open-loop FRF of the system $T(k)$ in Fig.~\ref{fig:damping_loop} is given as $$L(k) = G[H_1(k)+H_2(k)+C_m(k)].$$ Let $F(k) = H_1(k)+H_2(k)+C_m(k)$ such that $L(k) = GF(k)$; by the Nyquist stability criterion, the closed-loop system is stable if and only if $1+GF$ makes $n_{G}+n_F$ counter-clockwise encirclements of the origin (where $n_{G}$ and $n_F$ are, respectively, the number of RHP poles of $G$ and $F$).
+The open-loop FRF of the system $T(k)$ in Fig.~\ref{fig:damping_loop} is given as $$L(k) = G[H_1(k)+H_2(k)+e^{-j\omega \tau_{a}}P_2C_m(k)].$$ Let $F(k) = H_1(k)+H_2(k)+e^{-j\omega \tau_{a}}P_2C_m(k)$ such that $L(k) = GF(k)$; by the Nyquist stability criterion, the closed-loop system is stable if and only if $1+GF$ makes $n_{G}+n_F$ counter-clockwise encirclements of the origin (where $n_{G}$ and $n_F$ are, respectively, the number of right-half plane (RHP) poles of $G$ and $F$).
 The Nyquist plot of $1+GF$ must also not pass through the origin.
@@
 \begin{split}
-z^{\star}(k)z_0+z_0^{\star}z(k) > 0 \\
+z^{\star}(k)z_0+z_0^{\star}z(k) > 0 \qquad 
 \forall \omega \in \Omega
@@
 \begin{align*}
-z(k) &= 1+G[H_1(k)+H_2(k)+C_m(k)] \\
-z_0 &= 1+G[H_1(k_0)+H_2(k_0)+C_m(k_0)]
+z(k) &= 1+G[H_1(k)+H_2(k)+e^{-j\omega \tau_{a}}P_2C_m(k)] \\
+z_0 &= 1+G[H_1(k_0)+H_2(k_0)+e^{-j\omega \tau_{a}}P_2C_m(k_0)]
 \end{align*}
-with $\{G,H_1,H_2\} \in \mathscr{S}$. Then the closed-loop system $T$ is stable if the parameters in the set $k_0$ are stabilizing initial gains.
+with $\{G,H_1,H_2,P_2\} \in \mathscr{S}$. Then the closed-loop system $T$ is stable if the parameters in the set $k_0$ are stabilizing initial gains.
 \end{theorem}
@@
 \end{equation}
-where $F(k_0) = H_1(k_0) + H_2(k_0) + C_m(k_0)$.
+where $F(k_0) = H_1(k_0) + H_2(k_0) + e^{-\tau_{a}s}P_2 C_m(k_0)$.
 Note that $F(k)$ is strictly proper and $GF(k)$ is strictly proper; therefore, the winding number of $z^{\star}(k)z_0$ can be evaluated over $\Omega$ instead of the $D$-contour.
@@
 
-\subsection{Initializing Controller}
 For the given structure in Figure.~\ref{fig:damping_loop}, it remains to be shown how to select the initial stabilizing controllers in order to guarantee the stability of the closed-loop system.
-From the control structure of the power converter control system, it can be observed that if all the gains in Figure.~\ref{fig:damping_loop} are set to zero, then the system will be in open-loop.
-However, since $G \in \mathscr{S}$, then selecting $k_0 = 0$ will guarentee the stability of the closed-loop system.
-
-If the initializing controllers are selected such that the performance with these controllers is far from the desired performance, then it is possible that either the optimization problem yields no feasible solution, or that the solver runs into numerical problems (which leads to infeasible solutions).
-One method to resolve this problem is to apply relaxation techniques where a relaxed optimization problem is solved; the solution to the relaxed problem can then be used as the initializing controllers for the non-relaxed problem.
+From the control structure of the power converter control system, it can be observed that if all the controller gains in Figure.~\ref{fig:damping_loop} are set to zero, then the system will be in open-loop.
+However, since $G \in \mathscr{S}$, then selecting $k_0 = 0$ will guarantee the stability of the closed-loop system.
 
 \subsection{Convex Optimization via Semi-Definite Programming}
-All of the optimization problems considered in section \ref{sec:loop_shape} are known as semi-infinite programming (SIP) problems since there are a finite number of optimization variables $k$ and an infinite number of constraints with respect to $\omega$.
+All of the optimization problems considered in Section \ref{sec:controlperformance} are known as semi-infinite programming (SIP) problems since there are a finite number of optimization variables $k$ and an infinite number of constraints with respect to $\omega$.
 To solve any of these problems, the optimization algorithm can be converted to a semi-definite programming (SDP) problem.
@@
 \label{sec:case}
-The focus of this case study will be on the SATURN power converter, which incorporates the control methodology shown in Figure.~\ref{fig:damping_loop} and uses the filter shown in Figure.~\ref{fig:circuit}.
+The focus of this case study will be on the SATURN power converter, which incorporates the control structure shown in Figure.~\ref{fig:damping_loop} and uses the power converter with the architecture shown in Figure.~\ref{fig:circuit}.
 The SATURN converter is used in the Large Hardron Collider, in injector machines, in experimental areas to power warm magnets, and for DC or pulsed applications.
-In this power converter, a $18\:kV/50\:Hz$ transformer is used with a diode rectifier and a DC-Link filter for the AC/DC conversion.
-An IGBT bridge (4 quadrant operation) is then used for a DC/DC conversion, and the output of this bridge is then fed into the filter (i.e, $v_i$ in Fig.~\ref{fig:circuit}).
-For this application, two identical modules are assembled in series (which doubles the output voltage) where the equivalent switching frequency of this bridge is $5 \: kHz$.
-A schematic of the SATURN modules are shown in Fig.~ \ref{fig:schematic}.
-A complete assembly of the SATURN power converter is shown in Fig.~\ref{fig:saturn_pc} while the load (i.e., the magnet) is shown in Fig.~\ref{fig:load}.
+In this power converter, a 18 kV$/$50 Hz transformer is used with a diode rectifier and a DC-Link filter for the AC/DC conversion.
+An IGBT bridge (4 quadrant operation) is then used for a DC/DC conversion, and the output of this bridge is then fed into the filter.
+For this application, two identical modules are assembled in series (which doubles the output voltage) where the equivalent switching frequency of this bridge is 5 kHz.
+A complete assembly of the SATURN power converter is shown in Fig.~\ref{fig:saturn_pc}.
+Table.~\ref{tab:specs} displays the values of the system characteristics of this power converter.
 
@@
 \centering
-\caption{My caption}
-\label{my-label}
+\caption{System characteristics of SATURN power converter}
+\label{tab:specs}
 \begin{tabular}{c|c|c}
@@
 Transformer Weight                                                             & $4500$                     & kg    \\ \hline
+DSP sampling rate                                                             & $5000$                     & Hz    \\ \hline
 Control Type                                                                   & RegFGC3 Type 10 / Ethernet \cite{CKS11} & $-$  
@@
 \end{table}
-
-\begin{figure}
-\centering
-\includegraphics[width=\columnwidth]{../pics/schematic}
-\caption{Schematic of the SATURN modules assembled in series.}
-\label{fig:schematic}
-\end{figure}
 
@@
 
+\iffalse
 \begin{figure}
@@
 \end{figure} 
+\fi
 
 \subsection{Frequency Response Measurement}
-Since the proposed method uses a data-driven methodology with frequency-domain data, the FRF of each subsystem within the power converter control system must be obtained.
-In other words, we must obtain the FRF of $G$, $H$, $P_1$, and $P_2$.
-The signals that are accessible for the measurements are the inputs to the capacitor banks ($U_{dc}$ in Fig.~\ref{fig:schematic}, which is approximately equal to $v_r$ in Fig.~\ref{fig:damping_loop}), and the outputs of the sensors $P_1$ and $P_2$.
-Therefore, when all of the controller gains are set to zero, we are able to obtain the frequency responses of $GHP_1$ and $GP_2$.
-However, note that $G$ appears independently of $P_2$ in (\ref{eq:Tclp}) and (\ref{eq:Tcl}); since $P_1$ and $P_2$ are sensors with very high bandwidths relative to $G$ (approximately $10 \: kHz$), then $G \approx GP_2$  at frequencies less than $1 \: kHz$.
+Since the proposed method is based on a data-driven methodology with frequency-domain data, the FRF of each subsystem within the power converter control system must be obtained.
+In other words, we must obtain the FRF of $G$, $H$, $P_1$, $P_2$, and the ADCs.
+The signals that are accessible for the measurements are shown in Fig.~\ref{fig:damping_loop}, which are the outputs of the sensors $P_1$ and $P_2$ and the input of the converter control system (which goes into an ADC).
+However, note that $G$ appears independently of $P_2$ in (\ref{eq:Tclp}) and (\ref{eq:Tcl}); since $P_1$ and $P_2$ are sensors with very high bandwidths relative to $G$ (approximately 10 kHz), then $G \approx GP_2$  at frequencies less than 1 kHz.
+The FRF of the ADCs in the control loop are not measured since the output of these ADCs are digital signals.
+As stated in section \ref{sec:system}, these ADCs can be considered as pure time delays; since these delays are known to be within specific ranges, a multi-model design can be formulated to incorporate this uncertainty in the design.
 
@@
 \includegraphics[width=\columnwidth]{../pics/G.eps}
-\caption{Frequency response measurement from the input of the capacitor banks to the output of sensor $P_2$ (with all controller gains set to zero).}
+\caption{Frequency response measurement of $GP_2$.}
 \label{fig:G}
@@
 \includegraphics[width=\columnwidth]{../pics/GHP1.eps}
-\caption{Frequency response measurement from the input of the capacitor banks to the output of sensor $P_1$ (with all controller gains set to zero).}
+\caption{Frequency response measurement of $GHP_1$.}
 \label{fig:GHP1}
@@
 \subsection{Controller Synthesis}
-For this application, it was desired to shape $T^{\prime}(k)$ and $T(k)$ such that a bandwidth of $300 \: Hz$ and $500 \: Hz$ is attained, respectively (where both achieve a damping of $\zeta = 0.8$).
+For this application, it was desired to shape $T^{\prime}(k)$ and $T(k)$ such that a bandwidth of 300 Hz and 500 Hz is attained, respectively (where both achieve a damping of $\zeta = 0.8$).
 Note that in both of these TF's, a pure delay appears in the numerator; therefore, the performance of the loop-shape algorithm can be improved by specifying a desired loop-shape $T_d(s) = T_d^*(s) e^{-s\tau}$ where $T_d^*(s)$ was selected as a standard second order process, i.e.,
@@
 
-Although the delay in $G$ was captured in the frequency response measurement, it is known that there also exists an additional measurement delay $\tau_e$ that was not captured in the identification experiment.
-This delay occurs after digitization of the analog signals at the outputs of $P_1$ and $P_2$ (when the system is operating in closed-loop mode).
-The value of the delay is uncertain and is known to be in the range of $\tau_e \in [0,30]\mu s$.
+Although the delay $\tau$ from the power electronics was captured in the frequency response measurement, the delay $\tau_{a}$ from the ADCs in the control loop was not.
+However, the output of the TFA includes an ADC which is captured in the experiment, an ADC that is not present during normal operation.
+Therefore the difference of these delays should be considered in the controller synthesis.
+The value of this delay is uncertain and is known to be in the range of $\tau_{a} \in [0,30]\mu s$.
 Therefore, a multi-model design can be considered where the additional delay can be gridded in this range and incorporated into the closed-loop TF's.
-The grid was established in intervals of $5 \: \mu s$ (i.e., $\tau_{e_i} = [0,5,\ldots30] \mu s$, $i = 1,\ldots,7$).
+The grid was established in intervals of $5 \: \mu s$ (i.e., $\tau_{a_i} = [0,5,\ldots30] \mu s$, $i = 1,\ldots,7$).
 
@@
 \end{equation}
-where $T_i(k)$ and $T_i^{\prime}(k)$ are the closed-loop TF's that incorporate the additional $i$-th delay in $\tau_{e_i}$; $T_d$ is the desired closed-loop TF for loop-shaping $T(k)$ (with a desired bandwidth of $f_d = 500 \: Hz$ and damping $\zeta = 0.8$); $T_d^{\prime}$ is the desired closed-loop TF for loop-shaping $T^{\prime}(k)$ (with a desired bandwidth of $f_d^{\prime} = 300 \: Hz$ and damping $\zeta^{\prime} = \zeta$).
+where $T_i(k)$ and $T_i^{\prime}(k)$ are the closed-loop TF's that incorporate the additional $i$-th delay in $\tau_{a_i}$; $T_d$ is the desired closed-loop TF for shaping $T(k)$ (with a desired bandwidth of $f_d = 500$ Hz and damping $\zeta = 0.8$); $T_d^{\prime}$ is the desired closed-loop TF for shaping $T^{\prime}(k)$ (with a desired bandwidth of $f_d^{\prime} = 300$ Hz and damping $\zeta^{\prime} = \zeta$).
 In the $\mathcal{H}_2$ sense, the optimization problem to consider is as follows:
@@
 \end{equation}
-These optimization problems can be transformed to convex problems by implementing the methods outlined in section \ref{sec:loop_shape}. 
+These optimization problems can be transformed to convex problems by implementing the methods outlined in Section \ref{sec:controlperformance}. 
 \subsection{Experimental Results}
@@
 Since the transfer function analyzer provides the gain and phase at discrete frequency points, the optimization problem then becomes an SDP problem.
-For solving the $\mathcal{H}_2$ problem in SDP form, the objective function in (\ref{eq:case_study_opt_2}) must be discretized where $\int \gamma(\omega) d\omega \rightarrow \sum_i \gamma(\omega_i)$.
+For solving the $\mathcal{H}_2$ problem in SDP form, the objective function in (\ref{eq:case_study_opt_2}) must be discretized where $\int \gamma(\omega) d\omega \rightarrow \sum_i \gamma_i$.
 
 For comparative purposes, controllers were designed by considering the model of the process.
-Since there is uncertainty associated with the delay $\tau$, a multi-model approach can be implemented to ensure that the performance is attained for the uncertain values.
-Therefore, for the model-based design, the problem in (\ref{eq:case_study_opt}) and (\ref{eq:case_study_opt_2}) was solved by gridding in both $\tau$ and $\tau_e$.
+Since there was uncertainty associated with the delay $\tau$, a multi-model approach was implemented to ensure that the performance was attained for the uncertain values.
+Therefore, for the model-based design, the problem in (\ref{eq:case_study_opt}) and (\ref{eq:case_study_opt_2}) was solved by gridding in both $\tau$ and $\tau_{a}$.
 
-Fig.~\ref{fig:d_loop} shows the closed-loop frequency response of $|T^{\prime}(j\omega)|$ while Fig.~\ref{fig:v_loop} shows the closed-loop frequency response of $|T(j\omega)|$ for the solutions obtained by minimizing both the $\mathcal{H}_{\infty}$ and $\mathcal{H}_2$ norms of the process.
-From these figures, it can be observed that the model-based design produces the worst performance while the data-driven based design achieves the desired performance for both $T(j\omega)$ and $T^{\prime}(j\omega)$.
+The closed-loop frequency response of $|T^{\prime}|$ and $|T|$ are shown in Fig.~\ref{fig:d_loop} and Fig.~\ref{fig:v_loop} (respectively) for the solutions obtained by minimizing both the $\mathcal{H}_{\infty}$ and $\mathcal{H}_2$ norms of the process.
+From these figures, it can be observed that the model-based design produces the worst performance while the data-driven based design achieves the desired performance for both $T$ and $T^{\prime}$.
 The performance achieved by the data-driven method (in both the $\mathcal{H}_{\infty}$ and $\mathcal{H}_2$ minimization cases) are comparable.
@@
 \includegraphics[width=\columnwidth]{../pics/d_loop_mag.eps}
-\caption{The closed-loop response of $|T^{\prime}(j\omega)|$; data-driven method with $\mathcal{H}_{\infty}$ performance (red line); data-driven method with $\mathcal{H}_2$ performance (blue line); model-based approach with $\mathcal{H}_2 / \mathcal{H}_\infty$ performance (yellow line); $-3 \: dB$ point representing $300 \: Hz$ bandwidth (dashed-black line).}
+\caption{The closed-loop response of $|T^{\prime}|$; data-driven method with $\mathcal{H}_{\infty}$ performance (red line); data-driven method with $\mathcal{H}_2$ performance (blue line); model-based approach with $\mathcal{H}_2 / \mathcal{H}_\infty$ performance (yellow line); -3 dB point representing 300 Hz bandwidth (dashed-black line).}
 \label{fig:d_loop}
@@
 \includegraphics[width=\columnwidth]{../pics/v_loop_mag.eps}
-\caption{The closed-loop response of $|T(j\omega)|$; data-driven method with $\mathcal{H}_{\infty}$ performance (red line); data-driven method with $\mathcal{H}_2$ performance (blue line); model-based approach with $\mathcal{H}_2 / \mathcal{H}_\infty$ performance (yellow line); $-3 \: dB$ point representing $500 \: Hz$ bandwidth (dashed-black line).}
+\caption{The closed-loop response of $|T|$; data-driven method with $\mathcal{H}_{\infty}$ performance (red line); data-driven method with $\mathcal{H}_2$ performance (blue line); model-based approach with $\mathcal{H}_2 / \mathcal{H}_\infty$ performance (yellow line); -3 dB point representing $500$ Hz bandwidth (dashed-black line).}
 \label{fig:v_loop}
@@
 A frequency-domain approach has been used in order to avoid the problem of unmodeled dynamics associated with parametric models.
-A non-convex loop-shaping constraint was convexified by linearizing the non-convex function around a stabilizing operating point.
+A non-convex model reference constraint was convexified by linearizing the non-convex function around a stabilizing operating point.
 This linearization process allowed the use of the Shur Complement Lemma to construct an LMI and solve a convex optimization problem.
@@
 The experiments have confirmed that the data-driven approach significantly reduces the conservativeness associated with the modeling process.
-For future work, it will be desired to develop a method that ensures feasibility (given a set of initializing controllers) without applying relaxation techniques.
+For future work, it will be desired to develop a method (in a data-driven sense) that will implement a search algorithm such that the global optimal solution to the $\mathcal{H}_{\infty}$ problem can be obtained.
 

### 2017-02-27 Papers/Nonlinear Optimization/Latex/Draft/Draft.tex
updated files

--- 2017-02-14 Papers/Nonlinear Optimization/Latex/Draft/Draft.tex
@@
 \begin{abstract}
-In this paper, a new frequency-domain method for designing robust controllers is proposed that provides optimal $\mathcal{H}_{\infty}$ performance.
-A nonlinear optimization problem is formulated which guarantees the stability of the closed-loop system whilst ensuring robust performance.
-It is shown that the optimal solution to the $\mathcal{H}_\infty$ problem is attained for a fixed-structure controller without any conservatism.
-A convexified version of the $\mathcal{H}_{\infty}$ criterion has been established in many works and have utilized a similar frequency gridding process; therefore, it is of interest to determine the definiteness of the solution produced by this convex optimization method with respect to the solution of the optimal $\mathcal{H}_{\infty}$ problem proposed in this work.
+In this paper, a new data-driven method for designing robust controllers is proposed that provides $\mathcal{H}_{\infty}$ performance.
+A nonlinear optimization problem is formulated which optimizes the parameters of the fixed-structure controller basis function and guarantees the stability of the closed-loop system whilst ensuring robust performance.
+It is shown that by optimizing the controller basis function parameters, the $\mathcal{H}_\infty$ performance can be significantly improved (without any conservatism).
+A convexified version of the $\mathcal{H}_{\infty}$ criterion has been established in many works and have utilized a similar frequency gridding process; therefore, it is of interest to determine the definiteness of the solution produced by this convex optimization method with respect to the solution of the $\mathcal{H}_{\infty}$ formulation proposed in this work.
+The simulation examples illustrate how the proposed method can be used to eliminate the sensitivity associated with the controller basis function parameters and optimize the system performance.
 \end{abstract}
@@
 \section{Introduction}
-The uncertainties associated with many of today's complex systems pose challenging tasks for engineers and researchers within the control systems community.
-These uncertainties can cause performance degradations and stability problems that may lead to catastrophic events.
-Robust controller design methods seek to rectify this issue by designing controllers that ensure proper stability margins whilst maintaining suitable performance.
+Due to the significant technological advances in the control systems industry, controller design schemes for practical applications are becoming less trivial.
+In order to simplify the design process, systems are approximated with low-order models in order to reduce the complexity of the design strategy.
+However, this approximation can lead to stability and performance degradations since these low-order models are subject to model uncertainty.
+The data-driven control strategy mitigates the problems associated with the model based controller design since the data-driven scheme avoids the problem of unmodeled dynamics associated with low-order parameteric models.
+A survey on the differences between the model-based control and data-driven control schemes has been addressed in \cite{HW13} and \cite{FK13a}.
+The data-driven controller design methodology can be realized in two manners: using time-domain or frequency-domain data.
+In this paper, the frequency-domain approach will be utilized for the controller design scheme.
+It is important to note that the term ``data-driven"  in this paper signifies that the controller synthesis is independent of the parametric model of the process.
+In other words, controllers are synthesized by only using the frequency response of the process.
 
-The robust controller design methodology can be realized in two manners: using time-domain or frequency-domain data.
-In this paper, the frequency-domain approach will be utilized for the controller design scheme.
-In a data-driven setting, this frequency domain approach can be used to avoid unmodeled dynamics associated with parametric models.
-A survey on the differences associated with model-based control and data-driven control has been addressed in \cite{HW13} and \cite{BCE12}.
-The authors in \cite{HDAV10} use the frequency response data of a stable system to design an optimal controller through a symmetric root locus technique.
+%The authors in \cite{HDAV10} use the frequency response data of a stable system to design an optimal controller through a symmetric root locus technique.
 A robust frequency-domain control design method has been established in \cite{KNND13b} that requires a solution to a non-linear optimization problem.
@@
 Robust controller design methods belonging to the $\mathcal{H}_{\infty}$ control framework minimizes the $\mathcal{H}_{\infty}$ norm of a weighted closed-loop sensitivity function.
+This minimization is usually accomplished by formulating an optimization problem; the main concern in solving this optimization problem is convexity and ensuring closed-loop stability.
 Solving the $\mathcal{H}_{\infty}$ problem can be accomplished in a variety of manners.
+For fixed-structure controllers, many works use linearly parameterized (LP) controllers in order to convexify the $\mathcal{H}_{\infty}$ problem and ensure that a global solution is obtained.
 A convex approximation of the $\mathcal{H}_\infty$ criterion has been discussed in \cite{KG10} and \cite{KGL08} where convex constraints are imposed on the Nyquist diagram.
-The problem is convexified by constructing a linearly parameterized controller and devising linear constraints with respect to a desired open-loop transfer function.
-A frequency-domain approach for computing low-order multivariable linearly parameterized controllers is presented in \cite{SOW10}.
+The problem is convexified by constructing a LP controller and devising linear constraints with respect to a desired open-loop transfer function.
+A frequency-domain approach for computing low-order multivariable LP controllers is presented in \cite{SOW10}.
 The $\mathcal{H}_{\infty}$ constraints are convexified around an initial stabilizing controller.
@@
 More recent works that implement an iterative loop-shaping method that ensures $\mathcal{H}_{\infty}$ performance have been devised in \cite{UYY16} and \cite{KK16}.
-These methods use the concepts from \cite{BHA16} to linearize non-convex constraints around an operating point.
+These methods use the concepts from \cite{BHA16} to linearize non-convex constraints around an operating point and implement LP controllers to ensure convexity.
 
-In some of the works asserted above, it has been proved that a convex approximation of the $\mathcal{H}_{\infty}$ problem yields favorable results; however, these approximations do not yield the true global optimal solution to the $\mathcal{H}_{\infty}$ problem.
-This paper presents an extension of the work in \cite{KNZ16}, and its purpose is to devise a new frequency-domain approach for obtaining the optimal solution to the $\mathcal{H}_{\infty}$ problem.
-In \cite{KNZ16}, it was shown that the optimal solution is obtained when the order of the controller increases to infinity; in the proposed method, the optimal solution can be obtained for a fixed low-order fully-parameterized controller (which has desirable practical implications).
+In some of the works asserted above, it has been proved that a convex approximation of the $\mathcal{H}_{\infty}$ problem yields favorable results; however, the linear parameterization process limits the performance of these control systems since it is unknown a priori which controller basis function optimizes the performance.
+For certain applications, the selection of the fixed-structure basis function can be sensitive to both the order and the free parameters of the basis function (such as the Laguerre parameter in the basis function presented in \cite{KNZ16}).
+This paper presents an extension of the work in \cite{KNZ16}, and its purpose is to devise a new data-driven approach for improving the performance associated with the $\mathcal{H}_{\infty}$ problem.
+In \cite{KNZ16}, it was shown that by solving a convex optimization problem, the optimal solution is obtained when the order of the controller increases to infinity.
+In the proposed method, the solution can be improved for a fixed structure low-order fully-parameterized controller (which has desirable practical implications) by formulating non LP controllers where the basis function parameters are optimized.
 A nonlinear optimization problem is formulated to guarantee stability of the closed-loop system while ensuring robust performance (without any approximation).
-Additionally, it will be shown that the proposed method produces a solution that converges to the global optimal solution of the $\mathcal{H}_{\infty}$ problem under certain conditions.
 A preset frequency grid will be used to satisfy the robust performance condition and solve for a finite number of constraints.
@@
 \begin{equation} \label{eq:Laguerre}
-\phi_{\{x,y\}_1}(s)=1,\quad \phi_{\{x,y\}_q}(\bm{\rho},s) = \frac{\sqrt{2 \rho_c}(s-\rho_c)^{q-2}}{(s+\rho_c)^{q-1}}
+\phi_{\{x,y\}_1}(s)=1,\ \phi_{\{x,y\}_q}(\bm{\rho},s) = \frac{\sqrt{2 \rho_{\{x,y \}}^c}\left(s-\rho_{\{x,y \}}^c\right)^{q-2}}{\left(s+\rho_{\{x,y \}}^c\right)^{q-1}}
 \end{equation}
-for $q = 2,\ldots,\{n_x,n_y\}$, where $\rho_c \in \mathbb{R}_+$. For discrete-time systems, the Laguerre basis function can be expressed as follows:
+for $q = 2,\ldots,\{n_x,n_y\}$, where $\rho_{\{x,y \}}^c \in \mathbb{R}_+$.
+The subscript $\{x,y \}$ is used to represent the basis function for the controller $X(\bm{\rho},s) $ or $Y(\bm{\rho},s) $.
+For discrete-time systems, the Laguerre basis function can be expressed as follows:
 \begin{equation} \label{eq:Laguerre_z}
-\phi_{\{x,y\}_1}(z)=1,\quad \phi_{\{x,y\}_q}(\bm{\rho},z) = \frac{\rho_d^*(1-\rho_d z)^{q-2}}{(z-\rho_d)^{q-1}}
+\phi_{\{x,y\}_1}(z)=1,\quad \phi_{\{x,y\}_q}(\bm{\rho},z) = \frac{\rho_{\{x,y \}}^*\left(1-\rho_{\{x,y \}}^d z\right)^{q-2}}{\left(z-\rho_{\{x,y \}}^d\right)^{q-1}}
 \end{equation}
-where $\rho_d^* = \sqrt{1-\rho_d^2}$ and $\{\rho_d \in \mathbb{R}: -1 < \rho_d < 1\}$.
-Note that when $\rho_d = 0$, the discrete-time Laguerre basis function becomes a simple finite-impulse response (FIR) filter.
+where $\rho_{\{x,y \}}^* = \sqrt{1-(\rho_{\{x,y \}}^d)^2}$ and $$\{\rho_{\{x,y \}}^d \in \mathbb{R}: -1 < \rho_{\{x,y \}}^d < 1\}$$ Note that when $\rho_{\{x,y \}}^d = 0$, the discrete-time Laguerre basis function becomes a simple finite-impulse response (FIR) filter.
 
@@
 \begin{aligned} \label{eq:S}
-S(s) &:= e/r =[1+L(\bm{\rho},s)]^{-1} \\ &=  M(s)Y(\bm{\rho},s)[N(s)X(\bm{\rho},s)+M(s)Y(\bm{\rho},s)]^{-1}\\
+S(s) &:= e(s)/r(s) =[1+L(\bm{\rho},s)]^{-1} \\ &=  M(s)Y(\bm{\rho},s)[N(s)X(\bm{\rho},s)+M(s)Y(\bm{\rho},s)]^{-1}\\
 \end{aligned}
@@
 \begin{aligned} \label{eq:T}
-T(s) &:= y/r =L(\bm{\rho},s)[1+L(\bm{\rho},s)]^{-1} \\ &=  N(s)X(\bm{\rho},s)[N(s)X(\bm{\rho},s)+M(s)Y(\bm{\rho},s)]^{-1}\\
+T(s) &:= y(s)/r(s) =L(\bm{\rho},s)[1+L(\bm{\rho},s)]^{-1} \\ &=  N(s)X(\bm{\rho},s)[N(s)X(\bm{\rho},s)+M(s)Y(\bm{\rho},s)]^{-1}\\
 \end{aligned}
 \end{equation}
-where $L(\bm{\rho},s) = G(s)K(\bm{\rho},s)$; $r$ is the reference input; $y$ is the system output; $e$ is the tracking error signal (i.e., $e = r-y$).
+where $L(\bm{\rho},s) = G(s)K(\bm{\rho},s)$; $r(s)$ is the frequency function of the reference input; $y(s)$ is the frequency function of the system output; $e(s)$ is the frequency function of the tracking error signal (i.e., $e(s) = r(s)-y(s)$).
 From the above definitions of the sensitivity functions, it can be observed that $S(s)+T(s)=1$.
@@
 \subsection{Optimal $\mathcal{H}_{\infty}$ Performance}
+In order to preserve the convexity of the $\mathcal{H}_{\infty}$ problem (with fixed-structure controllers), it is necessary to invoke linearly parameterized controllers that contain basis functions with fixed values (as asserted by the various works mentioned in the Introduction).
+For example, the problem in (\ref{eq:convex_con}) is convex only if $X(\bm{\rho})$ and $Y(\bm{\rho})$ are linearly parameterized.
+Therefore, the value of $\rho_c$ in the Laguerre basis functions (\ref{eq:Laguerre}) must be fixed a priori.
+The solution to the convex problem guarantees a global solution; however, the solution may not be the optimal global solution to the \textit{convex problem} since the the Laguerre parameter is not optimized.
+
 In \cite{KNZ16}, it is shown that when the orders of $X(\bm{\rho})$ and $Y(\bm{\rho})$ approach infinity, then $\gamma$ from (\ref{eq:convex_con}) approaches the optimal solution to the $\mathcal{H}_{\infty}$ problem.
@@
 \end{equation}
-where $F(\bm{\rho})$ can be chosen such that it incorporates the Laguerre basis functions defined in (\ref{eq:Laguerre}), i.e.,
+Note that $F(\bm{\rho}) $ must be a stable basis function (as asserted in Lemma.\ref{lem1}) in order to ensure that the closed-loop system is stable.
+Therefore, $F(\bm{\rho})$ can be chosen such that it incorporates the Laguerre basis functions defined in (\ref{eq:Laguerre}), i.e.,
 \begin{equation} \label{eq:Laguerre_sum_c}
@@
 \end{equation}
-where $\rho_o \in \mathbb{R}_+$.
-It should be noted that the optimal solution to the $\mathcal{H}_\infty$ problem is achieved when $K(\bm{\rho}) = X(\bm{\rho})Y^{-1}(\bm{\rho})$ has the same structure as the optimal controller.
-However, if the structure of the optimal controller is unknown a priori, then one can simply fix the order of the basis $F(\bm{\rho})$ and vary the orders of the controllers $X(\bm{\rho})$ and $Y(\bm{\rho})$ until $\gamma$ converges to a constant value.
-The concept of this method will be shown in one of the examples in section \ref{sec:sim}.
+where $\rho_o \in \mathbb{R}_+$. A similar representation can be made for discrete-time systems (i.e., using the Laguerre basis functions in (\ref{eq:Laguerre_z})).
 
+\iffalse
 It will now be shown that the solution to the optimization problem in (\ref{eq:opt_true}) converges monotonically to the optimal solution of the $\mathcal{H}_\infty$ problem as the order of $F(\bm{\rho})$ increases.
@@
 
+\fi
 Note that the constraint in the optimization problem (\ref{eq:opt_true}) is not convex and a non-linear optimization algorithm will need to be implemented in order to solve this problem.

### 2017-02-27 Papers/Loop Shaping Voltage Loop (CERN)/Latex/Draft_2/Draft_2.tex
updated files

@@
 H_1(k) &:= k_iP_1H;  &H_2(k) &:= k_uP_2e^{-j\omega \tau_{a}} \\
-G &:= G_0e^{-j\omega\tau}; &C_m(k) &:= k_{m_1}+k_{m_2}\frac{t_se^{-j\omega}}{1-e^{-j\omega}}\\ 
+H_3(k) &:=  P_2C_m(k)e^{-j\omega\tau_{a}}; &G &:= G_0e^{-j\omega\tau} \\ 
 \end{aligned}
 \end{equation}
+\begin{equation*}
+C_m(k) := k_{m_1}+k_{m_2}\frac{t_se^{-j\omega}}{1-e^{-j\omega}}
+\end{equation*}
 where $k = [k_i,k_u,k_{m_1},k_{m_2}]$.
@@
 T^{\prime}(k) &= \frac{G(1+k_u)}{1+G[H_1(k)+H_2(k)]} \label{eq:Tclp}  \\ 
-T(k) &= \frac{G[1+k_u+C_m(k)]}{1+G[H_1(k)+H_2(k)+e^{-\tau_{a}s} P_2C_m(k)]}  \label{eq:Tcl} 
+T(k) &= \frac{G[1+k_u+C_m(k)]}{1+G[H_1(k)+H_2(k)+H_3(k)]}  \label{eq:Tcl} 
 \end{align}
@@
 w(k) &= G[1+k_u+C_m(k)] \\
-z(k) &= 1+G[H_1(k)+H_2(k)+e^{-j\omega \tau_{a}}P_2C_m(k)]
+z(k) &= 1+G[H_1(k)+H_2(k)+H_3(k)]
 \end{aligned}
@@
 \end{equation}
-for all $\omega \in \Omega$, where $$z_0 = 1+G[H_1(k_0) + H_2(k_0)+e^{-j\omega \tau_{a}}P_2C_m(k_0)]$$ and $k_0 =[k_{i,0},k_{u,0},k_{m_1,0},k_{m_2,0}  ]$ are the initializing gains.
+for all $\omega \in \Omega$, where $$z_0 = 1+G[H_1(k_0) + H_2(k_0)+H_3(k_0)]$$ and $k_0 =[k_{i,0},k_{u,0},k_{m_1,0},k_{m_2,0}  ]$ are the initializing gains.
 
@@
 \end{definition}
-The open-loop FRF of the system $T(k)$ in Fig.~\ref{fig:damping_loop} is given as $$L(k) = G[H_1(k)+H_2(k)+e^{-j\omega \tau_{a}}P_2C_m(k)].$$ Let $F(k) = H_1(k)+H_2(k)+e^{-j\omega \tau_{a}}P_2C_m(k)$ such that $L(k) = GF(k)$; by the Nyquist stability criterion, the closed-loop system is stable if and only if $1+GF$ makes $n_{G}+n_F$ counter-clockwise encirclements of the origin (where $n_{G}$ and $n_F$ are, respectively, the number of right-half plane (RHP) poles of $G$ and $F$).
+The open-loop FRF of the system $T(k)$ in Fig.~\ref{fig:damping_loop} is given as $$L(k) = G[H_1(k)+H_2(k)+H_3(k)].$$ Let $F(k) = H_1(k)+H_2(k)+H_3(k)$ such that $L(k) = GF(k)$; by the Nyquist stability criterion, the closed-loop system is stable if and only if $1+GF$ makes $n_{G}+n_F$ counter-clockwise encirclements of the origin (where $n_{G}$ and $n_F$ are, respectively, the number of right-half plane (RHP) poles of $G$ and $F$).
 The Nyquist plot of $1+GF$ must also not pass through the origin.
@@
 \begin{align*}
-z(k) &= 1+G[H_1(k)+H_2(k)+e^{-j\omega \tau_{a}}P_2C_m(k)] \\
-z_0 &= 1+G[H_1(k_0)+H_2(k_0)+e^{-j\omega \tau_{a}}P_2C_m(k_0)]
+z(k) &= 1+G[H_1(k)+H_2(k)+H_3(k)] \\
+z_0 &= 1+G[H_1(k_0)+H_2(k_0)+H_3(k_0)]
 \end{align*}
-with $\{G,H_1,H_2,P_2\} \in \mathscr{S}$. Then the closed-loop system $T$ is stable if the parameters in the set $k_0$ are stabilizing initial gains.
+with $\{G,H_1,H_2,H_3\} \in \mathscr{S}$. Then the closed-loop system $T$ is stable if the parameters in the set $k_0$ are stabilizing initial gains.
 \end{theorem}
@@
 \end{equation}
-where $F(k_0) = H_1(k_0) + H_2(k_0) + e^{-\tau_{a}s}P_2 C_m(k_0)$.
+where $F(k_0) = H_1(k_0) + H_2(k_0) + H_3(k_0)$.
 Note that $F(k)$ is strictly proper and $GF(k)$ is strictly proper; therefore, the winding number of $z^{\star}(k)z_0$ can be evaluated over $\Omega$ instead of the $D$-contour.

### 2017-02-28 Papers/Loop Shaping Voltage Loop (CERN)/Latex/Draft_2/Draft_2.tex
Update Draft_2.tex

@@
 
-\author{Achille Nicoletti$^{1}$ and Michele Martino$^{1}$ and Alireza Karimi$^{2}$% <-this % stops a space
+\author{Achille Nicoletti$^{1,2}$ and Michele Martino$^{1}$ and Alireza Karimi$^{2}$% <-this % stops a space
 \thanks{*This work was not supported by any organization}% <-this % stops a space
@@
 The method proposed in this paper is an extension of \cite{KK16} to the model reference control problem and invokes a new data-driven control design scheme for specific power converter applications at CERN.
-Currently, the load (i.e., the magnet of the particle accelerator) is approximated as a simple first-order system (series $RL$ circuit); however, it has been shown in \cite{KZ98}, \cite{NW95} and \cite{NS79} that the vacuum chamber of the magnet is also frequency dependent (mainly due to the coupling effects of the beam and deformations in the chamber geometry).
-In fact, the authors in \cite{NW95} assert that even small deformations in the beam pipe can drastically change the impedance of the system and create stability issues.
+Currently, the load (i.e., the magnet of the particle accelerator) is often approximated as a simple first-order system (series $RL$ circuit) even though it has been shown in \cite{Shafer1}, \cite{Shafer2} and \cite{Ravaioli1} that both real and imaginary part of its impedance are ferquency dependent and its behavior is also affected by the vacuum chamber of the magnet.
 Therefore, it is appropriate to consider a data-driven based design to regulate the power converter control system.
@@
 \end{figure*}
-A schematic of the power converter control system is shown in Fig.~\ref{fig:circuit}.
+A schematic of the power converter with its control system is shown in Fig.~\ref{fig:circuit}.
 Specific portions of the schematic are color-coded in order to construct the associated block diagram.
@@
 The input voltage for one of the high frequency (HF) filters will be denoted as $v_i$ while the output voltage of the filter (for one branch) will be denoted as $v_0$.
-The TF from $v_i$ to $v_0$ describes the output filter of the power converter for one branch.
+The TF from $v_i$ to $v_0$ describes the output filter of the power converter for one branch; the HF filter is needed to remove the high frequency components of the PWM voltage at the output of the SMPS power stage (SMPS Switched Mode Power Supply).
 For general applications at CERN, the objective is to control the current in the magnet such that the error between this output current and a delayed version of the reference current is minimized.
 However, the objective of this paper is to design and implement a controller to shape the FRF between the reference voltage and $v_0$.
-This intermediate control is performed due to the fact that the output typically possesses large resonances, and a controller is required to attenuate these resonances in order to ensure better performance in the current loop.
-These large resonances are present because the values of the filter resistances are small (in order to reduce the power losses).
-Large resistance values can attenuate the resonances at the price of larger power losses.
+This intermediate control is performed due to the fact that the HF filter typically possesses large resonances, and a controller is required to attenuate these resonances in order to ensure better performance in the current loop.
+Large resonances are present because the values of the filter resistances are kept small in order to reduce the power losses.
+Large resistance values can attenuate the resonances at the price of larger power losses and would therefore compromise energy efficiency.
 Another reason for implementing this type of control structure at CERN is for commissioning purposes; if/when faults occur in the system, each loop can be verified one at a time to ensure quality operation.
@@
 This block diagram is color-coded to correlate with the structure of the schematic in Fig.~\ref{fig:circuit}.
-The analog-to-digital converter (ADC) is used to process the information from the analog system to the DSP; $G_0(s)$ represents the TF from $v_i$ to $v_0$; $H(s)$ represents the TF from $v_0$ to $i_c$ (the current through the capacitor in the HF filter); $P_1(s)$ and $P_2(s)$ are sensors (i.e., low-pass filters); $k_i$ and $k_u$ are the control variable gains; $\tau \: [s]$ is an actuation delay that is used to approximate the dynamics of the power electronics; and $C(s)$ is a PI controller, i.e., $$C(z^{-1}) = k_{p_1} + k_{p_2}\frac{t_s z^{-1}}{1-z^{-1}}$$ where $t_s \: [s]$ is the sampling rate of the DSP.
+The analog-to-digital converter (ADC) is used to process the information from the analog system to the DSP; $G_0(s)$ represents the TF from $v_i$ to $v_0$; $H(s)$ represents the TF from $v_0$ to $i_c$ (the current through the capacitor in the HF filter); $P_1(s)$ and $P_2(s)$ are sensors (i.e., low-pass filters); $k_i$ and $k_u$ are the control variable gains; $\tau \: [s]$ is an actuation delay that is used to approximate the dynamics of the power electronics; and $C(z^{-1})$ is a PI controller, i.e., $$C(z^{-1}) = k_{p_1} + k_{p_2}\frac{t_s z^{-1}}{1-z^{-1}}$$ where $t_s \: [s]$ is the sampling rate of the DSP.
 The ADCs have very fast dynamics relative to the other subsystems in the loop; for this reason, it is appropriate to consider the ADCs as pure time delays (which will be denoted with a delay $\tau_{a} \: [s]$).
@@
 \begin{equation*}
-C_m(k) := k_{m_1}+k_{m_2}\frac{t_se^{-j\omega}}{1-e^{-j\omega}}
+C_m(k) := k_{m_1}+k_{m_2}\frac{t_se^{-j\omega t_{s}}}{1-e^{-j\omega t_{s}}}
 \end{equation*}
@@
 \begin{tabular}[c]{@{}c@{}}$I_0$\\ (Output Current)\end{tabular}               & $850$                      & A     \\ \hline
-Input Power                                                                    & $18$                       & kV    \\ \hline
+AC Input                                                                       & $18$                       & kV    \\ \hline
 Input Frequency                                                                & $50$                       & Hz    \\ \hline
 \begin{tabular}[c]{@{}c@{}}IGBT equivalent \\ switching frequency\end{tabular} & $5000$                     & Hz    \\ \hline
-Transformer Weight                                                             & $4500$                     & kg    \\ \hline
 DSP sampling rate                                                              & $5000$                     & Hz    \\ \hline
@@
 where $f_d$ is the desired closed-loop bandwidth.
-In other words, $T_d$ is simply a delayed version of the second order process.
 There is some uncertainty associated with the delay $\tau$; the range of this delay is $\tau \in [0,200]\mu s$ with a nominal value of $100 \mu s$.
@@
 \includegraphics[width=\columnwidth]{../pics/d_loop_mag.eps}
-\caption{The closed-loop response of $|T^{\prime}|$; data-driven method with $\mathcal{H}_{\infty}$ performance (red line); data-driven method with $\mathcal{H}_2$ performance (blue line); model-based approach with $\mathcal{H}_2 / \mathcal{H}_\infty$ performance (yellow line); -3 dB point representing 300 Hz bandwidth (dashed-black line).}
+\caption{Measured closed-loop response of $|T^{\prime}|$; data-driven method with $\mathcal{H}_{\infty}$ performance (red line); data-driven method with $\mathcal{H}_2$ performance (blue line); model-based approach with $\mathcal{H}_2 / \mathcal{H}_\infty$ performance (yellow line); -3 dB point representing 300 Hz bandwidth (dashed-black line).}
 \label{fig:d_loop}
@@
 \includegraphics[width=\columnwidth]{../pics/v_loop_mag.eps}
-\caption{The closed-loop response of $|T|$; data-driven method with $\mathcal{H}_{\infty}$ performance (red line); data-driven method with $\mathcal{H}_2$ performance (blue line); model-based approach with $\mathcal{H}_2 / \mathcal{H}_\infty$ performance (yellow line); -3 dB point representing $500$ Hz bandwidth (dashed-black line).}
+\caption{Measured closed-loop response of $|T|$; data-driven method with $\mathcal{H}_{\infty}$ performance (red line); data-driven method with $\mathcal{H}_2$ performance (blue line); model-based approach with $\mathcal{H}_2 / \mathcal{H}_\infty$ performance (yellow line); -3 dB point representing $500$ Hz bandwidth (dashed-black line).}
 \label{fig:v_loop}
